### 2017-02-15 asyncleakyn.tex
First commit

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle}
\author{Zoey Zhou}
\date{\today}  
\usepackage{graphicx}
\graphicspath{ {c:/Users/cuizy/Downloads/} }
\begin{document}

\maketitle

\section{Intro}
Biological modeling uses from stochastic to continuous to boolean models.  We propose an asynchronous circuit scheme for modeling the cell cycle of the bacteria Caulobacter Crescentus.   Asynchronous circuits are a type of digital circuits where the values are boolean, either 0 or 1, and the boolean functions are implemented through logic gates.  Digital circuits can be synchronous, where all of the logic gates in the circuit are controlled by some global clock, which ensures that the next values for all of the gates are updated at the same time.  Thus problems where various gate delays causing fluctuations in the circuit can be avoided.  In an asynchronous circuit, there is no global clock, and the gates update real time so different computational delay times for each gate cause real effects which may be propagated through the circuit.  Thus for an asynchronous circuit to provide reliable function, these random delays must be designed into the system.  A more stringent condition of asynchronous circuits known as speed independence ensures that no matter the delay for each gate, the circuit will function the same way. 
 different levels of detail

\section{Correct boolean model}
We expect biological systems to behave similarly to an asynchronous circuit because in biological systems there are no 'global clocks' that regulate the timing.  Because there is high variability between cells, and molecular interactions are of a stochastic nature, production from each gene element can have varying delay.  This variability differs from cell to cell and from one cycle to the next. Thus we would also expect a type of speed independence property to ensure that most of the time, the cells work reliably regardless of the random delays and advance through the cell cycle to produce new cells.
\newline \newline
From the bottom up, we extract properties from biological networks and show how it is analogous to the well developed CMOS technology.  We start at the physics level and demonstrate certain properties so that we can group gene elements together and represent them with a higher level boolean model.  We then show how this boolean model can be abstracted into a higher level forming building blocks that we can use in an asynchronous circuit. 
\newline \newline
In past papers, gene regulatory networks has been modeled as boolean circuits with each gene/protein element represented by a boolean gate.  Each gene logic gate has inputs, usually its activators and repressors, to determine whether the protein is being actively produced or not.  These are usually modeled as AND or OR gates with its promoter binding compounds as its only inputs.  However, in our investigation using the ODE model of each gene, we found that degradation is a crucial part of the logic gates as well.  Protein degradation can be sped up through controlling the production of degradation enzymes.  Meanwhile for stable proteins, it is possible for the base degradation rate, the half life of the protein to be equivalent to the length of the cell cycle, the only reduction in protein concentration coming from the splitting of cells.  Thus there needs to be a separate way of representing the production of proteins from its degradation.  We take inspiration from Complementary Metal–Oxide–Semiconductor (CMOS) technology.  In CMOS there is a pull up network and a pull down network.  In the inverter example, the pull up network consists of a PMOS and the pull down network consists of a NMOS.  PMOS behaves, on first order approximation, as a wire when the input voltage is low and as an open circuit when the input voltage is high.  NMOS is the opposite, it behaves as an open when the input voltage is low and as a wire when the input voltage is high.  Thus when the input voltage is low, the output voltage is pulled up by the PMOS to a high voltage.  Meanwhile when the input voltage is high, the output voltage is pulled down to ground by the NMOS.  The transcriptional and translational regulation of these genes are similar to a pull up network while the accelerated degradation is similar to a pull down network.  If the background degradation is significantly slower, this effect can be thought of as the parasitic capacitance that slowly leak the charge of the output signal.  Overtime it degrades the signal however for short time scales it retains its voltage value and is a dynamic memory element.
\newline
\includegraphics[width=\textwidth]{mosinv}
\newline \newline
Many biological functions can be modeled with the Hill function, including mRNA production.  The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.  As such, much of the design properties of CM
OS circuits can be carried over.    In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.  In general the equation is of the form: $\frac{dprotein}{dt}=g(inputs)-protein\cdot\lambda$  where the function $g()$ is a sigmoidal curve such as the Hill function and $\lambda$ is the degradation constant.  This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.  If we treat each protein as its own gate, there exists similar restorative properties of the protein gate.
%new, about the thresholds
\newline \newline
Thresholds are a concept used in engineering to divide a continuous region of signal into some discrete categories such as ‘0’ or ‘1’ for a binary system.  The basic requirement is that the thresholds must allow sustained propagation throughout a chain of components, that is a ‘0’ output from one component is read as a ‘0’ input to the next component and the information is retained during processing.  Usually there are a separate low and high threshold and an in between region in which the signal is undetermined. (ie. if the signal is below the low threshold then it is a 0 and if the signal is above the high threshold it is a 1)
\newline
\includegraphics[width=\textwidth]{thresholds}
\newline
One basic property thresolds must satisfy is to allow proper propagation of the signal.  That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.  In addition, if the signal is monotonic such as monotonically decreasing in the case of inverters then all inputs below the input low threshold or above the input high threshold gives valid output signals.  In multi input systems such as in biology where there can be multiple inputs to the same 'gate'.  In biological systems where the ODE model is a sigmomidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.  Thus this satisfies our monotonic requirement and allow for proper propagation.  In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.  (expand?)
%Sigmoidal, All the things about how they connect, why they are good latches/ memory elements, completion signals?
\section{Static and Dynamic Memory}
There are certain network motifs that we have identified in our model of Caulobacter that allows cells to have some sort of memory.  There are positive feedback loops such as in CtrA where once enough production of CtrA starts the feedback, it will remain locked in that high state.  Until degradation overpowers the feedback and pulls CtrA back down to a low state.  This bistable property is also how latches in digital circuits store memory.  However for other proteins that do not have this positive feedback, we take inspiration from dynamic memory and look into the short term behavior instead.  As mentioned earlier, when the degradation term is slow the actual changes in protein concentration over time is slow as well and can act as a memory element.  If we assume the inputs are held constant, there is a closed form exponential solution to our ODE model.  (z is the output protein concentration)
$\Delta t= -log(z_f-z_{ss})/ \lambda+ log(z_0-z_{ss})/ \lambda$ This is the amount of time it takes for the protein concentration to go from $z_0$ to $z_f$, initial protein concentration to final protein concentration, with a steady state concentration due to the input parameters of $z_{ss}$.
\newline
In a set reset gate, there are two inputs, both of which must be 1 to set the output to 1, and both must be 0 to set the output to 0.  If one input is 0 and one is 1 then the output does not change and is in the hold state.  This is an important element for constructing asynchronous digital circuits.  
In our model we wish to verify the set reset property of each gene gate.  We use the above equation to check if the time for maximum set or reset transitions is smaller than the time during the hold state.  
Let the input thresholds be:  0 is between $in_{min0}$ and $in_{max0}$ and 1 is between $in_{min1}$ and $in_{max1}$, (the fanout thresholds $fanout_0$ and $fanout_1$ must be between $g(in_{max0})$ and $g(in_{min1})$ )
The maximum time it takes to set or reset in terms of output values is then: \newline
Set- $out_{min0}$ - $fanout_1$ where the input is changed to inmin1 \newline
Reset- $out_{max1}$ - $fanout_0$ where the input is changed to inmax0 \newline
For holds we want the minimum time it stays in output 0 or 1 as the inputs are changed \newline
$out_{max0}$ - $fanout_0$ with max \newline
$out_{min1}$ - $fanout_1$ \newline
\[\Delta t_{set}= - \frac{1}{\lambda} log(g(in_{min1})-fanout_1)/(g(in_{min1}) -g(in_{min0}))
\]
\[\Delta t_{reset}= -\frac{1}{\lambda} log(fanout_0 –g(in_{max0}))/(g(in_{max1}) – g(in_{max0}))
\]
\[\Delta t_{hold0}= -\frac{1}{\lambda} log(z_{ss} -fanout_0)/(z_{ss} -g(in_{max0}))				
\]
\[\Delta t_{hold1}= -\frac{1}{\lambda} log(fanout_1 -z_{ss})/(g(in_{min1}) -z_{ss})
\]

\newline Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.  Thus we can abstract these biological motifs as a series of static and dynamic memories connected to each other.

\section{Leakiness}
Interestingly, there are a couple examples even in the Caulobacter cell where if you knockout one of the key components of the core cell cycle proteins that the rest of the cycle still tries to proceed.  For example, experiments where GcrA or CcrM has been deleted should halt the cell cycle since they start the transcription of CtrA and DnaA respectively.  However, it has been shown that after some delay DnaA and CtrA levels accumulate enough such that the cell can enter the next phase of the cycle.  This may be attributed to a base rate of leakiness from their promoters and other stochastic effects.  We analyze the likely causes of this observation.

CtrA has positive self-feedback.  Plotting the solutions of the Hill kinetics and a diagonal line, representing that all CtrA are phosphorylated to CtrAP during this feedback, shows that this causes CtrA to be bistable. (figure \ref{fig:ctrapc})  However if you include leakiness of the promoter, that shifts the curve of CtrAP vs CtrA up such that even in the presence of no CtrAP, there is still some CtrA produced from the base rate.  If the leakiness from the promoter is large enough, it can shift the curve up so much that there is only one stable point of the system, where ctrA is high. (figure \ref{fig:ctrapl}) This would explain why deletion of GcrA and the P1 promoter where GcrA binds to delays the accumulation of CtrA.  In an earlier paper \cite{compgenre} Michaelis-Menton (MM) kinetics was used.  In their model, they also observed a restart of CtrA even when the upstream transcription factor GcrA was not present.  This is because the MM curve produces only one stable equilibrium so CtrA will always go high if given enough time.

\includegraphics[width=\textwidth]{ctrapc}
\includegraphics[width=\textwidth]{ctrapl}
\newline \newline
For DnaA, there is evidence that in cells with DnaA lacking the CcrM binding site, the phenotype is not as severe as deleting DnaA directly.  Instead the cell cycle is slowed down.  Thus, there is reason to believe that DnA is also controled by a leaky promoter.

\begin{thebibliography}{9}
\bibitem{compgenre} 
S M Murray, G Panis, C Fumeaux, P H Viollier , M Howard. 
\textit{Computational and Genetic Reduction of a Cell Cycle to Its Simplest, Primordial Components}. 
PLOS Biology, December 31, 2013.

\end{thebibliography}

\end{document}

### 2017-02-15 asyncleakyn.tex
updated importance of sigmoidal and threshold intro

@@
 The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.
-As such, much of the design properties of CM
-OS circuits can be carried over.
+As such, much of the design properties of CMOS circuits can be carried over.
+The importance of the sigmoidal shape of the input vs output transfer curve during steady state allows for restoring property of the signal and hence unsullied propagation in its next stages.
 In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.
@@
 This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.
-If we treat each protein as its own gate, there exists similar restorative properties of the protein gate.
+If we treat each protein as its own gate, there exists similar restorative properties of the CMOS gate.
 %new, about the thresholds
 \newline \newline
-Thresholds are a concept used in engineering to divide a continuous region of signal into some discrete categories such as ‘0’ or ‘1’ for a binary system.
-The basic requirement is that the thresholds must allow sustained propagation throughout a chain of components, that is a ‘0’ output from one component is read as a ‘0’ input to the next component and the information is retained during processing.
-Usually there are a separate low and high threshold and an in between region in which the signal is undetermined.
-(ie.
-if the signal is below the low threshold then it is a 0 and if the signal is above the high threshold it is a 1)
+The input and outputs of electronic devices similar to the chemical concentrations in a cell are actually continuous (analog).
+The concept of a binary '1' or '0' is actually extracted from the original analog signal.
+Thresholds allow the conversion of an analog signal into a binary signal.
+Usually there is a low and a high threshold, and an in between region in which the signal is undetermined.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
 \newline

### 2017-02-16 asyncleakyn.tex
signal propagate

@@
 A more stringent condition of asynchronous circuits known as speed independence ensures that no matter the delay for each gate, the circuit will function the same way.
- different levels of detail
+% different levels of detail
 
@@
 \newline \newline
-The input and outputs of electronic devices similar to the chemical concentrations in a cell are actually continuous (analog).
-The concept of a binary '1' or '0' is actually extracted from the original analog signal.
+The inputs and outputs of electronic devices are similar to the chemical concentrations in a cell which are all actually continuous values (analog).
+The concept of a binary '1' or '0' is extracted from the original analog signal.
 Thresholds allow the conversion of an analog signal into a binary signal.
-Usually there is a low and a high threshold, and an in between region in which the signal is undetermined.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
+Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
+The in between region is undetermined meaning it is neither a '1' or a '0'.
 \newline
@@
 One basic property thresolds must satisfy is to allow proper propagation of the signal.
+The output of a gate should read as the same binary value into the input of the following gate.
 That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.
-In addition, if the signal is monotonic such as monotonically decreasing in the case of inverters then all inputs below the input low threshold or above the input high threshold gives valid output signals.
-In multi input systems such as in biology where there can be multiple inputs to the same 'gate'.
-In biological systems where the ODE model is a sigmomidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.
+There is a naturally defined output threshold given the input thresholds.
+That is passing the input threshold through the gate function G().
+In addition, if the signal is monotonic then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.
+The reasoning is because for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_j)$ since G() is monotonic.
+We also need to consider multiple input systems such as in biology where there can be multiple inputs to the same gate.
+In biological systems where the ODE model is a sigmoidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.
 Thus this satisfies our monotonic requirement and allow for proper propagation.
@@
 (expand?)
+\newline
+The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.  
 %Sigmoidal, All the things about how they connect, why they are good latches/ memory elements, completion signals?

### 2017-02-22 asyncleakyn.tex
big change

@@
 \section{Correct boolean model}
+In current designs of digital circuits, these are mostly synchronous circuits.
+They are called synchronous due to the existence of a global clock which controls each logic gate.
+The clock signals ensures that each gate are updated at the right time and also given enough time to propagate the correct output to the next gate.
+This avoids transmitting the wrong intermediate signal, which can cause an error in the final output compared to what we would expect.
+There are also asynchronous circuit designs, where there is no such clocks and the variable delay times may cause one transition to happen before another at random.
+()  Thus asynchronous systems must be designed more carefully to allow for these random events.
 We expect biological systems to behave similarly to an asynchronous circuit because in biological systems there are no 'global clocks' that regulate the timing.
@@
 \newline \newline
-From the bottom up, we extract properties from biological networks and show how it is analogous to the well developed CMOS technology.
-We start at the physics level and demonstrate certain properties so that we can group gene elements together and represent them with a higher level boolean model.
+From the bottom up, we extract properties from biological networks and use analogies with the well developed CMOS technology.
+We start at the molecular level and demonstrate certain properties so that we can group gene elements together and represent them with a higher level boolean model.
 We then show how this boolean model can be abstracted into a higher level forming building blocks that we can use in an asynchronous circuit.
 \newline \newline
-In past papers, gene regulatory networks has been modeled as boolean circuits with each gene/protein element represented by a boolean gate.
+
+The physics of gene protein interactions in the cell are congruent with properties that make it a valid digital circuit as well.
+In past papers, gene regulatory networks has been modeled as boolean circuits with each gene/protein element represented by a boolean logic gate.
+Each gene logic gate has inputs, such as activators and repressors, to determine whether the protein is being actively produced or not.
+The mRNA production here can be modeled with the Hill function.
+The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.
+As such, much of the design properties of CMOS circuits can be carried over.
+There are two important properties that gates, which we use as building blocks in circuits, must satisfy.
+The existence of a threshold, and the faithful propagation of a signal through a circuit, even when connected in a loop.
+We examine these properties by first looking at the steady state solution of the equation for protein production.
+The steady state solution is important because within a reasonable amount of time this is the output concentration of the protein given the inputs.
+This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.
+The sigmoidal shape of the input vs output transfer curve during steady state allows for restoring property of the signal and hence faithful propagation in its next stages.
+In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.
+In general the protein production equation is of the form: $\frac{dprotein}{dt}=g(inputs)-protein\cdot\lambda$  where the function $g()$ is a sigmoidal curve such as the Hill function and $\lambda$ is the degradation constant.
+It's steady state solution is $protein=g(inputs)/\lambda$, easily verifiable as also a sigmoidal Hill function.
+%new, about the thresholds
+\newline \newline
+The inputs and outputs of electronic devices are similar to the chemical concentrations in a cell which are all actually continuous values (analog).
+The concept of a binary '1' or '0' is extracted from the original analog signal.
+Thresholds allow the conversion of an analog signal into a binary signal.
+Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
+The in between region is undetermined meaning it is neither a '1' or a '0'.
+\newline
+\includegraphics[width=\textwidth]{thresholds}
+\newline
+Thus we must verify the thresholds are upheld so that for all signals below the low threshold, it is read into the gate as a '0' and produces the correct corresponding output.
+This must also be verified for all signals above the high threshold.
+We first work with a single input and make some assumptions:  1) that passing the signal at the low and high threshold though the gate produces the proper binary output signal, 2) the gate function is a monotonic function.
+Then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.
+We first assume the function G() is monotonically increasing, the reasoning is thus for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_i)$.
+The same could be shown for $input high$ and $x_j$.
+If the function G() is monotonically decreasing then the inequality sign of the previous argument is flipped and the correct operation of the circuit still holds.
+We verify that our initial assumptions hold in that we can set the output low and high thresholds accordingly, and the Hill function is indeed a monotonic function.
+%there are actually examples where this fails 0->0 in monotonically decreasing... need to fix too
+\newline
+The next step is when gates are connected to each other, signals must propagate meaningfully as well.
+The output of a gate should read as the same binary value into the input of the following gate based on their respective thresholds.
+That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.
+Multiple inputs are common in biology where there can be activators and repressors and even degradation enzymes involved in one gene product.
+This is easily reducible to the familiar problem in one dimension.
+In biological systems where the ODE model is a sigmoidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.
+Thus this satisfies our monotonic requirement and allow for proper propagation.
+% In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.
+(expand?)
+\newline
+The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.
+For the signals to allow a certain amount of noise to enter the system, we would want the output thresholds of one gate to be as far away from the input thresholds of the next gate as possible.
+Thus when noise gets added to the output signal, it still has a good chance to transmit the correct binary data to the next stage.
+In addition, these components can be connected in a loop.
+In electronics, since the outputs and inputs are measured against the same unit of measurement, the voltage, the additional requirement is that the gain must be greater than 1.
+This means that the slope of the function should be greater than 1.
+Because we are using different chemical species at each stage to transmit the biological signal, we need to scale the slopes of the function accordingly.
+%Sigmoidal, All the things about how they connect, why they are good latches/ memory elements, completion signals?
+\newline \newline
+Changing rates of degradation of proteins is an important aspect of the circuit that has been often ignored in previous models.
+In past papers, gene regulatory networks has been modeled as boolean circuits with each gene/protein element represented by a boolean logic gate.
 Each gene logic gate has inputs, usually its activators and repressors, to determine whether the protein is being actively produced or not.
@@
 Meanwhile for stable proteins, it is possible for the base degradation rate, the half life of the protein to be equivalent to the length of the cell cycle, the only reduction in protein concentration coming from the splitting of cells.
+These proteins, once produced would remain in the cells for a very long time and essentially considered 'on' even when transcription and/or translation has stopped.
 Thus there needs to be a separate way of representing the production of proteins from its degradation.
@@
 Overtime it degrades the signal however for short time scales it retains its voltage value and is a dynamic memory element.
+(write about dynamic memory later?)
 \newline
+\includegraphics[width=\textwidth]{mosinaction}
 \includegraphics[width=\textwidth]{mosinv}
 \newline \newline
-Many biological functions can be modeled with the Hill function, including mRNA production.
-The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.
-As such, much of the design properties of CMOS circuits can be carried over.
-The importance of the sigmoidal shape of the input vs output transfer curve during steady state allows for restoring property of the signal and hence unsullied propagation in its next stages.
-In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.
-In general the equation is of the form: $\frac{dprotein}{dt}=g(inputs)-protein\cdot\lambda$  where the function $g()$ is a sigmoidal curve such as the Hill function and $\lambda$ is the degradation constant.
-This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.
-If we treat each protein as its own gate, there exists similar restorative properties of the CMOS gate.
-%new, about the thresholds
-\newline \newline
-The inputs and outputs of electronic devices are similar to the chemical concentrations in a cell which are all actually continuous values (analog).
-The concept of a binary '1' or '0' is extracted from the original analog signal.
-Thresholds allow the conversion of an analog signal into a binary signal.
-Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
-The in between region is undetermined meaning it is neither a '1' or a '0'.
-\newline
-\includegraphics[width=\textwidth]{thresholds}
-\newline
-One basic property thresolds must satisfy is to allow proper propagation of the signal.
-The output of a gate should read as the same binary value into the input of the following gate.
-That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.
-There is a naturally defined output threshold given the input thresholds.
-That is passing the input threshold through the gate function G().
-In addition, if the signal is monotonic then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.
-The reasoning is because for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_j)$ since G() is monotonic.
-We also need to consider multiple input systems such as in biology where there can be multiple inputs to the same gate.
-In biological systems where the ODE model is a sigmoidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.
-Thus this satisfies our monotonic requirement and allow for proper propagation.
-In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.
-(expand?)
-\newline
-The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.  
-%Sigmoidal, All the things about how they connect, why they are good latches/ memory elements, completion signals?
 \section{Static and Dynamic Memory}
@@
 
+\section{Asynchronous circuits}
+One important aspect of asynchronous circuit design is having memory elements.
+This is because for a asynchronous circuit to be able to function, it must receive feedback signals from the next stage so that it knows if it needs to hold its current value, or if the next stage has received it's signal and can go to the next stage in processing.
+
 \section{Leakiness}

### 2017-03-06 asyncleakyn.tex
added sr latch and c-element

@@
 \newline \newline
-
 The physics of gene protein interactions in the cell are congruent with properties that make it a valid digital circuit as well.
@@
 %there are actually examples where this fails 0->0 in monotonically decreasing... need to fix too
-\newline
+\newline \newline
 The next step is when gates are connected to each other, signals must propagate meaningfully as well.
@@
 (expand?)
-\newline
+\newline \newline
 The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.
@@
 In the inverter example, the pull up network consists of a PMOS and the pull down network consists of a NMOS.
-PMOS behaves, on first order approximation, as a wire when the input voltage is low and as an open circuit when the input voltage is high.
-NMOS is the opposite, it behaves as an open when the input voltage is low and as a wire when the input voltage is high.
+PMOS behaves, on first order approximation, as a conductor when the input voltage is low and as an open switch when the input voltage is high.
+NMOS is the opposite, it behaves as an open switch when the input voltage is low and as a conductor when the input voltage is high.
 Thus when the input voltage is low, the output voltage is pulled up by the PMOS to a high voltage.
@@
 The transcriptional and translational regulation of these genes are similar to a pull up network while the accelerated degradation is similar to a pull down network.
-If the background degradation is significantly slower, this effect can be thought of as the parasitic capacitance that slowly leak the charge of the output signal.
-Overtime it degrades the signal however for short time scales it retains its voltage value and is a dynamic memory element.
-(write about dynamic memory later?)
+If the background degradation is significantly slower, this effect can be thought of as similar to the parasitic capacitance that slowly leak the charge of the output signal.
+Overtime it degrades the output signal however for short time scales the output retains its voltage value and can be considered a dynamic memory element.
+Dynamic memory elements are important in asynchronous circuits because they can hold the signal for some time until they receive input, usually from elements further down the circuit to signal that the current output has been acknowledged and processed already and does not need to hold anymore.
+\newline \newline
+%(write about dynamic memory later?)
 \newline
 \includegraphics[width=\textwidth]{mosinaction}
-\includegraphics[width=\textwidth]{mosinv}
-\newline \newline
+\begin{center}
+\includegraphics{mosinv}
+\end{center}
 \section{Static and Dynamic Memory}
-There are certain network motifs that we have identified in our model of Caulobacter that allows cells to have some sort of memory.
-There are positive feedback loops such as in CtrA where once enough production of CtrA starts the feedback, it will remain locked in that high state.
+There are certain network motifs in biology that allows cells to have some sort of memory.
+Our main examples are from Caulobacter but these motifs are present in other cells and thus this analysis is widely applicable.
+%There are positive feedback loops such as in CtrA where once enough production of CtrA starts the feedback, it will remain locked in that high state.
 Until degradation overpowers the feedback and pulls CtrA back down to a low state.
 This bistable property is also how latches in digital circuits store memory.
-However for other proteins that do not have this positive feedback, we take inspiration from dynamic memory and look into the short term behavior instead.
-As mentioned earlier, when the degradation term is slow the actual changes in protein concentration over time is slow as well and can act as a memory element.
-If we assume the inputs are held constant, there is a closed form exponential solution to our ODE model.
-(z is the output protein concentration)
-$\Delta t= -log(z_f-z_{ss})/ \lambda+ log(z_0-z_{ss})/ \lambda$ This is the amount of time it takes for the protein concentration to go from $z_0$ to $z_f$, initial protein concentration to final protein concentration, with a steady state concentration due to the input parameters of $z_{ss}$.
+We take inspiration from dynamic memory and look into the short term behavior of each gate.
+As mentioned in the previous section, when the degradation term is slow, the changes in protein concentration over time is slow as well.
+For very stable proteins, the half life of the protein is then only from splitting of the cells during each cell cycle.
+We examine whether using experimentally determined parameters, it is possible to view these gates as memory elements.
+For our analysis, we assume that the inputs are held constant.
+Then there is a closed form exponential solution of our ODE model.
+We can then determine the time elapsed from a given starting state to a final state.
+(z is the output protein concentration, and c is the total contribution by the inputs, a constant if the inputs are held constant, $\lambda$ is the degradation rate)
+\[\frac{dz}{dt}=c-z\cdot\lambda
+\]
+The solution to this ODE is the exponential:
+\[z(t)=((z_0\cdot\lambda-c)e^{(-\lambda\cdot t)}+c)/\lambda
+\]
+Where $z_0$ is the inital concentration of the protein.
+To find the time elapsed between $z_0$ and some $z_f$ just substitute $z(t)=z_f$.
+We also note that at steady state $c=z_{ss}\cdot\lambda$.
+Rearranging the equation for time:
+\[\Delta t= -log(z_f-z_{ss})/ \lambda+ log(z_0-z_{ss})/ \lambda
+\]
+ This is the amount of time it takes where $z_0$ is the initial protein concentration and $z_f$ is the final protein concentration.
 \newline
-In a set reset gate, there are two inputs, both of which must be 1 to set the output to 1, and both must be 0 to set the output to 0.
-If one input is 0 and one is 1 then the output does not change and is in the hold state.
-This is an important element for constructing asynchronous digital circuits.
+%something about robustness?
+\begin{center}
+\includegraphics{celement}
+\end{center}
+The Muller C-element is useful in the design of asynchronous circuits.
+If every signal in a circuit is connected with C-elements then it ensures that the circuit can run robustly and has the speed independence property.
+Thus we would ideally want the elements we see in biological circuits to operate similarly to the C-element.
+A common CMOS implementation of a C-element is shown with two inputs A and B, and an output C.
+It operates similarly as the inverter example.
+In this C-element example, when A and B are both high, the pull down network is activated, while there are open switches in the pull up network and the output is connected to the ground.
+When both A and B are low, the opposite is true and the output is pulled to $V_{cc}$.
+However when A and B are different signals ie A is high and B is low or when A is low and B is high, then there is no path through either the pull up or the pull down network and the previous value of the output is retained.
+This state is called a 'hold'.
+\newline 
+\begin{center}
+\includegraphics{srlatch}
+\end{center}
+Set reset latches have a similar modes of operation with output high output low and hold but also differs in an important detail.
+In a set reset latch, there are two inputs, called a set and a reset.
+We look at the set reset NOR latch.
+When set is high and reset is low then the output signal is 'set' or becomes high.
+When set is low and reset is high then the output signal is 'reset' or becomes low.
+If both inputs are low then the output does not change and is in the hold state.
+The last state when both inputs are high gives an undefined output represented by 'X', usually this element does not go into this state.
+The similarities between set reset latches and C-elements are quite apparent.
+It is basically equivalent if you treat the reset signal of the set reset latch as an inverted second signal for the C-element.
+However, when A is high and B is low, there is a hold state for the C-element whereas that corresponds to a high set and high reset and thus an undefined output for the set reset latch.
+\newline  \newline
 In our model we wish to verify the set reset property of each gene gate.
@@
 \]
-
-\newline Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.
+%can expand these equations... how we got to it
+Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.
 Thus we can abstract these biological motifs as a series of static and dynamic memories connected to each other.

### 2017-03-08 asyncleakyn.tex
added sr latch and c-element

@@
 \]
+or
+\[\Delta t= -log(z_{ss}-z_f)/ \lambda+ log(z_{ss}-z_0)/ \lambda
+\]
+because the expression inside the log must be positive.
+(Note that this means $z_f$ and $z_0$ must be on the 'same side' as $z_{ss}$, this makes conceptual sense because this is an exponential decay or rise towards the final steady state value, it cannot cross the steady state value.)
  This is the amount of time it takes where $z_0$ is the initial protein concentration and $z_f$ is the final protein concentration.
@@
 \newline  \newline
-In our model we wish to verify the set reset property of each gene gate.
-We use the above equation to check if the time for maximum set or reset transitions is smaller than the time during the hold state.
-Let the input thresholds be:  0 is between $in_{min0}$ and $in_{max0}$ and 1 is between $in_{min1}$ and $in_{max1}$, (the fanout thresholds $fanout_0$ and $fanout_1$ must be between $g(in_{max0})$ and $g(in_{min1})$ )
-The maximum time it takes to set or reset in terms of output values is then: \newline
-Set- $out_{min0}$ - $fanout_1$ where the input is changed to inmin1 \newline
-Reset- $out_{max1}$ - $fanout_0$ where the input is changed to inmax0 \newline
-For holds we want the minimum time it stays in output 0 or 1 as the inputs are changed \newline
-$out_{max0}$ - $fanout_0$ with max \newline
-$out_{min1}$ - $fanout_1$ \newline
+In our model we wish to verify the set reset and hold property of each gene gate.
+We use the exponential solution to the ODE equation.
+Given the appropriate inputs we would like for all of the set and and reset transitions to take a shorter length of time than the temporary hold states.
+More formally, we would like the worst case/longest set and reset transition times to be shorter than the worst case/shortest hold times.
+First we define some of the parameters and variables that we use.
+Define the input thresholds as:  $in_{min0}$ is the smallest acceptable input to represent an input '0' and $in_{max0}$ is the largest acceptable input to represent an input '1'.
+Similarly, $in_{min1}$ is the smallest acceptable input to represent an input '1' and $in_{max1}$ is the largest acceptable input to represent an input '1'.
+$fanout_0$ and $fanout_1$ represent the '0' and '1' input thresholds to the next components respectively.
+There is an additional constraint where fanout thresholds $fanout_0$ and $fanout_1$ must be between $g(in_{max0})$ and $g(in_{min1})$ so that all legal input values provide legal outputs that feed into the next layer of components to be processed.
+\newline \newline
+To find the maximum and minimum times for set reset and hold, we analyze the equation for time.
+To find the maximum set time, since set is when the output rises from '0' to '1' we can assume that $z_{ss}>z_f, z_0$ and use the second form of the time equation.
+$\Delta t$ is monotonically increasing in $z_f$ and monotonically decreasing in $z_0$.
+Since $z_{ss}$ is involved in two terms we need further analysis to see its effects on time.
+Taking the derivative with respect to $z_{ss}$:
+\[\frac{d\Delta t}{dz_{ss}}=- \frac{1}{(z_{ss}-z_f)}\frac{1}{\lambda}+ \frac{1}{(z_{ss}-z_0)}\frac{1}{\lambda}
+\]
+To find the maximum set time, we want to use the maximum $z_f$ where $z_f$ crosses the threshold to become a '1' signal and the minimum $z_0$ where $z_0$ is a '0' signal.
+So we have $z_f=fanout_1$ and $z_0=g(in_{min0})$ using the monotonicity of the function g().
+$z_{ss}$ is the steady state achieved by some constant input.
+This input must be a valid '1' input so that set occurs and the steady state is also a valid '1' output.
+Thus $z_{ss}$ must be bounded by: $g(in_{min1})\leq z_{ss}\leq g(in_{max1})$, and from earlier constraints we know that $fanout_1<z_{ss}$ and $fanout_1>g(in_{min0})$ so that:
+\[z_{ss}-fanout1< z_{ss}-g(in_{min0})
+\]
+\[\frac{1}{z_{ss}-fanout1}>\frac{1}{z_{ss}-g(in_{min0})}
+\]
+The derivative $\frac{d\Delta t}{dz_{ss}}$ is always negative in this case, so the smallest possible value in $z_{ss}$'s domain maximizes the set time, which is $z_{ss}=g(in_{min1})$.
+%Can insert a picture here too
+The maximum time for a set to occur can be rewritten as:
 \[\Delta t_{set}= - \frac{1}{\lambda} log(g(in_{min1})-fanout_1)/(g(in_{min1}) -g(in_{min0}))
 \]
+Next we find the maximum reset time.
+(output goes from '1' to '0' while an input '0' is applied)  Since it is an exponential decay, we use the first formula for time.
+$\Delta t$ is monotonically decreasing in $z_f$ and monotonically increasing in $z_0$.
+Again take the derivative of the time equation with respect to $z_{ss}$:
+\[\frac{d\Delta t}{dz_{ss}}= \frac{1}{(z_f-z_{ss})}\frac{1}{\lambda}- \frac{1}{(z_0-z_{ss})}\frac{1}{\lambda}
+\]
+To find the maximum reset time, we want to use the minimum $z_f$ where $z_f$ crosses the threshold to become a '0' signal and the maximum $z_0$ where $z_0$ is a '1' signal.
+So we have $z_f=fanout_0$ and $z_0=g(in_{max1})$ using the monotonicity of the function g().
+$z_{ss}$ is an output '0' valued steady state achieved by a constant input that is also a valid '0' on the input side.
+Thus $z_{ss}$ must be bounded by: $g(in_{min0})\leq z_{ss}\leq g(in_{max0})$, and from earlier constraints we know that $z_{ss}<fanout_0$ and $fanout_0<g(in_{max1})$ so that:
+\[fanout0-z_{ss}< g(in_{max1})-z_{ss}
+\]
+\[\frac{1}{fanout0-z_{ss}}>\frac{1}{g(in_{max1})-z_{ss}}
+\]
+The derivative $\frac{d\Delta t}{dz_{ss}}$ is always positive in this case, so the largest possible value in $z_{ss}$'s domain maximizes the set time, which is $z_{ss}=g(in_{max0})$.
+The maximum time for a set to occur can be rewritten as:
 \[\Delta t_{reset}= -\frac{1}{\lambda} log(fanout_0 –g(in_{max0}))/(g(in_{max1}) – g(in_{max0}))
 \]
-\[\Delta t_{hold0}= -\frac{1}{\lambda} log(z_{ss} -fanout_0)/(z_{ss} -g(in_{max0}))				
+For holds we want a minimum bound on the time the output remains within the '0' or '1' regions as the inputs are changed.
+We first look at how long a signal stays in the '0' region, or hold 0 case.
+We assume that the output eventually rises from the initial '0' value so that $z_{ss}>z_0$.
+Note that if $z_{ss}<fanout_0$ then the output signal will be held at '0' indefinitely.
+So we look at the case where $z_{ss}>fanout_0$.
+Similar to finding the set time, we use the second form of the time equation.
+This time we would like to find the minimum value for the time.
+Since $\Delta t$ is monotonically increasing in $z_f$ and monotonically decreasing in $z_0$, we want to use the minimum $z_f$ such that the output stops being a valid '0' signal, that is $fanout_0$, and use the maximum $z_0$ that is a valid input '0', that is $g(in_{max0})$.
+Additionally since the derivative of this equation with respect to $z_{ss}$ is always negative, we apply the largest possible 'hold' input where both active production and degradation are still considered '0'.
+That is the baseline degradation and $in_{max0}$.
+Because the degradation is different, the value $z_{ss}$ differs from $g(in_{max0})$, the input output pair has a different transfer function, call it $g'()$ so that the steady state output is $g'(in_{max0})$
+\[\Delta t_{hold0}= -\frac{1}{\lambda} log(g'(in_{max0}) -fanout_0)/(g'(in_{max0}) -g(in_{max0}))				
 \]
-\[\Delta t_{hold1}= -\frac{1}{\lambda} log(fanout_1 -z_{ss})/(g(in_{min1}) -z_{ss})
+The analysis is similar for the minimum time a signal stays in the '1' region, or hold 1 case.
+For this case the output eventually decays from the initial '1' value so $z_{ss}<z_0$.
+Again, if $z_{ss}>fanout_1$ then the output signal will be held at '1' indefinitely.
+So we look at the case where $z_{ss}<fanout_1$.
+Similar to finding the reset time, we use the first form of the time equation.
+We would like to find the minimum value for the time.
+Since $\Delta t$ is monotonically decreasing in $z_f$ and monotonically increasing in $z_0$, we want to use the maximum $z_f$ such that the output stops being a valid '1' signal, that is $fanout_1$, and use the minimum $z_0$ that is a valid input '1', that is $g(in_{min1})$.
+Additionally since the derivative of this equation with respect to $z_{ss}$ is always positive, we apply the smallest possible 'hold' input where both active production and degradation are still considered '0'.
+That is the baseline degradation and $in_{min0}$.
+Again due to the difference in degradation rate, we use a different input output transfer function $g'()$ so that the steady state output is $g'(in_{min0})$
+\[\Delta t_{hold1}= -\frac{1}{\lambda} log(fanout_1 -g'(in_{min0}))/(g(in_{min1}) -g'(in_{min0}))
 \]
-%can expand these equations... how we got to it
 Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.

### 2017-03-08 asyncleakyn.tex
added sr latch and c-element

@@
 For holds we want a minimum bound on the time the output remains within the '0' or '1' regions as the inputs are changed.
-We first look at how long a signal stays in the '0' region, or hold 0 case.
+We first look at how long a signal stays in the '0' region, or the hold 0 case.
 We assume that the output eventually rises from the initial '0' value so that $z_{ss}>z_0$.
@@
 \]
-The analysis is similar for the minimum time a signal stays in the '1' region, or hold 1 case.
+The analysis is similar for the minimum time a signal stays in the '1' region, or the hold 1 case.
 For this case the output eventually decays from the initial '1' value so $z_{ss}<z_0$.

### 2017-03-10 asyncleakyn.tex
finished adding to dynamic memory

@@
 \graphicspath{ {c:/Users/cuizy/Downloads/} }
+\usepackage{amsmath}
 \begin{document}
@@
 \end{center}
-\section{Static and Dynamic Memory}
+\section{Dynamic Memory}
 There are certain network motifs in biology that allows cells to have some sort of memory.
@@
 \begin{center}
-\includegraphics{srlatch}
+
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}| } 
+ \hline
+\textbf{S} & \textbf{R} & \textbf{Qnext} & \textbf{Action} \\
+\hline
+1 & 0 & 1 & set \\
+\hline
+0 & 1 & 0 & reset \\ 
+\hline
+0 & 0 & Q & hold state \\ 
+\hline
+1 & 1 & X & not allowed\\ 
+\hline
+\end{tabular}
+
 \end{center}
+
 Set reset latches have a similar modes of operation with output high output low and hold but also differs in an important detail.
@@
 The derivative $\frac{d\Delta t}{dz_{ss}}$ is always negative in this case, so the smallest possible value in $z_{ss}$'s domain maximizes the set time, which is $z_{ss}=g(in_{min1})$.
-%Can insert a picture here too
+%insert some graph here
 The maximum time for a set to occur can be rewritten as:
@@
 \]
-Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.
-Thus we can abstract these biological motifs as a series of static and dynamic memories connected to each other.
+We check the function of the gcrA gene module against these equations.
+We use parameter values that were previously determined for the ODE model from both experimental data and reasonable approximations based on these experiments.
+\begin{center}
+
+\begin{tabular}{|p{1.8cm}|p{1cm}|p{1cm}|p{7cm}| } 
+ \hline
+\textbf{Parameter} & \textbf{Value} & \textbf{Units} & \textbf{Parameter explanation} \\
+\hline
+$\lambda_{sw}$ & 10.5 & min & GcrA half-life in swarmer \\ 
+\hline
+$\lambda_{st}$ & 42 & min & GcrA half-life in stalked \\ 
+\hline
+$issw$ & 0 or 1 & & boolean value where 1 indicates cell is in the swarmer state \\
+\hline
+$p_{gcrA}$ & 2.2 & nM/s & Maximum synthesis rate of GcrA from the promoter \\ 
+\hline
+$c_{HalfCtrA}$ & 1760 & nM & Concentration of CtrA~P that yields half of the maximum expression of CtrA-regulated genes\\
+\hline
+$c_{HalfDef}$ & 660 & nM & Default concentration of transciption factors ie. gcrA that yields half of the maximum expression of target genes\\
+\hline
+\end{tabular}
+
+\end{center}
+The equation for the ODE of just the gcrA gene module is:
+\[
+\begin{split}
+\frac{d gcrA}{d t}=\frac{2.2}{(1+(\frac{660}{dnaA})^2)\cdot (1+(\frac{ctrAP}{1760})^2)}-gcrA\cdot (\frac{log(2)}{60\cdot 42} \\
++(issw)\cdot \frac{log(2)}{60\cdot 10.5})
+\end{split}
+\]
+And the equation for the steady state is:
+\[gcrA_{ss}=\frac{2.2}{(1+(\frac{660}{dnaA})^2)\cdot (1+(\frac{ctrAP}{1760})^2)\cdot (\frac{log(2)}{60\cdot 42}
++(issw)\cdot \frac{log(2)}{60\cdot 10.5})}
+\]
+The various input and output thresholds that we use are:
+\[in_{min0}: dnaA=0, ctrAP=1760  \Rightarrow g(in_{min0})=0, g'(in_{min0})=0
+\]
+\[in_{max0}: dnaA=150, ctrAP=0  \Rightarrow g(in_{max0})=267, g'(in_{max0})=393
+\]
+\[in_{min1}: dnaA=660, ctrAP=1760  \Rightarrow g(in_{min1})=2666 %wouldn't this be a pareto frontier thing?
+\]
+\[in_{max1}: dnaA=1000, ctrAP=0  \Rightarrow g(in_{max1})=3800
+\]
+\[fanout_0=600
+\]
+\[fanout_1=1100
+\]
+With these set of parameters and thresholds the set rest and hold times are:
+\[\Delta t_{set}=1934.23749
+\]
+\[\Delta t_{reset}=1716.50821
+\]
+\[\Delta t_{hold0}= inf
+\]
+\[\Delta t_{hold1}=3218.61297
+\]
+The minimum hold times here are longer than the maximum set reset times and so for short periods of time, this element can be considered as a set-reset memory element.
+Since these are the worst possible bounds, in practice set reset times would be shorter and the hold times would be even longer.
+Thus we can abstract these biological motifs as a series of dynamic memories connected to each other.
 

### 2017-03-22 asyncleakyn.tex
split electronics and bio

@@
 \section{Correct boolean model}
-In current designs of digital circuits, these are mostly synchronous circuits.
+Current designs of digital circuits use mostly synchronous circuits.
 They are called synchronous due to the existence of a global clock which controls each logic gate.
-The clock signals ensures that each gate are updated at the right time and also given enough time to propagate the correct output to the next gate.
+The clock signals ensures that each gate are updated at the right time, synchronously, and also are given enough time to process the inputs into the correct output to the next gate.
 This avoids transmitting the wrong intermediate signal, which can cause an error in the final output compared to what we would expect.
-There are also asynchronous circuit designs, where there is no such clocks and the variable delay times may cause one transition to happen before another at random.
-()  Thus asynchronous systems must be designed more carefully to allow for these random events.
+There are also asynchronous circuit designs, where there are no such clocks and each gate may finish processing its inputs at random.
+The delay times, the time from when an input is applied until the proper output is reached, is thus variable.
+This may cause certain transitions to happen before others at one time, and later than other during another processing of the inputs.
+Depending on the circuit topology, changing the order of when these outputs are available may change the final logic output, usually an event that we would like to avoid if we want the circuit to perform reliably.
+Thus asynchronous systems must be designed more carefully to allow for these random events.
+To understand how digital circuits and especially asynchronous digital circuits are designed, we first look at the pieces from the ground up.
+We review the basics of a complementary metal-oxide-semiconductor (CMOS) circuit, what digital circuits mean and some general properties for digital circuits to function.
+\newline \newline
+%expand more about continuous to binary (check)
+The inputs and outputs of electronic devices are voltage values which are continuous for example can take any value between a minimum value like 0 V and some maximum value $V_{max}$ .
+Circuits that operate using these continuous values to transmit signals and therefore information are called analog circuits.
+Digital circuits are an abstraction on top of these underlying analog circuits.
+They restrict the information passed by the signals so that the continuum of possible values for the signal are not all significant.
+Only two values are allowed in digital circuits, '1' or '0'.
+The binary value of'1' or '0' is extracted from the original analog signal by thresholds.
+Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
+The in between region is undetermined meaning it is neither a '1' or a '0'.
+For this reason a digital value of high or '1' are synonymous and also represented in the circuit by a high voltage value.
+The same is true of a digital value of low or '0' is represented in the circuit by a low voltage value.
+There are many reasons why we would want the drastic reduction of the amount of information carried from an analog system to a digital system.
+The main reasons are due to process variation when fabricating these devices and noise.
+Variation means that each device does not function exactly as how it is specified, but each has some percentage difference between its true value and the design.
+Noise degrades the signal, and makes it hard to use the raw analog signal, for example when adding two numbers together.
+Digital circuits greatly reduce these issues because instead of the actual value, only a high or low signal matters.
+\newline
+\includegraphics[width=\textwidth]{thresholds}
+\newline
+Present day circuits generally use metal–oxide–semiconductor field-effect transistors (MOSFETs) in their designs.
+These devices has three connections, the gate, the drain and the source.
+The gate allows some voltage to be applied over the device but is not actually connected to the drain or the source.
+Depending on the relative voltage of the gate and source and drain and source, the drain and source may have no current flowing between them, effectively functioning as an open circuit, or approximately as a resistor.
+%do I need to go in more detail?
+\newline
+\begin{center}
+\includegraphics{mosfet}
+\end{center}
+\newline \newline
+In CMOS there is the concept of a pull up network and a pull down network.
+Based on the logic of the pull up and pull down networks, they can either function as an open in the circuit, or as some connective component.
+So that when the pull up network is connected, and when the pull down network is effectively an open, the output signal gets pulled high.
+While if the pull down network is connected and the pull up network is an open, the output signal gets pulled low.
+In the inverter example, the pull up network consists of a PMOS that is connected to a voltage supply of $V_{dd}$ on one end and the pull down network consists of a NMOS which is connected to ground on one end.
+PMOS behaves, on first order approximation, as a resistor when the input voltage is low and as an open switch when the input voltage is high.
+NMOS is the opposite, it behaves as an open switch when the input voltage is low and as a resistor when the input voltage is high.
+Thus when the input voltage is low, the output voltage is pulled up by the PMOS to $V_{dd}$.
+Meanwhile when the input voltage is high, the output voltage is pulled down to ground by the NMOS.
+The voltage transfer characteristic (VTC) of the inverter is a sigmoid.
+This can be worked out using the equations of the MOSFET in different regions of operation.
+It is in fact also a sigmoid in the other boolean logic gates that we use such as AND and OR gates.
+%(write about dynamic memory later?)
+\newline \newline
+\includegraphics[width=\textwidth]{mosinaction2}
+\begin{center}
+\includegraphics{vtc}
+\end{center}
+\newline \newline
+
+Memory elements are important in asynchronous circuits because they can hold the signal for some time until they receive input, usually from elements further down the circuit to signal that the current output has been acknowledged and processed already and does not need to hold anymore.
+This can be implemented in a number of ways but one method is adding a capacitor to the output.
+The equation of a capacitor is
+\[I(t)=C\frac{dV(t)}{dt}
+\]
+It can be thought of as being charged up by the voltage as a high voltage is applied from $V_{out}$, or discharges when $V_{out}$ is low.
+When in an RC circuit, the capacitor charges and discharges exponentially.
+This is a valid way of maintaining the output voltage at either high or low for short amounts of time.
+\begin{center}
+\includegraphics{mosinv}
+\end{center}
+
+\newline
+%This is generic... can be applied to both
+We must also verify some properties when these circuit components are connected to each other.
+To ensure that they operate correctly as part of a larger circuit.
+First we want verify the thresholds are upheld so that for all signals below the low threshold, it is read into the gate as a '0' and produces the correct corresponding output.
+This must be verified for all signals above the high threshold as well.
+We first work with a single input and make some assumptions:  1) that passing the signal at the low and high threshold though the gate produces the proper binary output signal, 2) the gate function is a monotonic function.
+Then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.
+We first assume the function G() is monotonically increasing, the reasoning is that for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_i)$.
+The same could be shown for $input high$ and $x_j$.
+If the function G() is monotonically decreasing then the inequality sign of the previous argument is flipped and the correct operation of the circuit still holds.
+(We verify that our initial assumptions hold in that we can set the output low and high thresholds accordingly, and sigmoidal functions are indeed monotonic functions.
+)
+%there are actually examples where this fails 0->0 in monotonically decreasing... need to fix too
+\newline \newline
+The next step is when gates are connected to each other, signals must propagate meaningfully as well.
+The output of a gate should read as the same binary value into the input of the following gate based on their respective thresholds.
+That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.
+Multiple inputs are common in biology where there can be activators and repressors and even degradation enzymes involved in one gene product.
+This is easily reducible to the familiar problem in one dimension.
+\newline \newline
+The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.
+For the signals to allow a certain amount of noise to enter the system, we would want the output thresholds of one gate to be as far away from the input thresholds of the next gate as possible.
+Thus when noise gets added to the output signal, it still has a good chance to transmit the correct binary data to the next stage.
+In addition, these components can be connected in a loop.
+In electronics, since the outputs and inputs are measured against the same unit of measurement, the voltage, the additional requirement is that the gain must be greater than 1.
+This means that the slope of the function should be greater than 1.
+\newline \newline
+
+\section{Dynamic Memory}
+%some intro about memory?
+%EE
+We have seen in the previous section how short term memory elements can be implemented with capacitors.
+We examine some other ideal memory elements we would like as part of an asynchronous circuit, such as the Muller C-element.
+The Muller C-element is useful in the design of asynchronous circuits.
+If every signal in a circuit is connected with C-elements then it ensures that the circuit can run robustly and has the speed independence property.
+Thus we would ideally want the elements we see in biological circuits to operate similarly to the C-element.
+A common CMOS implementation of a C-element is shown with two inputs A and B, and an output C.
+It operates similarly as the inverter example.
+In this C-element example, when A and B are both high, the pull down network is activated, while there are open switches in the pull up network and the output is connected to the ground.
+When both A and B are low, the opposite is true and the output is pulled to $V_{cc}$.
+However when A and B are different signals ie A is high and B is low or when A is low and B is high, then there is no path through either the pull up or the pull down network and the previous value of the output is retained.
+This state is called a 'hold'.
+\begin{center}
+\includegraphics{celement}
+\end{center}
+\begin{center}
+
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}| } 
+ \hline
+\textbf{In1} & \textbf{In2} & \textbf{Qnext} & \textbf{Action} \\
+\hline
+1 & 1 & 1 & set \\
+\hline
+0 & 0 & 0 & reset \\ 
+\hline
+0 & 1 & Q & hold state \\ 
+\hline
+1 & 0 & Q & hold state\\ 
+\hline
+\end{tabular}
+
+\end{center}
+
+\newline
+%EE
+Set reset latches have a similar modes of operation with output high output low and hold but also differs in an important detail.
+In a set reset latch, there are two inputs, called a set and a reset.
+We look at the set reset NOR latch.
+When set is high and reset is low then the output signal is 'set' or becomes high.
+When set is low and reset is high then the output signal is 'reset' or becomes low.
+If both inputs are low then the output does not change and is in the hold state.
+The last state when both inputs are high gives an undefined output represented by 'X', usually this element does not go into this state.
+The similarities between set reset latches and C-elements are quite apparent.
+It is basically equivalent if you treat the reset signal of the set reset latch as an inverted second signal for the C-element.
+However, when A is high and B is low, there is a hold state for the C-element whereas that corresponds to a high set and high reset and thus an undefined output for the set reset latch.
+\begin{center}
+
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}| } 
+ \hline
+\textbf{S} & \textbf{R} & \textbf{Qnext} & \textbf{Action} \\
+\hline
+1 & 0 & 1 & set \\
+\hline
+0 & 1 & 0 & reset \\ 
+\hline
+0 & 0 & Q & hold state \\ 
+\hline
+1 & 1 & X & not allowed\\ 
+\hline
+\end{tabular}
+
+\end{center}
+
+\section{Biology equivalent}
+%BIO
 We expect biological systems to behave similarly to an asynchronous circuit because in biological systems there are no 'global clocks' that regulate the timing.
@@
 \newline \newline
+%BIO
 From the bottom up, we extract properties from biological networks and use analogies with the well developed CMOS technology.
@@
 \newline \newline
+%BIO
 The physics of gene protein interactions in the cell are congruent with properties that make it a valid digital circuit as well.
@@
 The mRNA production here can be modeled with the Hill function.
-The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.
+The sigmoidal shape of the Hill function is reminiscent of VTC of CMOS gates.
 As such, much of the design properties of CMOS circuits can be carried over.
@@
 It's steady state solution is $protein=g(inputs)/\lambda$, easily verifiable as also a sigmoidal Hill function.
-%new, about the thresholds
 \newline \newline
-The inputs and outputs of electronic devices are similar to the chemical concentrations in a cell which are all actually continuous values (analog).
-The concept of a binary '1' or '0' is extracted from the original analog signal.
-Thresholds allow the conversion of an analog signal into a binary signal.
-Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.
-The in between region is undetermined meaning it is neither a '1' or a '0'.
-\newline
-\includegraphics[width=\textwidth]{thresholds}
-\newline
-Thus we must verify the thresholds are upheld so that for all signals below the low threshold, it is read into the gate as a '0' and produces the correct corresponding output.
-This must also be verified for all signals above the high threshold.
-We first work with a single input and make some assumptions:  1) that passing the signal at the low and high threshold though the gate produces the proper binary output signal, 2) the gate function is a monotonic function.
-Then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.
-We first assume the function G() is monotonically increasing, the reasoning is thus for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_i)$.
-The same could be shown for $input high$ and $x_j$.
-If the function G() is monotonically decreasing then the inequality sign of the previous argument is flipped and the correct operation of the circuit still holds.
-We verify that our initial assumptions hold in that we can set the output low and high thresholds accordingly, and the Hill function is indeed a monotonic function.
-%there are actually examples where this fails 0->0 in monotonically decreasing... need to fix too
-\newline \newline
-The next step is when gates are connected to each other, signals must propagate meaningfully as well.
-The output of a gate should read as the same binary value into the input of the following gate based on their respective thresholds.
-That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.
-Multiple inputs are common in biology where there can be activators and repressors and even degradation enzymes involved in one gene product.
-This is easily reducible to the familiar problem in one dimension.
+%BIO
  In biological systems where the ODE model is a sigmoidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.
-Thus this satisfies our monotonic requirement and allow for proper propagation.
+Thus this satisfies our monotonic requirement from the analysis in the previous section and ensures that proper propagation occurs through the circuit with the appropriate choices of thresholds.
 % In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.
 (expand?)
-\newline \newline
-The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.
-For the signals to allow a certain amount of noise to enter the system, we would want the output thresholds of one gate to be as far away from the input thresholds of the next gate as possible.
-Thus when noise gets added to the output signal, it still has a good chance to transmit the correct binary data to the next stage.
-In addition, these components can be connected in a loop.
-In electronics, since the outputs and inputs are measured against the same unit of measurement, the voltage, the additional requirement is that the gain must be greater than 1.
-This means that the slope of the function should be greater than 1.
-Because we are using different chemical species at each stage to transmit the biological signal, we need to scale the slopes of the function accordingly.
+%BIO
+%\newline \newline
+%Because we are using different chemical species at each stage to transmit the biological signal, we need to scale the slopes of the function accordingly.  
 %Sigmoidal, All the things about how they connect, why they are good latches/ memory elements, completion signals?
 \newline \newline
+%BIO
 Changing rates of degradation of proteins is an important aspect of the circuit that has been often ignored in previous models.
@@
 Thus there needs to be a separate way of representing the production of proteins from its degradation.
-We take inspiration from Complementary Metal–Oxide–Semiconductor (CMOS) technology.
-In CMOS there is a pull up network and a pull down network.
-In the inverter example, the pull up network consists of a PMOS and the pull down network consists of a NMOS.
-PMOS behaves, on first order approximation, as a conductor when the input voltage is low and as an open switch when the input voltage is high.
-NMOS is the opposite, it behaves as an open switch when the input voltage is low and as a conductor when the input voltage is high.
-Thus when the input voltage is low, the output voltage is pulled up by the PMOS to a high voltage.
-Meanwhile when the input voltage is high, the output voltage is pulled down to ground by the NMOS.
-The transcriptional and translational regulation of these genes are similar to a pull up network while the accelerated degradation is similar to a pull down network.
+We take inspiration from CMOS technology.
+We recall that CMOS employs pull up networks and pull down networks to produce an output value of either high or low.
+The transcriptional and translational regulation of genes are similar to a pull up network while the accelerated degradation is similar to a pull down network.
 If the background degradation is significantly slower, this effect can be thought of as similar to the parasitic capacitance that slowly leak the charge of the output signal.
 Overtime it degrades the output signal however for short time scales the output retains its voltage value and can be considered a dynamic memory element.
-Dynamic memory elements are important in asynchronous circuits because they can hold the signal for some time until they receive input, usually from elements further down the circuit to signal that the current output has been acknowledged and processed already and does not need to hold anymore.
-\newline \newline
-%(write about dynamic memory later?)
-\newline
-\includegraphics[width=\textwidth]{mosinaction}
-\begin{center}
-\includegraphics{mosinv}
-\end{center}
-\section{Dynamic Memory}
+
 There are certain network motifs in biology that allows cells to have some sort of memory.
@@
 %something about robustness?
-\begin{center}
-\includegraphics{celement}
-\end{center}
-The Muller C-element is useful in the design of asynchronous circuits.
-If every signal in a circuit is connected with C-elements then it ensures that the circuit can run robustly and has the speed independence property.
-Thus we would ideally want the elements we see in biological circuits to operate similarly to the C-element.
-A common CMOS implementation of a C-element is shown with two inputs A and B, and an output C.
-It operates similarly as the inverter example.
-In this C-element example, when A and B are both high, the pull down network is activated, while there are open switches in the pull up network and the output is connected to the ground.
-When both A and B are low, the opposite is true and the output is pulled to $V_{cc}$.
-However when A and B are different signals ie A is high and B is low or when A is low and B is high, then there is no path through either the pull up or the pull down network and the previous value of the output is retained.
-This state is called a 'hold'.
-\newline
-\begin{center}
 
-\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}| } 
- \hline
-\textbf{S} & \textbf{R} & \textbf{Qnext} & \textbf{Action} \\
-\hline
-1 & 0 & 1 & set \\
-\hline
-0 & 1 & 0 & reset \\ 
-\hline
-0 & 0 & Q & hold state \\ 
-\hline
-1 & 1 & X & not allowed\\ 
-\hline
-\end{tabular}
-
-\end{center}
-
-Set reset latches have a similar modes of operation with output high output low and hold but also differs in an important detail.
-In a set reset latch, there are two inputs, called a set and a reset.
-We look at the set reset NOR latch.
-When set is high and reset is low then the output signal is 'set' or becomes high.
-When set is low and reset is high then the output signal is 'reset' or becomes low.
-If both inputs are low then the output does not change and is in the hold state.
-The last state when both inputs are high gives an undefined output represented by 'X', usually this element does not go into this state.
-The similarities between set reset latches and C-elements are quite apparent.
-It is basically equivalent if you treat the reset signal of the set reset latch as an inverted second signal for the C-element.
-However, when A is high and B is low, there is a hold state for the C-element whereas that corresponds to a high set and high reset and thus an undefined output for the set reset latch.
 \newline  \newline
@@
 \]
-\[in_{min1}: dnaA=660, ctrAP=1760  \Rightarrow g(in_{min1})=2666 %wouldn't this be a pareto frontier thing?
+\[in_{min1}: dnaA=660, ctrAP=1760  \Rightarrow g(in_{min1})=2666 %wouldn't this be a pareto frontier thing?  NO because of the monoticities in each var
 \]

### 2017-04-05 asyncleakyn.tex
added to hold times in VLSI

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
 
@@
 \end{center}
-\newline \newline
+\newline
 In CMOS there is the concept of a pull up network and a pull down network.
@@
 %(write about dynamic memory later?)
-\newline \newline
+\newline
 \includegraphics[width=\textwidth]{mosinaction2}
@@
 \end{center}
-\newline \newline
+\newline
 
@@
 This is a valid way of maintaining the output voltage at either high or low for short amounts of time.
+We work these t in detail in a later section.
 \begin{center}
@@
 This state is called a 'hold'.
+Note that this is different from a hold time, which is a synchronous digital circuit concept.
+Hold time is the amount of time that a valid signal retains its value.
+It is useful to know to ensure that the signal maintains its correct value to allow downstream gates to properly compute the output.
+This is also important to our system since we are using dynamic memory.
+%added hold time
 \begin{center}
@@
 \end{center}
+As stated previously, the equation for a capacitor is:
 
+\[I(t)=C\frac{dV(t)}{dt}
+\]
+When we analyze the CMOS inverter connected to a load capacitance, when the input is high, the p-MOS is effectively off and the n-MOS operating in linear region can be approximately modeled as a resistor.
+Equating the current from the resistor and capacitor, we find that the equation for Vout is:
+\[\frac{-V_{out}(t)}{R}=C\frac{dV_{out}(t)}{dt}
+\]
+When the input is low, the n-MOS is effectively off and the p-MOS operating in linear region can be approximated as a resistor.
+Equating the current from the resistor and capacitor, the equation for Vout is:
+\[\frac{Vdd-V_{out}(t)}{R}=C\frac{dV_{out}(t)}{dt}
+\]
+\includegraphics[width=\textwidth]{mosinactionRC}
+These differential equations can be written in a more general form of 
+\[\frac{dV(t)}{dt}=C -\lambda \cdot V(t)
+\]
+Where $C$ and $\lambda$ are constants and the solution to this differential equation is an exponential of the form
+\[V(t)=((V_0\cdot\lambda-C)e^{(-\lambda\cdot t)}+C)/\lambda
+\]
+where $V_0$ is the initial value of V at time t=0
+\newline \newline
+Next we define some timing terminology.
+Define the input thresholds as:  $in_{min0}$ is the smallest acceptable input to represent an input '0' and $in_{max0}$ is the largest acceptable input to represent an input '1'.
+Similarly, $in_{min1}$ is the smallest acceptable input to represent an input '1' and $in_{max1}$ is the largest acceptable input to represent an input '1'.
+$out_{max0}$ and $out_{min1}$ corresponds to the output signal after putting the input signal at the appropriate input thresholds through the gate.
+$fanout_0$ and $fanout_1$ represent the '0' and '1' input thresholds to the next components respectively.
+\newline \newline
+Three values are of importance to us, the transition time between 0->1, the transition time between 1->0, and the time that the gate is in the hold state.
+Using the inverter example, the transition time between 0->1 is when the output is initially a valid 0 (so the initial input is 1), at time t=0, the input changes to 0 which prompts the output to change to 1.
+We assume an output low threshold of 0.8V ($out_{max0}$) and a fanout high threshold of 4V ($fanout_1$).
+The transition time is the time it takes between the output from below the low threshold until the ouput reaches the high fanout threshold.
+\includegraphics[width=\textwidth]{t0to1}
+Rearranging the equation to find time elapsed:
+\[\Delta t_{0->g1}= -log(V_{ss}-fanout_1)/ \lambda+ log(V_{ss}-V_0)/ \lambda
+\]
+Where $V_{ss}$ is the steady state output of the gate after the output finishes transitioning, usually Vdd in this case. \newline \newline
+Similarly, the transition time between 1->0 is when the output transitions from a 1 to a 0.
+We assume an output high threshold of 4.5V($out_{min1}$) and a fanout low threshold of 1V ($fanout_0$).
+\newline
+\includegraphics[width=\textwidth]{t1to0}
+The time elapsed is:
+\[\Delta t_{1->0}= -log(V_0-V_{ss})/ \lambda+ log(fanout_0-V_{ss})/ \lambda
+\]
+Where $V_{ss}$ is the steady state output of the gate after the output finishes transitioning, usually 0V in this case. \newline \newline
+The time a gate stays in the 'hold' state, is when the output switches and the charge on the capacitor discharges or accumulates but still has a valid 1 or 0 for some time.
+So it is the time it takes between a high output to reach fanout high threshold as it is discharging, or a low output to reach fanout low threshold as it is charging.
+\newline
+\includegraphics[width=\textwidth]{hold0to1}
+\includegraphics[width=\textwidth]{hold1to0}
+The corresponding elapsed time are:
+\[\Delta t_{hold 0}= -log(V_{ss}-fanout_0)/ \lambda+ log(V_{ss}-V_0)/ \lambda
+\]
+\[\Delta t_{hold 1}= -log(V_0-V_{ss})/ \lambda+ log(fanout_1-V_{ss})/ \lambda
+\]
+Where $V_{ss}$ is usually Vdd in the first equation and 0V in the second one.
+Note that for an inverter the time for hold state is a lot less than the transitions from 0 to 1 or 1 to 0.\newline \newline
 \section{Biology equivalent}
@@
 
-\newline  \newline
+\newline 
 In our model we wish to verify the set reset and hold property of each gene gate.
@@
 First we define some of the parameters and variables that we use.
-Define the input thresholds as:  $in_{min0}$ is the smallest acceptable input to represent an input '0' and $in_{max0}$ is the largest acceptable input to represent an input '1'.
+Define the input thresholds as the previous section:  $in_{min0}$ is the smallest acceptable input to represent an input '0' and $in_{max0}$ is the largest acceptable input to represent an input '1'.
 Similarly, $in_{min1}$ is the smallest acceptable input to represent an input '1' and $in_{max1}$ is the largest acceptable input to represent an input '1'.
@@
 There is an additional constraint where fanout thresholds $fanout_0$ and $fanout_1$ must be between $g(in_{max0})$ and $g(in_{min1})$ so that all legal input values provide legal outputs that feed into the next layer of components to be processed.
-\newline \newline
+\newline
 To find the maximum and minimum times for set reset and hold, we analyze the equation for time.

### 2017-06-20 restartm1.tex
restart method analysis

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\title{A method for restarting}
\author{Zoey Zhou}
\date{\today}  
\usepackage{graphicx}
\graphicspath{ {c:/Users/cuizy/Downloads/} }

\usepackage{amsthm}
\newtheorem*{definition}{Definition}
\newtheorem*{claim}{Claim}

\begin{document}
\section{Analysis for a restarting method}

\begin{definition}A state graph consists of <V, S, T> where V is the ordered set of signals where $1\leq k \leq n$ indexes into V and gives the signal $v_k$.  S is the set of all states in the state graph
and s(k) denotes the (binary) value of the state at signal $v_k$.  T is the set of all transitions in the state graph $T \subseteq S X S$ where $(s_i, s_j)$ denotes a transition from the state $s_i$ to $s_j$ 
with a single transition in some variable.\end{definition}
\begin{definition}Two state graphs $G_A$ and $G_B$ are similar if there exists a one to one mapping function f: $V_A \to V_B$.  So that for all $s \in S_A$, $\exists$ $s' \in S_B$ such that for all i in $n_A$,
$s(i)=s'(f(i))$, for simplicity we write $s\to s'$. And for all pairs of $(s,t) \in T_A$, $\exists (s',t') \in T_B$ and also for all pairs of $(s',t') \in T_B$, $\exists (s,t) \in T_A$ with $s\to s'$, $t\to t'$.\end{definition}

\begin{claim}Given some graph $G_A$ if we insert a signal that is a constant value (ie. 0 for all states) to form $G_B$ then $G_A$ is similar to $G_B$  \end{claim}
\begin{proof}
If we add the new signal to the beginning of the set of signals, $V_B={v_0} \cup V_A$ then the function f is just f(i)=i+1 for $1\leq i \leq n$.  And for all $s \in S_A$, we have $s\to s'$ where $s' \in S_B$.
Also the transitions in $G_B$ occur between (s',t') if and only if there is a transition (s,t) in $G_A$ with $s\to s'$, $t\to t'$.  Thus $G_A$ is similar to $G_B$
\end{proof}

Starting with a circuit that is a valid implementation of state graph $G$, we modify the circuit as follows, we add a $Restart_A$ signal, for every input A to the set or reset logic of some gate, we replace with 
$A$ or $Restart_A$.  The $Restart_A$ gate is implemented with a $0 \to 1$ restartable generalized C-element with no set signal, and a reset logic that is a copy of the reset logic of $A$.  If we allow a 0 signal 
being reset as staying in the 0 state then if we start at some state s0 from the original state graph $G$ and assign $Restart_A$ an initial value of 0 then the new state graph $G'$ we build from the new circuit starting
at state <0, s0>, the $Restart_A$ signal is a constant 0.  For all states $s \in S$ and corresponding state in the new state graph s'=<0, s>, then for every t such that $(s,t) \in T$, then $(s', t') \in T'$ where 
t'=<0, t> and since adding the new logic of $A$ or $Restart_A$ while $Restart_A$ is a constant 0 does not add new transitions to the new state graph that does not exist in $G$, this is an if and only if relation 
for all transitions starting from state s and s'.  Then by induction since there is an initial state s0 in $G$ and <0, s0> in $G'$, the rest of the states and transitions remain the same as in the original state graph $G$ 
with only an addition of the constant $Restart_A=0$ signal.  By our earlier claim, this new state graph $G'$ is similar to the original $G$.
\newline \newline
In the case of a stuck at fault in signal A, so that the $0\to1$ transition does not happen even when A is being set, then when enough time elapses the $Restart_A$ signal will go high. We build the resulting state graph from 
the circuit starting from this new state.  Since the new logic is $A$ or $Restart_A$, with $A$ now a constant 0 signal, and $Restart_A$ has the same reset logic as $A$, use the same argument as in the above paragraph 
but switch the signals so that we view $Restart_A$ as $A$ and $A$ as $Restart_A$, then the new state graph $G''$ that we build again has all of the states and trasitions as the original state graph $G$.  There is a slight 
difference in the mapping function f where f(1)= 1 (assuming A is the first signal in V) and f(i)=i+1 for $1< i \leq n$, then again it is inserting a constant signal to the original graph and thus $G''$ is similar to $G$.
\newline \newline
Thus this construction of a restartable circuit provides the same sequences of states as in the original circuit during normal operation as well as fault mode operation.  If we use the values of signals other than A, we cannot 
distinguish between the two circuits as it runs.

\end{document}

### 2019-04-04 draft_together3.tex
together draft

\documentclass[12pt]{report}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{suthesis-2e}
\usepackage[font=small,labelfont=bf]{caption}

\doublespacing

\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem*{definition}{Definition}
\newtheorem*{claim}{Claim}
\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem*{property}{Property}

%\usepackage[nottoc]{tocbibind} %Adds "References" to the table of contents
\usepackage{cite}

\title{Background for transient faults in asynchronous circuits}
\author{Zoey Zhou}
\date{\today}  
\usepackage{graphicx}
\graphicspath{ {c:/Desktop/} }

\begin{document}
\chapter{Introduction}
Digital circuits and its widespread use has spurred on many of present day technology.  Digital circuits differs from analog circuits in that its signals (voltages) can be represented as discrete values whereas signals in analog circuits are represented by continuous voltages.  This is achieved by delimiting the ranges of voltages that correspond to a particular discrete value.  Many digital circuits use binary values, that is the signals can only take on the value `logic 0' or `logic 1' (or low/high).  One advantage of only allowing discrete values is that digital circuits are much more robust to noise fluctuations in voltage.  Disregarding the lower level implementation, one can also abstract the function of digital circuits in terms of gates.\\

Although digital circuits are less sensitive to errors due to noise, it can experience other faults in its electronics which ultimately may lead to failure of the component.  Faults may arise due to fabrication defects and radiation such as from space.  Moreover due to new technology and shrinking transistor sizes for MOSFETs, radiation have caused more noticeable effects even at sea level. Thus designing fault free circuits is an important problem to study and solve.  \\  %can still be expanded

This work focuses on a class of digital circuits known as asynchronous circuits.  There is an arbitrary delay on the gates of asynchronous circuits so that each design must be additionally verified to operate correctly under such delays.  There is a variety of uses of asynchronous circuits because it has speedups over synchronous circuits and is also useful for synchronous systems where there is significant clock skew or combining components with different clock cycles and/or interfacing with the real world.  There are some previous work that has been done to make asynchronous circuits fault tolerant to soft errors.  The design is based on duplicating the circuit and only works for quasi-delay-insensitive circuits which requires a lot of assumptions about how the delays in the underlying transistors function.  The main contributions of this work are that it extends the previous work by proposing a new design.  The new design also follows the duplication strategy but makes fault tolerant the class of semi-modular speed independent circuits (a class of circuits about the same size as QDI circuits) with looser assumptions on the delay and without significant overhead.  Namely the only assumption is that the combinational logic components are composed of gates and that each gate is allowed to have arbitrary delay, instead of assuming that there is no delay in these components.  Previous designs do not work for this more generalized case of circuits.  This work also proves that such a fault tolerant model will always work and correct transient faults.  This allows for circuits to be more robust to different types of errors that may occur and prolong the lifetime and types of environments this circuit can be used for.

\section{Synchronous vs Asynchronous circuits}
Digital circuits can be divided into two types, synchronous and asynchronous.  The time it takes for gates to process input signals and then propagate the output to the next gates in a digital circuit may vary widely.  If the timing is somehow off, it is possible for the outputs to be different from the desired value and may cause harm. In synchronous systems this timing variation is dealt with by using a global clock.  The clock is then fed into each flip flop so that the flip flop outputs will lock and update the signals synchronously. The clock cycle frequency is chosen so that all of the gates can finish processing and the correct values are locked for the next cycle. That is, the clock cycle is usually designed to accommodate the slowest logic element. The design of synchronous systems can be complex and is not necessary to understand in detail for this work. \\
\includegraphics[width=\textwidth]{syncex}
\captionof{figure}{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
%possible picture of clock and flip flops?.... redraw as my own

Asynchronous circuits, as the name suggests, do not depend on a clock. As a result there are varying time delays in its components. The goal of designing asynchronous circuits is to make circuits that achieves some specification in spite of the time delays. That is, irrespective of the time delays, the circuit behaves the same way. One main reason that asynchronous circuits are used is that because it does not require clocks to propagate signals, instead as soon as one logic element finishes the signal goes directly to the next element.  This can allow the circuits to have speedups as it is not waiting for the slowest element for each clock cycle.  The resulting circuit is also very robust as it already accounts for possible variations in manufacturing that contribute to varying time delays.  Additionally even in synchronous systems, small asynchronous circuits are needed to match the inputs coming in from different circuits with different clock frequencies or from the outside world.  For large synchronous circuits clock skew from different parts of the system is also an issue and may be solved with asynchronous methods. \\ %Martin did not give references for these....prob ok then
\includegraphics[width=\textwidth]{asyncex}
\captionof{figure}{Example of a simple asynchronous circuit.  Note that there are no clocks and the signals can propagate at any time}

However, because the signals can arrive at the input at any time, the design is more complicated to ensure that the entire circuit functions correctly.  From a high level view the circuits are designed so that the signals progress irrespective of the delays.  This property is called Delay Insensitivity or Speed Independence depending on the underlying delay assumptions such as the maximum length of delays and on which components.  Even if this is designed correctly, when implemented there can still be hazards.  A hazard is when a certain sequence of delays of the circuit cause unwanted signal transitions to occur.  This may then propogate to other parts of the circuits and cause unwanted behavior.  When trying to eliminate hazards, the underlying delay assumptions are important as well as the implementation details such as gates and transistors. Given the same design under one implementation the circuit may have hazards while under another implemention the circuit will be hazard-free.  Some of the different delay assumptions that could be made are that the delays only occur at gates, or delays only occur on the wires or the delays occur on both gates and wires \cite{myers_book_2004}. Furthermore the bounds on the delay can vary as well. The most stringent case is if we assume that the delay can be arbitrarily long and takes on a value anywhere in the interval $(0,\infty)$ \cite{myers_book_2004}.  Circuits built under the unbounded gates and wires delay model are called Delay Insensitive circuits.  We will not use this delay model because the class of Delay Insensitive circuits is very restricted.  In particular one can only use buffers, inverters, and Muller C-elements to build Delay Insensitive circuits \cite{Martin_1990_DI} \cite{Martin1986_DI}.\\ %2nd reference not necessary

The asynchronous delay model that we consider is the unbounded gate delay model.  Circuits that can handle any delay under this model are called Speed Independent circuits. The unbounded gate delay model assumes that delays only appear on the gates and the delays can be arbitrarily long in the interval $(0,\infty)$.  The wire delays are negligible.  In addition we assume all forks, which is splitting a signal into multiple branches, do not have any time delays between each of its branches.  These assumptions are reasonable because the delays on the wires only change the operation of a circuit if the wire has forks.  (Otherwise you can lump the wire delay with the previous gate)  When a wire has forks, it is usually true in implementation that the delay between different branches of the fork is less than the delay for gates so that they arrive at the next gates at the same time from the perspective of the relevant gates.  This is also termed isochronic forks.  We focus on the unbounded gate delay model because the delay being unbounded is a pretty harsh requirement and would allow more circuits to work in a real life setting. \\ %how if we assume both gates and wires have delay cannot create many SI circuits, and also Muller is one of the broader classes that we can use

Muller circuits is the approach that D. E. Muller originally proposed based on this delay model \cite{Muller_59}.  Since then a number of synthesis methods following this design has been produced.  Usually the synethsis methods begin with some higher-level specification such as signal transition graph or petri nets and translate into a state graph.  State graphs describes the progression of changes of a finite number of signals.  (The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allows the circuit to function according to the state graph is synthesized.  The end result is a hazard-free and speed independent asynchronous circuit.   
There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.  \\  %add refs to gen C etc

\section{Organization of this work}
%why are async circuits important, timing delay etc
Because these various faults can interfere with the function of the circuit and even result in harmful operations(catastrophic failures), there has been a lot of work put into making digital circuits fault tolerant. Most of the fault tolerant solutions has been investigated for synchronous digital circuits.  Because the timing difference between different signals arriving do not have to be considered for synchronous circuits, they can use error correcting codes and redundancy techniques such as triple modular redundancy (TMR). Unfortunately many of these techniques have problems if directly implemented in asynchronous circuits.\\

In the rest of this work, in chapter two, I will first introduce the different types of common faults and their causes.  As well as the common fault models that researchers use when investigating these faults.  Then I will go into depth about the asynchronous circuit models that are relevant to this work.  I will then go through the existing body of work on fault tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.  In chapter three, I will show why the existing fault tolerant methods are insufficient and propose a new fault free method for asynchronous transient faults.  I will prove using logical proofs as well as formal verification methods to show why my new method always works.  In the final chapter, chapter four, I will conclude on how to better build fault free asynchronous circuits and suggest some possible new research directions.
%Overview:  why is the problem important  \\  maybe I can extend the Introduction a bit more
\chapter{Background}
\section{Faults}
Faults can be split into permanent and non-permanent faults.  Non-permanent faults are further split into transient and intermittent faults \cite{jha_gupta_2003}. %copied 
A fault is defined as the physical difference between the good or correct system and the current system.  An error may be caused by a fault, which is when the state of the system differs from the state of the good system and thus unable to perform some specified function.  Hidden faults are also possible where the fault does not cause an error \cite{jha_gupta_2003}. \\

Permanent faults refer to the presence of a fault that affects the functional behavior of a system(circuit) permanently.  Some examples that may cause permanent faults are: incorrect connections between integrated circuits, broken components or parts of components, incorrect silicon and metal connections (manufacturing problem), and functional design errors.  Most permanent faults occur during fabrication.  There are many existing literature that cover permanent faults and the different tests at production time that can uncover the presence and location of these faults. \cite{jha_gupta_2003} \cite{giz_book_2006}.  We ignore the possible manufacturing problems and assume that the circuit is free from those problems.  Instead we consider the permanent faults that develop during operation from radiation.  For example, high energy ions can impact the transistors and the circuit causing short-circuiting, rupture of the gate oxide insulation and other permanent faults.\\ %copied from SEE eetimes article

Non-permanent faults is defined as faults that affect the system's functional behavior for a finite but unknown period of time.  They can occur at random moments and are categorized into two types, intermittent and transient faults.  Intermittent faults are caused by non-environmental conditions such as loose connections, deteriorating or aging components, critical timing (hazards and race conditions), resistance and capacitance variations (which may lead to timing faults), physical irregularities, and noise.  Intermittent faults usually affects the system for a shorter time period than the application time of a test developed for permanent faults and thus may not be detected using such a test.  Intermittent faults can transition into permanent faults naturally but may take a long time from hours up to months.  \\

Transient faults are caused by environmental conditions such as cosmic rays, $\alpha$-particles, pollution, humidity, temperature, pressure, vibration, power supply fluctuations, electromagnetic interference, static electrical discharges, and ground loops.  In particular $\alpha$-particles are a major cause of these faults.  These $\alpha$-particles can interact with the semiconductor material which results in the generation of electron-hole pairs. When these $\alpha$-particles collide and interact with the circuit it can induce a voltage/current pulse.  Also known as single-event transients (SETs), if the width of this pulse or transient is wide enough it may propagate through the circuit.  $\alpha$-particles may also interact with a memory element (of which flip flops, latches and C-elements are most relevant to this work) and cause a bit flip in the state of the memory element. This is also known as single-event upsets (SEUs), SEUs include both single-bit and multi-bit upsets but single-bit upsets are most common and much work has been done to eradicate failures from SEUs.  
Transient faults may be hard to detect because it appears sporadically and may not affect the system during testing. \\

In this work we will not be concerned with intermittent faults since it can be thought of as a transition between transient to permanent faults.  Instead the two main fault modes we will look into are transient and permanent faults.  In both radiation effects, also called single event effects (SEEs), figure prominently.  SEEs are an umbrella term that covers the aforementioned SETs and SEUs as well as the single event effects causing permanent faults.  There are two main sources of radiation, one is cosmic rays from space which interact with the atmosphere to produce high energy neutrons.  Another is that $\alpha$-particles can be caused by trace impurities of radioactive elements present in the packaging material of the chip and the silicon substrate.  Radiation from cosmic rays become more severe at higher elevations while the latent source in packaging is difficult to eliminate.  Thus initially a lot of the work in fault tolerant design was done for aviation and space flight.

%failure mechanisms - physical and electrical causes of faults% maybe not that useful... may not need to go in depth

 %digital circuits
%Types of faults transient/perm (and possibly subcases too) \\
%Asynchronous circuits (different types) possibly synchronous too? (and our circuit model based on Meyer) \\
%Then talk about the fault tolerant solutions () \\
\section{Asynchronous Circuit and Synthesis}
In the previous chapter we described how an asynchronous circuit works from a higher level perspective and in particular that it should work under varying delays.  In this section we will cover some definitions and properties of the circuit and also how we can synthesize the circuit from a higher level specification.  Both Speed Independent and Delay Insensitive technologies will be introduced.  There are differences but also many similarities between the two methods.  Even though this work is based on the Speed Independent model, there has been some previous work done on the Quasi-delay Insensitive model so I wanted to provide some context to make a direct comparison.

\subsection{Speed Independent Circuits}
As mentioned in the introduction, the unbounded gate delay model assumes an arbitrary delay on all the gates and ignores any delay on wires.  This delay model is the basis for Muller circuits \cite{Muller_59}.  State graphs describe how we would like the circuit to function.  
Muller circuits are then synthesized from the state graphs.
\begin{definition}A state graph consists of $\langle W, S, T\rangle$ where $W$ is the set of finite signals $\{w_1 .. w_n\}$.  $S$ is the set of functions $[W \to \{0,1\}]$ %<-this might not be right math... and s(k) denotes the (binary) value of the state at signal $v_k$.  
which maps each variable to a boolean.  An element of $S$ is called a {\em state}. $T$ is the transition relation of the state graph, $T \subseteq S \times S$.  \end{definition}

State graphs can also be thought of as each state having a boolean value for each of the signal variables, and states can be named by these values.  For the state graphs that we work with, we assume all states are distinct and that in each transition, only one of the signal values change.  The transition arrows are usually labelled with the signal variable and in which direction the change occurs to help with an easier understanding of the graph. 
\includegraphics[width=\textwidth]{stategraphex}
\captionof{figure}{Example of a state graph.  The order of the variables in each state are x,y}
State graphs can be implemented as an asynchronous circuit where the signals of a state graph $V$ maps one-to-one to wires in the circuit.  Then the set of states $S$ can also describe the state of wires of the circuit.  \\

Next we describe the set of {\em transitions} of a circuit where only one signal value changes more formally.  
We write $s(w)$ for the value of signal $w$ in state $s$, and write $T(s, s')$ when there is a transition from $s$ to $s'$.

A transition has the additional constraint that only one signal is allowed to change between the two states in the transition:
\begin{property}For all $s$ and $s'$ in $S$, whenever $T(s,s')$ holds, there is exactly one $w \in W$ such that $s(w)\neq s'(w)$.
\end{property}
There may be multiple transitions from a state $s$.  A related concept is when the state of a circuit changes when one or more circuit elements is unstable, leading to a change in its output signal.  An unstable element is said to be {\em excited}.

\begin{definition}A wire $w$ in the circuit is {\em excited} in state $s$ if there exists a $s'$ such that $T(s,s')$ and $s(w) \neq s'(w)$. % Alternatively we define a function $f_v$ for wire $v$ such that if wire $v$ is excited in state $s_i$ then $f_v(s_i)$ takes on the value after the excited wire transitions and $f_v(s_i)\neq s_i(v)$.  If wire $v$ is not excited then $f_v(s_i)= s_i(v)$. 
\end{definition} %delete second part if I don't use f_u() later
%For example we propose $f_s$ and $f_r$ as functions that maps the current state to the output of the set and reset blocks respectively.
%(may need to change this definition to s'=/=s) <- added in

Note that from a state $s$ it is possible for multiple wires to be excited as defined above because there may be multiple transitions from $s$ to different states.  Each of the transitions causes a different signal to change.
%[Explain that multiple elements can be excited in the same state because there can be transitions to several different states, and each of those transitions can change a different signal.]
%[Think about including examples: a boolean gate and a C element ]

We consider semi-modular circuits because they are a subset of speed independent circuits and is a large enough class to include some interesting and useable circuits. A simple explanation of semi-modularity is that once a wire is excited, it stays excited until it transitions to the excited value. Formally this can be defined as follows: %proof that semi-modular circuits are also speed independent
\begin{definition}An asynchronous circuit is {\em semi-modular} if for every pair of states $s$ and $s'$ such that $T(s,s')$ holds, and let $v$ and $w$ be wires such that $s(w) \neq s'(w)$ and $w\neq v$, then if $v$ is excited in state $s$, $v$ is also excited in state $s'$ \end{definition}

%ADD SPECIFIC CONDITIONS THAT ALLOW SYNTHESIS
When the state graph have the following properties, it is possible to synthesize a hazard free and speed independent asynchronous circuit following the state graph.  Each variable from the state graph is implemented as a gate logic that takes other variables/wires as inputs and outputs a variable/wire.  We next look at how such a gate logic can be made.\\

%C-elements
The C-element proposed by Muller is an important building block for asynchronous circuits.  It acts as a memory element in that it receives two inputs.  When both inputs are low, the C-element output goes low, and when both inputs are high the C-element output goes high.  However when the inputs are mismatched then the output gets held at its previous value.  This can be achieved in a number of ways such as a gate implementation as well as a transistor level implementation with feedback using a weak transistor, other implementations use capacitance to achieve this weak feedback.
\includegraphics[width=\textwidth]{celement}
\captionof{figure}{ a. logic of the C-element. A, B are inputs, C is the output \\  b. diagram of a C-element at the gate level   c. transistor-level implementation}

C-elements can be used in various asynchronous circuit designs and is an essential component of Muller circuits.  \\

The two specific Muller circuit implementations that we consider are the generalized C-element and standard C-implementations.  We assume that the circuits we want to make fault tolerant follow these implementations.    
For each wire in the state graph there is a gate logic that controls the value of the wire.  We look at two conditions, set, the condition for the wire to transition to a high value; and reset, the condition for the wire to transition to a low value.  The gate logic then implements the set and reset conditions. The details of how this is implemented is that we use the state graph to generate the set and reset conditions. For each set and reset there is an ON-set, OFF-set and Don't Care set.  ON-set are all states in the state graph where the wire is excited and a transition will occur.  That is for the set condition, it must evaluate to TRUE for these states so that the wire can transition to high.  OFF-set includes all states where the set condition must evaluate to FALSE which is the states where the wire is excited but to the opposite value, which is low for set, as well as all states in the state graph where the wire value is at the opposite value, again low for set.  The rest of the states are in the Don't Care set which includes states that are not included in the state diagram.  It does not matter what the set condition evaluates to in these states as they do not disturb the function of the circuit. The same procedure applies as well in finding the ON-set, OFF-set and Don't Care set for reset except substituting in reset for set and flipping the value of the wire where needed. The set and reset conditions then must include all states in the ON-set and not include all states in the OFF-set so that the wire transitions according to the underlying state graph.  The set and reset can be implemented separately with logic and the gate logic for the wire includes logic for both set and reset and also the combination of them into the output wire.   \\   %Beerel and Myers.... also expand?

Even though the generalized C-element is presented as a C-element with set and reset as inputs, the transistor level implementation differs slightly.  We assume a transistor level implementation of the set and reset combined with the C-element so that there is only one delay for the entire logic block.  In addition this is not a normal C-element because set is used exclusively for the pull-up logic and reset is used for the pull-down logic.  In a normal C-element we allow for any four combinations of the values of the set and reset input wires.  However using the pull-up and pull-down logic setup, we do not allow for when both set and reset is `ON' as the output wire would simultaneously be connected to the high voltage and ground.  Such an output would have indeterminable voltage values and violate the digital assumptions.  Thus, the set and reset logic is designed so that they cannot overlap.  This corresponds to $\overline{set}\vee\overline{reset} $ is always TRUE.\\
\begin{center}
\includegraphics[width=.7\textwidth]{genC}
\end{center}
\captionof{figure}{transistor level implementation of a generalized C-element.  The + signs are the set logic inputs and - signs are the reset logic inputs.  For this particular element, set is in3 AND in4 while reset is in1 AND in2.}

The main difference is that the set logic and the reset logic must be designed so that they do not turn `ON' at the same time.\\

For the standard C-implementation, we allow for more variation in delay.  For the gate logic of each variable in the state graph, we look at the set and reset logic as composition of various gates (such as AND, OR, NOT).  Each of these gates can have their own delay that is arbitrary in length that is instantized as an intermediate wire.  Thus the logic must be synthesized more carefully to eliminate hazards that can occur in these intermediate wires.  In particular the set and reset must be activated at states only when the wire is appropriately excited.  As a result, the standard C-implementation has a number of set logic functions combined by an OR gate and fed into one input of the C-element.  There will also be a number of reset logic functions combined by an OR gate and passed through an inverter and fed into another input of the C-element.  This implementation uses the standard C-element so that if the set and reset inputs are mismatched, the output is held.  In general the synthesis can be changed so that there is a hazard-free implementation using only two-input gates.

 %explain sop?

 \subsection{Quasi Delay Insensitive Circuits}
 %QDI
Quasi Delay Insensitive Circuits (QDI) are related to Delay Insensitive Circuits.  Previously we mentioned that Delay Insensitive circuits operate under the assumption that both the gate and the wire have unbounded gate delays.  In particular each branch of a fork will have different delays and can be treated as separate wires.  One result about Delay Insensitive circuits is that it is a very restricted class.  Instead if that condition is relaxed so that some of the forks are allowed to be isochronic, then a more general class of circuits can be constructed.  Note that in the case where all forks are isochronic, then this becomes the same as speed independent circuits.  \\

The gates of a QDI circuit is formed from Production Rules (PRs).  For the single output case, a gate takes a set of variables as inputs and outputs a variable.  Again a transition on the variable $x$ is denoted as $x\uparrow$, a transition from $x=0$ to $x=1$; and $x\downarrow$, a transition from $x=1$ to $x=0$.  Then the two PRs associated with the gate with output $x$ is :
\begin{align*}
   B_u\mapsto x\uparrow \\
   B_d\mapsto x\downarrow 
\end{align*}
Where $B_u$ and $B_d$ are called guards.  Each guard is a boolean condition formed by some combination of the input variables.  When a guard is evaluated to be $True$ then the transition is activated.  When it is $False$ then the corresponding transition does not happen.  Note that similar to the generalized C-elements, both guards cannot be active at the same time.  In addition it is assumed that each guard is in a sum of products of the input variables.  The PRs of a circuit are evaluated all at the same time.  At any point in time, if a transition is activated, it will transition in a finite amount of time as long as the corresponding guard is held at $True$.  This is due to the assumption of the arbitrary delay of a gate.  Note that again, like the generalized C-element implementation, we assume that the transistor level implementation of a PR allow any arbitrary sum of products to be made where there are no delays within the logic of the sum of products.\\

Another important property of QDI circuits is \textit{stability}.  A guard is stable if it evaluates to False after the transition of the output variable is complete.  This eliminates any hazards that may arise when a guard is True and before the output has fully transitioned, the guard then evaluates to False and the transition is terminated.  This may cause a blip in the voltage, an incomplete transition, where the circuit may interpret it as either no transition or two consecutive transitions.  One additional assumption is that the PRs cannot be \textit{self-invalidating}.  That is, when a transition on an output occurs, it cannot immediately falsify the guard.  With this assumption, it can be shown that the output of a gate cannot also be its own input variable.  There are no self-loops.

\section{Fault Tolerant solutions}

%soft error protection <- error correcting codes for SRAM memory
Because faults cannot be eliminated in digital circuits, different methodologies have been used to make the circuits fault tolerant.  Much of the research done in this area are for synchronous circuits.  There has also been some research for asynchronous circuits using some similar techniques. First we present an overview of some common techniques for synchronous circuits, then introduce the current techniques for asynchronous circuits.  Some of the techniques in asynchronous design borrows or are inspired by the much more developed fault tolerant synchronous circuits field.  However due to the difference in timing assumptions of the two types of circuits the techniques are not completely transferable.  We describe why some of the solutions from synchronous circuits cannot be directly applied to asynchronous circuits.\\

%- used in the early days for space and flight, and systems that CANNOT go offline/errors like stocks and banking.
%- different techniques... explain a bit about each
%-hardware, software, hybrid, 
%-detection vs correction
%- ECC/ parity checking (needs software/ controller) (Mitra's method)
%-TMR is still super important (possibly why TMR is not viable for async)
In the early days there were certain systems for which eliminating faults and errors were very important.  These include space and aviation control systems where due to the altitude there are more radiation and thus more faults.  In addition faults that cause error is very detrimental to these systems and may cause failures leading to loss of life.  Other examples of systems requiring reliable circuits include banking and stock market applications where the system must function without error for hours at a time and in case of any error may have devastating consequences, such as a bit flip of the most significant bit in a money transaction. \\

Solutions for eliminating these transient fault induced errors include physical, hardware, software or a mix of the previous.  Some commonly used techniques are transistor sizing, circuit hardening, hardware duplication, and time redundancy \cite{Mitra_08_softerrors}.  Transistor sizing is a physics based technique and does not reduce as much soft errors as the other techniques.  Circuit hardening is on the physics level, where it uses intrinsic properties such as resistive or capacitive hardening, or combining the transistors differently to have less effects from transient faults. (?)  Hardware duplication, is a common technique that tries to eliminate soft errors on the circuit level.  This is achieved by having multiple duplicates of a circuit and often comparing the value from each duplicate to find and eliminate errors.  For example Triple Modular Redundancy (TMR) has been used since the beginning of the field and is still a good solution for eliminating single soft errors.  The advantages are that it is able to eliminate nearly all soft errors but also due to the duplication, the area for each circuit and additional power increases substantially (correlates to the number of additional duplicates).  Time redundancy techniques re-use the same circuitry to compute values multiple times to ensure there is no error.  This technique is not completely hardware based and requires software to manage re-using the same circuity with the same inputs over time.  The area of the circuit does not change but the speed of the circuit worsens substantially. \\

There is also the additional distinction between error detection versus error correction.  In general it is easier to detect an error than to correct it.  For example using hardware duplication, only 2 copies are required to detect an error but 3 copies (TMR) to correct the error.  For different parts of the system there are also different strategies.  For example in memory components such as SRAM, soft error correction is usually done using error-correction codes.  These codes are compared to the bits that are stored to ensure that there are no errors.  They are designed to handle a predefined maximum number of errors.  For example Hamming codes where each codeword are at least a distance of 3 apart can handle one error.  This method is not purely hardware based and a controller system and software is used to match the codes and detect and correct any errors.  For a control circuit, there are also a variety of strategies.  Again, one could make use of error correcting codes or parity bits to detect or correct errors in combinational logic \cite{McCluskey_99}.  This uses a combination of hardware and software.  A completely software approach is to run a program on some input, then run the program again on a transformed version of the input where the output can be mapped back to the original output \cite{Mitra_softwareerror}.  If the output and the transformed output do not match then the fault is detected.  Lastly, for hardware only methods, even now TMR is a commonly used method because of its robustness and ensures error correction. \\
%However these cannot be used for latches or flip flops.  In these circuits,    Some of these techniques only detect errors but do not correct them.\\

Triple Modular Redundancy is a technique where each combinational logic unit is copied three times and then fed into a latch that performs a majority voting operation.  That is, if at least 2 out of the 3 signals agree on a value, the output becomes that value.  Additionally, to counter possible faults on the single output wire, the majority vote unit can also be copied three times and it's output wire fed appropriately as input to the three copies of the downstream combinational logic.  This would resolve both transient and permanent single faults.  However the downside is that the circuit needs to be copied three times so the area is three times larger and the power consumption as well.  In addition there must be many adaptations for this to work in asynchronous circuits as the signals can arrive in different orders.  We give an example of why TMR does not work in an asynchronous circuit as it does in a synchronous circuit below.  We assume that in the original circuit that each logic block has some input wires and an output wire.  In the TMR scheme, each logic block is triplicated and to remove single points of failure, we also triplicate the majority voter that the three copies of the output wire feeds into.  There are also three distinct copies of each input signal that correspond to outputs from the three voters.  This is the basic scheme that synchronous circuits with TMR uses.  Because this circuit is asynchronous, we assume that each logic block is composed of gates that has some arbitrary delay that is independent of other gates.  This is true under both delay assumptions of speed independent and delay insensitive circuits.  We ignore whether a fault can be in the voter for now. 
\begin{center}
\includegraphics[width=\textwidth]{tmrcounterex}
\end{center}
\captionof{figure}{An example of an error if a fault occurs in an asynchronous TMR circuit}
Initially all output wire values are `0's.  Then since the input signals are distinct copies of each other, it is possible for one set to finish transitions (new) before the other two sets and the first logic block transitions to a `1'.  Then a transient fault arrives on the output of the second logic block which transitions to a `1' as well.  The majority voter would then transition to a `1'.  However the upset from transient faults usually happen within a short time period and the old inputs eventually force the output of the second logic block back to `0'.  Then the majority voter would transition to a `0' so that causes a hazard on the output of the majority voter.  %depends on if the logic gate was combinational logic.... which I guess we can assume it is
%NEEDS FIXING AND CHECKING
It is also possible for the `1' from the majority voter to feed into other logic units which is effectively an early transition.  That early transition will then put the circuit into states that are not specified by the original state graph and thus the next states cannot be predicted.
\\

%also included detection schemes because there is so few works in the literature...
David and Ginosar (1995) prove that a specific type of asynchronous circuit called self-timed combinational logic is self-checking under stuck-at-faults \cite{self_timed}.  (Stuck-at-faults are permanent faults where a wire value is stuck at 0 or 1)  That is if there is a single stuck-at-fault, the circuit will either stall or give an illegal output so that faults can be detected.  Each input and output is encoded by 2 bits also known as dual rail encoding.  10 represents 0, 01 represents 1, and 00 represents undefined or the system is not yet ready.  11 is an illegal output that only occurs under certain faults.  Each logic unit is composed of four subunits, three of which control the inputs and outputs and includes many C-elements.  The fourth one implements the combinational logic.  The combinational logic requires the implementation to be such that each output bit is monotonous given the input bits.  A further restriction is that the combinational logic is composed of only AND and OR gates.
\\

Verdel and Makris proposes that simply porting the duplication strategy for error detection from synchronous circuits does not work for asynchronous circuits \cite{async_dup_ced}.  This is because the duplication strategy relies on both the original and duplicate to output the same value.  Some modifications that they propose to make the duplication error detection strategy work is to assume additional timing requirements.  That both copies should output the same value within a certain time determined by a pre-set delay element.  Everytime one of the signals transitions to a new value, and the duplicates are mismatched the timer starts and if they stays mismatched when the timer ends an error is detected.  They look at stuck-at-faults and premature firing faults.  There are also cases when the timer detection does not work and for those cases they propose using additional hardware to look at the states of all the wires to see if an illegal state was reached.  They present an example of a control circuit for data computations.  The main restrictions of this method is the additional timing assumptions they make about two copies of a circuit, and that the extra hardware components are assumed to be fault-free.  Also it requires an additional comparison unit for each pair of signals which may be costly.  Only one copy of the duplicates produce output signals that interfaces with the other units so that if there is an error on that signal it is not detected until some time after the error has propagated.
\\

Almukhaizim and Sinanoglu (2007) propose a Triple Modular Redundancy (TMR) based method of solving transient errors but requires a hazard-free majority voter.  Transferring the TMR method that solves faults for the synchronous circuits to asynchronous requires the change that 2/3 copies agreeing is not good enough but 3/3 is needed to propagate a signal.  This is due to the asynchronous property where signals can change at any given time and thus one signal changing plus a transient error may cause the output wire to transition prematurely.  For permanent errors there is an additional problem of deadlock and this configuration does not solve it completely. \\
\\
In the paper by Manohar and Peng (2005), they add in new circuitry that solves faults for a specific asynchronous adder circuit \cite{PengManohar_asyncadder}.  The faults that they consider are fabrication defects, permanent faults and unrecoverable failures.  New nodes and edges are added to make it k fault tolerant.  They detect when there is a deadlock at which time it reconfigures the circuit by trial and error of all the possible combinations until the circuit is no longer deadlocked.   \\

Naqvi (2014) shows how to solve transient faults on muller pipelines \cite{Naqvi_mullerpipeline}.  Muller pipelines make use of handshaking protocols.  The assumptions they make are that only one fault occurs per handshake cycle.  They used formal verification to show that it works for one pipeline component. \\
\\
Jang and Martin (2005)’s paper considers the problem of single SEUs in QDI circuits \cite{JangMartin_SEUQDI}.  In the original functioning circuit, an SEU may cause a) a transition to a deadlocked state, an illegal state with no further possible transitions, b) abnormal, a transition to another state in the state graph and skip or adds certain transitions/signalling, c) tolerant where it transitions to an illegal state but the PRs are unaffected and eventually resumes to a valid state in the state graph.  They solve this problem by duplicating the circuit and appending C-elements to the end of each of the original wires .  In addition to duplicating the circuit they change the production rule set so that if the rule is about wire $X$ is true in the original circuit, in the new circuit the rule is $X^1$ and $X^2$ both have to be true.  For example
\begin{align*}
   B_u (...,x,...)\mapsto z\uparrow \\
   B_d (...,\lnot x,...)\mapsto z\downarrow
\end{align*}
after duplicating the circuit and adding in C-elements becomes:
\begin{align*}
   B_u^{double} (...,x_a\wedge x_b,...) & \mapsto z'_a\uparrow, z'_b\uparrow\\
   B_d^{double} (...,\lnot x_a\wedge \lnot x_b,...) & \mapsto z'_a\downarrow, z'_b\downarrow\\
   z'_a \wedge z'_b& \mapsto z_a\uparrow, z_b\uparrow\\
   \lnot z'_a\wedge \lnot z'_b& \mapsto z_a\downarrow, z_b\downarrow
\end{align*}
The last two production rules correspond to the additional C-elements added.  
They prove that with this new circuit, single SEU errors do not cause transitions to deadlocked states, nor abnormal transitions and thus are corrected.  Given the transistor-based QDI assumptions, any changes to the production rules are implemented at the transistor level and assumed to not add any delays.  In addition QDI logic is implemented in sum-of-products form and the production rules are excited only in the appropriate non-illegal states.  Faults are assumed to occur on the input/output wires as well as the new wires that feed into the C-elements.  Another assumption is every loop in the control circuit is at least length 3 to prevent deadlock. %not sure about this, may only be relevant for when they don't double the inputs
\\

The circuit transformation that Jang and Martin proposes work for their assumptions and specific implementation of QDI circuits at the transistor level.  However it is not reasonable to assume that any PR can be implementation with transistors with no delay.  Also for a simple 2-element inverter circuit their transformation also can end up in a deadlocked state after an SEU.  After the duplication and addition of C-element.  
\begin{center}
\includegraphics[width=.7\textwidth]{transfex}
\end{center}
Then if a 0->1 SEU occurs at $c_1^B$, it is possible for this circuit to deadlock.
\begin{center}
\includegraphics[width=.7\textwidth]{transfexc}
\end{center}
%fix later... it's technically that a simple duplicate and C-element scheme does not work

In some of the previous work they make additional assumptions such as the checking circuit is fault free.  We propose an asynchronous circuit transformation on a more general type of circuits, control circuits.  The transformed circuit can function under single transient faults.  In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits.

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Normal operation analysis}
As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
As the circuit follows the state graph, there may be multiple transitions per state and each path through the states and transitions may be different.  We want to record the succession of states and transitions and so we define a trace as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $\sigma_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(\sigma_i,\sigma_{i+1})$ for $\forall i \in \mathbb{N}$.\end{definition} 
%add finite traces
% all states or just the state graph ones

We want to define a notion of equivalence between two cicrcuits.  What we observe are the succession of signals which form the trace.  Thus we define circuits as equivalent if the traces are the same. 
\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B.  In other words: $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
\end{definition}
%good enough for now, do I need if and only if?

%An additional property of the asynchronous circuit is that one can view each wire as a separate black box.  For a wire $v$, inputs from the rest of the circuit ($I_v$ and $I_v \subseteq$ V) feed into a gate and outputs the wire value $v$.  We call the instantaneous value of the gate for $v$ of a state $s$ as $f_v(s|_I)$, where f is the function $f:[I \to \{0,1\}] \to \{0,1\}$ and $s|_I$ is the state $s$ projected on the input variables $I_v$.  If inputs to the gate remain constant, the output $v$ will eventually take the value specified by $f_v(s|_I)$  %maybe change v again, also the f(s) vs f(I) thing...

We make a fault tolerant circuit by the following circuit transformation: make a duplicate copy of the logic blocks to each wire.  We label the duplicated circuit halves as circuit A and circuit B.  Then for each output wire $w$ we connect the output of the logic blocks from each circuit half to three layers of c-elements as shown in figure \ref{fig:dupscheme}.  We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ and $c1^B$, $c2^B$, $c3^B$ for circuits A and B respectively.  In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements producing $c2^A$ and $c2^B$.  These are then the inputs to the second layer of C-elements producing $c3^A$ and $c3^B$.  These are then the inputs to the third layer of C-elements producing $w^A$ and $w^B$.  We can (arbitrarily) label one of the final C-element outputs as $w^A$ and the other output as $w^B$.  These then connect to other gates in circuit A and circuit B respectively.  \\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie. all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{circuitforproof3}
  \caption{Duplicating the original logic for each output wire and adding 3 layers of C-elements}
  \label{fig:dupscheme}
\end{figure}

Because the transformed circuit has some extra wires, we want to define a correspondence to compare wires of the original circuit with those of the fault tolerant circuit halves.  A state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.  Half of those bits are obviously from the A half of the circuit and half are from the B half.  The state graph for a fault tolerant circuit is defined on this combined state.  We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ are made up of the wires $w^A$ that correspond to the original wires $w$.  The half-circuit mapping $h^B$ is similarly defined to map to $s^B$.  We extend $h^A$ and $h^B$ pointwise to traces, in other words, $h$ is applied individually to each state in $\sigma$.  %not sure if I want the mapping to be from variable to variable or specific state to state
For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). The resulting trace may have successive repeated states and we delete the repeats to obtain a valid trace on the shortened wires.  %do I need to define all the new transitions in duplicated circuit?  maybe
\\

We want to show this circuit behaves similar to the original circuit under normal operation.  In other words we want to prove that after applying either mapping of $h^A$ or $h^B$, the resultant circuit and the original circuit are equivalent.  We first prove lemma 1 which states for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs in the original circuit.  However this does not guarantee that such a transition always exists so we also need to prove lemma 2 to show that a transition always exists and the circuit cannot deadlock.  These two properties combined together show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\

Note that there are some extra wires in the logic blocks in both the original and duplicated circuit.  We actually don't worry about the exact values of these wires other than that if the inputs follow the semi-modularity property then the logic block as an entirety behaves with the semi-modularity property(as long as it is initialized appropriately).  Here it does not suffice for the inputs to be a sequence of valid states and state transitions in the state graph.  This is because the semi-modularity property of the logic block is that if the logic block output is excited then it must remain excited until a transition occurs.  Since certain inputs, even if they are valid states, may cause the logic block to become unexcited before a transition occurs, we want a more stringent criteria.  The inputs must uphold the semi-modularity property which waits at certain input states until the output transitions, in addition to being valid states and state transitions from the state graph.  Then if the wires within the logic block is consistent with Semi-Modularity, that is if the inputs follow Semi-Modularity then there are no glitches at the output and if the output is excited it remains excited until the output changes. \\%newly added

The initial state in the original circuit must be assigned wire values that is consistent with semi-modularity.  For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.  The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s. The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.  Given these we will show how to define a corresponding initial state in the duplicated circuit.  %should I delete intermediate?
\begin{definition} A {\em valid initial state} for the A half of a duplicated circuit is defined as follows.  Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the Semi-Modularity property.  Assign the wire values within the logic block to corresponding wires in the half duplicated circuit.  Then assign the value $w$ to corresponding wires in the half duplicated circuit so that $w=c1^A=c2^A=c3^A=w^A$. The same assignment of wire values can also be applied for the B half of a duplicated circuit.
\end{definition}
%\textbf{
For all subsequent discussion in this document, when we talk about the trace of a duplicated circuit we assume that both sides start from the same valid initial state.  I will not include this assumption in the following lemma definitions to avoid complicated wording.  %}  
However for Lemma 1 we only require one half to start from a valid initial state.  
One additional assumption we make about the gates and wire values (including in the presence of faults) are that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the incoming wires.\\

\begin{lemma}[1]
Let $\sigma_n$ be the sequence of the first n states of a trace $\sigma$ in the duplicated circuit (the trace is possibly finite).  If a trace $\sigma$ starts from a valid initial state in the half circuit A, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit.  By symmetry this is also satisfied for the half circuit B.

%In the duplicated circuit, for all traces $\{\sigma\}$ that starts from a valid initial state for half of the circuit ${A,B}$, the following is true.  At each state $s_n$ in the trace mapped to $h^{A,B}(s_n)$ in the original circuit, a wire $w$ is excited if and only if exactly one of the following is true: the gate is excited or $x'^{A,B}\neq x^{A,B}$ or $x^{A,B}\neq w^{A,B}$.  (So for a wire that is not excited in the original circuit, neither the gates or the c-element is excited in the duplicated circuit.)
%need to modify to include two layer c-elements

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
\begin{proof}
Without loss of generality we prove that this property holds for the A half of the circuit, the same reasoning can then be applied to the B half of the circuit.  We prove this lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is
\begin{itemize}
\item For a length $n$ sequence $\sigma_n$ in the duplicated circuit, this maps to $h^{A}(\sigma_n)$, a prefix of a trace of the original circuit.
\item Every logic block is in a Semi-Modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s_k$ of $\sigma_n$ it is true that a wire $w$ in the original circuit of state $h^A(s_k)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  As a consequence a wire $w$ is unexcited if and only if none of the previous three conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses holds for any valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit from its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a Semi-Modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and the duplicated half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit (the logic block output is excited).  Together with the definition of the valid initial state $c1^A=c2^A=c3^A=w^A$ (no excitations within the C-element chain), if $w$ is excited in $h^A(s_k)$, then only $c1^A$ is excited.  Conversely if $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$ then $w$ is excited in $h^A(s_k)$.  All C-element chains in the duplicated have at most one wire in the chain excited. This shows the initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the sequence of the first $k$ states in a trace (for traces length greater than or equal to $k$).  We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.  In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.  Then we show that for all possible $s_{k+1}$ logic block remains in a Semi-Modularity consistent state.  Finally for all wires in $s_{k+1}$, the second induction hypothesis is true.\\

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in $h^A(s_k)$ and its corresponding wires in the A-half $s_k$.  For each excited wire $w$, the last induction hypothesis narrows the possible cases and we examine the next state if a transition occurs in each case. %logic gate excited = c1^A excited
\begin{itemize}
\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, which satisfies the third induction hypothesis for wire $w$.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires which are also inputs to logic blocks did not change so the logic blocks are in a Semi-Modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus the third induction hypothesis is true for wire $w$.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.   
\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus the third induction hypothesis is true for wire $w$.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.

\item The fourth case is when the signal propapagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a valid state in the original Semi-Modular circuit and the A-half logic blocks at state $s_k$ are Semi-Modularity consistent, inputs to all logic blocks in the A-half are also Semi-Modularity consistent. Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by Semi-Modularity)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (if we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Since $w$ is now unexcited, wire $w$ does not contradict the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by Semi-Modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, this does not contradict the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, that is not excited in $h^A(s_k)$, then in states $s_{k}$ and $s_{k+1}$,  $c1^A=c2^A=u^A$.  But since $u$ is excited then $c1^A$ of $u$ is excited.  Thus the third induction hypothesis holds for these wires $u$ as well.  
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, logic gate is not excited and $c1^A=c2^A=c3^A=u^A$ and the third induction hypothesis holds for these wires.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

%so technically one exception is the original w.... but w sort of counts in newly excited if it is indeed newly excited  
%need to expand on newly excited wires
%do I need to define transitions as it occurs here?

%prove each half separately
\end{proof}

Note that the previous proof does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g. does not cause hazards in the C-element output).  Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.  It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.  Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For all traces $\sigma$ in the duplicated circuit (for both halves starting in the same valid initial state), for any state in a trace, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the duplicated circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (the 0's and 1's inverted) and after case 11 the state transition goes through the second half of the cases with figure \ref{fig:l21} inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of lemma 1, those properties can be applied directly.\\

We look at the base case for every wire $w$ in the original circuit.  Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.  A wire $w$ can be either excited or unexcited in the original circuit. If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).  If $w$ is excited then applying lemma 1 the logic blocks must be excited which is case 2.  Thus this property is true for the base case. \\

In the induction step, assume that the induction hypothesis is true for state $s_k$ and show it is true for $s_{k+1}$.  \\

We examine all possible $s_{k+1}$.  That is for all possible transitions from $s_k$, verify that each $s_{k+1}$ has output wire blocks that is in one of the cases in the above figure.  It is clear that the arrows point to next cases which can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires within the C-elements are self-contained.  Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
\begin{itemize}
\item
Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
\item
Case 2a/2b:  In case 2a, $c1^A$ is excited and can transition to case 3a.  Similarly case 2b can transition to case 3c.  From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.  However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to Semi-Modularity and lemma 1.
\item
Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).  The logic block in A-half (B-half) cannot be excited again with $c1^A=1$ ($c1^B=1$) because that violates lemma 1.  From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.  The excited logic blocks cannot become unexcited due to Semi-Modularity and lemma 1.
\item
Case 4a/4b:
The excited logic block in both cases can transition and end up in case 5.  The excited logic block cannot become unexcited due to Semi-Modularity and lemma 1.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
\item
%Case 3a/3b:   If a transition occurs in these cases for wire block $w$, the only excited wires are $c1^{B}$ or $c1^{A}$ respectively.  By the same argument as case 2, the excitation state of the 4C-element for all wires in $s_{n+1}$ must remain the same (other than the one that transitions).  Thus in $s_{n+1}$ wire block $w$ is in case 4 while all other wire blocks remains in the same case from $s_n$ and thus all wire blocks are in a case in the figure. \\
Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires.  Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
\item
Cases 9/10a/10b:  In cases 1-8a/8b all the transition happen on intermediate wires so the state of the other wire blocks must remain the same.  In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.  In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.  If any logic blocks are in case 9, its logic block cannot change excitations because it would violate lemma 1.  Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than those included in the figure.  We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its logic block to be excited. For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.  This is shown by contradiction.  \\
Assume that there exists another logic block in case 10a and that $w^A$ transition causes an excitation in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).  All wire blocks are assumed to be in cases 1-10 in state $s_k$.  If there is an output wire mismatch such that for all wire $u\in W$ where $u^A\neq u^B$ then $c2^A=c2^B$ since it must be in cases 10a or 10b.  This is also true for those wires in state $s_{k+1}$ and the newly mismatched wire $w$.  Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in state $s_{k+1+m}$ (other than the one of interest).  In $s_{k+1+m}$ the excited logic block must still be excited due to semi-modularity.  But also the logic block in the other half must be excited since all of the input wires are equal.  This violates lemma 1 for that half and produces a contradiction.  Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.  Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires and causing a contradiction with lemma 1.

%still a slight problem here
\end{itemize}
This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
By induction on the consecutive states of the trace, this shows that all wire blocks of a duplicated circuit are in a case in figure \ref{fig:l21} for all traces. \\
\end{proof}
%may be that I don't need how all the intermediate wires go... but just need the at most one of input excitation and outputs can be mismatched.  But this needs to include if outputs are mismatched then the C-element is the same.... which I think I need to show the signals propagating through??
\begin{lemma}[2.2]
For all traces $\sigma$ in the duplicated circuit (that start in the same valid initial state), deadlock does not occur.
\end{lemma}
\begin{proof}
To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the duplicated circuit.  $s_k$ can be split into two cases, one is that for every wire block $w$ all wires in the A half and B half are equal that is $w^A=w^B$, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.  In the first case, if every output wire pair are equal, then $h^A(s_n)=h^B(s_n)$ and there exists an excited wire $u$ in the original circuit.  By lemma 1 both halves of the duplicated circuit for $u$ is excited.  By the lemma 2.1, the circuit must be in case 2-6 for $u$.  In each of these cases at least one wire is excited.  \\
In the second case, for some wire $v$ such that $v^A\neq v^B$, then using lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.  Since there are next transitions for both cases, deadlock does not occur.
\end{proof}

Combining the results of the previous lemmas yield the following result:
\begin{theorem}[1]
For all traces $\sigma$ in the duplicated circuit starting from valid initial states, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.  (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
\end{theorem}

%with these 3 properties show the original claim
\section{Single transient fault analysis}
%fix this
\begin{definition}A transient fault on a wire $x$ can happen so that from the start of the transient fault $x= \lnot x^{init}$.  At some time later, the wire is able to transition again based on its inputs. %do I need to talk about when transient is not ~x?  ie hold same value?  That's the same as a longer delay
\end{definition}
Next we will show that adding a single transient fault to any wire will still allow one of the half circuits to progress as normal.  Since the 'good' half will always progress according to the original state graph if a transition is available, we just need to prove that it never deadlocks.  To do this we prove some properties that are true when we add a single transient fault.  We split the wires into two sets based on their properties when a single transient fault is added.  Lemma 3.1 shows that if a single fault is added to $c1$, $c2$ or $c3$ wires of the wire block for some wire $w$, the output wires still follow the original state graph.  Lemma 4 shows that if an fault is added to any of the other wires, then the $c1$, $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.  Then we combine these lemmas to show that this implies that there is no deadlock.
\begin{lemma}[3]
For all traces $\sigma$ in the duplicated circuit, with a single transient fault occurring on a $c2$ or $c3$ wire of some wire $w$ at any point in the trace, then $h^{A}(\sigma_n)$ and $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
\end{lemma}
\begin{proof}
Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.  We use NuSMV to verify that adding a transient fault to one of the $c2$ or $c3$ wires do not change the input-output characteristic of the local circuit.  Under normal operation, by lemma 2.1 the pair of inputs and outputs cycle through 00 00 00$\rightarrow$ 01 00 00 or 10 00 00 $\rightarrow$ 11 00 00 $\rightarrow$ 11 01 00 or 11 10 00 $\rightarrow$ 11 11 00 or 11 11 00 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.  Thus the property verified in NuSMV is that when a single transient fault can happen spontaneously on wires $c2$ or $c3$, the cycle mentioned previously is always true.    %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
We go through an example of a transient on $c3^A$ to demonstrate why this happens.  By lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.
\begin{itemize}
	\item
If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b it does not cause any changes in excitations in the local circuit.  In particular since $w^A$ and $w^B$ do not change, then by semi-modularity the excited/unexcitedness of logic blocks are maintained.  So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^A$ value flipped. Eventually they all transition to state 8a and proceed from there as usual.
	\item
If the current state is 7 progresses the state to 8a, the correct transition.	
	\item
      If the current state is 8a then when $c3^A$ experiences a transient, the state
 becomes identical to state 7.  It will then proceed from state 7 as usual.   
	\item
If the circuit experiences a fault in state 9, it will revert back to state 8b.  
	\item
If the circuit experiences a fault in state 10a or 10b, $w_B$ or $w_A$ will go from excited to non excited respectively.  $c3^A$ will be excited but there are no other excitations in the local circuit.  Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited or transition on any subsequent states while $w^A$ and $w^B$ do not change (same argument as in lemma 2.1 can be used since the other wire blocks do not have transients and thus in one of the states in cases 2.1).  Then the local circuit will stay in this transient induced state until $c3^A$ finally changes and the circuit returns to its state before the transient.
\end{itemize}
%c3
A similar reasoning would then apply if a transient fault occurs in $c1^A$, and also for the $B$ half.  
\end{proof}

\includegraphics[width=.8\textwidth]{gatew}

\begin{figure}
  \centering
    \includegraphics{flowl4c3v2}
  \caption{The wires in each row are in order of $c1$, $c2$ and $c3$.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  Note that case 5 transitions according to case 1 except with the 0's and 1's inverted.  The states transitions after that are inverted versions of state 2-4 until it transitions back to state 1 (uninverted).}
  \label{fig:l4}
\end{figure}

\begin{lemma}[4]
For all traces $\sigma$ in the duplicated circuit, that allows adding a fault to any wire other than $c2$ or $c3$ at some time step $n$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ is always in a state of Figure \ref{fig:l4}.
\end{lemma}
\begin{proof}
Without loss of generality we prove this is true when a fault occurs in the A half.  Then we can assume Lemma 1 is true for the B half.  We show by induction that when the fault is not in $c2$ and $c3$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.  Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\

The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\

In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of figure \ref{fig:l4}, then at $s_{k+1}$ we look at the possible next states.  We don't assume anything about the non $c2$ and $c3$ wires for the A-half so that $c1^A$ may change values due to a fault.  However we do expect $c1^A$ to be either a 1 or 0 and that even with hazards on $c1^A$, $c2$ transitions to either 0 or 1.  We indicate the possibly faulty $c1^A$ by the symbol X.
\begin{itemize}
	\item
Case 1:  $c2$, $c3$ are not excited.  $c1^B$ can be excited depending on the inputs to the logic block.  Therefore, if there is a transition from this state it must be to case 2.
\item
Case 2/3a/3b:  $c2$ can be excited depending on $c1^A$.  $c1^B$ cannot transition to 0 due to Semi-Modularity of wire $w$ and Lemma 1.  Therefore, if there is a transition it must be from case 2 to case 3a or 3b, and case 3a or 3b to case 4.
%I might need to show the excited ness of the good logic gate
\item
Cases 4/5a/5b:  $c1^B$ cannot transition to 0 due to the same reasoning above.  $c2$ is not excited. The only possible transitions are on the $c3$ wires and since there are no faults on them they must transition from case 4 to case 5a or 5b, and from case 5a or 5b to 6.
\end{itemize}
By induction, the property we set out to prove is true, the $c2$ and $c3$ wires will be in a case of figure \ref{fig:l4}. 
The same logic applies to when a fault occurs in the B half and the A half is fault free.  
\end{proof}
The importance of this property is that at most one of $c2$ or $c3$ pairs can be mismatched.  And thus all output pairs at deadlock must be equal.

\begin{theorem}[2]
With the addition of a single transient fault, and for all $n \in \mathbb{N}$, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then one of $h^{A,B}(\sigma_n)$ (the non faulty half) is a prefix of a trace in the original circuit.  And the circuit does not deadlock.  
\end{theorem}
\begin{proof}
Without loss of generality we can assume the fault occurs in the A half of the circuit.  First by lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.  Thus we only look at when the fault occurs on all other wires. 
Next, we prove that a deadlocked circuit in this scheme must have at least one pair of output wires which have different values.  That is $w^A\neq w^B$ for some wire $w$.
This is shown by contradiction.  Assume that the circuit is deadlocked at state $s$ and $v^A = v^B$ for all wires $v$ from the original circuit.  If a transient occurs, one can wait until that wire is free to transition.  There
 must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in lemma 4.
\begin{itemize}
	\item
	Case 1: Since $w$ is excited then by lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
\item
Case 2:  $c1^A$ may be 0 or 1.  If $c1^A=0$, since the inputs to A half and B half are equal then $c1^A$ must be excited and can transition to 1.  If $c1^A=1$ then it can transition to case 3a or 3b.
\item
Case 3a/3b:  $c1^A$ may be 0 or 1.  If $c1^A=0$, since the inputs to A half and B half are equal then $c1^A$ must be excited and can transition to 1.  If $c1^A=1$ then it can transition to case 4.
\item
Case 4/5a/5b:  $c3$ is excited and can transition.
\end{itemize}
Thus a transition can always occur and the circuit is not deadlocked which leads to a contradiction.  To remain deadlocked, it must be true that there exists a wire where $w^A\neq w^B$, which implies its $c1^A\neq c1^B$ and $c2^A\neq c2^B$ and $c3^A\neq c3^B$.  But we have shown in lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault. Thus deadlock is not possible.  And applying lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit. 
\end{proof}

\bibliography{biblio}
\bibliographystyle{unsrt}
%\bibliographystyle{plain}

%\begin{thebibliography}{9} %9 if number of items between 0-9, 99 if 10-99 etc
%\bibitem{digitaltesting1} 
%N. K. Jha and S. Gupta,
%\textit{Testing of Digital Systems}. 
%Cambridge: Cambridge University Press, 2003.

%\end{thebibliography}
\end{document}

### 2019-04-05 draft_together3.tex
editing proof with better english part 1

@@
 As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
-As the circuit follows the state graph, there may be multiple transitions per state and each path through the states and transitions may be different.
-We want to record the succession of states and transitions and so we define a trace as follows:
+We want to define a trace, to describe the different paths a circuit can take as it follows the state graph.
+Different paths can occur because there are states with multiple transitions from that state.
+We record the succession of states and transitions by the trace which is defined as follows:
 \begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $\sigma_i$ is the $i^{th}$ term of the sequence.
 Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(\sigma_i,\sigma_{i+1})$ for $\forall i \in \mathbb{N}$.\end{definition}
+Even if there is only one transition from each state of a state graph, that is a linear state graph, our definition of trace is consistent with that.  \\
 %add finite traces
@@
 
-We want to define a notion of equivalence between two cicrcuits.
-What we observe are the succession of signals which form the trace.
-Thus we define circuits as equivalent if the traces are the same.
-\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B.
-In other words: $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
+[If the set of traces are equal then the state graph is equal]
+
+Given two circuits, how can we determine when their basic functionality is the same even if they are implemented with different gates and circuit elements?
+We define a notion of equivalence between two circuits.
+We want the underlying state graph representation of the circuits to be equivalent.
+However only the signals and the sequence of its transitions from the circuit is observable.
+In other words the trace is observable.
+Thus we define circuits as equivalent if the set of traces of the two circuits are the same.
+\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B (up to a permutation of the variable names).
+In other words, if it is possible to pair wires in A and B in such a way that $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
 \end{definition}
-%good enough for now, do I need if and only if?
+%good enough for now, do I need if and only if? <-NO, xxx if xxx in math lingo is iff
 
@@
 
-We make a fault tolerant circuit by the following circuit transformation: make a duplicate copy of the logic blocks to each wire.
-We label the duplicated circuit halves as circuit A and circuit B.
-Then for each output wire $w$ we connect the output of the logic blocks from each circuit half to three layers of c-elements as shown in figure \ref{fig:dupscheme}.
+We make a circuit fault tolerant by the following transformation on an existing semi-modular circuit: make a duplicate copy of the logic blocks of each wire $w$.
+We label the duplicated logic blocks as belonging to circuit A or circuit B.
+Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.
 We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ and $c1^B$, $c2^B$, $c3^B$ for circuits A and B respectively.
-In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements producing $c2^A$ and $c2^B$.
-These are then the inputs to the second layer of C-elements producing $c3^A$ and $c3^B$.
-These are then the inputs to the third layer of C-elements producing $w^A$ and $w^B$.
-We can (arbitrarily) label one of the final C-element outputs as $w^A$ and the other output as $w^B$.
-These then connect to other gates in circuit A and circuit B respectively.
-\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
+In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements outputting $c2^A$ and $c2^B$.
+These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.
+These are then the inputs to the third layer of C-elements outputting $w^A$ and $w^B$.
+We can label one of the final C-element outputs as $w^A$ and the other output as $w^B$.
+These then connect to other logic blocks in circuit A and circuit B respectively.
+Note that at some steps of the labelling which side is A and B can be somewhat arbitrary because the outputs of pairs of C-elements with the same inputs are symmetric.
+The symmetry is broken by connecting the final output $w^A$ to all its circuit A gate inputs and $w^B$ to all its circuit B gate inputs.
+All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
 all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
@@
 
-Because the transformed circuit has some extra wires, we want to define a correspondence to compare wires of the original circuit with those of the fault tolerant circuit halves.
+Because the circuit transformation introduces extra wires, we want to define a correspondence to compare states of the original circuit with those of the A-half and B-half of the fault tolerant circuit.
 A state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
@@
 The state graph for a fault tolerant circuit is defined on this combined state.
-We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ are made up of the wires $w^A$ that correspond to the original wires $w$.
-The half-circuit mapping $h^B$ is similarly defined to map to $s^B$.
-We extend $h^A$ and $h^B$ pointwise to traces, in other words, $h$ is applied individually to each state in $\sigma$.
+We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
+The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.
+The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are ignored.
+We extend $h^A$ pointwise to traces, in other words, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.
 %not sure if I want the mapping to be from variable to variable or specific state to state
-For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit).
-The resulting trace may have successive repeated states and we delete the repeats to obtain a valid trace on the shortened wires.
+%For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
+The resulting trace may have successive repeated states and we delete the neighboring repeats to obtain a valid trace on the shortened list of wires.
 %do I need to define all the new transitions in duplicated circuit?
@@
 
-We want to show this circuit behaves similar to the original circuit under normal operation.
-In other words we want to prove that after applying either mapping of $h^A$ or $h^B$, the resultant circuit and the original circuit are equivalent.
-We first prove lemma 1 which states for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs in the original circuit.
-However this does not guarantee that such a transition always exists so we also need to prove lemma 2 to show that a transition always exists and the circuit cannot deadlock.
-These two properties combined together show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
+To prove claims about the fault tolerance of this circuit, we must first prove that the circuit behaves similar to the original circuit under normal operation.
+That is, after applying a mapping of $h^A$, the set of traces of the resultant circuit and that of the original circuit are equal.
+And likewise after applying a mapping of $h^B$.
+We prove Lemma 1 which shows for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs in the original circuit.
+This property is independent of the signals on the other half circuit and is useful later in proving fault tolerance under a single transient fault.
+%as long as it does not violate digital abstraction
+However Lemma 1 does not guarantee that such a transition always exists so Lemma 2 is needed to show that a transition always exists and as a consequence the circuit cannot deadlock.
+These two Lemmas combine together to show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\% and all traces in the original can be mapped to duplicated after h mapping?
+<-this is obvious though by setting the A half and B half to both transition according to original trace
 
-Note that there are some extra wires in the logic blocks in both the original and duplicated circuit.
-We actually don't worry about the exact values of these wires other than that if the inputs follow the semi-modularity property then the logic block as an entirety behaves with the semi-modularity property(as long as it is initialized appropriately).
-Here it does not suffice for the inputs to be a sequence of valid states and state transitions in the state graph.
-This is because the semi-modularity property of the logic block is that if the logic block output is excited then it must remain excited until a transition occurs.
-Since certain inputs, even if they are valid states, may cause the logic block to become unexcited before a transition occurs, we want a more stringent criteria.
-The inputs must uphold the semi-modularity property which waits at certain input states until the output transitions, in addition to being valid states and state transitions from the state graph.
-Then if the wires within the logic block is consistent with Semi-Modularity, that is if the inputs follow Semi-Modularity then there are no glitches at the output and if the output is excited it remains excited until the output changes.
+The internal wires in the logic blocks that are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.
+The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.
+The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.
+This arises from the original synthesis method to synthesize the circuit from an underlying state graph.
+Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.
+The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.
+Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
+%maybe needs an example
+Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.
+Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following property is true:  if the inputs follow semi-modularity then there are no glitches at the output and that once the output is excited it remains excited until it transitions.
 \\%newly added
 
-The initial state in the original circuit must be assigned wire values that is consistent with semi-modularity.
+As mentioned in the previous paragraph, the internal wires The initial state in the original circuit must be assigned wire values that is consistent with semi-modularity.
 For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
@@
 \begin{definition} A {\em valid initial state} for the A half of a duplicated circuit is defined as follows.
-Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the Semi-Modularity property.
+Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the semi-modularity property.
 Assign the wire values within the logic block to corresponding wires in the half duplicated circuit.

### 2019-04-07 draft_together3.tex
up to lemma 2

@@
 We record the succession of states and transitions by the trace which is defined as follows:
-\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $\sigma_i$ is the $i^{th}$ term of the sequence.
-Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(\sigma_i,\sigma_{i+1})$ for $\forall i \in \mathbb{N}$.\end{definition}
+\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.
+Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.
+We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition}
 Even if there is only one transition from each state of a state graph, that is a linear state graph, our definition of trace is consistent with that.  \\
@@
 
-As mentioned in the previous paragraph, the internal wires The initial state in the original circuit must be assigned wire values that is consistent with semi-modularity.
-For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
+The initial wire values of a circuit is equally important.
+In the original circuit, all states of a trace are states in the underlying state graph.
+In particular the initial wire values corresponding to the initial state $s$ must also be a state in the underlying state graph.
+In addition, as mentioned in the previous paragraph, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.
+The fault tolerant circuit must be initialized in a similar way.
+We introduce one possible initialization for the fault tolerant circuit based on the initialization of the original circuit.
+This covers how to initialize both the duplicated copies as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
+%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
 The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s.
@@
 %should I delete intermediate?
-\begin{definition} A {\em valid initial state} for the A half of a duplicated circuit is defined as follows.
-Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the semi-modularity property.
-Assign the wire values within the logic block to corresponding wires in the half duplicated circuit.
-Then assign the value $w$ to corresponding wires in the half duplicated circuit so that $w=c1^A=c2^A=c3^A=w^A$.
-The same assignment of wire values can also be applied for the B half of a duplicated circuit.
+\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed as follows.
+Given any state in the original circuit state graph $s \in S$, assume that there exists initial wire values that correspond to $s$.
+In addition, for each wire $w$, the internal wire values within the logic block of $w$ are semi-modularity consistent.
+Construct the valid initial state by copying the internal wire values to corresponding internal wires in the A half circuit.
+Then assign the value $w$ to appropriate wires in the A half circuit such as $w=c1^A=c2^A=c3^A=w^A$.
+The same construction can be applied for the B half circuit as well.
 \end{definition}
 %\textbf{
-For all subsequent discussion in this document, when we talk about the trace of a duplicated circuit we assume that both sides start from the same valid initial state.
+For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.
 I will not include this assumption in the following lemma definitions to avoid complicated wording.
 %}
-However for Lemma 1 we only require one half to start from a valid initial state.  
-One additional assumption we make about the gates and wire values (including in the presence of faults) are that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the incoming wires.\\
+The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\
+
+One additional assumption that we make about the gates and wire values (including in the presence of faults) is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\
 
 \begin{lemma}[1]
-Let $\sigma_n$ be the sequence of the first n states of a trace $\sigma$ in the duplicated circuit (the trace is possibly finite).
-If a trace $\sigma$ starts from a valid initial state in the half circuit A, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit.
-By symmetry this is also satisfied for the half circuit B.
+If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
+The trace $\sigma$ can be finite or infinite in length.
+%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
+By symmetry this is also true for the B half if we exchange A and B in the statement above.
 
@@
 \begin{proof}
-Without loss of generality we prove that this property holds for the A half of the circuit, the same reasoning can then be applied to the B half of the circuit.
+Without loss of generality we prove that this property holds for the A half, the same reasoning can then be applied to the B half.
 We prove this lemma by induction on all traces of the circuit of length $n$.
-The induction hypothesis is
+The induction hypothesis is:
 \begin{itemize}
-\item For a length $n$ sequence $\sigma_n$ in the duplicated circuit, this maps to $h^{A}(\sigma_n)$, a prefix of a trace of the original circuit.
-\item Every logic block is in a Semi-Modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
-\item In every state $s_k$ of $\sigma_n$ it is true that a wire $w$ in the original circuit of state $h^A(s_k)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
+\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
+\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
+\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
 The case where two or more of the three conditions being true does not exist in this setting.
-As a consequence a wire $w$ is unexcited if and only if none of the previous three conditions are true.
+Also a wire $w$ is unexcited if and only if none of the four excited conditions are true.
 \\
@@
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show in the base case that the induction hypotheses holds for any valid initial state (ie. all possible traces of length 1). 
+We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
 \begin{itemize}
-\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit from its construction.
+\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.
 Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.
-\item We assigned the wire values so that the logic blocks are in a Semi-Modularity consistent state.  
-\item For any wire $w$, since the input wire values are identical in the original circuit and the duplicated half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit (the logic block output is excited).
-Together with the definition of the valid initial state $c1^A=c2^A=c3^A=w^A$ (no excitations within the C-element chain), if $w$ is excited in $h^A(s_k)$, then only $c1^A$ is excited.
-Conversely if $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$ then $w$ is excited in $h^A(s_k)$.
-All C-element chains in the duplicated have at most one wire in the chain excited.
-This shows the initial state also satisfies the last part of the induction hypothesis.
+\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
+\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.
+This case can also interpreted as the logic block being excited.
+Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.
+As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.
+By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.
+This shows the valid initial state also satisfies the last part of the induction hypothesis.
 %is this enough....
@@
 
-The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the sequence of the first $k$ states in a trace (for traces length greater than or equal to $k$).
+The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the subsequence for a trace $\sigma$ with length greater than or equal to $k$.
 We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
 In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.
-Then we show that for all possible $s_{k+1}$ logic block remains in a Semi-Modularity consistent state.
-Finally for all wires in $s_{k+1}$, the second induction hypothesis is true.\\
+Then we show that for all possible $s_{k+1}$ logic block remains in a semi-modularity consistent state.
+Finally for all wires in $s_{k+1}$, the third induction hypothesis is true.\\
 
@@
 If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.
-Thus we only need to consider the wires $w$ which are excited in the original circuit in $h^A(s_k)$ and its corresponding wires in the A-half $s_k$.
-For each excited wire $w$, the last induction hypothesis narrows the possible cases and we examine the next state if a transition occurs in each case.
+Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.
+For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur.
 %logic gate excited = c1^A excited
+%possibly add graph to illustrate this
 \begin{itemize}
 \item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
-Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, which satisfies the third induction hypothesis for wire $w$.
+Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.
 Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.
@@
 Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.
-The output wires which are also inputs to logic blocks did not change so the logic blocks are in a Semi-Modularity consistent state.
+The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.
 The induction hypotheses are true for any transition from this case.
@@
 \item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
-Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus the third induction hypothesis is true for wire $w$.
-This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.
+Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
+This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
 \item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.
 In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.
-Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus the third induction hypothesis is true for wire $w$.
-This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.
+Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
+This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
 
@@
 Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.
-Also since $h^A(s_{k+1})$ is a valid state in the original Semi-Modular circuit and the A-half logic blocks at state $s_k$ are Semi-Modularity consistent, inputs to all logic blocks in the A-half are also Semi-Modularity consistent.
+Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent.
 Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.
-(excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by Semi-Modularity)
+(excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)
 \begin{itemize}
 \item
-$w$ is unexcited in state $h^A(s_{k+1})$ (if we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.
-Since $w$ is now unexcited, wire $w$ does not contradict the third induction hypothesis.
+$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.
+Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.
 \item
-For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by Semi-Modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.
-Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, this does not contradict the third induction hypothesis.
+For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.
+Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.
 \item
-For all newly excited wires $u$ in $h^A(s_{k+1})$, that is not excited in $h^A(s_k)$, then in states $s_{k}$ and $s_{k+1}$,  $c1^A=c2^A=u^A$.
-But since $u$ is excited then $c1^A$ of $u$ is excited.
-Thus the third induction hypothesis holds for these wires $u$ as well.
+For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.
+But since $u$ is excited then $c1^A$ in the A half must be excited.
+Thus wires of this type satisfy the third induction hypothesis.
 \item
-Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, logic gate is not excited and $c1^A=c2^A=c3^A=u^A$ and the third induction hypothesis holds for these wires.
+Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.
+Thus wires of this type satisfy the third induction hypothesis.
 \end{itemize}
@@
 does not cause hazards in the C-element output).
-Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.
+Thus this Lemma is true regardless of whether there is a fault or not in the other half of the circuit.
 It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.
+%maybe move this to in front of L1
 Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.
@@
 \begin{lemma}[2.1]
-For all traces $\sigma$ in the duplicated circuit (for both halves starting in the same valid initial state), for any state in a trace, all wire blocks are in one of the cases in figure \ref{fig:l21}.
+For any state in a trace $\sigma$ of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
 \end{lemma}
 \begin{proof}
-We show by induction that for the duplicated circuit, each wire block will be in one of the cases in the above figure.
-The figure halves the number of cases, case 11 is the inversion of case 1 (the 0's and 1's inverted) and after case 11 the state transition goes through the second half of the cases with figure \ref{fig:l21} inverted.
+We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.
+The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.
 Thus we only need to analyze up to case 10.
-Because both halves satisfy the conditions of lemma 1, those properties can be applied directly.\\
+Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\
 

### 2019-04-07 draft_together3.tex
hereafter delete valid initial state from lemma defs

@@
 
-The internal wires in the logic blocks that are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.
+The internal wires in the logic blocks which are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.
 The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.
@@
 Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.
-Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following property is true:  if the inputs follow semi-modularity then there are no glitches at the output and that once the output is excited it remains excited until it transitions.
+Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions.
 \\%newly added
@@
 \begin{lemma}[1]
-If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
+If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then:
+\begin{itemize}
+\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
+\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
+\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
+And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
+\end{itemize}
+
 The trace $\sigma$ can be finite or infinite in length.  
@@
 \begin{lemma}[2.1]
-For any state in a trace $\sigma$ of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
+For any state in a trace of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
 \end{lemma}

### 2019-04-08 draft_together3.tex
edited til end.. need to motivate each lemma and possibly add new diagrams

@@
 \begin{lemma}[1]
-If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then:
+If $\sigma$ is the trace of the fault tolerant circuit, then in the A half:
 \begin{itemize}
@@
 %$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
-\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
+\item The second case is when the signal propagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
 Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
 This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
-\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.
+\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.
 In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.
@@
 
-\item The fourth case is when the signal propapagates down to $w^A$.
+\item The fourth case is when the signal propagates down to $w^A$.
 In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.
@@
 Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent.
-Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.
+Then we look at the third induction hypothesis by partitioning all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.
 (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)
@@
 \begin{lemma}[2.1]
-For any state in a trace of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
+For any state in a trace of the fault tolerant circuit, the wire blocks are in one of the cases in figure \ref{fig:l21}.
 \end{lemma}
 \begin{proof}
-We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.
-The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.
-Thus we only need to analyze up to case 10.
-Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\
+We show by induction that for the fault tolerant circuit, each wire block is in one of the cases in the above figure.
+The figure halves the number of cases, as case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transitions go through the same cases in figure \ref{fig:l21} from 1-11 but inverted.
+Thus we only need to analyze possible transitions from each case up to case 10.
+Also, Lemma 1 applies to both A half and B half.\\
 
@@
 If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).
-If $w$ is excited then applying lemma 1 the logic blocks must be excited which is case 2.
+If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.
 Thus this property is true for the base case.
@@
 
-In the induction step, assume that the induction hypothesis is true for state $s_k$ and show it is true for $s_{k+1}$.  \\
-
-We examine all possible $s_{k+1}$.
-That is for all possible transitions from $s_k$, verify that each $s_{k+1}$ has output wire blocks that is in one of the cases in the above figure.
-It is clear that the arrows point to next cases which can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires within the C-elements are self-contained.
+In the induction step, assume that the induction hypothesis is true for state $s_k$ and we show that it is true for $s_{k+1}$.  \\
+
+For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.
+It is clear that the arrows represent transitions and logic block changes that can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires in the C-element chains behave as the arrows indicate.
 Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
@@
 From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.
-However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to Semi-Modularity and lemma 1.
+However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
 \item
 Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).
-The logic block in A-half (B-half) cannot be excited again with $c1^A=1$ ($c1^B=1$) because that violates lemma 1.
+The logic block in A-half (B-half) cannot be excited again while $c1^A=1$ ($c1^B=1$) because that violates lemma 1.
 From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
-The excited logic blocks cannot become unexcited due to Semi-Modularity and lemma 1.
+The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.
 \item
 Case 4a/4b:
-The excited logic block in both cases can transition and end up in case 5.
-The excited logic block cannot become unexcited due to Semi-Modularity and lemma 1.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
+A logic block is excited in both cases and can transition to case 5.
+The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.
+The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).
 \item
@@
 Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
-\item
-Cases 9/10a/10b:  In cases 1-8a/8b all the transition happen on intermediate wires so the state of the other wire blocks must remain the same.
+The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).
+\item
+Cases 9/10a/10b:  In cases 1-8a/8b all transitions happen on intermediate wires so the state of the other wire blocks must remain the same.
 In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.
 In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.
-If any logic blocks are in case 9, its logic block cannot change excitations because it would violate lemma 1.
-Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than those included in the figure.
-We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its logic block to be excited.
+If any logic blocks are in case 9, its logic block cannot change excitations because it would violate Lemma 1.
+Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.
+The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.
+\\
+We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
 For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.
 This is shown by contradiction.
-\\
-Assume that there exists another logic block in case 10a and that $w^A$ transition causes an excitation in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
-All wire blocks are assumed to be in cases 1-10 in state $s_k$.
-If there is an output wire mismatch such that for all wire $u\in W$ where $u^A\neq u^B$ then $c2^A=c2^B$ since it must be in cases 10a or 10b.
-This is also true for those wires in state $s_{k+1}$ and the newly mismatched wire $w$.
-Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in state $s_{k+1+m}$ (other than the one of interest).
-In $s_{k+1+m}$ the excited logic block must still be excited due to semi-modularity.
-But also the logic block in the other half must be excited since all of the input wires are equal.
-This violates lemma 1 for that half and produces a contradiction.
+Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
+In state $s_k$ an output wire mismatch is possible only if it is in cases 10a or 10b.
+Thus for all wires $u$ where $u^A\neq u^B$, $c2^A=c2^B$ (which includes $v$).
+$w^A$ transitioning does that change the values of those wires so the property is true in state $s_{k+1}$ as well.
+It is also true of the newly mismatched wire $w$.
+In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
+Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in a later state (other than wire $v$).
+In that later state, the excited logic block of $v$ must still be excited due to semi-modularity.
+Since the input wires on both halves are equal, the logic block in the other half must be excited while its output wire is excited too.
+This violates Lemma 1 and produces a contradiction.
 Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
 From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
-Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires and causing a contradiction with lemma 1.
+Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.
 
@@
 This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
-By induction on the consecutive states of the trace, this shows that all wire blocks of a duplicated circuit are in a case in figure \ref{fig:l21} for all traces. \\
+By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit are in a case in figure \ref{fig:l21} for all traces. \\
 \end{proof}
@@
 which I think I need to show the signals propagating through??
+It is now easy to show that deadlock does not occur since each wire block must be in one of the configurations of figure \ref{fig:l21}.
 \begin{lemma}[2.2]
-For all traces $\sigma$ in the duplicated circuit (that start in the same valid initial state), deadlock does not occur.
+For all traces $\sigma$ in the fault tolerant circuit, deadlock does not occur.
 \end{lemma}
 \begin{proof}
-To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the duplicated circuit.
-$s_k$ can be split into two cases, one is that for every wire block $w$ all wires in the A half and B half are equal that is $w^A=w^B$, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.
+To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the fault tolerant circuit.
+The state $s_k$ can be split into two cases, one is that all output wire pairs in the A half and B half are equal, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.
 In the first case, if every output wire pair are equal, then $h^A(s_n)=h^B(s_n)$ and there exists an excited wire $u$ in the original circuit.
-By lemma 1 both halves of the duplicated circuit for $u$ is excited.
-By the lemma 2.1, the circuit must be in case 2-6 for $u$.
+By Lemma 1 both halves of the duplicated circuit for $u$ is excited.
+By Lemma 2.1, the circuit must be in case 2-6 for $u$.
 In each of these cases at least one wire is excited.
 \\
-In the second case, for some wire $v$ such that $v^A\neq v^B$, then using lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.
+In the second case, for some wire $v$ such that $v^A\neq v^B$, then using Lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.
 Since there are next transitions for both cases, deadlock does not occur.
@@
 
-Combining the results of the previous lemmas yield the following result:
+Combining the results of the previous Lemmas yield the following result:
 \begin{theorem}[1]
-For all traces $\sigma$ in the duplicated circuit starting from valid initial states, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the fault tolerant circuit, where $\sigma_n$ is the sequence of the first $n$ states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
@@
 %fix this
-\begin{definition}A transient fault on a wire $x$ can happen so that from the start of the transient fault $x= \lnot x^{init}$.
-At some time later, the wire is able to transition again based on its inputs.
+\begin{definition}A transient fault on a wire $w$ causes a transition $w= \lnot w^{prev}$.
+After this event it is assumed that the wire can freely transition based on its inputs.
 %do I need to talk about when transient is not ~x?
@@
 \end{definition}
-Next we will show that adding a single transient fault to any wire will still allow one of the half circuits to progress as normal.
-Since the 'good' half will always progress according to the original state graph if a transition is available, we just need to prove that it never deadlocks.
-To do this we prove some properties that are true when we add a single transient fault.
-We split the wires into two sets based on their properties when a single transient fault is added.
-Lemma 3.1 shows that if a single fault is added to $c1$, $c2$ or $c3$ wires of the wire block for some wire $w$, the output wires still follow the original state graph.
-Lemma 4 shows that if an fault is added to any of the other wires, then the $c1$, $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
+Next we will show that if a single transient fault occurs on any wire, the half circuit that does not contain the fault will still transition normally.
+Applying Lemma 1, we know that the 'good' half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.
+To do this we prove some properties that are true when a single transient fault occurs on a wire.
+We partition the wires into two sets based on their properties when a single transient fault is added.
+Lemma 3.1 shows that if a single fault occurs on the $c2$ or $c3$ wires for some wire $w$, the output wires still follow the original state graph.
+Lemma 4 shows that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
 Then we combine these lemmas to show that this implies that there is no deadlock.
@@
 Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.
-We use NuSMV to verify that adding a transient fault to one of the $c2$ or $c3$ wires do not change the input-output characteristic of the local circuit.
-Under normal operation, by lemma 2.1 the pair of inputs and outputs cycle through 00 00 00$\rightarrow$ 01 00 00 or 10 00 00 $\rightarrow$ 11 00 00 $\rightarrow$ 11 01 00 or 11 10 00 $\rightarrow$ 11 11 00 or 11 11 00 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.
-Thus the property verified in NuSMV is that when a single transient fault can happen spontaneously on wires $c2$ or $c3$, the cycle mentioned previously is always true.
+We use NuSMV to verify that if a transient fault occurs on one of the $c2$ or $c3$ wires of wire $w$, the input-output characteristic of the local C-element chain do not change.
+Under normal operation, by Lemma 2.1 the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through 00 00 $\rightarrow$ 01 00 or 10 00 $\rightarrow$ 11 00 $\rightarrow$ 11 01 or 11 10 $\rightarrow$ 11 11 or 11 11 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.
+Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2$ or $c3$, the cycle mentioned previously is always true.
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.
-We go through an example of a transient on $c3^A$ to demonstrate why this happens.
-By lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.
+We go through an example of a transient on $c3^A$ to demonstrate why this is true.
+By Lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.
 \begin{itemize}
@@
 \begin{lemma}[4]
-For all traces $\sigma$ in the duplicated circuit, that allows adding a fault to any wire other than $c2$ or $c3$ at some time step $n$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ is always in a state of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the fault tolerant circuit, where a fault occurs on a wire other than $c2$ or $c3$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ are always in a state of Figure \ref{fig:l4}.
 \end{lemma}
@@
 
-The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
+The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from Lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
 
@@
 We don't assume anything about the non $c2$ and $c3$ wires for the A-half so that $c1^A$ may change values due to a fault.
-However we do expect $c1^A$ to be either a 1 or 0 and that even with hazards on $c1^A$, $c2$ transitions to either 0 or 1.
+However we do expect $c1^A$ to be either a 1 or 0 and that even with hazards on $c1^A$, $c2$ wires transition to either 0 or 1.
 We indicate the possibly faulty $c1^A$ by the symbol X.
@@
 \begin{theorem}[2]
-With the addition of a single transient fault, and for all $n \in \mathbb{N}$, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then one of $h^{A,B}(\sigma_n)$ (the non faulty half) is a prefix of a trace in the original circuit.
+When a single transient fault occurs, and for all $n \in \mathbb{N}$, if $\sigma$ is a trace in the fault tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) is a prefix of a trace in the original circuit.
 And the circuit does not deadlock.
@@
 To remain deadlocked, it must be true that there exists a wire where $w^A\neq w^B$, which implies its $c1^A\neq c1^B$ and $c2^A\neq c2^B$ and $c3^A\neq c3^B$.
-But we have shown in lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault.
+But we have shown in Lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault.
 Thus deadlock is not possible.
-And applying lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit.
+And applying Lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit.
 \end{proof}

### 2019-04-09 draft_together3.tex
finished current edit of proofs/ added in descriptions of each L and T in its beginning

@@
 \chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
-\section{Normal operation analysis}
-As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
-We want to define a trace, to describe the different paths a circuit can take as it follows the state graph.
-Different paths can occur because there are states with multiple transitions from that state.
+\section{Traces and circuit equivalence}
+We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
+Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.
+To solve this problem we add C-elements to synchronize the two versions of the same signal.
+In the rest of this chapter we define a way to compare two circuits and to show their equivalence.
+Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.
+Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
+
+Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
+We first define a trace, to describe the different paths a circuit can take as it follows the state graph.
+Different paths can occur because each state may have multiple transitions from that state.
 We record the succession of states and transitions by the trace which is defined as follows:
@@
 We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition}
-Even if there is only one transition from each state of a state graph, that is a linear state graph, our definition of trace is consistent with that.  \\
+Our definition of trace includes the case where there is only one transition from each state of a state graph, that is a linear state graph.  \\
 %add finite traces
 % all states or just the state graph ones
-
-[If the set of traces are equal then the state graph is equal]
 
@@
 Thus we define circuits as equivalent if the set of traces of the two circuits are the same.
+[We use the assumption that if the set of traces are equal then the state graph is equal.]
 \begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B (up to a permutation of the variable names).
@@
 If inputs to the gate remain constant, the output $v$ will eventually take the value specified by $f_v(s|_I)$  %maybe change v again, also the f(s) vs f(I) thing...
+\section{Fault Tolerant transformation}
 
@@
 
-To prove claims about the fault tolerance of this circuit, we must first prove that the circuit behaves similar to the original circuit under normal operation.
+\section{Normal operation analysis}
+To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similar to the original circuit under normal operation.
 That is, after applying a mapping of $h^A$, the set of traces of the resultant circuit and that of the original circuit are equal.
 And likewise after applying a mapping of $h^B$.
-We prove Lemma 1 which shows for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs in the original circuit.
-This property is independent of the signals on the other half circuit and is useful later in proving fault tolerance under a single transient fault.
+This goal is achieved by proving several Lemmas.
+Lemma 1 shows for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs of the original circuit.
+This property is independent of the signals on the other half circuit which is significant later in proving fault tolerance under a single transient fault as the half without the fault will transition as normal by Lemma 1.
 %as long as it does not violate digital abstraction
-However Lemma 1 does not guarantee that such a transition always exists so Lemma 2 is needed to show that a transition always exists and as a consequence the circuit cannot deadlock.
+One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\
+
+Note that Lemma 1 does not guarantee that a transition always exists from a given state so Lemma 2 is needed to show that a transition always exists and as a consequence the circuit cannot deadlock.
 These two Lemmas combine together to show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\% and all traces in the original can be mapped to duplicated after h mapping?
@@
 
-One additional assumption that we make about the gates and wire values (including in the presence of faults) is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\
+This leads to Lemma 1, with the description and proof as follows:
 
@@
 
-Note that the previous proof does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g.
+Note as described previously that the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g.
 does not cause hazards in the C-element output).
 Thus this Lemma is true regardless of whether there is a fault or not in the other half of the circuit.
-It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.
-%maybe move this to in front of L1
-Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.
+It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1
+
+This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transitions in a completely predictable pattern and thus deadlock does not occur.
 
@@
 
-Combining the results of the previous Lemmas yield the following result:
+Combining the results of the previous Lemmas shows that the fault tolerant circuit is equivalent to the original circuit under normal operation.  This is defined formally in a theorem as follows:
 \begin{theorem}[1]
-For all traces $\sigma$ in the fault tolerant circuit, where $\sigma_n$ is the sequence of the first $n$ states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the fault tolerant circuit, $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
 \end{theorem}
-
+\begin{proof}
+Apply Lemma 1 then $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace.  From Lemma 2.2, no deadlock occurs so it is true for all $n\in \mathbb{N}$.
+\end{proof}
 %with these 3 properties show the original claim
@@
 %fix this
+Next we consider what happens to the fault tolerant circuit under a single transient fault which is defined as follows:
 \begin{definition}A transient fault on a wire $w$ causes a transition $w= \lnot w^{prev}$.
@@
 \end{definition}
-Next we will show that if a single transient fault occurs on any wire, the half circuit that does not contain the fault will still transition normally.
-Applying Lemma 1, we know that the 'good' half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.
+Next we will show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit.
+Applying Lemma 1, we know that the fault free half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.
 To do this we prove some properties that are true when a single transient fault occurs on a wire.
 We partition the wires into two sets based on their properties when a single transient fault is added.
-Lemma 3.1 shows that if a single fault occurs on the $c2$ or $c3$ wires for some wire $w$, the output wires still follow the original state graph.
+Lemma 3 shows that if a single fault occurs on the $c2$ or $c3$ wires for some wire $w$, the output wires still follow the original state graph.
 Lemma 4 shows that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
-Then we combine these lemmas to show that this implies that there is no deadlock.
+Then we combine these Lemmas to show that there is no deadlock.
 \begin{lemma}[3]
@@
 \end{figure}
+Next we show that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions in a completely predictable pattern analogous to Lemma 2.1.
+The main difference is that because a fault may be present we cannot fully predict the value of one of $c1^A$ or $c1^B$.
+The following property is true despite not knowing one of the $c1$ wire values and leads to the conclusion that the output wire pairs can never be different at deadlock.
 
@@
 \end{proof}
-The importance of this property is that at most one of $c2$ or $c3$ pairs can be mismatched.  And thus all output pairs at deadlock must be equal.
+The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
+The next theorem shows that this implies all output pairs at deadlock must be equal so there is a possible next condition which contradicts the definition of deadlock.
+Thus the fault tolerant circuit does not deadlock under a single transient fault.
+
+%Then the following corollary holds:
+%\begin{corollary}[4.2]
+%All output pairs at deadlock must be equal
+%\end{corollary}
 
 \begin{theorem}[2]
-When a single transient fault occurs, and for all $n \in \mathbb{N}$, if $\sigma$ is a trace in the fault tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) is a prefix of a trace in the original circuit.
+When a single transient fault occurs, if $\sigma$ is a trace in the fault tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) for all $n \in \mathbb{N}$ is a prefix of a trace in the original circuit.
 And the circuit does not deadlock.
@@
 Without loss of generality we can assume the fault occurs in the A half of the circuit.
-First by lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.
+First by Lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.
 Thus we only look at when the fault occurs on all other wires.
@@
 There
- must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in lemma 4.
+ must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in Lemma 4.
 \begin{itemize}
 	\item
-	Case 1: Since $w$ is excited then by lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
+	Case 1: Since $w$ is excited then by Lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
 \item

### 2019-04-12 draft_together3.tex
before major DD change from 4/10

@@
 Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
-We first define a trace, to describe the different paths a circuit can take as it follows the state graph.
-Different paths can occur because each state may have multiple transitions from that state.
+We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.
+Different paths can occur because each state may have multiple alternative transitions from that state.
 We record the succession of states and transitions by the trace which is defined as follows:
-\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.
-Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.
-We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition}
-Our definition of trace includes the case where there is only one transition from each state of a state graph, that is a linear state graph.  \\
+\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.
+Formally this is written as $\sigma: 0\ldots n-1 \to S$ and $n \in \mathbb{N}$.
+ Also every pair of consecutive states are transitions such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$.
+We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition}
+Thus a circuit as well as its underlying state graph corresponds to a set of traces.  
+set of initial states
+and state graph has a set of traces
+Our definition of trace includes the case where there is only one transition from each state of a state graph, that is, a linear state graph.  \\
 %add finite traces
@@
 Without loss of generality we prove that this property holds for the A half, the same reasoning can then be applied to the B half.
-We prove this lemma by induction on all traces of the circuit of length $n$.
+We prove this Lemma by induction on all traces of the circuit of length $n$.
 The induction hypothesis is:
@@
 For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur.
+Refer to figure \ref{fig:l1helper} for an example of what happens in each of the cases.
+These are drawn for when $w$ transitions from $0\rightarrow1$ but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting 1's and 0's.
 %logic gate excited = c1^A excited
 %possibly add graph to illustrate this
+\begin{figure}
+  \centering
+    \includegraphics[width=\textwidth]{gatewl1}
+  \caption{Different cases of the induction step for proving Lemma 1.  a) case 1, b) case 2, c) case 3, d) case 4}
+  \label{fig:l1helper}
+\end{figure}
+
 \begin{itemize}
@@
 A wire $w$ can be either excited or unexcited in the original circuit.
-If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).
+If the wire $w$ is unexcited, applying Lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).
 If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.
@@
 Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).
-The logic block in A-half (B-half) cannot be excited again while $c1^A=1$ ($c1^B=1$) because that violates lemma 1.
+The logic block in A-half (B-half) cannot be excited again while $c1^A=1$ ($c1^B=1$) because that violates Lemma 1.
 From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
@@
 We use NuSMV to verify that if a transient fault occurs on one of the $c2$ or $c3$ wires of wire $w$, the input-output characteristic of the local C-element chain do not change.
-Under normal operation, by Lemma 2.1 the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through 00 00 $\rightarrow$ 01 00 or 10 00 $\rightarrow$ 11 00 $\rightarrow$ 11 01 or 11 10 $\rightarrow$ 11 11 or 11 11 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.
+Under normal operation, by Lemma 2.1 the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through the wire values shown in figure \ref{fig:l3helper}.
 Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2$ or $c3$, the cycle mentioned previously is always true.
+\begin{figure}
+  \centering
+    \includegraphics{L3helperfull}
+  \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
+This forms the input and output characteristic of a wire block under normal operation.}
+  \label{fig:l3helper}
+\end{figure}
+
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
@@
 $c3^A$ will be excited but there are no other excitations in the local circuit.
-Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited or transition on any subsequent states while $w^A$ and $w^B$ do not change (same argument as in lemma 2.1 can be used since the other wire blocks do not have transients and thus in one of the states in cases 2.1).
+Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited or transition on any subsequent states while $w^A$ and $w^B$ do not change (same argument as in Lemma 2.1 can be used since the other wire blocks do not have transients and thus in one of the states in cases 2.1).
 Then the local circuit will stay in this transient induced state until $c3^A$ finally changes and the circuit returns to its state before the transient.

### 2019-04-15 draft_together3.tex
after major DD change added two sections

@@
 \chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
+\chaptermark{Fault Tolerant Circuit}
 \section{Traces and circuit equivalence}
 We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
-Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.
+Due to the asynchronous nature of how signals are processed, each resulting half circuits may have signals of corresponding wires at different values.
 To solve this problem we add C-elements to synchronize the two versions of the same signal.
+An example of this transformation applied to the simple inverter circuit is shown in figure \ref{fig:dupschemeex}.
+Both the duplication and the additional C-elements configuration are shown.
 In the rest of this chapter we define a way to compare two circuits and to show their equivalence.
@@
 Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
-
-Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
+\begin{figure}
+  \centering
+    \includegraphics[width=.9\textwidth]{transf3Csimp}
+  \caption{a) original circuit b) after the fault tolerant transformation}
+  \label{fig:dupschemeex}
+\end{figure}
+
+Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially to evaluate whether they implement the same state graph.  
 We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.
@@
 \begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.
-Formally this is written as $\sigma: 0\ldots n-1 \to S$ and $n \in \mathbb{N}$.
+Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
  Also every pair of consecutive states are transitions such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$.
 We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition}
-Thus a circuit as well as its underlying state graph corresponds to a set of traces.  
-set of initial states
-and state graph has a set of traces
-Our definition of trace includes the case where there is only one transition from each state of a state graph, that is, a linear state graph.  \\
-%add finite traces
-% all states or just the state graph ones
-
-Given two circuits, how can we determine when their basic functionality is the same even if they are implemented with different gates and circuit elements?
-We define a notion of equivalence between two circuits.
-We want the underlying state graph representation of the circuits to be equivalent.
-However only the signals and the sequence of its transitions from the circuit is observable.
+Thus a circuit has a set of traces.  
+For a given circuit there is also a set of initial states from the set of traces which corresponds to the states in the state graph.
+In other words, for all $s_0$, the first state of a trace of the circuit, $s\in S$.
+\\
+
+%Note that our definition of trace also includes the case where there is only one transition from each state of a state graph, which results in a linear state graph.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=.6\textwidth]{sm_counter2}
+  \caption{a) original circuit for wire w b) an erroneous initialization}
+  \label{fig:sm_counter2}
+\end{figure}
+
+The original circuit is semi-modular by design.
+But the design only covers cases where the wires are in a state in the state graph.
+That is, hazards may occur if the state of the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.
+This will not happen in the fault-free case if the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
+However it is a possibility when faults do occur and a reason why we need to transform the circuit to protect against faults.
+An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
+The circuit for wire $w$ is taken out of a semi-modular circuit.
+However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not a semi-modularity consistent initialization.
+The output wire $w$ is excited to 1 while the inputs from $x,y,z$ will cause $w$ to transition to 0.
+Depending on the timing of the gates, $w$ may stay at 0 or experience a glitch to 1 then back to 0.
+The extra layers of gates in the logic block can be thought of as extra delays that can store and propagate the wrong values.
+More detailed discussion of how to initialize the circuit will be explored after we define the fault tolerant transformation.\\
+
+Given two circuits, how can we determine when their basic functionality is the same, especially if they are implemented with different gates and circuit elements?
+We define a notion of equivalence between two circuits through their sets of traces.
+%We want the underlying state graph representation of the circuits to be equivalent.
+However only the signals and the sequence of transitions from the circuit is observable.
 In other words the trace is observable.
@@
 [We use the assumption that if the set of traces are equal then the state graph is equal.]
-\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B (up to a permutation of the variable names).
-In other words, if it is possible to pair wires in A and B in such a way that $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
+\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B.
+In other words, $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
 \end{definition}
+
+We are now ready to explore how to make a circuit fault-tolerant.
 %good enough for now, do I need if and only if? <-NO, xxx if xxx in math lingo is iff
@@
 
-We make a circuit fault tolerant by the following transformation on an existing semi-modular circuit: make a duplicate copy of the logic blocks of each wire $w$.
-We label the duplicated logic blocks as belonging to circuit A or circuit B.
+We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
+We also label the duplicated logic blocks as belonging to circuit A or circuit B.
 Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.
-We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ and $c1^B$, $c2^B$, $c3^B$ for circuits A and B respectively.
-In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements outputting $c2^A$ and $c2^B$.
+We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ for circuit A and $c1^B$, $c2^B$, $c3^B$ for circuit B.
+In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and inputs to two C-elements outputting $c2^A$ and $c2^B$.
 These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.
@@
     \includegraphics[width=\textwidth]{circuitforproof3}
-  \caption{Duplicating the original logic for each output wire and adding 3 layers of C-elements}
+  \caption{Fault tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
   \label{fig:dupscheme}
@@
 
-Because the circuit transformation introduces extra wires, we want to define a correspondence to compare states of the original circuit with those of the A-half and B-half of the fault tolerant circuit.
-A state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
+We want to show that a half circuit of the fault tolerant circuit is functioning correctly.
+To do this, we define a correspondence between states of the original circuit and states of the fault tolerant circuit.
+As a result of the circuit transformation, a state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
 Half of those bits are obviously from the A half of the circuit and half are from the B half.
@@
 The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.
-The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are ignored.
-We extend $h^A$ pointwise to traces, in other words, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.
+The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are hidden by $h^A$ or $h^B$.
+We extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.
 %not sure if I want the mapping to be from variable to variable or specific state to state
 %For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
-The resulting trace may have successive repeated states and we delete the neighboring repeats to obtain a valid trace on the shortened list of wires.
-%do I need to define all the new transitions in duplicated circuit?
-maybe
-\\
+The resulting trace may have successive repeated states.
+So we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.
+The result should be a trace from the original circuit.
+ Using this mapping we will show that the original circuit is equivalent to half of the fault tolerant circuit in both the absence and presence of a single transient fault.
+%do I need to define all the new transitions in duplicated circuit?  maybe
+\\
+
+%[Why is this the best we can do?]
+We compare to each half circuit because it is not easy to synchronize and compare the signals between the two halves, especially if we reuse the logic blocks from the original circuit.
+A simple idea we tried was to insert another C-element before the input is fed into the logic, to synchronize the wires on both halves.
+The problem with that is in the original circuit, a wire value change propagates to all inputs at the same time.
+Adding another layer of C-elements create varying delays at the input to logic blocks and the isochronic fork assumption is violated.
+Thus the resulting circuit will not function according to the specified state graph.
+(an example can be provided but not sure if needed?)\\
+\begin{figure}
+  \centering
+    \includegraphics[width=.8\textwidth]{counterexhalf}
+  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault tolerant circuit}
+  \label{fig:counterexhalf}
+\end{figure}
+
+Next we look at the traces of each half circuit.
+Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where the states are given nominal names (state 0, state 1, ...
+etc) and each transition is labeled with the transitioning wire.
+Suppose we apply our fault tolerant transformation to such a circuit based on this state graph.
+Both halves will transition based on this state graph, with the added caveat that for a wire to transition in any one half, it must be excited in both halves at the current state.
+Starting in {\em state 0} it is possible in the A-half for $a^A$ to transition to {\em state 1} and in the B-half for $c^B$ to transition to {\em state 2}.
+We assume that $a^B$ and $c^A$ do not complete their transitions yet.
+Immediately, in the A-half $b^A$ is excited and in the B-half $b^B$ is excited.
+Then, suppose the transition on wire $b^A$ and $b^B$ occurs.
+That is, the A-half transitions to {\em state 3} and the B-half transitions to {\em state 5}.
+And finally, the excited $a^B$ and $c^A$ transitions so that both halves are in {\em state 6}.
+The trace so far for the A-half is (state 0, state 1, state 3, state 6) while for the B-half it is (state 0, state 2, state 5, state 6).
+Thus the two halves need not have the same trace.
+The current fault tolerant transformation synchronizes the outputs of the logic blocks with C-elements.
+If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
+This points to looking at properties of each half circuit as the right thing to do.\\
+
+Another problem that the fault tolerant transformation cannot resolve is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.
+We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.
+Following the same transitions outlined above, $b^A$ and $b^B$ can finish its transition before $a^B$ and $c^A$ transitions.
+Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined state no longer maps back to a valid state in the original state graph.
+Another approach we may take is to record the first transition of a wire in either half of the fault tolerant circuit.
+For example if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.
+This approach ensures the resulting trace is a trace in the original circuit (can be shown by Lemma 1 and Lemma 2.1 in the next section) however, in the presence of faults, it is easy to see that it does not provide any fault tolerance.\\
+
+For the aforementioned reasons, we choose to use the $h^A$ and $h^B$ mappings and compare each half circuit against the original circuit.
+Out of the various comparisons methods and circuit transformations that we tried, it is the most reasonable and results in some nice properties.
+We will next demonstrate that the half circuits are equivalent to the original circuit in the absence of faults.
+Then we show that a similar property is true even when a single fault may occur.
 
 \section{Normal operation analysis}
-To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similar to the original circuit under normal operation.
-That is, after applying a mapping of $h^A$, the set of traces of the resultant circuit and that of the original circuit are equal.
-And likewise after applying a mapping of $h^B$.
-This goal is achieved by proving several Lemmas.
-Lemma 1 shows for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs of the original circuit.
-This property is independent of the signals on the other half circuit which is significant later in proving fault tolerance under a single transient fault as the half without the fault will transition as normal by Lemma 1.
-%as long as it does not violate digital abstraction
-One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\
-
-Note that Lemma 1 does not guarantee that a transition always exists from a given state so Lemma 2 is needed to show that a transition always exists and as a consequence the circuit cannot deadlock.
-These two Lemmas combine together to show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\% and all traces in the original can be mapped to duplicated after h mapping?
-<-this is obvious though by setting the A half and B half to both transition according to original trace
-
-The internal wires in the logic blocks which are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.
-The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.
+To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.
+That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
+And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.
+We show this through several Lemmas.
+Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.
+This is a strong result; it is true for arbitrary behavior of
+signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
+This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
+%One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
+\\
+
+Note that Lemma 1 allows for the possiblity of deadlock.
+Lemma 2 shows deadlock does not occur during normal operation.
+Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
+% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
+%[so no deadlock in normal operation??]
+
+Now we will discuss the proper wire initializations before going into the Lemmas.
+In normal operation, the fault tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.
+This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault tolerant circuit.
 The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.
@@
 
-The initial wire values of a circuit is equally important.
-In the original circuit, all states of a trace are states in the underlying state graph.
-In particular the initial wire values corresponding to the initial state $s$ must also be a state in the underlying state graph.
-In addition, as mentioned in the previous paragraph, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.
-The fault tolerant circuit must be initialized in a similar way.
-We introduce one possible initialization for the fault tolerant circuit based on the initialization of the original circuit.
-This covers how to initialize both the duplicated copies as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
+What values to initialize the wires of a circuit to is very important.
+We want certain properties to hold for all states that the circuit goes through, and such properties must also hold for the initial state.
+On one hand, the initial state $s$ must be a state in the underlying state graph.
+Thus the wire values is initialized to be consistent with that property.
+On the other hand, as mentioned previously, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.
+We assume that we can initialize the wire values of the original circuit to satisfy these two properties.
+Given this, we pick convenient initializations for the fault tolerant circuit.
+The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
 %For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
@@
 %\textbf{
-For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.
+This is one out of many possible initializations that can fit the behavior we want.
+Thus this definition is stronger than it needs to be but is used for the sake of conveniece.
+In Lemma 1, we will show why this definition allows for the behavior that we want in the fault tolerant circuit.\\
+
+To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
+One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.\\
+%For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.
 I will not include this assumption in the following lemma definitions to avoid complicated wording.
 %}
-The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\
-
-This leads to Lemma 1, with the description and proof as follows:
+%The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\
+
+This leads to the definition and proof of Lemma 1 as follows:
 
 \begin{lemma}[1]
-If $\sigma$ is the trace of the fault tolerant circuit, then in the A half:
+If $\sigma$ is the trace of the fault tolerant circuit and the A half is fault free, then in the A half:
 \begin{itemize}
@@
 \item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
-\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
-And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
+\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ in the fault tolerant circuit.
+(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
 \end{itemize}
 
-The trace $\sigma$ can be finite or infinite in length.  
 %Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
@@
 \end{lemma}
+The trace $\sigma$ can be finite or infinite in length in accordance with the definition of a trace. 
 \begin{proof}
-Without loss of generality we prove that this property holds for the A half, the same reasoning can then be applied to the B half.
-We prove this Lemma by induction on all traces of the circuit of length $n$.
-The induction hypothesis is:
+We prove this Lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
 \begin{itemize}
@@
 \begin{itemize}
-\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
+\item The first case is for an excited wire $w$.
+The corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
 Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.

### 2019-04-15 draft_together3.tex
Updates from Overleaf

--- 2019-04-09 draft_together3.tex
@@
 \section{Traces and circuit equivalence}
-We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
+We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
 Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.
@@
 Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.
-Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
-
-Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
+Finally we show that if a single transient fault occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
+
+Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially to evaluate whether they implement the same state graph.  
 We first define a trace, to describe the different paths a circuit can take as it follows the state graph.
-Different paths can occur because each state may have multiple transitions from that state.
-We record the succession of states and transitions by the trace which is defined as follows:
+Different paths can occur because there may be multiple transitions from each state.
+We call the succession of states and transitions the trace which is defined as follows:
 \begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.
 Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.
-We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition}
+We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition}
 Our definition of trace includes the case where there is only one transition from each state of a state graph, that is a linear state graph.  \\

### 2019-04-15 draft_together3.tex
edited new sections again

--- 2019-04-15 draft_together3.tex
@@
 \section{Traces and circuit equivalence}
-We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
-Due to the asynchronous nature of how signals are processed, each resulting half circuits may have signals of corresponding wires at different values.
+We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
+Due to the asynchronous nature of how signals are processed, corresponding wires in the resulting half circuits may have different values.
 To solve this problem we add C-elements to synchronize the two versions of the same signal.
@@
 Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.
-Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
+Finally we show that if a single transient fault occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
 \begin{figure}
@@
 
-Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially to evaluate whether they implement the same state graph.  
+Other than the basic terminology for asynchronous circuits, we also want terminology to compare two circuits based on their function.  
 We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.
-Different paths can occur because each state may have multiple alternative transitions from that state.
-We record the succession of states and transitions by the trace which is defined as follows:
+Different paths can occur because there may be multiple transitions from each state.
+We call the succession of states and transitions the trace which is defined as follows:
 \begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.
-Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
- Also every pair of consecutive states are transitions such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$.
-We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition}
+%Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
+ Also every pair of consecutive states in a trace are transitions% such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$
+ .  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
 Thus a circuit has a set of traces.  
-For a given circuit there is also a set of initial states from the set of traces which corresponds to the states in the state graph.
-In other words, for all $s_0$, the first state of a trace of the circuit, $s\in S$.
-\\
+A circuit also has a set of initial states where the traces can begin in.  The set of initial states are the same as the set of states in the state graph.\\
 
@@
 But the design only covers cases where the wires are in a state in the state graph.
-That is, hazards may occur if the state of the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.
-This will not happen in the fault-free case if the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
-However it is a possibility when faults do occur and a reason why we need to transform the circuit to protect against faults.
+That is, hazards may occur if the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.
+This does not happen in the fault-free case where the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
+However when faults do occur, the circuit may become unpredictable and a reason why we need to transform the circuit to protect against faults.
 An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
-The circuit for wire $w$ is taken out of a semi-modular circuit.
-However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not a semi-modularity consistent initialization.
+The logic circuit for wire $w$ is taken out of a semi-modular circuit.
+However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not semi-modularity consistent.
 The output wire $w$ is excited to 1 while the inputs from $x,y,z$ will cause $w$ to transition to 0.
@@
 The extra layers of gates in the logic block can be thought of as extra delays that can store and propagate the wrong values.
-More detailed discussion of how to initialize the circuit will be explored after we define the fault tolerant transformation.\\
+More detailed discussion on how to initialize and keep the circuit semi-modular is explored in the subsequent section.\\
 
@@
 
-We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
-We also label the duplicated logic blocks as belonging to circuit A or circuit B.
+We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in figure \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
+We also label the duplicated logic blocks as belonging to circuit A or circuit B in agreement to the wire naming.
 Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.
@@
 These then connect to other logic blocks in circuit A and circuit B respectively.
-Note that at some steps of the labelling which side is A and B can be somewhat arbitrary because the outputs of pairs of C-elements with the same inputs are symmetric.
-The symmetry is broken by connecting the final output $w^A$ to all its circuit A gate inputs and $w^B$ to all its circuit B gate inputs.
+Note that when labelling the C-elements and its outputs, which side is A and B can be somewhat arbitrary because the output pairs are symmetric.
+The symmetry is broken when connecting the final output wire $w^A$ to all the circuit A gate inputs and wire $w^B$ to all the circuit B gate inputs.
 All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
@@
 
-We want to show that a half circuit of the fault tolerant circuit is functioning correctly.
+We want to show that a half circuit from the fault tolerant circuit has correct function.
 To do this, we define a correspondence between states of the original circuit and states of the fault tolerant circuit.
 As a result of the circuit transformation, a state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
-Half of those bits are obviously from the A half of the circuit and half are from the B half.
+Half of those bits are obviously from the A half and half are from the B half of the circuit.
 The state graph for a fault tolerant circuit is defined on this combined state.
@@
 %[Why is this the best we can do?]
-We compare to each half circuit because it is not easy to synchronize and compare the signals between the two halves, especially if we reuse the logic blocks from the original circuit.
+We compare each half circuit because it is not easy to synchronize and compare the signals between both halves, especially if we reuse the logic blocks from the original circuit.
 A simple idea we tried was to insert another C-element before the input is fed into the logic, to synchronize the wires on both halves.
 The problem with that is in the original circuit, a wire value change propagates to all inputs at the same time.
-Adding another layer of C-elements create varying delays at the input to logic blocks and the isochronic fork assumption is violated.
+Adding another layer of C-elements creates delays at the input to logic blocks and the isochronic fork assumption is violated.
 Thus the resulting circuit will not function according to the specified state graph.
@@
 Next we look at the traces of each half circuit.
-Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where the states are given nominal names (state 0, state 1, ...
+Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where each state is given a nominal name (state 0, state 1, ...
 etc) and each transition is labeled with the transitioning wire.
 Suppose we apply our fault tolerant transformation to such a circuit based on this state graph.
-Both halves will transition based on this state graph, with the added caveat that for a wire to transition in any one half, it must be excited in both halves at the current state.
-Starting in {\em state 0} it is possible in the A-half for $a^A$ to transition to {\em state 1} and in the B-half for $c^B$ to transition to {\em state 2}.
+Both halves in the fault tolerant circuit will transition based on this state graph, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
+Starting in {\em state 0}, it is possible for the A-half to transition to {\em state 1} ($a^A$ transitions) and for the B-half to transition to {\em state 2} ($c^A$ transitions).
 We assume that $a^B$ and $c^A$ do not complete their transitions yet.
-Immediately, in the A-half $b^A$ is excited and in the B-half $b^B$ is excited.
+Immediately, in the A-half, $b^A$ is excited and in the B-half, $b^B$ is excited.
 Then, suppose the transition on wire $b^A$ and $b^B$ occurs.
@@
 Thus the two halves need not have the same trace.
-The current fault tolerant transformation synchronizes the outputs of the logic blocks with C-elements.
+One criticism may be that the current fault tolerant transformation synchronizes at the outputs of the logic blocks.
 If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
+We have already shown earlier that synchronizing the input signals while keeping the original logic block also can result in error.
 This points to looking at properties of each half circuit as the right thing to do.\\
@@
 We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.
-Following the same transitions outlined above, $b^A$ and $b^B$ can finish its transition before $a^B$ and $c^A$ transitions.
-Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined state no longer maps back to a valid state in the original state graph.
+Following the same transitions outlined above, $b^A$ and $b^B$ can finish their transitions before $a^B$ and $c^A$ transitions.
+Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined trace no longer maps back to a valid trace in the original state graph.
 Another approach we may take is to record the first transition of a wire in either half of the fault tolerant circuit.
-For example if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.
-This approach ensures the resulting trace is a trace in the original circuit (can be shown by Lemma 1 and Lemma 2.1 in the next section) however, in the presence of faults, it is easy to see that it does not provide any fault tolerance.\\
+For example, if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.
+This approach ensures the resulting trace is a trace in the original circuit (can be shown by Lemma 1 and Lemma 2.1 in the next section), however, in the presence of faults, it is easy to see that it does not provide any fault tolerance.\\
 

### 2019-04-17 draft_together3.tex
draft

@@
 If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
-We have already shown earlier that synchronizing the input signals while keeping the original logic block also can result in error.
+We have already shown earlier that synchronizing the input signals while keeping the original logic block can also result in error.
 This points to looking at properties of each half circuit as the right thing to do.\\
 
-Another problem that the fault tolerant transformation cannot resolve is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.
+Another wrong approach for the fault tolerant transformation is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.
 We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.

### 2019-04-17 draft_together3.tex
edited proofs a bit

@@
 \item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
-\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ in the fault tolerant circuit.
-(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
+\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
+(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
 \end{itemize}
@@
 \begin{proof}
-We prove this Lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
+We prove this lemma by induction on all traces of length $n$.  The induction hypothesis is the same as the items in the definition of the lemma but for traces of length $n$:
 \begin{itemize}
-\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
+\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$, the first n states of the trace, maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
 \item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
-\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
-The case where two or more of the three conditions being true does not exist in this setting.
-Also a wire $w$ is unexcited if and only if none of the four excited conditions are true.
-\\
+\item In every state $s$ of $\sigma_n$, a wire $w$ in state $h^A(s)$ is excited in the original circuit is excited if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
+No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.
+A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.\\
 %Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned....
@@
 \begin{itemize}
-\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.
+\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.
 Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.
-\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
-\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.
-This case can also interpreted as the logic block being excited.
-Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.
+\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state.  
+\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half, both $c1^A$ and $w$ are outputs of logic blocks in the same topology and $c1^A=w$, then $c1^A$ is excited if and only if $w$ is excited in the original circuit.
+This case can also be interpreted as the logic blocks in their respective circuits being excited.
+Additionally there are no excitations within the C-element chain of the fault tolerant circuit because the valid initial state assigns $c1^A=c2^A=c3^A=w^A$.
 As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.
@@
 
-The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the subsequence for a trace $\sigma$ with length greater than or equal to $k$.
+The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the first $k$ states of a trace $\sigma$ with length greater than or equal to $k$.
 We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
@@
 From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.
-If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.
+If the transition occurs on the B-half then no wire values changed in the A-half and the induction hypothesis remain true.
 Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.
@@
 Refer to figure \ref{fig:l1helper} for an example of what happens in each of the cases.
-These are drawn for when $w$ transitions from $0\rightarrow1$ but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting 1's and 0's.
+These are drawn for when $w$ transitions from $0\rightarrow1$, but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting the 1's and 0's.
 %logic gate excited = c1^A excited
@@
 \item The first case is for an excited wire $w$.
-The corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
+In the fault tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
 Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.
-Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.
+Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and unexcited wires, the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.
 Thus the third induction hypothesis is true for all output wires.
@@
 \item
-$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.
-Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.
+The wire $w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half circuit, $w^A$ transitions so that $c3^{A}= w^{A}$.
+So both $w$ is unexcited and the corresponding wires in the fault tolerant circuit are unexcited, thus wire $w$ satisfies the third induction hypothesis.
 \item
@@
 
-Note as described previously that the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g.
+Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g.
 does not cause hazards in the C-element output).
-Thus this Lemma is true regardless of whether there is a fault or not in the other half of the circuit.
+Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.
 It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1
@@
 We look at the base case for every wire $w$ in the original circuit.
-Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.
+In the fault tolerant circuit, the valid initial state initializes the wires to: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.
 A wire $w$ can be either excited or unexcited in the original circuit.
@@
 For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.
-It is clear that the arrows represent transitions and logic block changes that can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires in the C-element chains behave as the arrows indicate.
-Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
+It is clear that the arrows represent transitions and logic block changes that can occur.
+We can also easily verify that the wires in the C-element chains behave only as the arrows indicate, thus we need to show that additional changes due to the logic blocks cannot occur.
+Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we need only to verify for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
 \begin{itemize}
@@
 In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.
-If any logic blocks are in case 9, its logic block cannot change excitations because it would violate Lemma 1.
-Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.
+If any logic blocks are in case 9, its logic block cannot change excitations because Lemma 1 would be violated.
+Thus far, we have shown using Lemma 1that the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.
 The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.

### 2019-04-26 draft_together3.tex
after fixing the logic flow before changing lemma 2 entirely

@@
 %should I delete intermediate?
-\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed as follows.
-Given any state in the original circuit state graph $s \in S$, assume that there exists initial wire values that correspond to $s$.
-In addition, for each wire $w$, the internal wire values within the logic block of $w$ are semi-modularity consistent.
-Construct the valid initial state by copying the internal wire values to corresponding internal wires in the A half circuit.
-Then assign the value $w$ to appropriate wires in the A half circuit such as $w=c1^A=c2^A=c3^A=w^A$.
+\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed from an initial state of the original circuit.
+The wire values in the logic block and $w$ in the original circuit are copied to the corresponding wires in the A half.
+The additional wires from the C-element chain are also assigned the same value as $w$.
+That is, first assign to $w^A$ the value of $w$, then assign to $c1^A$ $c2^A$ $c3^A$ the value of $w^A$ as well.
 The same construction can be applied for the B half circuit as well.
@@
 %\textbf{
-This is one out of many possible initializations that can fit the behavior we want.
-Thus this definition is stronger than it needs to be but is used for the sake of conveniece.
-In Lemma 1, we will show why this definition allows for the behavior that we want in the fault tolerant circuit.\\
-
-To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
+This definition is stronger than it needs to be but is convenient.\\
+
+%To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
 One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.\\
@@
 \begin{lemma}[1]
-If $\sigma$ is the trace of the fault tolerant circuit and the A half is fault free, then in the A half:
+If $\sigma$ is the trace of the fault tolerant circuit where the A half begins in a valid initial state and is fault free, then the following three properties are true:
 \begin{itemize}
-\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
-\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
-\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
+\item P1: The half-circuit mapping of a prefix of $\sigma$, $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit, regardless of the wire values in the B half.
+\item P2: The logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
+\item P3: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
 (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
@@
 %Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).
-By symmetry this is also true for the B half if we exchange A and B in the statement above.
 
@@
 \end{lemma}
-The trace $\sigma$ can be finite or infinite in length in accordance with the definition of a trace. 
+
 \begin{proof}
-We prove this lemma by induction on all traces of length $n$.  The induction hypothesis is the same as the items in the definition of the lemma but for traces of length $n$:
-\begin{itemize}
-\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$, the first n states of the trace, maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
-\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
-\item In every state $s$ of $\sigma_n$, a wire $w$ in state $h^A(s)$ is excited in the original circuit is excited if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
-No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.
-A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.\\
-%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned....
-forget if I explained or not
-\end{itemize}
+Let $\sigma$ be an arbitrary trace of fault tolerant circuit.
+We will show that for every prefix $\sigma_n$ of length $n$, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit, by induction on $n$.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
+We show the induction hypotheses hold in the base case $sigma_1$ consisting of state $s_1$, a valid initial state.
 \begin{itemize}
 \item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.
-Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.
-\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state.  
-\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half, both $c1^A$ and $w$ are outputs of logic blocks in the same topology and $c1^A=w$, then $c1^A$ is excited if and only if $w$ is excited in the original circuit.
-This case can also be interpreted as the logic blocks in their respective circuits being excited.
-Additionally there are no excitations within the C-element chain of the fault tolerant circuit because the valid initial state assigns $c1^A=c2^A=c3^A=w^A$.
-As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.
-By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.
-This shows the valid initial state also satisfies the last part of the induction hypothesis.
-%is this enough....
-that the existing states follow that iff statement?
+Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit and P1 holds.
+\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state and P2 holds.
+\item 
+For any wire, $c1^A$, $c2^A$, $c3^A$ and $w^A$ are assigned the same values by the valid initial state.
+Thus any excitations must be on $c1^A$.
+Since the wires that inputs into all logic blocks have the same values in the original and fault tolerant circuit, and the logic blocks are in semi-modularity consistent states then if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault tolerant circuit.
+Similarly if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault tolerant circuit.
+This shows the valid initial state satisfies P3.    %is this enough.... that the existing states follow that iff statement?
 \end{itemize}
 
-The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the first $k$ states of a trace $\sigma$ with length greater than or equal to $k$.
+The induction step is to assume that the induction hypotheses is true for $\sigma_k$.
 We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
-In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.
-Then we show that for all possible $s_{k+1}$ logic block remains in a semi-modularity consistent state.
-Finally for all wires in $s_{k+1}$, the third induction hypothesis is true.\\
-
-From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.
-If the transition occurs on the B-half then no wire values changed in the A-half and the induction hypothesis remain true.
-Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.
-For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur.
-Refer to figure \ref{fig:l1helper} for an example of what happens in each of the cases.
-These are drawn for when $w$ transitions from $0\rightarrow1$, but the transition from $1\rightarrow0$ can also be visualized with the same figure by inverting the 1's and 0's.
+In particular for all possible next states from the current state $s_k$, we show that either the output wires have not transitioned, or in the case of a transition that it is also a transition of the original circuit.
+Then we show that the logic blocks in all possible next states remain in a semi-modularity consistent state.
+And finally that P3 is true and all wire blocks in the next states are in one of the cases in figure \ref{fig:l1helper}.\\
+
+From state $s_k$, we look at all possible transitions; a transition may occur on excited gates or c-elements.
+Transitions in the B-half do not change wire values in the A-half and can be ignored.
+Thus we only need to consider the wires that may change in the A-half circuit which by P3 can only occur in the wire blocks of wires that are excited in the original circuit in state $h^A(s_k)$.
+For each excited wire block $w$, %need to define wire block
+P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
 %logic gate excited = c1^A excited
@@
 \begin{itemize}
-\item The first case is for an excited wire $w$.
+\item We consider cases 1-3 together (a-c in Figure \ref{fig:l1helper}) for some excited wire $w$ in the original circuit.
+For each case, it is clear that in the fault tolerant circuit, the transition propagates down the C-element chain as shown in the figure.
+Then P3 holds for wire $w$.
+For all other output wires, P3 also holds because the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$, so the input into the logic blocks do not change and thus excitation of all wires in the original circuit do not change in the next state.
+The state of the corresponding wire blocks in the fault tolerant circuit also do not change in the next state.
+Thus P3 holds for all wires in the next state.
+Another consequence of $h^A(s_{k+1})=h^A(s_k)$ is that P1 holds.
+And lastly no output wire transitions implies the logic blocks stay in a semi-modularity consistent state so that P2 holds.
+
+%\item The first case is for an excited wire $w$.
 In the fault tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
@@
 %$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
-\item The second case is when the signal propagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
+%\item The second case is when the signal propagates down to $c2^A$.
+In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.
 Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
 This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
-\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.
+%\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.
 In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.
-Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
+%Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
 This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
 
-\item The fourth case is when the signal propagates down to $w^A$.
-In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.
-Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.
-Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent.
-Then we look at the third induction hypothesis by partitioning all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.
-(excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)
+\item Case 4 is when the transition propagates down to $w^A$ in the fault tolerant circuit as shown in Figure \ref{fig:l1helper} d.
+This corresponds to $w$ transitioning in the original circuit, and because $w$ is excited in state $h^A(s_k)$ then the transition to the next state is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and P1 holds.
+Because $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, then inputs to all logic blocks in the A-half are also semi-modularity consistent in state $s_{k+1}$ and P2 holds.
+Next we show P3 holds by looking at the single wire that changes.
+Wire $w$ fanouts to other logic blocks which may change their excitations in response to the change in wire $w$.
+Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
+%these are the only possibilities in the original... look at what happens to these wires in the FT circuit
 \begin{itemize}
 \item
-The wire $w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half circuit, $w^A$ transitions so that $c3^{A}= w^{A}$.
-So both $w$ is unexcited and the corresponding wires in the fault tolerant circuit are unexcited, thus wire $w$ satisfies the third induction hypothesis.
-\item
-For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.
-Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.
-\item
-For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.
-But since $u$ is excited then $c1^A$ in the A half must be excited.
-Thus wires of this type satisfy the third induction hypothesis.
-\item
-Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.
-Thus wires of this type satisfy the third induction hypothesis.
+For excited wires $v$ in state $h^A(s_k)$ which are also excited in state $h^A(s_{k+1})$ in the original circuit, by semi-modularity $c1^A$ of $v$ in the A-half circuit will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy P3.
+%semi-modularity part still needs to be fixed
+\item
+By semi-modularity, the only wire in the original circuit that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (we disregard the possibility that w can be immediately excited again).
+In the A-half circuit, $w^A$ transitions so that the $w$ wire block is in state Figure \ref{fig:l1helper} e.
+Both $w$ in the original circuit is unexcited and the corresponding wire block in the A-half circuit is unexcited, thus wire $w$ satisfies P3.
+\item
+For wires $u$ that transition from unexcited in state $h^A(s_{k})$ to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in state Figure \ref{fig:l1helper} e.
+But since $u$ in the original circuit is excited in the new state and $c1^A=u$, then $c1^A$ in the A-half circuit must also be excited so that the wire block $u$ is in state Figure \ref{fig:l1helper} a.
+Thus wires of this type satisfy P3.
+\item
+Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic block is also unexcited in the A-half circuit and the wire block stays in state Figure \ref{fig:l1helper} e.
+Thus wires of this type satisfy P3.
 \end{itemize}
@@
 \end{proof}
-
+By symmetry this is also true for the B half if we exchange A and B in the statement of the lemma above.  
 Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g.
@@
 
-This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transitions in a completely predictable pattern and thus deadlock does not occur.
+This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transition in a completely predictable pattern and thus deadlock does not occur.
+To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
+One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.
 
@@
 \begin{lemma}[2.1]
-For any state in a trace of the fault tolerant circuit, the wire blocks are in one of the cases in figure \ref{fig:l21}.
+For any trace of the fault tolerant circuit, each wire block follow the state diagram in Figure \ref{fig:l21} (up to 0 and 1 inversion).
 \end{lemma}
 \begin{proof}
-We show by induction that for the fault tolerant circuit, each wire block is in one of the cases in the above figure.
-The figure halves the number of cases, as case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transitions go through the same cases in figure \ref{fig:l21} from 1-11 but inverted.
-Thus we only need to analyze possible transitions from each case up to case 10.
-Also, Lemma 1 applies to both A half and B half.\\
-
-We look at the base case for every wire $w$ in the original circuit.
-In the fault tolerant circuit, the valid initial state initializes the wires to: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.
-A wire $w$ can be either excited or unexcited in the original circuit.
-If the wire $w$ is unexcited, applying Lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).
-If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.
-Thus this property is true for the base case.
-\\
-
-In the induction step, assume that the induction hypothesis is true for state $s_k$ and we show that it is true for $s_{k+1}$.  \\
-
-For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.
-It is clear that the arrows represent transitions and logic block changes that can occur.
-We can also easily verify that the wires in the C-element chains behave only as the arrows indicate, thus we need to show that additional changes due to the logic blocks cannot occur.
-Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we need only to verify for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
+We show this lemma by induction.
+The state diagram in Figure \ref{fig:l21} is incomplete in the sense that after case 11, there are more transitions.
+However, case 11 is symmetric to case 1 with only the 0's and 1's inverted and so the transitions from case 11 is symmetric to the transitions from case 1 with 0's and 1's inverted until it loops back to case 1.
+Because of this symmetry, we only need to analyze possible transitions from each case up to case 10.
+Also, Lemma 1 applies to both A half and B half which we will use in the body of this proof.\\
+
+We look at the base case of $\sigma_1$ which is also $s_1$ initialized as a valid initial state.
+For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
+Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault tolerant circuit are in case 2 of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
+Thus the lemma property holds for the base case.
+\\
+%is this the pick a trace thing again? (instead of for all traces of length n)
+In the induction step, assume that the induction hypothesis is true for trace $\sigma_k$ and we show that it is true for $\sigma_{k+1}$ by looking at state $s_k$.  \\
+
+For all possible transitions from $s_k$, we must verify that wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
+It is easy to see that the transitions (black arrows) in the figure are the only possible wire transitions when the wire blocks are in a state in the state diagram.
+Thus we need to investigate the state changes when such a transition happens to the wire block that transitions as well as its effects on all other wire blocks.
+
+%It is clear that transitions and logic block changes in the state diagram can occur.
+Furthermore, we can easily verify that the wires in the C-element chains ($c1$, $c2$, $c3$, $w$) behave as the arrows indicate with no additional possibilities.
+Thus we need to show that no additional changes in the logic blocks can occur.
+%Because the arrows do not always indicate wire transitions (some are changes in excitation of the logic blocks which are in response to transitions of other output wires), we need only to verify for the transitions that do occur (black arrows), that they do not cause the other logic blocks (and itself) to behave inappropriately.
 \begin{itemize}
-\item
-Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
-\item
-Case 2a/2b:  In case 2a, $c1^A$ is excited and can transition to case 3a.
-Similarly case 2b can transition to case 3c.
-From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.
+%\item
+%Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
+\item
+Cases $2a\rightarrow 3a$, $2b\rightarrow 3c$, $3b\rightarrow 4a$, $3b\rightarrow 4b$, $4a\rightarrow 5$, $4b\rightarrow 5$, $5\rightarrow 6a$, $5\rightarrow 6b$, $6a\rightarrow 7$, $6b\rightarrow 7$, $7\rightarrow 8a$, $7\rightarrow 8b$, $8a\rightarrow 9$, $8b\rightarrow 9$:
+These transitions are on intermediate wires and , other than an excited logic block transition, the logic blocks do not change excitations because  
+In case 2a, when $c1^A$ transitions, 
+It is also possible that the unexcited logic block becomes excited and go to case 3b at the next state.
 However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
-\item
-Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).
-The logic block in A-half (B-half) cannot be excited again while $c1^A=1$ ($c1^B=1$) because that violates Lemma 1.
-From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
+Case 2b is similar.
+\item
+Case 3a/3b/3c:  In case 3a, it is possible for the logic block in B-half to become excited, and change to 4a.
+The logic block in A-half cannot be excited again while $c1^A=1$ because that violates Lemma 1.
+Case 3c is similar to 3a.
+From case 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
 The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.
@@
 Case 4a/4b:
-A logic block is excited in both cases and can transition to case 5.
+In case 4a, the logic block in B-half is excited and can transition to case 5.
 The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).
+The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as the above cases (Lemma 1).
+Case 4b is similar.
 \item
@@
 \\
-Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires.
-Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).
-\item
-Cases 9/10a/10b:  In cases 1-8a/8b all transitions happen on intermediate wires so the state of the other wire blocks must remain the same.
-In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.
-In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.
-If any logic blocks are in case 9, its logic block cannot change excitations because Lemma 1 would be violated.
-Thus far, we have shown using Lemma 1that the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.
-The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.
-\\
+Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in figure \ref{fig:l21}.
+The only possible additional transitions would come from the logic block but we know that the already transitioned logic block cannot be excited again by Lemma 1.
+\item
+Cases 9/10a/10b:  The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
+A similar reasoning can be applied to case 9.
+By Lemma 1, if any wire blocks are in case 9 and the transition is not in this wire block, then its logic blocks cannot change excitations.
+Wire blocks in cases 10a/10b are tricky because we must use a different technique to show that the logic blocks cannot be excited because half of the circuit has completed its transitions.
+%Wire blocks in cases 10a/10b are tricky because we cannot directly apply Lemma 1 on the half that has completed its transition to show that its logic block cannot be excited.
+We   In cases 1-8a/8b, all transitions happen on intermediate wires so the other wires blocks stay in their previous states.  
+Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
 We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
@@
 \end{definition}
-Next we will show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit.
+Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit.
 Applying Lemma 1, we know that the fault free half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.
@@
 \begin{lemma}[3]
-For all traces $\sigma$ in the duplicated circuit, with a single transient fault occurring on a $c2$ or $c3$ wire of some wire $w$ at any point in the trace, then $h^{A}(\sigma_n)$ and $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the duplicated circuit, if a single transient fault occurring on a $c2$ or $c3$ wire of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ and $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 \end{lemma}
@@
   \centering
-    \includegraphics{L3helperfull}
+    \includegraphics{flowl2c3a}
   \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
@@
 %c3
-A similar reasoning would then apply if a transient fault occurs in $c1^A$, and also for the $B$ half.  
+Similar reasoning would then apply if a transient fault occurs in $c2^A$, and also for the $c2$ and $c3$ wires in the $B$ half.  
 \end{proof}
@@
 \end{figure}
-Next we show that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions in a completely predictable pattern analogous to Lemma 2.1.
+Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions in a completely predictable pattern analogous to Lemma 2.1.
 The main difference is that because a fault may be present we cannot fully predict the value of one of $c1^A$ or $c1^B$.
@@
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault tolerant circuit, where a fault occurs on a wire other than $c2$ or $c3$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ are always in a state of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs on a wire other than $c2$ or $c3$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ are always in a state of Figure \ref{fig:l4}.
 \end{lemma}

### 2019-04-28 draft_together3.tex
almost done L2, change order of w itself

@@
 The state diagram in Figure \ref{fig:l21} is incomplete in the sense that after case 11, there are more transitions.
-However, case 11 is symmetric to case 1 with only the 0's and 1's inverted and so the transitions from case 11 is symmetric to the transitions from case 1 with 0's and 1's inverted until it loops back to case 1.
+However, case 11 is symmetric to case 1 with only the 0's and 1's inverted and so the transitions from case 11 is also symmetric to the transitions from case 1 with 0's and 1's inverted until it loops back to case 1.
 Because of this symmetry, we only need to analyze possible transitions from each case up to case 10.
@@
 %is this the pick a trace thing again? (instead of for all traces of length n)
+
 In the induction step, assume that the induction hypothesis is true for trace $\sigma_k$ and we show that it is true for $\sigma_{k+1}$ by looking at state $s_k$.  \\
 
-For all possible transitions from $s_k$, we must verify that wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
-It is easy to see that the transitions (black arrows) in the figure are the only possible wire transitions when the wire blocks are in a state in the state diagram.
-Thus we need to investigate the state changes when such a transition happens to the wire block that transitions as well as its effects on all other wire blocks.
+In state $s_k$, all wire blocks are in a case in the state diagram from the induction hypothesis.
+It is easy to see that the only possible wire transitions in state $s_k$ are the transitions (black arrows) in the state diagram.
+%In addition, if $w$ is the transitioning wire block then because $w$ does not feedback to itself and the input wires do not transition, the logic blocks do not change excitations (other than when $c1$ transitions).
+Thus the black arrows show the only possible transitions in the state diagram from state $s_k$.
+For each transition, we must verify that all wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
+Thus we need to investigate the changes in the wire block that transitions as well as the transition's effects on all other wire blocks.
+%For all possible transitions from $s_k$, we must verify that wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
+It is easy to see that the transitions (black arrows) in the figure are the only possible wire transitions when the wire blocks are in a case in the state diagram.
+Thus we need to investigate the state changes when a wire block transitions as well as the transition's effects on all other wire blocks.
 
@@
 \item
-Cases $2a\rightarrow 3a$, $2b\rightarrow 3c$, $3b\rightarrow 4a$, $3b\rightarrow 4b$, $4a\rightarrow 5$, $4b\rightarrow 5$, $5\rightarrow 6a$, $5\rightarrow 6b$, $6a\rightarrow 7$, $6b\rightarrow 7$, $7\rightarrow 8a$, $7\rightarrow 8b$, $8a\rightarrow 9$, $8b\rightarrow 9$:
-These transitions are on intermediate wires and , other than an excited logic block transition, the logic blocks do not change excitations because  
-In case 2a, when $c1^A$ transitions, 
-It is also possible that the unexcited logic block becomes excited and go to case 3b at the next state.
+Cases $2a\rightarrow 3a$, $2b\rightarrow 3c$, $3b\rightarrow 4a$, $3b\rightarrow 4b$, $4a\rightarrow 5$, $4b\rightarrow 5$, $5\rightarrow 6a$, $5\rightarrow 6b$, $6a\rightarrow 7$, $6b\rightarrow 7$, $7\rightarrow 8a$, $7\rightarrow 8b$, $8a\rightarrow 9$, $8b\rightarrow 9$: \\
+Let the transition be on wire block $w$.  The transition is on an intermediate wire so the logic blocks of $w$ do not change excitations other than when $c1$ transitions.  
+For the same reason, the transition does not affect the excitations in logic blocks of wire blocks other than $w$, thus those wire blocks stay in the same state in $s_{k+1}$.  
+%In case 2a, when $c1^A$ transitions, 
+%It is also possible that the unexcited logic block becomes excited and go to case 3b at the next state.
 However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
 Case 2b is similar.
-\item
-Case 3a/3b/3c:  In case 3a, it is possible for the logic block in B-half to become excited, and change to 4a.
+%\item
+%Case 3a/3b/3c:  In case 3a, it is possible for the logic block in B-half to become excited, and change to 4a.
 The logic block in A-half cannot be excited again while $c1^A=1$ because that violates Lemma 1.
@@
 The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.
-\item
-Case 4a/4b:
-In case 4a, the logic block in B-half is excited and can transition to case 5.
+%\item
+%Case 4a/4b:
+%In case 4a, the logic block in B-half is excited and can transition to case 5.
 The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.
@@
 Case 4b is similar.
-\item
+%\item
 %Case 3a/3b:   If a transition occurs in these cases for wire block $w$, the only excited wires are $c1^{B}$ or $c1^{A}$ respectively.
@@
 \\
-Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in figure \ref{fig:l21}.
+%Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in figure \ref{fig:l21}.
 The only possible additional transitions would come from the logic block but we know that the already transitioned logic block cannot be excited again by Lemma 1.
 \item
-Cases 9/10a/10b:  The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
+Cases $9\rightarrow10a$, $9\rightarrow10b$, $10a\rightarrow11$, $10b\rightarrow11$:  \\
+Again let the transition be in wire block $w$.
+The transition is on an output wire which can change logic block excitations.
+We first show that the logic blocks are not excited in wire block $w$ itself after the transition.
+This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
+Next, we examine the effects of the transitions on wire blocks $v$ where $v\neq w$ and $v$ may be in any cases of Figure \ref{fig:l21}.  
+%The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
 A similar reasoning can be applied to case 9.
@@
 %Wire blocks in cases 10a/10b are tricky because we cannot directly apply Lemma 1 on the half that has completed its transition to show that its logic block cannot be excited.
-We   In cases 1-8a/8b, all transitions happen on intermediate wires so the other wires blocks stay in their previous states.  
-Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
-We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
+%In cases 1-8a/8b, all transitions happen on intermediate wires so the other wires blocks stay in their previous states.  
+\begin{itemize}
+\item
+If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three cases: each half has either an excited logic block and excited wire block, unexcited logic block and excited wire block, or unexcited logic block and unexcited wire block.
+The new transition cannot cause an excited logic block to become unexcited (e.g., A-half in case 2a) as it would violate semi-modularity in the original circuit.
+The transition also cannot excite a logic block when the wire block is still excited (e.g., A-half in case 4a) as it would violate P3 in Lemma 1.
+It is possible for unexcited logic blocks with unexcited wire blocks to become excited (e.g., both A and B-half in case 1); all such case changes are covered by the blue arrows.
+Thus we have shown that for $v$ in cases 1-8a/8b, transitions of $v$ caused by wire changes in $w$ follow the state diagram.
+%Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
+\item
+Next we show that a wire transition in $w$ does not change excitations in logic blocks of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
+First we assume that wire block $v$ is in case 10a, and that the $w^A$ transition excites the A-half of the logic block of $v$ in state $s_{k+1}$.
+The $w^B$ transition can be ignored because the logic block in the B-half of $v$ cannot be excited as it would violate P3 in Lemma 1.
+In state $s_k$, an output wire mismatch is possible only if the wire blocks are in cases 10a or 10b.
+Thus for all mismatched wires $u$ in state $s_k$, $c2^A=c2^B$ (${u}$ includes $v$).
+Wire $w^A$ transitioning does not change the values of those wires so in state $s_{k+1}$, wires $u$ stay mismatched and their $c2^A=c2^B$.
+In state $s_{k+1}$, there is also one newly mismatched wire $w$, which also has $c2^A=c2^B$.
+In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
+Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal at a later state while keeping wire $v$ mismatched.
+In that later state, the excited A-half logic block of $v$ must still be excited due to semi-modularity in the original circuit.
+%semi-modularity...
+also why is A-half excited?
+Also SM
+Since the input wires on both halves of wire block $v$ are equal and $c1^A=c1^B$, then the B-half logic block must be excited too.
+The state for the B-half violates P3 of Lemma 1 and a contradiction is found.
+Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the logic blocks of a wire in case 10a.
+Wires in case 10b are similar.
+\end{itemize}
+%Lastly we also show that the logic blocks are not excited in wire block $w$ itself after the transition.
+This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
+\\
+Therefore the transitions in this case allow all wire blocks of the circuit to follow the state diagram in Figure \ref{fig:l21}.\\
+
+%We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
 For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.
 This is shown by contradiction.
-Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
+%Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
 In state $s_k$ an output wire mismatch is possible only if it is in cases 10a or 10b.
 Thus for all wires $u$ where $u^A\neq u^B$, $c2^A=c2^B$ (which includes $v$).
-$w^A$ transitioning does that change the values of those wires so the property is true in state $s_{k+1}$ as well.
+$w^A$ transitioning does not change the values of those wires so the property is true in state $s_{k+1}$ as well.
 It is also true of the newly mismatched wire $w$.
@@
 Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
-From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
+%From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
 Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.
@@
 \end{itemize}
-This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
-By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit are in a case in figure \ref{fig:l21} for all traces. \\
+This shows that all wire blocks in all possible $s_{k+1}$ follow the state diagram, and the induction step is complete.\\
+By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit follow the state diagram in Figure \ref{fig:l21} for all traces. \\
 \end{proof}

### 2019-04-28 draft_together3.tex
editing L3 L4

@@
 That is, first assign to $w^A$ the value of $w$, then assign to $c1^A$ $c2^A$ $c3^A$ the value of $w^A$ as well.
-The same construction can be applied for the B half circuit as well.
+The same construction applies for the B half circuit as well.
 \end{definition}
@@
 \end{proof}
-By symmetry this is also true for the B half if we exchange A and B in the statement of the lemma above.  
+By symmetry this is also true for the B half if we exchange A and B in the statement of Lemma 1.  
 Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g.
@@
 \item
-If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three cases: each half has either an excited logic block and excited wire block, unexcited logic block and excited wire block, or unexcited logic block and unexcited wire block.
-The new transition cannot cause an excited logic block to become unexcited (e.g., A-half in case 2a) as it would violate semi-modularity in the original circuit.
-The transition also cannot excite a logic block when the wire block is still excited (e.g., A-half in case 4a) as it would violate P3 in Lemma 1.
+If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three: each half has either an excited logic block and excited wire block, unexcited logic block and excited wire block, or unexcited logic block and unexcited wire block.
+For excited logic block and excited wire block (e.g., A-half in case 2a), the new transition cannot cause the excited logic block to become unexcited as it would violate semi-modularity in the original circuit.
+For unexcited logic block and excited wire block (e.g., A-half in case 4a), the transition also cannot excite the logic block as it would violate P3 in Lemma 1.
 It is possible for unexcited logic blocks with unexcited wire blocks to become excited (e.g., both A and B-half in case 1); all such case changes are covered by the blue arrows.
-Thus we have shown that for $v$ in cases 1-8a/8b, transitions of $v$ caused by wire changes in $w$ follow the state diagram.
+Thus we have shown that for $v$ in cases 1-8a/8b, changes in $v$ caused by a transition in $w$ follow the state diagram.
 %Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
 \item
-Next we show that a wire transition in $w$ does not change excitations in logic blocks of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
+Next we show that a transition in $w$ does not change excitations in logic blocks of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
 First we assume that wire block $v$ is in case 10a, and that the $w^A$ transition excites the A-half of the logic block of $v$ in state $s_{k+1}$.
@@
 Wire $w^A$ transitioning does not change the values of those wires so in state $s_{k+1}$, wires $u$ stay mismatched and their $c2^A=c2^B$.
-In state $s_{k+1}$, there is also one newly mismatched wire $w$, which also has $c2^A=c2^B$.
+In state $s_{k+1}$, there is one newly mismatched wire, $w$, which also has $c2^A=c2^B$.
 In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
@@
 \end{definition}
-Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit.
-Applying Lemma 1, we know that the fault free half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.
-To do this we prove some properties that are true when a single transient fault occurs on a wire.
+Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
+Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.
+But we have not proved that the A-half does not stop prematurely compared to the original circuit.
+Towards this goal, we prove two lemmas:  Lemma 3 shows if a single fault occurs on the $c2$ or $c3$ wires of some wire $w$, the output wires still follow the original state graph.
+Lemma 4 shows if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
+Then these lemmas combine to show that there is no deadlock.
+
+%To do this we prove some properties that are true when a single transient fault occurs on a wire.
 We partition the wires into two sets based on their properties when a single transient fault is added.
@@
 Then we combine these Lemmas to show that there is no deadlock.
+
 \begin{lemma}[3]
-For all traces $\sigma$ in the duplicated circuit, if a single transient fault occurring on a $c2$ or $c3$ wire of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ and $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For any trace $\sigma$ in the duplicated circuit, if a single transient fault occur on wire $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 \end{lemma}
 \begin{proof}
-Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.
-We use NuSMV to verify that if a transient fault occurs on one of the $c2$ or $c3$ wires of wire $w$, the input-output characteristic of the local C-element chain do not change.
-Under normal operation, by Lemma 2.1 the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through the wire values shown in figure \ref{fig:l3helper}.
-Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2$ or $c3$, the cycle mentioned previously is always true.
+We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain do not change.
+Under normal operation, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through the wire values shown in Figure \ref{fig:l3helper}.
+Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2^A$ or $c3^B$, the transitions follow the state diagram in Figure \ref{fig:l3helper}.
 \begin{figure}
@@
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
-We go through an example of a transient on $c3^A$ to demonstrate why this is true.
-By Lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.
+We go through an example of a transient on $c3^B$ to demonstrate why this is true.
+By Lemma 2.1 the normal circuit is in a state in Figure \ref{fig:l21}, so we observe the transient induced trace with the transient occurring at each state in Figure \ref{fig:l21}.
 \begin{itemize}
 	\item
-If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b it does not cause any changes in excitations in the local circuit.
+If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b the transient does not cause any changes in excitations in the local circuit.
 In particular since $w^A$ and $w^B$ do not change, then by semi-modularity the excited/unexcitedness of logic blocks are maintained.
-So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^A$ value flipped.
-Eventually they all transition to state 8a and proceed from there as usual.
-	\item
-If the current state is 7 progresses the state to 8a, the correct transition.	
-	\item
-      If the current state is 8a then when $c3^A$ experiences a transient, the state
+So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^B$ value flipped.
+Eventually they all transition to state 8b and proceed from there as usual.
+	\item
+If the current state is 7, the transient changes the state to 8b, a valid transition.	
+      \item
+If the current state is 8a, the transient changes the state to 9, a valid transition.	
+	\item
+      If the current state is 8b then when the transient occurs on $c3^B$, the state
  becomes identical to state 7.  It will then proceed from state 7 as usual.   
 	\item
-If the circuit experiences a fault in state 9, it will revert back to state 8b.  
-	\item
-If the circuit experiences a fault in state 10a or 10b, $w_B$ or $w_A$ will go from excited to non excited respectively.
-$c3^A$ will be excited but there are no other excitations in the local circuit.
-Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited or transition on any subsequent states while $w^A$ and $w^B$ do not change (same argument as in Lemma 2.1 can be used since the other wire blocks do not have transients and thus in one of the states in cases 2.1).
-Then the local circuit will stay in this transient induced state until $c3^A$ finally changes and the circuit returns to its state before the transient.
+If the current state is 9 then when the transient occurs, the state reverts back to state 8a.  
+	\item
+If the current state is 10a or 10b, then when the transient occurs, $w_B$ or $w_A$ changes from excited to non excited respectively.
+Wire $c3^B$ is excited but there are no other excitations in the wire block.
+Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited in any subsequent states while $w^A$ and $w^B$ are mismatched (by the same argument as in Lemma 2.1 for cases 10a/10b since the other wire blocks do not have transients).
+Then the wire block will stay in this transient induced state until $c3^B$ finally transitions and the wire block returns to its state before the transient.
 \end{itemize}
 %c3
-Similar reasoning would then apply if a transient fault occurs in $c2^A$, and also for the $c2$ and $c3$ wires in the $B$ half.  
+Similar reasoning would then apply if a transient fault occurs in $c2^B$.  
 \end{proof}
-
-\includegraphics[width=.8\textwidth]{gatew}
-
+By symmetry this is also true for transients in the A half if we exchange A and B in the statement of Lemma 3.\\
+
+%\includegraphics[width=.8\textwidth]{gatew}
 \begin{figure}
@@
 \end{figure}
-Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions in a completely predictable pattern analogous to Lemma 2.1.
-The main difference is that because a fault may be present we cannot fully predict the value of one of $c1^A$ or $c1^B$.
-The following property is true despite not knowing one of the $c1$ wire values and leads to the conclusion that the output wire pairs can never be different at deadlock.
+
+We showed that if a fault occurs on $c2$ or $c3$ wires then there is no observable differences in the output wires between the faulty circuit and fault free circuit.  
+Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions according to Figure \ref{fig:l4} which is analogous to Lemma 2.1.
+The main difference is that because a fault may be present, we cannot predict the value of either $c1^A$ or $c1^B$.
+The following property is true despite not knowing one of the $c1$ wire values and leads to the conclusion that the output wire pairs can never be mismatched at deadlock.
 
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs on a wire other than $c2$ or $c3$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ are always in a state of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block $w\in W$ are always in a state of Figure \ref{fig:l4}.
 \end{lemma}
 \begin{proof}
-Without loss of generality we prove this is true when a fault occurs in the A half.
-Then we can assume Lemma 1 is true for the B half.
-We show by induction that when the fault is not in $c2$ and $c3$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.
+The fault is in the B-half so Lemma 1 applies for the A half.
+We show by induction that when the fault is not in $c2^B$ and $c3^B$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.
 Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\
 
-The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from Lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
-
-In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of figure \ref{fig:l4}, then at $s_{k+1}$ we look at the possible next states.
-We don't assume anything about the non $c2$ and $c3$ wires for the A-half so that $c1^A$ may change values due to a fault.
-However we do expect $c1^A$ to be either a 1 or 0 and that even with hazards on $c1^A$, $c2$ wires transition to either 0 or 1.
-We indicate the possibly faulty $c1^A$ by the symbol X.
+The base case is for the valid initial state with no faults, projecting the states of Figure \ref{fig:l21} from Lemma 2.1 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
+
+In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of Figure \ref{fig:l4}, then we look at all possible next states $s_{k+1}$.
+We don't assume anything about the non $c2$ and $c3$ wires for the B-half so that $c1^B$ may change values due to a fault.
+However we do expect $c1^B$ to be either a 1 or 0 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.
+We indicate the possibly faulty $c1^B$ by the symbol X.
 \begin{itemize}

### 2019-04-30 draft_together3.tex
fixed through theorem 2

@@
 For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
-Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault tolerant circuit are in case 2 of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
+Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault tolerant circuit are in case 3b of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
 Thus the lemma property holds for the base case.
@@
 Towards this goal, we prove two lemmas:  Lemma 3 shows if a single fault occurs on the $c2$ or $c3$ wires of some wire $w$, the output wires still follow the original state graph.
-Lemma 4 shows if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
+Lemma 4 shows if a fault occurs on any of the other wires, then the $c2$ or $c3$ wires follow a similar state graph as the non-fault case and thus the output wire pairs can never be different at deadlock.
 Then these lemmas combine to show that there is no deadlock.
@@
 \end{lemma}
-\begin{proof}
-We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain do not change.
-Under normal operation, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through the wire values shown in Figure \ref{fig:l3helper}.
-Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2^A$ or $c3^B$, the transitions follow the state diagram in Figure \ref{fig:l3helper}.
+%need major rewording maybe after defining faulty trace
 \begin{figure}
   \centering
-    \includegraphics{flowl2c3a}
+    \includegraphics{L3helperfull}
   \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
@@
 
+\begin{proof}
+We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain does not change.
+Under normal operation, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) follow the state diagram shown in Figure \ref{fig:l3helper}.
+Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2^B$ or $c3^B$, the transitions follow the state diagram in the figure.
+The fault is masked when this happens.
+\\
+% this is kind of by induction, the inputs from the other parts of the system will be correct as long as the output of $w$ is correct.
+The error is masked if the input output characteristic is still the same
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
-We go through an example of a transient on $c3^B$ to demonstrate why this is true.
-By Lemma 2.1 the normal circuit is in a state in Figure \ref{fig:l21}, so we observe the transient induced trace with the transient occurring at each state in Figure \ref{fig:l21}.
+We go through an example of a transient fault on $c3^B$ to demonstrate why the resulting trace follows the state diagram.
+By Lemma 2.1, the normal circuit is in a state in Figure \ref{fig:l21}, so we observe all possible transient induced traces by placing a transient starting at each state in Figure \ref{fig:l21}.
 \begin{itemize}
 	\item
-If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b the transient does not cause any changes in excitations in the local circuit.
-In particular since $w^A$ and $w^B$ do not change, then by semi-modularity the excited/unexcitedness of logic blocks are maintained.
-So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^B$ value flipped.
-Eventually they all transition to state 8b and proceed from there as usual.
-	\item
-If the current state is 7, the transient changes the state to 8b, a valid transition.	
-      \item
-If the current state is 8a, the transient changes the state to 9, a valid transition.	
-	\item
-      If the current state is 8b then when the transient occurs on $c3^B$, the state
- becomes identical to state 7.  It will then proceed from state 7 as usual.   
-	\item
-If the current state is 9 then when the transient occurs, the state reverts back to state 8a.  
-	\item
-If the current state is 10a or 10b, then when the transient occurs, $w_B$ or $w_A$ changes from excited to non excited respectively.
-Wire $c3^B$ is excited but there are no other excitations in the wire block.
-Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited in any subsequent states while $w^A$ and $w^B$ are mismatched (by the same argument as in Lemma 2.1 for cases 10a/10b since the other wire blocks do not have transients).
-Then the wire block will stay in this transient induced state until $c3^B$ finally transitions and the wire block returns to its state before the transient.
+If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, or 6b in Figure \ref{fig:l21}, the transient does not change excitations in the local circuit.
+In particular, since $w^A$ and $w^B$ do not change, then by semi-modularity the excitation of logic blocks do not change.
+So the transient fault induced state graph is a copy of Figure \ref{fig:l21} containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^B$ value flipped.
+Eventually all fault states transition to state 8b and proceed from there as usual.
+	\item
+If the current state is 7, then the transient changes the state to 8b, a valid transition.	
+      \item
+If the current state is 8a, then the transient changes the state to 9, a valid transition.	
+	\item
+      If the current state is 8b, then the transient reverts the state back to state 7.  It will then proceed from state 7 as usual.   
+	\item
+If the current state is 9, then the transient reverts the state back to state 8a.  Again, it will proceed from state 8a as usual.  
+	\item
+If the current state is 10a, then when the transient occurs, $w_B$ changes from excited to non excited; and if the current state is 10b, $w_A$ changes.
+In both cases, wire $c3^B$ is excited but there are no other excitations in the wire block.
+Thus $w^A$ and $w^B$ stay mismatched and by semi-modularity, the logic blocks in these wire blocks cannot be excited in any subsequent states (by the same argument as in Lemma 2.1 for cases 10a/10b).
+Then the wire block will stay in this transient induced state until $c3^B$ finally transitions and the wire block returns to either 10a or 10b.
 \end{itemize}
@@
   \centering
-    \includegraphics{flowl4c3v2}
+    \includegraphics{flowl4c3a}
   \caption{The wires in each row are in order of $c1$, $c2$ and $c3$.
@@
 
-We showed that if a fault occurs on $c2$ or $c3$ wires then there is no observable differences in the output wires between the faulty circuit and fault free circuit.  
-Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions according to Figure \ref{fig:l4} which is analogous to Lemma 2.1.
-The main difference is that because a fault may be present, we cannot predict the value of either $c1^A$ or $c1^B$.
-The following property is true despite not knowing one of the $c1$ wire values and leads to the conclusion that the output wire pairs can never be mismatched at deadlock.
+We showed that if a fault occurs on the $c2$ or $c3$ wires then there are no observable differences in the output wires between the faulty circuit and the fault free circuit.  
+Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transition according to Figure \ref{fig:l4}.
+The state graph of Figure \ref{fig:l4} is similar to projecting the state graph of Figure \ref{fig:l21} onto the $c1$, $c2$ and $c3$ wires, with the exception that the $c1$ wire value is not known in the faulty half.
+Despite this, the following lemma is true and we can then conclude that the output wire pairs are never mismatched at deadlock.
 
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block $w\in W$ are always in a state of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
 \end{lemma}
 \begin{proof}
-The fault is in the B-half so Lemma 1 applies for the A half.
-We show by induction that when the fault is not in $c2^B$ and $c3^B$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.
-Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\
-
-The base case is for the valid initial state with no faults, projecting the states of Figure \ref{fig:l21} from Lemma 2.1 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
-
-In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of Figure \ref{fig:l4}, then we look at all possible next states $s_{k+1}$.
-We don't assume anything about the non $c2$ and $c3$ wires for the B-half so that $c1^B$ may change values due to a fault.
-However we do expect $c1^B$ to be either a 1 or 0 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.
-We indicate the possibly faulty $c1^B$ by the symbol X.
+The fault is in the B-half so Lemma 1 applies for the A-half.
+We show by induction that when the fault is not in $c2^B$ and $c3^B$, in the resulting trace, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in Figure \ref{fig:l4}.
+We only analyze for cases 1-5 because transitions from case 6 is symmetric to transitions from case 1 with 0's and 1's inverted until the state ends back in case 1.\\
+
+The base case of $\sigma_1$ consists of state $s_1$ which is the valid initial state with no faults.
+As noted in Lemma 2.1, the state of each of the wire blocks must be in case 1 or case 3b of Figure \ref{fig:l21}.
+Projecting these states onto the $c1$, $c2$ and $c3$ wires results in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
+
+In the induction step we assume that $\sigma_k$ follows Figure \ref{fig:l4} and in particular, each wire block at state $s_k$ is in a case of the figure.
+For each case that a wire block may be in, we then investigate the case changes in all possible next states $s_{k+1}$.
+It is possible that a fault has already been introduced in the B-half on wires other than $c2$ and $c3$, so that $c1^B$ may be affected by the fault.
+Despite the possibility of a fault, we assume that wire $c1^B$ has value of either 0 or 1 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.
+The possibly faulty wire value $c1^B$ is represented by the symbol X.
+In all the cases below we do not consider if $c1^B$ transitions because that will result in the wire block staying in the same case.
 \begin{itemize}
 	\item
-Case 1:  $c2$, $c3$ are not excited.  $c1^B$ can be excited depending on the inputs to the logic block.  Therefore, if there is a transition from this state it must be to case 2.
-\item
-Case 2/3a/3b:  $c2$ can be excited depending on $c1^A$.
-$c1^B$ cannot transition to 0 due to Semi-Modularity of wire $w$ and Lemma 1.
-Therefore, if there is a transition it must be from case 2 to case 3a or 3b, and case 3a or 3b to case 4.
+Case 1:  $c2$, $c3$ are not excited.  $c1^A$ can be excited depending on the inputs to the logic block.  Therefore, a transition from this case must be to case 2.
+\item
+Case 2/3a/3b:  $c2$ can be excited depending on $c1^B$.
+$c1^A$ cannot be excited to 0 due to semi-modularity of wire $w$ and Lemma 1.
+Therefore, a transition from case 2 must be to case 3a or 3b, and from case 3a or 3b to case 4.
 %I might need to show the excited ness of the good logic gate
 \item
-Cases 4/5a/5b:  $c1^B$ cannot transition to 0 due to the same reasoning above.
-$c2$ is not excited.
-The only possible transitions are on the $c3$ wires and since there are no faults on them they must transition from case 4 to case 5a or 5b, and from case 5a or 5b to 6.
+Cases 4/5a/5b:  $c1^A$ cannot be excited to 0 due to the same reasoning above.
+The $c2$ wires are not excited but the $c3$ wires are excited.
+Therefore, a transition from case 4 must be to case 5a or 5b, and from case 5a or 5b to 6.
 \end{itemize}
-By induction, the property we set out to prove is true, the $c2$ and $c3$ wires will be in a case of figure \ref{fig:l4}. 
-The same logic applies to when a fault occurs in the B half and the A half is fault free.  
+Thus, in the next state $s_{k+1}$, all wire blocks either stay in the same case or transition according to Figure \ref{fig:l4}.  
+By induction, the trace $\sigma$ also follows Figure \ref{fig:l4}.  
 \end{proof}
+By symmetry, this is also true if the fault occurs in the A half.  
 The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
-The next theorem shows that this implies all output pairs at deadlock must be equal so there is a possible next condition which contradicts the definition of deadlock.
-Thus the fault tolerant circuit does not deadlock under a single transient fault.
+The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault tolerant circuit does not deadlock under a single transient fault.
 
@@
 \begin{proof}
-Without loss of generality we can assume the fault occurs in the A half of the circuit.
-First by Lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.
-Thus we only look at when the fault occurs on all other wires.
+Without loss of generality, we can assume the fault occurs in the B half of the circuit.
+First by Lemma 3, we know that if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires.
+Thus we look at when the fault occurs on the remaining wires.
 Next, we prove that a deadlocked circuit in this scheme must have at least one pair of output wires which have different values.  That is $w^A\neq w^B$ for some wire $w$.
@@
 There
- must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in Lemma 4.
+ must exist a wire $w$ that is excited in the state $h^A(s)$ in the original circuit and for that wire block in the duplicated circuit, by Lemma 4 it must also be in a case in Figure \ref{fig:l4}.
+We examine each case in turn.
 \begin{itemize}
 	\item
-	Case 1: Since $w$ is excited then by Lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
-\item
-Case 2:  $c1^A$ may be 0 or 1.  If $c1^A=0$, since the inputs to A half and B half are equal then $c1^A$ must be excited and can transition to 1.  If $c1^A=1$ then it can transition to case 3a or 3b.
-\item
-Case 3a/3b:  $c1^A$ may be 0 or 1.  If $c1^A=0$, since the inputs to A half and B half are equal then $c1^A$ must be excited and can transition to 1.  If $c1^A=1$ then it can transition to case 4.
-\item
-Case 4/5a/5b:  $c3$ is excited and can transition.
+	Case 1: Since wire $w$ in the original circuit is excited, then by Lemma 1, the wire block $w$ is in case a or d in Figure \ref{fig:l1helper} and wires $c1^A$ or $w^A$ can transition.
+\item
+Case 2:  Wire $c1^B$ may be 0 or 1.
+If $c1^B=0$, since the inputs to A half and B half are equal then $c1^B$ must be excited and can transition to 1.
+If $c1^A=1$ then the wire block can transition to case 3a or 3b.
+\item
+Case 3a/3b:  Wire $c1^B$ may be 0 or 1.  If $c1^B=0$, again $c1^B$ can transition to 1.  If $c1^B=1$ then it can transition to case 4.
+\item
+Case 4/5a/5b:  Wire $c3$ is excited and can transition. 
 \end{itemize}
@@
 To remain deadlocked, it must be true that there exists a wire where $w^A\neq w^B$, which implies its $c1^A\neq c1^B$ and $c2^A\neq c2^B$ and $c3^A\neq c3^B$.
-But we have shown in Lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault.
-Thus deadlock is not possible.
-And applying Lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit.
+But this is not a possible case by Lemma 4.
+Thus deadlock is not possible when there is a single transient fault.
+And by Lemma 1, $h^A(\sigma_n)$ is a prefix of a trace in the original circuit.
 \end{proof}

### 2019-05-21 draft_together3.tex
finished conclusion, preliminary

@@
 \chapter{Introduction}
-Digital circuits and its widespread use has spurred on many of present day technology.
-Digital circuits differs from analog circuits in that its signals (voltages) can be represented as discrete values whereas signals in analog circuits are represented by continuous voltages.
-This is achieved by delimiting the ranges of voltages that correspond to a particular discrete value.
+Digital circuits is the basis of many of present day electronics.
+Digital circuits has signals which are represented as discrete values.
+This is achieved by choosing a range of voltages that correspond to each discrete value.
 Many digital circuits use binary values, that is the signals can only take on the value `logic 0' or `logic 1' (or low/high).
@@
 %why are async circuits important, timing delay etc
-Because these various faults can interfere with the function of the circuit and even result in harmful operations(catastrophic failures), there has been a lot of work put into making digital circuits fault tolerant.
+Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work put into making digital circuits fault tolerant.
 Most of the fault tolerant solutions has been investigated for synchronous digital circuits.
@@
 
-In the rest of this work, in chapter two, I will first introduce the different types of common faults and their causes.
-As well as the common fault models that researchers use when investigating these faults.
+In this work, we propose a new fault tolerant circuit transformation on asynchronous semi-modular control circuits.
+We also propose a method of comparing the fault tolerant circuit with the original circuit, by comparing traces with the half circuit.
+The fault free half of the fault tolerant circuit behaves like the original circuit under single transient faults.
+In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\
+
+In the rest of this work, in chapter two, I will first introduce the different types of common faults and their causes, as well as the common fault models that researchers use when investigating these faults.
 Then I will go into depth about the asynchronous circuit models that are relevant to this work.
@@
 
-In some of the previous work they make additional assumptions such as the checking circuit is fault free.
-We propose an asynchronous circuit transformation on a more general type of circuits, control circuits.
-The transformed circuit can function under single transient faults.
-In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits.
+The approach that we use to make circuits fault tolerant will be described in the next chaper.
+Some of the previous works makes additional assumptions such as the checking circuit is fault free or that only one fault can occur on an arbitrarily large transistor gate.
+We allow for standard two-input gates and assume that all gates in our model are subject to faults.
+Our fault tolerant transformation procedure is for a class of circuits, semi-modular control circuits, which includes many circuits.
 
@@
 %Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
- Also every pair of consecutive states in a trace are transitions% such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$
- .  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
+ Also every pair of consecutive states in a trace are transitions.  % such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$
+We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
 Thus a circuit has a set of traces.
-A circuit also has a set of initial states where the traces can begin in.  The set of initial states are the same as the set of states in the state graph.\\
-
+A circuit also has a set of initial states where the traces can begin in.
+The set of initial states are the same as the set of states in the state graph.\\%new 4/30
+
+Note that we allow the circuit to have external wire inputs and stopping states.  
+\begin{definition}A {\em stopping state} is a state where there are no excitations in the wires in the circuit and the circuit is waiting for the external inputs.\end{definition} 
+A trace of finite length ends in a stopping state where the external inputs never arrive and the circuit is stopped.
+A related concept is a deadlocked state which is a state where the circuit prematurely stops and defined as follows:
+\begin{definition}A {\em deadlocked state} is a state where there are no excitations in the wires in the circuit and is not a stopping state.\end{definition}
+A deadlocked state does not appear in a well designed circuit, but may appear after a circuit transformation (i.e., the new circuit stops at states where the original circuit do not), or when there are faults.
+Thus we want to design a circuit transformation where there are no deadlocked states.\\ %end new
 %Note that our definition of trace also includes the case where there is only one transition from each state of a state graph, which results in a linear state graph.
@@
 This does not happen in the fault-free case where the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
-However when faults do occur, the circuit may become unpredictable and a reason why we need to transform the circuit to protect against faults.
+However when faults do occur, the circuit may become unpredictable which is a reason why we need to transform the circuit to protect against faults.
 An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
@@
 The resulting trace may have successive repeated states.
-So we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.
+So next we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.
 The result should be a trace from the original circuit.
@@
 
-Next we look at the traces of each half circuit.
+Next we examine the traces of each half circuit.
 Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where each state is given a nominal name (state 0, state 1, ...
@@
 \section{Normal operation analysis}
-To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.
-That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
-And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.
-We show this through several Lemmas.
-Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.
-This is a strong result; it is true for arbitrary behavior of
-signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
-This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
-%One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
-\\
-
-Note that Lemma 1 allows for the possiblity of deadlock.
-Lemma 2 shows deadlock does not occur during normal operation.
-Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
-% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
-%[so no deadlock in normal operation??]
-
 Now we will discuss the proper wire initializations before going into the Lemmas.
@@
 
+To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.
+That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
+And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.
+We show this through several Lemmas.
+Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.
+This is a strong result; it is true for arbitrary behavior of
+signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
+This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
+%One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
+\\
+
+Note that Lemma 1 allows for the possiblity of deadlock.
+Lemma 2 shows deadlock does not occur during normal operation.
+Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
+% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
+%[so no deadlock in normal operation??]
+
 This leads to the definition and proof of Lemma 1 as follows:
@@
 \item P3: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
+We also call this condition: wireblock $w$ is excited.
 (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
@@
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of fault tolerant circuit.
-We will show that for every prefix $\sigma_n$ of length $n$, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit, by induction on $n$.
+Let $\sigma$ be an arbitrary trace of the fault tolerant circuit.
+We will show that for any prefix of the trace $\sigma_n$, where $n$ is any value from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit, by induction on $n$.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show the induction hypotheses hold in the base case $sigma_1$ consisting of state $s_1$, a valid initial state.
+We show the induction hypotheses hold in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state.
 \begin{itemize}
 \item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.
-Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit and P1 holds.
+Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and P1 holds.
 \item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state and P2 holds.
@@
 Thus any excitations must be on $c1^A$.
-Since the wires that inputs into all logic blocks have the same values in the original and fault tolerant circuit, and the logic blocks are in semi-modularity consistent states then if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault tolerant circuit.
+Since all output/input wires have the same values in the original and fault tolerant circuit and the logic blocks are in semi-modularity consistent states, then if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault tolerant circuit.
 Similarly if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault tolerant circuit.
@@
 
-The induction step is to assume that the induction hypotheses is true for $\sigma_k$.
+The induction step is to assume that the induction hypotheses is true for a length k prefix of the trace $\sigma_k$.
 We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
@@
 Then we show that the logic blocks in all possible next states remain in a semi-modularity consistent state.
-And finally that P3 is true and all wire blocks in the next states are in one of the cases in figure \ref{fig:l1helper}.\\
-
-From state $s_k$, we look at all possible transitions; a transition may occur on excited gates or c-elements.
+And finally that P3 is true and all wire blocks in the next states are in one of the cases in Figure \ref{fig:l1helper}.\\
+
+From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.
 Transitions in the B-half do not change wire values in the A-half and can be ignored.
-Thus we only need to consider the wires that may change in the A-half circuit which by P3 can only occur in the wire blocks of wires that are excited in the original circuit in state $h^A(s_k)$.
-For each excited wire block $w$, %need to define wire block
-P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
+Wire blocks in the A-half are in one of the cases in Figure \ref{fig:l1helper}, thus transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.
+By P3, if a wire block $w$ is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$..
+To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.
+
+% which by P3 applied to state $s_k$, implies that the corresponding wire is also excited in the original circuit.
+%By P3, wires in the fault tolerant circuit may change only if the wire block is excited, which implies wire $w$ is also excited in the original circuit in state $h^A(s_k)$.
+
+%Although we need to examine all excited wire blocks at state $s_k$, since they can only be in one of four states, then it suffices to look at what happens if a wire transitions from each state. 
+%  Thus for each excited wire block $w$, %need to define wire block
+
+%P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
 %logic gate excited = c1^A excited
@@
     \includegraphics[width=\textwidth]{gatewl1}
-  \caption{Different cases of the induction step for proving Lemma 1.  a) case 1, b) case 2, c) case 3, d) case 4}
+  \caption{Different cases of P3 for a wireblock a-d are excited and e is unexcited.  a) case 1, b) case 2, c) case 3, d) case 4, e) case 5}
   \label{fig:l1helper}
@@
 \begin{itemize}
-\item We consider cases 1-3 together (a-c in Figure \ref{fig:l1helper}) for some excited wire $w$ in the original circuit.
+\item We consider cases 1-3 together (a-c in Figure \ref{fig:l1helper}) for some excited wire block $w$.
 For each case, it is clear that in the fault tolerant circuit, the transition propagates down the C-element chain as shown in the figure.
-Then P3 holds for wire $w$.
-For all other output wires, P3 also holds because the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$, so the input into the logic blocks do not change and thus excitation of all wires in the original circuit do not change in the next state.
-The state of the corresponding wire blocks in the fault tolerant circuit also do not change in the next state.
-Thus P3 holds for all wires in the next state.
+The transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
+The wire $w$, in the original circuit, is then excited in state $h^A(s_{k+1})$ and P3 holds for wire $w$.
+For the remaining output wires, P3 holds because again $h^A(s_{k+1})=h^A(s_{k})$, so the excitation of all output wires in the original circuit do not change in state $h^A(s_{k+1})$.
+The wire blocks in the fault tolerant circuit also remain in the same case of Figure \ref{fig:l1helper} in $s_{k+1}$.
+Thus P3 holds for all wires in state $s_{k+1}$.
 Another consequence of $h^A(s_{k+1})=h^A(s_k)$ is that P1 holds.
@@
 
-\item Case 4 is when the transition propagates down to $w^A$ in the fault tolerant circuit as shown in Figure \ref{fig:l1helper} d.
-This corresponds to $w$ transitioning in the original circuit, and because $w$ is excited in state $h^A(s_k)$ then the transition to the next state is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and P1 holds.
+\item Case 4 is when $w^A$ transitions in the fault tolerant circuit, shown in case d of Figure \ref{fig:l1helper}.
+%The original circuit transitions to state $h^A(s_{k+1})$ where wire $w$ transitions.
+Thus $w$ transitions in the original circuit as seen by comparing $h^A(s_k)$ and $h^A(s_{k+1})$.  
+%applying the $h^A$ mapping to state $s_{k+1}$ indicates that $w$ transitions in the original circuit.  
+Because $w$ is excited in state $h^A(s_k)$, then the transition to the next state is a valid transition of the state graph (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and P1 holds.
 Because $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, then inputs to all logic blocks in the A-half are also semi-modularity consistent in state $s_{k+1}$ and P2 holds.
-Next we show P3 holds by looking at the single wire that changes.
-Wire $w$ fanouts to other logic blocks which may change their excitations in response to the change in wire $w$.
+Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.
+A change in wire $w$ fanouts to other logic blocks which may change their excitations in response.
 Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
@@
 \item
-For excited wires $v$ in state $h^A(s_k)$ which are also excited in state $h^A(s_{k+1})$ in the original circuit, by semi-modularity $c1^A$ of $v$ in the A-half circuit will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy P3.
+For wires $v$ that are excited in state $h^A(s_k)$ and excited in state $h^A(s_{k+1})$ in the original circuit, the wire block $v$ must be in cases 1-4 of Figure \ref{fig:l1helper} at state $s_k$.
+If $w^A$ does not feed into wire block $v$ then wire block $v$ stays in the same case in state $s_{k+1}$.
+Furthermore, if wire block $v$ is in case 1, then the inputs and $c1^A$ and $v$ wires match in the fault tolerant and original circuits, thus $c1^A$ is also excited in state $s_{k+1}$ and wire block $v$ remains in case 1.
+If wire block $v$ is in cases 2-4, then $c1^A\neq v$ and we cannot apply the same logic.
+The correct reasoning is outlined in Figure \ref{fig:sml1} and described as follows.
+Since $v$ is excited in state $h^A(s_{k+1})$, then $v$ can transition to a state $h^A(s_{k+2})$.
+Now we compare the original circuit in state $h^A(s_{k+2})$ and the fault tolerant circuit in state $s_{k+1}$.
+  The inputs of $v$ in state $h^A(s_{k+2})$ are equal to the inputs to wireblock $v$ in state $s_{k+1}$ (since $v$ is not its own input) and $c1^A=v$, therefore $c1^A$ must be unexcited in state $s_{k+1}$.
+Thus wire block $v$ stays in the same case for cases 2-4.
+We have shown for all such wires $v$, the corresponding wire block stays in the same case in the fault tolerant circuit, so P3 holds for wires of this type.
+%by semi-modularity $c1^A$ of $v$ in the A-half circuit will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy P3.
 %semi-modularity part still needs to be fixed
-\item
-By semi-modularity, the only wire in the original circuit that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (we disregard the possibility that w can be immediately excited again).
-In the A-half circuit, $w^A$ transitions so that the $w$ wire block is in state Figure \ref{fig:l1helper} e.
-Both $w$ in the original circuit is unexcited and the corresponding wire block in the A-half circuit is unexcited, thus wire $w$ satisfies P3.
-\item
-For wires $u$ that transition from unexcited in state $h^A(s_{k})$ to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in state Figure \ref{fig:l1helper} e.
-But since $u$ in the original circuit is excited in the new state and $c1^A=u$, then $c1^A$ in the A-half circuit must also be excited so that the wire block $u$ is in state Figure \ref{fig:l1helper} a.
-Thus wires of this type satisfy P3.
-\item
-Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic block is also unexcited in the A-half circuit and the wire block stays in state Figure \ref{fig:l1helper} e.
-Thus wires of this type satisfy P3.
+\begin{figure}
+  \centering
+    \includegraphics[width=\textwidth]{sml1}
+  \caption{An example of wire block $v$ in case 2.
+The firgure shows wire block $v$ in the fault tolerant circuit and wire $v$ in the original circuit in states $s_k$ and $s_{k+1}$.
+Each arrow denotes a transition}
+  \label{fig:sml1}
+\end{figure}
+\item
+By semi-modularity, if a wire is excited in state $h^A(s_{k})$ and does not transition, then it remains excited in state $h^A(s_{k+1})$.  
+Thus, the only wire that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (since $w$ is not its own input).
+  In state $s_{k+1}$, $w^A$ transitions and since $c1^A=w$, $c1^A$ remains unexcited, so wire block $w$ is in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wire $w$.  
+\item
+For wires $u$ that are unexcited in state $h^A(s_{k})$ and transition to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in case 5 of Figure \ref{fig:l1helper}.
+But since wire $u$ in the original circuit is excited in state $h^A(s_{k})$ and $c1^A=u$, then $c1^A$ is also excited in state $s_{k+1}$ and the wire block $u$ is in case 1 of Figure \ref{fig:l1helper}.
+Thus P3 holds for wires of this type.
+\item
+Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, $c1^A$ is unexcited and the wire block stays in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wires of this type. 
 \end{itemize}
@@
 This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
-Next, we examine the effects of the transitions on wire blocks $v$ where $v\neq w$ and $v$ may be in any cases of Figure \ref{fig:l21}.  
+It is also true that only wire blocks that $w^A$ and $w^B$ feed into, can change logic block excitations due to the transitions in $w^A$ and $w^B$.
+Next, we examine the effects of the transitions on wire blocks $v$ where $w$ feeds into $v$ and $v$ may be in any cases of Figure \ref{fig:l21}.  
 %The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
@@
 In state $s_k$, an output wire mismatch is possible only if the wire blocks are in cases 10a or 10b.
-Thus for all mismatched wires $u$ in state $s_k$, $c2^A=c2^B$ (${u}$ includes $v$).
-Wire $w^A$ transitioning does not change the values of those wires so in state $s_{k+1}$, wires $u$ stay mismatched and their $c2^A=c2^B$.
-In state $s_{k+1}$, there is one newly mismatched wire, $w$, which also has $c2^A=c2^B$.
+Thus for all mismatched wires $u$ in state $s_k$, $c3^A=c3^B$ (${u}$ includes $v$).
+Wire $w^A$ transitioning does not change the values of those wires so in state $s_{k+1}$, wires $u$ stay mismatched and their $c3^A=c3^B$.
+In state $s_{k+1}$, there is one newly mismatched wire, $w$, which also has $c3^A=c3^B$.
 In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
-Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal at a later state while keeping wire $v$ mismatched.
-In that later state, the excited A-half logic block of $v$ must still be excited due to semi-modularity in the original circuit.
+Then from $s_{k+1}$, we show there is a reachable state that contradicts the initial assumptions.
+We choose a sequence of transitions such that all mismatched wires except $v$ become equal.
+No other transitions occur.
+In that later state, the excited A-half logic block of $v$ is still excited due to semi-modularity in the original circuit.
 %semi-modularity...
@@
 The state for the B-half violates P3 of Lemma 1 and a contradiction is found.
-Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the logic blocks of a wire in case 10a.
-Wires in case 10b are similar.
+%may need a picture
+ Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the logic blocks of a wire in case 10a.  Wires in case 10b are similar.
 \end{itemize}
@@
 Next we consider what happens to the fault tolerant circuit under a single transient fault which is defined as follows:
-\begin{definition}A transient fault on a wire $w$ causes a transition $w= \lnot w^{prev}$.
-After this event it is assumed that the wire can freely transition based on its inputs.
+\begin{definition}A {\em transient fault} on a wire $w$ causes a transition $w= \lnot w^{prev}$.
+After this event, the wire can freely transition based on its inputs.
 %do I need to talk about when transient is not ~x?
@@
 \end{definition}
+\begin{figure}
+  \centering
+    \includegraphics[width=\textwidth]{faultexes}
+  \caption{Effects of a transient fault.  The left most figure is the state right before a transient fault occurs.  The transition due to the transient fault is denoted by the red F and arrow.   \\
+  a) An AND gate, the transient fault causes a transition in $w$ to 0 but the inputs resurrect it back to 1 sometime later.   \\
+  b) An AND gate that is excited before the transient fault.  The transient fault causes a transition that would happen anyway, $w$ stays at the correct value 1 after the transition.\\
+  c) A C-element.  Its inputs are mismatched so the gate is in a hold state.  When the transient fault causes a transition to 0, the faulty 0 value may persist.
+  }
+  \label{fig:faultx}
+\end{figure}
+Examples of the transient fault occuring to gates in different states are shown in Figure \ref{fig:faultx}.
+Depending on the inputs and the specific gate, the transient fault can cause a transition to a faulty value and transition back to the previous value; or it can cause a transition that would happen anyway and thus do not affect the gate/ circuit; or the faulty value may be stored in memory elements like the C-element in the hold state.
+
+%new 4/30
+We also want to define a faulty trace, which is the trace of a circuit that has a single transient fault.  Formally, the definition is as follows:
+\begin{definition}
+A {\em faulty trace} is a trace of the circuit where at some state $n$, a transient fault replaces the transition from $s_n$ to $s_{n+1}$.  The circuit continues to transition from $s_{n+1}$.   
+%there exists an $n$ where $\sigma_n$ is a prefix of a trace of the fault free circuit, then the $n+1$st transition is a transient fault.  After the fault occurs, the circuit continues to transition .
+\end{definition}
+Transitions after the fault is based on circuit rules and not necessarily the state graph.
+To see this, note that the state graph does not necessarily include all possible states of the circuit.
+The circuit synthesis technique is designed such that if the circuit is in a state of the state graph, the circuit follows the state graph.
+However, a fault may cause $s_{n+1}$ to be in a previously unreachable state.
+Then the transitions are governed by the circuit rules of the gates that make up the circuit.\\ %end new
+
 Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
@@
 \begin{lemma}[3]
-For any trace $\sigma$ in the duplicated circuit, if a single transient fault occur on wire $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For any trace $\sigma$ in the duplicated circuit, if a single transient fault occur on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 \end{lemma}
@@
 
+Thus we have shown that under a single transient fault that the transformed circuit has a half that behaves like the original circuit and the transformation is a fault tolerant transformation.
+
+\chapter{Conclusions}
+In this work, we have proposed a fault tolerant circuit transformation of asynchronous control circuits using duplication and a chain of C-elements.
+This is more transistor efficient than TMR and the doubled inputs duplication approaches.
+We also proposed a method of comparing the fault tolerant circuit with the original circuit, by comparing traces with the half circuit.
+And finally we showed the transformation of the circuit makes it fault tolerat to transient faults at the gate level implementation of the asynchronous circuit\\
+
+Some limitations of this work are that we assume multiple SEUs cannot occur simultaneously, in general.
+(It is ok if the faults are only in the c2 and c3 wires, or all faults are in one half).
+We also assume outputs of C-elements are always 0 or 1 even if one signal may be faulty.
+And we also limit our circuit model to semi-modular control circuits.\\
+
+Some future work to extend this model would be to allow for arbiters, mutual exclusion elements by making them transient fault tolerant as well.
+We can also extend fault tolerance to permanent faults, we have an initial idea of adding a timer and restart mechanism to get past the deadlock that accompanies permanent faults.
+
 \bibliography{biblio}

### 2019-07-04 draft_together.tex
before major revision

--- 2019-04-28 draft_together3.tex
@@
 \chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
-\chaptermark{Fault Tolerant Circuit}
-\section{Traces and circuit equivalence}
-We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
-Due to the asynchronous nature of how signals are processed, corresponding wires in the resulting half circuits may have different values.
-To solve this problem we add C-elements to synchronize the two versions of the same signal.
-An example of this transformation applied to the simple inverter circuit is shown in figure \ref{fig:dupschemeex}.
-Both the duplication and the additional C-elements configuration are shown.
-In the rest of this chapter we define a way to compare two circuits and to show their equivalence.
-Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.
-Finally we show that if a single transient fault occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
-\begin{figure}
-  \centering
-    \includegraphics[width=.9\textwidth]{transf3Csimp}
-  \caption{a) original circuit b) after the fault tolerant transformation}
-  \label{fig:dupschemeex}
-\end{figure}
-
-Other than the basic terminology for asynchronous circuits, we also want terminology to compare two circuits based on their function.  
-We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.
-Different paths can occur because there may be multiple transitions from each state.
-We call the succession of states and transitions the trace which is defined as follows:
-\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.
-%Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
- Also every pair of consecutive states in a trace are transitions% such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$
- .  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
-Thus a circuit has a set of traces.  
-A circuit also has a set of initial states where the traces can begin in.  The set of initial states are the same as the set of states in the state graph.\\
-
-%Note that our definition of trace also includes the case where there is only one transition from each state of a state graph, which results in a linear state graph.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=.6\textwidth]{sm_counter2}
-  \caption{a) original circuit for wire w b) an erroneous initialization}
-  \label{fig:sm_counter2}
-\end{figure}
-
-The original circuit is semi-modular by design.
-But the design only covers cases where the wires are in a state in the state graph.
-That is, hazards may occur if the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.
-This does not happen in the fault-free case where the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
-However when faults do occur, the circuit may become unpredictable and a reason why we need to transform the circuit to protect against faults.
-An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
-The logic circuit for wire $w$ is taken out of a semi-modular circuit.
-However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not semi-modularity consistent.
-The output wire $w$ is excited to 1 while the inputs from $x,y,z$ will cause $w$ to transition to 0.
-Depending on the timing of the gates, $w$ may stay at 0 or experience a glitch to 1 then back to 0.
-The extra layers of gates in the logic block can be thought of as extra delays that can store and propagate the wrong values.
-More detailed discussion on how to initialize and keep the circuit semi-modular is explored in the subsequent section.\\
-
-Given two circuits, how can we determine when their basic functionality is the same, especially if they are implemented with different gates and circuit elements?
-We define a notion of equivalence between two circuits through their sets of traces.
-%We want the underlying state graph representation of the circuits to be equivalent.
-However only the signals and the sequence of transitions from the circuit is observable.
-In other words the trace is observable.
-Thus we define circuits as equivalent if the set of traces of the two circuits are the same.
-[We use the assumption that if the set of traces are equal then the state graph is equal.]
-\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B.
-In other words, $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
+\section{Normal operation analysis}
+As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
+As the circuit follows the state graph, there may be multiple transitions per state and each path through the states and transitions may be different.
+We want to record the succession of states and transitions and so we define a trace as follows:
+\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $\sigma_i$ is the $i^{th}$ term of the sequence.
+$\sigma: \mathbb{N} \to S$ and $T(\sigma_i,\sigma_{i+1})$ for $\forall i \in \mathbb{N}$.\end{definition}
+%add finite traces
+% all states or just the state graph ones
+
+We want to define a notion of equivalence between two cicrcuits.
+What we observe are the succession of signals which form the trace.
+Thus we define circuits as equivalent if the traces are the same.
+\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
 \end{definition}
-
-We are now ready to explore how to make a circuit fault-tolerant.
-%good enough for now, do I need if and only if? <-NO, xxx if xxx in math lingo is iff
+%good enough for now, do I need if and only if?
 
@@
 If inputs to the gate remain constant, the output $v$ will eventually take the value specified by $f_v(s|_I)$  %maybe change v again, also the f(s) vs f(I) thing...
-\section{Fault Tolerant transformation}
-
-We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in figure \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
-We also label the duplicated logic blocks as belonging to circuit A or circuit B in agreement to the wire naming.
-Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.
-We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ for circuit A and $c1^B$, $c2^B$, $c3^B$ for circuit B.
-In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and inputs to two C-elements outputting $c2^A$ and $c2^B$.
-These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.
-These are then the inputs to the third layer of C-elements outputting $w^A$ and $w^B$.
-We can label one of the final C-element outputs as $w^A$ and the other output as $w^B$.
-These then connect to other logic blocks in circuit A and circuit B respectively.
-Note that when labelling the C-elements and its outputs, which side is A and B can be somewhat arbitrary because the output pairs are symmetric.
-The symmetry is broken when connecting the final output wire $w^A$ to all the circuit A gate inputs and wire $w^B$ to all the circuit B gate inputs.
-All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
+
+We make a fault tolerant circuit by the following circuit transformation: make a duplicate copy of the logic blocks to each wire.
+We label the duplicated circuit halves as circuit A and circuit B.
+Then for each output wire $w$ we connect the output of the logic blocks from each circuit half to three layers of c-elements as shown in figure \ref{fig:dupscheme}.
+We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ and $c1^B$, $c2^B$, $c3^B$ for circuits A and B respectively.
+In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements producing $c2^A$ and $c2^B$.
+These are then the inputs to the second layer of C-elements producing $c3^A$ and $c3^B$.
+These are then the inputs to the third layer of C-elements producing $w^A$ and $w^B$.
+We can (arbitrarily) label one of the final C-element outputs as $w^A$ and the other output as $w^B$.
+These then connect to other gates in circuit A and circuit B respectively.
+(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
 all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
@@
     \includegraphics[width=\textwidth]{circuitforproof3}
-  \caption{Fault tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
+  \caption{Duplicating the original logic for each output wire and adding 3 layers of C-elements}
   \label{fig:dupscheme}
@@
 
-We want to show that a half circuit from the fault tolerant circuit has correct function.
-To do this, we define a correspondence between states of the original circuit and states of the fault tolerant circuit.
-As a result of the circuit transformation, a state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
-Half of those bits are obviously from the A half and half are from the B half of the circuit.
-The state graph for a fault tolerant circuit is defined on this combined state.
-We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
-The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.
-The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are hidden by $h^A$ or $h^B$.
-We extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.
+Because the transformed circuit has some extra wires, we want to define a correspondence to be able to compare between the wires of the original circuit and that of the duplicated circuit halves.
+For the duplicated circuit, a combined state is the pairing of the state of circuit A and the state of circuit B.
+It has eight times the number of wires for each output wire in the original circuit.
+The state graph for a duplicated circuit is defined on this combined state.
+We define the half-circuit mapping $h^A: s^{full} \to s^A$ where $s^{full}$ is the combined state of a duplicated circuit and $s^A$ are made up of the wires $w^A$ that correspond to the original wires $w$.
+The half-circuit mapping $h^B$ is similarly defined to map to $s^B$.
+Note that the $h(\sigma)$ mappings are overloaded for a trace, where it outputs a mapped state for each of the states in a trace.
 %not sure if I want the mapping to be from variable to variable or specific state to state
-%For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
-The resulting trace may have successive repeated states.
-So we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.
-The result should be a trace from the original circuit.
- Using this mapping we will show that the original circuit is equivalent to half of the fault tolerant circuit in both the absence and presence of a single transient fault.
-%do I need to define all the new transitions in duplicated circuit?  maybe
-\\
-
-%[Why is this the best we can do?]
-We compare each half circuit because it is not easy to synchronize and compare the signals between both halves, especially if we reuse the logic blocks from the original circuit.
-A simple idea we tried was to insert another C-element before the input is fed into the logic, to synchronize the wires on both halves.
-The problem with that is in the original circuit, a wire value change propagates to all inputs at the same time.
-Adding another layer of C-elements creates delays at the input to logic blocks and the isochronic fork assumption is violated.
-Thus the resulting circuit will not function according to the specified state graph.
-(an example can be provided but not sure if needed?)\\
-\begin{figure}
-  \centering
-    \includegraphics[width=.8\textwidth]{counterexhalf}
-  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault tolerant circuit}
-  \label{fig:counterexhalf}
-\end{figure}
-
-Next we look at the traces of each half circuit.
-Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where each state is given a nominal name (state 0, state 1, ...
-etc) and each transition is labeled with the transitioning wire.
-Suppose we apply our fault tolerant transformation to such a circuit based on this state graph.
-Both halves in the fault tolerant circuit will transition based on this state graph, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
-Starting in {\em state 0}, it is possible for the A-half to transition to {\em state 1} ($a^A$ transitions) and for the B-half to transition to {\em state 2} ($c^A$ transitions).
-We assume that $a^B$ and $c^A$ do not complete their transitions yet.
-Immediately, in the A-half, $b^A$ is excited and in the B-half, $b^B$ is excited.
-Then, suppose the transition on wire $b^A$ and $b^B$ occurs.
-That is, the A-half transitions to {\em state 3} and the B-half transitions to {\em state 5}.
-And finally, the excited $a^B$ and $c^A$ transitions so that both halves are in {\em state 6}.
-The trace so far for the A-half is (state 0, state 1, state 3, state 6) while for the B-half it is (state 0, state 2, state 5, state 6).
-Thus the two halves need not have the same trace.
-One criticism may be that the current fault tolerant transformation synchronizes at the outputs of the logic blocks.
-If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
-We have already shown earlier that synchronizing the input signals while keeping the original logic block can also result in error.
-This points to looking at properties of each half circuit as the right thing to do.\\
-
-Another wrong approach for the fault tolerant transformation is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.
-We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.
-Following the same transitions outlined above, $b^A$ and $b^B$ can finish their transitions before $a^B$ and $c^A$ transitions.
-Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined trace no longer maps back to a valid trace in the original state graph.
-Another approach we may take is to record the first transition of a wire in either half of the fault tolerant circuit.
-For example, if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.
-This approach ensures the resulting trace is a trace in the original circuit (can be shown by Lemma 1 and Lemma 2.1 in the next section), however, in the presence of faults, it is easy to see that it does not provide any fault tolerance.\\
-
-For the aforementioned reasons, we choose to use the $h^A$ and $h^B$ mappings and compare each half circuit against the original circuit.
-Out of the various comparisons methods and circuit transformations that we tried, it is the most reasonable and results in some nice properties.
-We will next demonstrate that the half circuits are equivalent to the original circuit in the absence of faults.
-Then we show that a similar property is true even when a single fault may occur.
-
-\section{Normal operation analysis}
-To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.
-That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
-And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.
-We show this through several Lemmas.
-Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.
-This is a strong result; it is true for arbitrary behavior of
-signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
-This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
-%One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
-\\
-
-Note that Lemma 1 allows for the possiblity of deadlock.
-Lemma 2 shows deadlock does not occur during normal operation.
-Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
-% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
-%[so no deadlock in normal operation??]
-
-Now we will discuss the proper wire initializations before going into the Lemmas.
-In normal operation, the fault tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.
-This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault tolerant circuit.
-The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.
-This arises from the original synthesis method to synthesize the circuit from an underlying state graph.
-Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.
-The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.
-Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
-%maybe needs an example
-Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.
-Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions.
+For a trace in the duplicated circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit).
+The resulting trace may have successive repeated states and we delete the repeats to obtain a valid trace on the shortened wires.
+%do I need to define all the new transitions in duplicated circuit?
+maybe
+\\
+
+We want to show this circuit behaves similar to the original circuit under normal operation.
+In other words we want to prove that after applying either mapping of $h^A$ or $h^B$, the resultant circuit and the original circuit are equivalent.
+We first prove lemma 1 which states for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs in the original circuit.
+However this does not guarantee that such a transition always exists so we also need to prove lemma 2 to show that a transition always exists and the circuit cannot deadlock.
+These two properties combined together show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
+
+Note that there are some extra wires in the logic blocks in both the original and duplicated circuit.
+We actually don't worry about the exact values of these wires other than that if the inputs follow Semi-Modularity then the logic block as an entirety behaves with Semi-Modularity (as long as it is initialized appropriately).
+Here it does not suffice for the inputs to be a sequence of valid states and state transitions in the state graph.
+This is because the Semi-Modularity property of the logic block is that if the logic block output is excited then it must remain excited until a transition occurs.
+Since certain inputs, even if they are valid states, may cause the logic block to become unexcited before a transition occurs, we want a more stringent criteria.
+The inputs must uphold the Semi-Modularity property which waits at certain input states until the output transitions, in addition to being valid states and state transitions from the state graph.
+Then if the wires within the logic block is consistent with Semi-Modularity, that is if the inputs follow Semi-Modularity then there are no glitches at the output and if the output is excited it remains excited until the output changes.
 \\%newly added
 
-What values to initialize the wires of a circuit to is very important.
-We want certain properties to hold for all states that the circuit goes through, and such properties must also hold for the initial state.
-On one hand, the initial state $s$ must be a state in the underlying state graph.
-Thus the wire values is initialized to be consistent with that property.
-On the other hand, as mentioned previously, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.
-We assume that we can initialize the wire values of the original circuit to satisfy these two properties.
-Given this, we pick convenient initializations for the fault tolerant circuit.
-The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
-%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
+The initial state in the original circuit must be assigned wire values that is consistent with Semi-Modularity.
+For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
 The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s.
@@
 %should I delete intermediate?
-\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed from an initial state of the original circuit.
-The wire values in the logic block and $w$ in the original circuit are copied to the corresponding wires in the A half.
-The additional wires from the C-element chain are also assigned the same value as $w$.
-That is, first assign to $w^A$ the value of $w$, then assign to $c1^A$ $c2^A$ $c3^A$ the value of $w^A$ as well.
-The same construction applies for the B half circuit as well.
+\begin{definition} A {\em valid initial state} for the A half of a duplicated circuit is defined as follows.
+Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the Semi-Modularity property.
+Assign the wire values within the logic block to corresponding wires in the half duplicated circuit.
+Then assign the value $w$ to corresponding wires in the half duplicated circuit so that $w=c1^A=c2^A=c3^A=w^A$.
+The same assignment of wire values can also be applied for the B half of a duplicated circuit.
 \end{definition}
 %\textbf{
-This definition is stronger than it needs to be but is convenient.\\
-
-%To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
-One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.\\
-%For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.
+For all subsequent discussion in this document, when we talk about the trace of a duplicated circuit we assume that both sides start from the same valid initial state.
 I will not include this assumption in the following lemma definitions to avoid complicated wording.
 %}
-%The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\
-
-This leads to the definition and proof of Lemma 1 as follows:
+However for Lemma 1 we only require one half to start from a valid initial state.  
+One additional assumption we make about the gates and wire values (including in the presence of faults) are that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the incoming wires.\\
 
 \begin{lemma}[1]
-If $\sigma$ is the trace of the fault tolerant circuit where the A half begins in a valid initial state and is fault free, then the following three properties are true:
-\begin{itemize}
-\item P1: The half-circuit mapping of a prefix of $\sigma$, $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit, regardless of the wire values in the B half.
-\item P2: The logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
-\item P3: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
-(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
-\end{itemize}
-
-%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).
+Let $\sigma_n$ be the sequence of the first n states of a trace $\sigma$ in the duplicated circuit (the trace is possibly finite).
+The duplicated circuit has two half circuits $A$ or $B$, if a trace $\sigma$ starts from a valid initial state in the half circuit A, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit.
+Also if a trace starts from a valid initial state in the half circuit B, then $h^{B}(\sigma_n)$ is a prefix of a trace of the original circuit.
 
@@
 \end{lemma}
-
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of fault tolerant circuit.
-We will show that for every prefix $\sigma_n$ of length $n$, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit, by induction on $n$.
+Without loss of generality we prove that this property holds for the A half of the circuit, the same reasoning can then be applied to the B half of the circuit.
+We prove this lemma by induction on all traces of the circuit of length $n$.
+The induction hypothesis is
+\begin{itemize}
+\item For a length $n$ sequence $\sigma_n$ in the duplicated circuit, this maps to $h^{A}(\sigma_n)$, a prefix of a trace of the original circuit.
+\item Every logic block is in a Semi-Modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
+\item In every state $s_k$ of $\sigma_n$ it is true that a wire $w$ in the original circuit of state $h^A(s_k)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).
+The case where two or more of the three conditions being true does not exist in this setting.
+As a consequence a wire $w$ is unexcited if and only if none of the previous three conditions are true.
+\\
+Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned....
+forget if I explained or not
+\end{itemize}
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show the induction hypotheses hold in the base case $sigma_1$ consisting of state $s_1$, a valid initial state.
+We show in the base case that the induction hypotheses holds for any valid initial state (ie. all possible traces of length 1). 
 \begin{itemize}
-\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.
-Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit and P1 holds.
-\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state and P2 holds.
-\item 
-For any wire, $c1^A$, $c2^A$, $c3^A$ and $w^A$ are assigned the same values by the valid initial state.
-Thus any excitations must be on $c1^A$.
-Since the wires that inputs into all logic blocks have the same values in the original and fault tolerant circuit, and the logic blocks are in semi-modularity consistent states then if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault tolerant circuit.
-Similarly if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault tolerant circuit.
-This shows the valid initial state satisfies P3.    %is this enough.... that the existing states follow that iff statement?
+\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit from its construction.
+Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.
+\item We assigned the wire values so that the logic blocks are in a Semi-Modularity consistent state.  
+\item For any wire $w$, since the input wire values are identical in the original circuit and the duplicated half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit (the logic block output is excited).
+Together with the definition of the valid initial state $c1^A=c2^A=c3^A=w^A$ (no excitations within the C-element chain), if $w$ is excited in $h^A(s_k)$, then only $c1^A$ is excited.
+Conversely if $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$ then $w$ is excited in $h^A(s_k)$.
+All C-element chains in the duplicated have at most one wire in the chain excited.
+This shows the initial state also satisfies the last part of the induction hypothesis.
+%is this enough....
+that the existing states follow that iff statement?
 \end{itemize}
 
-The induction step is to assume that the induction hypotheses is true for $\sigma_k$.
+The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the sequence of the first $k$ states in a trace (for traces length greater than or equal to $k$).
 We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
-In particular for all possible next states from the current state $s_k$, we show that either the output wires have not transitioned, or in the case of a transition that it is also a transition of the original circuit.
-Then we show that the logic blocks in all possible next states remain in a semi-modularity consistent state.
-And finally that P3 is true and all wire blocks in the next states are in one of the cases in figure \ref{fig:l1helper}.\\
-
-From state $s_k$, we look at all possible transitions; a transition may occur on excited gates or c-elements.
-Transitions in the B-half do not change wire values in the A-half and can be ignored.
-Thus we only need to consider the wires that may change in the A-half circuit which by P3 can only occur in the wire blocks of wires that are excited in the original circuit in state $h^A(s_k)$.
-For each excited wire block $w$, %need to define wire block
-P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
+In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.
+Then we show that for all possible $s_{k+1}$ logic block remains in a Semi-Modularity consistent state.
+Finally for all wires in $s_{k+1}$, the second induction hypothesis is true.\\
+
+From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.
+If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.
+Thus we only need to consider the wires $w$ which are excited in the original circuit in $h^A(s_k)$ and its corresponding wires in the A-half $s_k$.
+For each excited wire $w$, the last induction hypothesis narrows the possible cases and we examine the next state if a transition occurs in each case.
 %logic gate excited = c1^A excited
-%possibly add graph to illustrate this
-\begin{figure}
-  \centering
-    \includegraphics[width=\textwidth]{gatewl1}
-  \caption{Different cases of the induction step for proving Lemma 1.  a) case 1, b) case 2, c) case 3, d) case 4}
-  \label{fig:l1helper}
-\end{figure}
-
 \begin{itemize}
-\item We consider cases 1-3 together (a-c in Figure \ref{fig:l1helper}) for some excited wire $w$ in the original circuit.
-For each case, it is clear that in the fault tolerant circuit, the transition propagates down the C-element chain as shown in the figure.
-Then P3 holds for wire $w$.
-For all other output wires, P3 also holds because the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$, so the input into the logic blocks do not change and thus excitation of all wires in the original circuit do not change in the next state.
-The state of the corresponding wire blocks in the fault tolerant circuit also do not change in the next state.
-Thus P3 holds for all wires in the next state.
-Another consequence of $h^A(s_{k+1})=h^A(s_k)$ is that P1 holds.
-And lastly no output wire transitions implies the logic blocks stay in a semi-modularity consistent state so that P2 holds.
-
-%\item The first case is for an excited wire $w$.
-In the fault tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
-Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.
-Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and unexcited wires, the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.
+\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
+Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, which satisfies the third induction hypothesis for wire $w$.
+Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.
 Thus the third induction hypothesis is true for all output wires.
 Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.
-The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.
+The output wires which are also inputs to logic blocks did not change so the logic blocks are in a Semi-Modularity consistent state.
 The induction hypotheses are true for any transition from this case.
@@
 %$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
-%\item The second case is when the signal propagates down to $c2^A$.
-In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.
-Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
-This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
-%\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.
+\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
+Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus the third induction hypothesis is true for wire $w$.
+This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.
+\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.
 In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.
-%Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.
-This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.
-
-\item Case 4 is when the transition propagates down to $w^A$ in the fault tolerant circuit as shown in Figure \ref{fig:l1helper} d.
-This corresponds to $w$ transitioning in the original circuit, and because $w$ is excited in state $h^A(s_k)$ then the transition to the next state is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and P1 holds.
-Because $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, then inputs to all logic blocks in the A-half are also semi-modularity consistent in state $s_{k+1}$ and P2 holds.
-Next we show P3 holds by looking at the single wire that changes.
-Wire $w$ fanouts to other logic blocks which may change their excitations in response to the change in wire $w$.
-Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
-%these are the only possibilities in the original... look at what happens to these wires in the FT circuit
+Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus the third induction hypothesis is true for wire $w$.
+This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.
+
+\item The fourth case is when the signal propapagates down to $w^A$.
+In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.
+Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.
+Also since $h^A(s_{k+1})$ is a valid state in the original Semi-Modular circuit and the A-half logic blocks at state $s_k$ are Semi-Modularity consistent, inputs to all logic blocks in the A-half are also Semi-Modularity consistent.
+Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.
+(excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by Semi-Modularity)
 \begin{itemize}
 \item
-For excited wires $v$ in state $h^A(s_k)$ which are also excited in state $h^A(s_{k+1})$ in the original circuit, by semi-modularity $c1^A$ of $v$ in the A-half circuit will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy P3.
-%semi-modularity part still needs to be fixed
-\item
-By semi-modularity, the only wire in the original circuit that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (we disregard the possibility that w can be immediately excited again).
-In the A-half circuit, $w^A$ transitions so that the $w$ wire block is in state Figure \ref{fig:l1helper} e.
-Both $w$ in the original circuit is unexcited and the corresponding wire block in the A-half circuit is unexcited, thus wire $w$ satisfies P3.
-\item
-For wires $u$ that transition from unexcited in state $h^A(s_{k})$ to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in state Figure \ref{fig:l1helper} e.
-But since $u$ in the original circuit is excited in the new state and $c1^A=u$, then $c1^A$ in the A-half circuit must also be excited so that the wire block $u$ is in state Figure \ref{fig:l1helper} a.
-Thus wires of this type satisfy P3.
-\item
-Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic block is also unexcited in the A-half circuit and the wire block stays in state Figure \ref{fig:l1helper} e.
-Thus wires of this type satisfy P3.
+$w$ is unexcited in state $h^A(s_{k+1})$ (if we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.
+Since $w$ is now unexcited, wire $w$ does not contradict the third induction hypothesis.
+\item
+For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by Semi-Modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.
+Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, this does not contradict the third induction hypothesis.
+\item
+For all newly excited wires $u$ in $h^A(s_{k+1})$, that is not excited in $h^A(s_k)$, then in states $s_{k}$ and $s_{k+1}$,  $c1^A=c2^A=u^A$.
+But since $u$ is excited then $c1^A$ of $u$ is excited.
+Thus the third induction hypothesis holds for these wires $u$ as well.
+\item
+Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, logic gate is not excited and $c1^A=c2^A=c3^A=u^A$ and the third induction hypothesis holds for these wires.
 \end{itemize}
@@
 \end{proof}
-By symmetry this is also true for the B half if we exchange A and B in the statement of Lemma 1.  
-Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g.
+
+Note that the previous proof does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g.
 does not cause hazards in the C-element output).
 Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.
-It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1
-
-This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transition in a completely predictable pattern and thus deadlock does not occur.
-To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
-One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.
+It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.
+Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.
 
@@
 \begin{lemma}[2.1]
-For any trace of the fault tolerant circuit, each wire block follow the state diagram in Figure \ref{fig:l21} (up to 0 and 1 inversion).
+For all traces $\sigma$ in the duplicated circuit (for both halves starting in the same valid initial state), for any state in a trace, all wire blocks are in one of the cases in figure \ref{fig:l21}.
 \end{lemma}
 \begin{proof}
-We show this lemma by induction.
-The state diagram in Figure \ref{fig:l21} is incomplete in the sense that after case 11, there are more transitions.
-However, case 11 is symmetric to case 1 with only the 0's and 1's inverted and so the transitions from case 11 is also symmetric to the transitions from case 1 with 0's and 1's inverted until it loops back to case 1.
-Because of this symmetry, we only need to analyze possible transitions from each case up to case 10.
-Also, Lemma 1 applies to both A half and B half which we will use in the body of this proof.\\
-
-We look at the base case of $\sigma_1$ which is also $s_1$ initialized as a valid initial state.
-For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
-Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault tolerant circuit are in case 2 of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
-Thus the lemma property holds for the base case.
-\\
-%is this the pick a trace thing again? (instead of for all traces of length n)
-
-In the induction step, assume that the induction hypothesis is true for trace $\sigma_k$ and we show that it is true for $\sigma_{k+1}$ by looking at state $s_k$.  \\
-
-In state $s_k$, all wire blocks are in a case in the state diagram from the induction hypothesis.
-It is easy to see that the only possible wire transitions in state $s_k$ are the transitions (black arrows) in the state diagram.
-%In addition, if $w$ is the transitioning wire block then because $w$ does not feedback to itself and the input wires do not transition, the logic blocks do not change excitations (other than when $c1$ transitions).
-Thus the black arrows show the only possible transitions in the state diagram from state $s_k$.
-For each transition, we must verify that all wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
-Thus we need to investigate the changes in the wire block that transitions as well as the transition's effects on all other wire blocks.
-%For all possible transitions from $s_k$, we must verify that wire blocks in the new state $s_{k+1}$ either remain in the same case or transition according to the state diagram in Figure \ref{fig:l21}.
-It is easy to see that the transitions (black arrows) in the figure are the only possible wire transitions when the wire blocks are in a case in the state diagram.
-Thus we need to investigate the state changes when a wire block transitions as well as the transition's effects on all other wire blocks.
-
-%It is clear that transitions and logic block changes in the state diagram can occur.
-Furthermore, we can easily verify that the wires in the C-element chains ($c1$, $c2$, $c3$, $w$) behave as the arrows indicate with no additional possibilities.
-Thus we need to show that no additional changes in the logic blocks can occur.
-%Because the arrows do not always indicate wire transitions (some are changes in excitation of the logic blocks which are in response to transitions of other output wires), we need only to verify for the transitions that do occur (black arrows), that they do not cause the other logic blocks (and itself) to behave inappropriately.
+We show by induction that for the duplicated circuit, each wire block will be in one of the cases in the above figure.
+The figure halves the number of cases, case 11 is the inversion of case 1 (the 0's and 1's inverted) and after case 11 the state transition goes through the second half of the cases with figure \ref{fig:l21} inverted.
+Thus we only need to analyze up to case 10.
+Because both halves satisfy the conditions of lemma 1, those properties can be applied directly.\\
+
+We look at the base case for every wire $w$ in the original circuit.
+Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.
+A wire $w$ can be either excited or unexcited in the original circuit.
+If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).
+If $w$ is excited then applying lemma 1 the logic blocks must be excited which is case 2.
+Thus this property is true for the base case.
+\\
+
+In the induction step, assume that the induction hypothesis is true for state $s_k$ and show it is true for $s_{k+1}$.  \\
+
+We examine all possible $s_{k+1}$.
+That is for all possible transitions from $s_k$, verify that each $s_{k+1}$ has output wire blocks that is in one of the cases in the above figure.
+It is clear that the arrows point to next cases which can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires within the C-elements are self-contained.
+Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.
 \begin{itemize}
-%\item
-%Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
-\item
-Cases $2a\rightarrow 3a$, $2b\rightarrow 3c$, $3b\rightarrow 4a$, $3b\rightarrow 4b$, $4a\rightarrow 5$, $4b\rightarrow 5$, $5\rightarrow 6a$, $5\rightarrow 6b$, $6a\rightarrow 7$, $6b\rightarrow 7$, $7\rightarrow 8a$, $7\rightarrow 8b$, $8a\rightarrow 9$, $8b\rightarrow 9$: \\
-Let the transition be on wire block $w$.  The transition is on an intermediate wire so the logic blocks of $w$ do not change excitations other than when $c1$ transitions.  
-For the same reason, the transition does not affect the excitations in logic blocks of wire blocks other than $w$, thus those wire blocks stay in the same state in $s_{k+1}$.  
-%In case 2a, when $c1^A$ transitions, 
-%It is also possible that the unexcited logic block becomes excited and go to case 3b at the next state.
-However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
-Case 2b is similar.
-%\item
-%Case 3a/3b/3c:  In case 3a, it is possible for the logic block in B-half to become excited, and change to 4a.
-The logic block in A-half cannot be excited again while $c1^A=1$ because that violates Lemma 1.
-Case 3c is similar to 3a.
-From case 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
-The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.
-%\item
-%Case 4a/4b:
-%In case 4a, the logic block in B-half is excited and can transition to case 5.
-The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as the above cases (Lemma 1).
-Case 4b is similar.
-%\item
+\item
+Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
+\item
+Case 2a/2b:  In case 2a, $c1^A$ is excited and can transition to case 3a.
+Similarly case 2b can transition to case 3c.
+From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.
+However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to Semi-Modularity and lemma 1.
+\item
+Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).
+The logic block in A-half (B-half) cannot be excited again with $c1^A=1$ ($c1^B=1$) because that violates lemma 1.
+From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
+The excited logic blocks cannot become unexcited due to Semi-Modularity and lemma 1.
+\item
+Case 4a/4b:
+The excited logic block in both cases can transition and end up in case 5.
+The excited logic block cannot become unexcited due to Semi-Modularity and lemma 1.
+The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
+\item
 %Case 3a/3b:   If a transition occurs in these cases for wire block $w$, the only excited wires are $c1^{B}$ or $c1^{A}$ respectively.
@@
 \\
-%Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in figure \ref{fig:l21}.
-The only possible additional transitions would come from the logic block but we know that the already transitioned logic block cannot be excited again by Lemma 1.
-\item
-Cases $9\rightarrow10a$, $9\rightarrow10b$, $10a\rightarrow11$, $10b\rightarrow11$:  \\
-Again let the transition be in wire block $w$.
-The transition is on an output wire which can change logic block excitations.
-We first show that the logic blocks are not excited in wire block $w$ itself after the transition.
-This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
-Next, we examine the effects of the transitions on wire blocks $v$ where $v\neq w$ and $v$ may be in any cases of Figure \ref{fig:l21}.  
-%The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
-A similar reasoning can be applied to case 9.
-By Lemma 1, if any wire blocks are in case 9 and the transition is not in this wire block, then its logic blocks cannot change excitations.
-Wire blocks in cases 10a/10b are tricky because we must use a different technique to show that the logic blocks cannot be excited because half of the circuit has completed its transitions.
-%Wire blocks in cases 10a/10b are tricky because we cannot directly apply Lemma 1 on the half that has completed its transition to show that its logic block cannot be excited.
-%In cases 1-8a/8b, all transitions happen on intermediate wires so the other wires blocks stay in their previous states.  
-\begin{itemize}
-\item
-If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three: each half has either an excited logic block and excited wire block, unexcited logic block and excited wire block, or unexcited logic block and unexcited wire block.
-For excited logic block and excited wire block (e.g., A-half in case 2a), the new transition cannot cause the excited logic block to become unexcited as it would violate semi-modularity in the original circuit.
-For unexcited logic block and excited wire block (e.g., A-half in case 4a), the transition also cannot excite the logic block as it would violate P3 in Lemma 1.
-It is possible for unexcited logic blocks with unexcited wire blocks to become excited (e.g., both A and B-half in case 1); all such case changes are covered by the blue arrows.
-Thus we have shown that for $v$ in cases 1-8a/8b, changes in $v$ caused by a transition in $w$ follow the state diagram.
-%Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
-\item
-Next we show that a transition in $w$ does not change excitations in logic blocks of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
-First we assume that wire block $v$ is in case 10a, and that the $w^A$ transition excites the A-half of the logic block of $v$ in state $s_{k+1}$.
-The $w^B$ transition can be ignored because the logic block in the B-half of $v$ cannot be excited as it would violate P3 in Lemma 1.
-In state $s_k$, an output wire mismatch is possible only if the wire blocks are in cases 10a or 10b.
-Thus for all mismatched wires $u$ in state $s_k$, $c2^A=c2^B$ (${u}$ includes $v$).
-Wire $w^A$ transitioning does not change the values of those wires so in state $s_{k+1}$, wires $u$ stay mismatched and their $c2^A=c2^B$.
-In state $s_{k+1}$, there is one newly mismatched wire, $w$, which also has $c2^A=c2^B$.
-In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
-Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal at a later state while keeping wire $v$ mismatched.
-In that later state, the excited A-half logic block of $v$ must still be excited due to semi-modularity in the original circuit.
-%semi-modularity...
-also why is A-half excited?
-Also SM
-Since the input wires on both halves of wire block $v$ are equal and $c1^A=c1^B$, then the B-half logic block must be excited too.
-The state for the B-half violates P3 of Lemma 1 and a contradiction is found.
-Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the logic blocks of a wire in case 10a.
-Wires in case 10b are similar.
-\end{itemize}
-%Lastly we also show that the logic blocks are not excited in wire block $w$ itself after the transition.
-This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
-\\
-Therefore the transitions in this case allow all wire blocks of the circuit to follow the state diagram in Figure \ref{fig:l21}.\\
-
-%We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
+Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires.
+Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.
+The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).
+\item
+Cases 9/10a/10b:  In cases 1-8a/8b all the transition happen on intermediate wires so the state of the other wire blocks must remain the same.
+In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.
+In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.
+If any logic blocks are in case 9, its logic block cannot change excitations because it would violate lemma 1.
+Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than those included in the figure.
+We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its logic block to be excited.
 For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.
 This is shown by contradiction.
-%Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
-In state $s_k$ an output wire mismatch is possible only if it is in cases 10a or 10b.
-Thus for all wires $u$ where $u^A\neq u^B$, $c2^A=c2^B$ (which includes $v$).
-$w^A$ transitioning does not change the values of those wires so the property is true in state $s_{k+1}$ as well.
-It is also true of the newly mismatched wire $w$.
-In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited.
-Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in a later state (other than wire $v$).
-In that later state, the excited logic block of $v$ must still be excited due to semi-modularity.
-Since the input wires on both halves are equal, the logic block in the other half must be excited while its output wire is excited too.
-This violates Lemma 1 and produces a contradiction.
+\\
+Assume that there exists another logic block in case 10a and that $w^A$ transition causes an excitation in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
+All wire blocks are assumed to be in cases 1-10 in state $s_k$.
+If there is an output wire mismatch such that for all wire $u\in W$ where $u^A\neq u^B$ then $c2^A=c2^B$ since it must be in cases 10a or 10b.
+This is also true for those wires in state $s_{k+1}$ and the newly mismatched wire $w$.
+Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in state $s_{k+1+m}$ (other than the one of interest).
+In $s_{k+1+m}$ the excited logic block must still be excited due to semi-modularity.
+But also the logic block in the other half must be excited since all of the input wires are equal.
+This violates lemma 1 for that half and produces a contradiction.
 Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
-%From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
-Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.
+From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
+Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires and causing a contradiction with lemma 1.
 
@@
 \end{itemize}
-This shows that all wire blocks in all possible $s_{k+1}$ follow the state diagram, and the induction step is complete.\\
-By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit follow the state diagram in Figure \ref{fig:l21} for all traces. \\
+This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
+By induction on the consecutive states of the trace, this shows that all wire blocks of a duplicated circuit are in a case in figure \ref{fig:l21} for all traces. \\
 \end{proof}
@@
 which I think I need to show the signals propagating through??
-It is now easy to show that deadlock does not occur since each wire block must be in one of the configurations of figure \ref{fig:l21}.
 \begin{lemma}[2.2]
-For all traces $\sigma$ in the fault tolerant circuit, deadlock does not occur.
+For all traces $\sigma$ in the duplicated circuit (that start in the same valid initial state), deadlock does not occur.
 \end{lemma}
 \begin{proof}
-To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the fault tolerant circuit.
-The state $s_k$ can be split into two cases, one is that all output wire pairs in the A half and B half are equal, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.
+To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the duplicated circuit.
+$s_k$ can be split into two cases, one is that for every wire block $w$ all wires in the A half and B half are equal that is $w^A=w^B$, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.
 In the first case, if every output wire pair are equal, then $h^A(s_n)=h^B(s_n)$ and there exists an excited wire $u$ in the original circuit.
-By Lemma 1 both halves of the duplicated circuit for $u$ is excited.
-By Lemma 2.1, the circuit must be in case 2-6 for $u$.
+By lemma 1 both halves of the duplicated circuit for $u$ is excited.
+By the lemma 2.1, the circuit must be in case 2-6 for $u$.
 In each of these cases at least one wire is excited.
 \\
-In the second case, for some wire $v$ such that $v^A\neq v^B$, then using Lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.
+In the second case, for some wire $v$ such that $v^A\neq v^B$, then using lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.
 Since there are next transitions for both cases, deadlock does not occur.
@@
 
-Combining the results of the previous Lemmas shows that the fault tolerant circuit is equivalent to the original circuit under normal operation.  This is defined formally in a theorem as follows:
+Combining the results of the previous lemmas yield the following result:
 \begin{theorem}[1]
-For all traces $\sigma$ in the fault tolerant circuit, $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the duplicated circuit starting from valid initial states, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
 \end{theorem}
-\begin{proof}
-Apply Lemma 1 then $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace.  From Lemma 2.2, no deadlock occurs so it is true for all $n\in \mathbb{N}$.
-\end{proof}
+
 %with these 3 properties show the original claim
@@
 %fix this
-Next we consider what happens to the fault tolerant circuit under a single transient fault which is defined as follows:
-\begin{definition}A transient fault on a wire $w$ causes a transition $w= \lnot w^{prev}$.
-After this event it is assumed that the wire can freely transition based on its inputs.
+\begin{definition}A transient fault on a wire $x$ can happen so that from the start of the transient fault $x= \lnot x^{init}$.
+At some time later, the wire is able to transition again based on its inputs.
 %do I need to talk about when transient is not ~x?
@@
 \end{definition}
-Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
-Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.
-But we have not proved that the A-half does not stop prematurely compared to the original circuit.
-Towards this goal, we prove two lemmas:  Lemma 3 shows if a single fault occurs on the $c2$ or $c3$ wires of some wire $w$, the output wires still follow the original state graph.
-Lemma 4 shows if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
-Then these lemmas combine to show that there is no deadlock.
-
-%To do this we prove some properties that are true when a single transient fault occurs on a wire.
-We partition the wires into two sets based on their properties when a single transient fault is added.
-Lemma 3 shows that if a single fault occurs on the $c2$ or $c3$ wires for some wire $w$, the output wires still follow the original state graph.
-Lemma 4 shows that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
-Then we combine these Lemmas to show that there is no deadlock.
-
+Next we will show that adding a single transient fault to any wire will still allow one of the half circuits to progress as normal.
+Since the 'good' half will always progress according to the original state graph if a transition is available, we just need to prove that it never deadlocks.
+To do this we prove some properties that are true when we add a single transient fault.
+We split the wires into two sets based on their properties when a single transient fault is added.
+Lemma 3.1 shows that if a single fault is added to $c1$, $c2$ or $c3$ wires of the wire block for some wire $w$, the output wires still follow the original state graph.
+Lemma 4 shows that if an fault is added to any of the other wires, then the $c1$, $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.
+Then we combine these lemmas to show that this implies that there is no deadlock.
 \begin{lemma}[3]
-For any trace $\sigma$ in the duplicated circuit, if a single transient fault occur on wire $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the duplicated circuit, with a single transient fault occurring on a $c2$ or $c3$ wire of some wire $w$ at any point in the trace, then $h^{A}(\sigma_n)$ and $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 \end{lemma}
 \begin{proof}
-We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain do not change.
-Under normal operation, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through the wire values shown in Figure \ref{fig:l3helper}.
-Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2^A$ or $c3^B$, the transitions follow the state diagram in Figure \ref{fig:l3helper}.
-\begin{figure}
-  \centering
-    \includegraphics{flowl2c3a}
-  \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
-This forms the input and output characteristic of a wire block under normal operation.}
-  \label{fig:l3helper}
-\end{figure}
-
+Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.
+We use NuSMV to verify that adding a transient fault to one of the $c2$ or $c3$ wires do not change the input-output characteristic of the local circuit.
+Under normal operation, by lemma 2.1 the pair of inputs and outputs cycle through 00 00 00$\rightarrow$ 01 00 00 or 10 00 00 $\rightarrow$ 11 00 00 $\rightarrow$ 11 01 00 or 11 10 00 $\rightarrow$ 11 11 00 or 11 11 00 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.
+Thus the property verified in NuSMV is that when a single transient fault can happen spontaneously on wires $c2$ or $c3$, the cycle mentioned previously is always true.
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.
-We go through an example of a transient on $c3^B$ to demonstrate why this is true.
-By Lemma 2.1 the normal circuit is in a state in Figure \ref{fig:l21}, so we observe the transient induced trace with the transient occurring at each state in Figure \ref{fig:l21}.
+We go through an example of a transient on $c3^A$ to demonstrate why this happens.
+By lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.
 \begin{itemize}
 	\item
-If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b the transient does not cause any changes in excitations in the local circuit.
+If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, 6b it does not cause any changes in excitations in the local circuit.
 In particular since $w^A$ and $w^B$ do not change, then by semi-modularity the excited/unexcitedness of logic blocks are maintained.
-So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^B$ value flipped.
-Eventually they all transition to state 8b and proceed from there as usual.
-	\item
-If the current state is 7, the transient changes the state to 8b, a valid transition.	
-      \item
-If the current state is 8a, the transient changes the state to 9, a valid transition.	
-	\item
-      If the current state is 8b then when the transient occurs on $c3^B$, the state
+So the transient induced state graph is a copy of the portion containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^A$ value flipped.
+Eventually they all transition to state 8a and proceed from there as usual.
+	\item
+If the current state is 7 progresses the state to 8a, the correct transition.	
+	\item
+      If the current state is 8a then when $c3^A$ experiences a transient, the state
  becomes identical to state 7.  It will then proceed from state 7 as usual.   
 	\item
-If the current state is 9 then when the transient occurs, the state reverts back to state 8a.  
-	\item
-If the current state is 10a or 10b, then when the transient occurs, $w_B$ or $w_A$ changes from excited to non excited respectively.
-Wire $c3^B$ is excited but there are no other excitations in the wire block.
-Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited in any subsequent states while $w^A$ and $w^B$ are mismatched (by the same argument as in Lemma 2.1 for cases 10a/10b since the other wire blocks do not have transients).
-Then the wire block will stay in this transient induced state until $c3^B$ finally transitions and the wire block returns to its state before the transient.
+If the circuit experiences a fault in state 9, it will revert back to state 8b.  
+	\item
+If the circuit experiences a fault in state 10a or 10b, $w_B$ or $w_A$ will go from excited to non excited respectively.
+$c3^A$ will be excited but there are no other excitations in the local circuit.
+Thus $w^A$ and $w^B$ do not change and by semi-modularity the logic gates to these wires cannot be excited or transition on any subsequent states while $w^A$ and $w^B$ do not change (same argument as in lemma 2.1 can be used since the other wire blocks do not have transients and thus in one of the states in cases 2.1).
+Then the local circuit will stay in this transient induced state until $c3^A$ finally changes and the circuit returns to its state before the transient.
 \end{itemize}
 %c3
-Similar reasoning would then apply if a transient fault occurs in $c2^B$.  
+A similar reasoning would then apply if a transient fault occurs in $c1^A$, and also for the $B$ half.  
 \end{proof}
-By symmetry this is also true for transients in the A half if we exchange A and B in the statement of Lemma 3.\\
-
-%\includegraphics[width=.8\textwidth]{gatew}
+
+\includegraphics[width=.8\textwidth]{gatew}
+
 \begin{figure}
@@
 
-We showed that if a fault occurs on $c2$ or $c3$ wires then there is no observable differences in the output wires between the faulty circuit and fault free circuit.  
-Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transitions according to Figure \ref{fig:l4} which is analogous to Lemma 2.1.
-The main difference is that because a fault may be present, we cannot predict the value of either $c1^A$ or $c1^B$.
-The following property is true despite not knowing one of the $c1$ wire values and leads to the conclusion that the output wire pairs can never be mismatched at deadlock.
-
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block $w\in W$ are always in a state of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the duplicated circuit, that allows adding a fault to any wire other than $c2$ or $c3$ at some time step $n$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ is always in a state of Figure \ref{fig:l4}.
 \end{lemma}
 \begin{proof}
-The fault is in the B-half so Lemma 1 applies for the A half.
-We show by induction that when the fault is not in $c2^B$ and $c3^B$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.
+Without loss of generality we prove this is true when a fault occurs in the A half.
+Then we can assume Lemma 1 is true for the B half.
+We show by induction that when the fault is not in $c2$ and $c3$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.
 Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\
 
-The base case is for the valid initial state with no faults, projecting the states of Figure \ref{fig:l21} from Lemma 2.1 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
-
-In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of Figure \ref{fig:l4}, then we look at all possible next states $s_{k+1}$.
-We don't assume anything about the non $c2$ and $c3$ wires for the B-half so that $c1^B$ may change values due to a fault.
-However we do expect $c1^B$ to be either a 1 or 0 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.
-We indicate the possibly faulty $c1^B$ by the symbol X.
+The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
+
+In the induction step we assume $s_k$ is a state where each wire $w$ is in a case of figure \ref{fig:l4}, then at $s_{k+1}$ we look at the possible next states.
+We don't assume anything about the non $c2$ and $c3$ wires for the A-half so that $c1^A$ may change values due to a fault.
+However we do expect $c1^A$ to be either a 1 or 0 and that even with hazards on $c1^A$, $c2$ transitions to either 0 or 1.
+We indicate the possibly faulty $c1^A$ by the symbol X.
 \begin{itemize}
@@
 \end{proof}
-The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
-The next theorem shows that this implies all output pairs at deadlock must be equal so there is a possible next condition which contradicts the definition of deadlock.
-Thus the fault tolerant circuit does not deadlock under a single transient fault.
-
-%Then the following corollary holds:
-%\begin{corollary}[4.2]
-%All output pairs at deadlock must be equal
-%\end{corollary}
+The importance of this property is that at most one of $c2$ or $c3$ pairs can be mismatched.  And thus all output pairs at deadlock must be equal.
 
 \begin{theorem}[2]
-When a single transient fault occurs, if $\sigma$ is a trace in the fault tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) for all $n \in \mathbb{N}$ is a prefix of a trace in the original circuit.
+With the addition of a single transient fault, and for all $n \in \mathbb{N}$, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then one of $h^{A,B}(\sigma_n)$ (the non faulty half) is a prefix of a trace in the original circuit.
 And the circuit does not deadlock.
@@
 Without loss of generality we can assume the fault occurs in the A half of the circuit.
-First by Lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.
+First by lemma 3 we know that if the fault occurs on $c2$ or $c3$ wire the circuit does not deadlock.
 Thus we only look at when the fault occurs on all other wires.
@@
 There
- must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in Lemma 4.
+ must be a wire $w$ that is excited in the state $h^B(s)$ in the original circuit and we look at that wire block in the duplicated circuit.  We examine each case in lemma 4.
 \begin{itemize}
 	\item
-	Case 1: Since $w$ is excited then by Lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
+	Case 1: Since $w$ is excited then by lemma 1 $c1^B$ or $w^B$ must be excited and can transition.
 \item
@@
 To remain deadlocked, it must be true that there exists a wire where $w^A\neq w^B$, which implies its $c1^A\neq c1^B$ and $c2^A\neq c2^B$ and $c3^A\neq c3^B$.
-But we have shown in Lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault.
+But we have shown in lemma 4 that $c2^A\neq c2^B$ and $c3^A\neq c3^B$ cannot occur at the same time under a single transient fault.
 Thus deadlock is not possible.
-And applying Lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit.
+And applying lemma 1, $h^B(\sigma_n)$ is a prefix of a trace in the original circuit.
 \end{proof}

### 2019-08-07 draft_together3.tex
added new chapter

@@
 \\ %Martin did not give references for these....prob ok then
+
 \includegraphics[width=\textwidth]{asyncex}
@@
 %Overview:  why is the problem important  \\  maybe I can extend the Introduction a bit more
+
 \chapter{Background}
@@
 %Then talk about the fault tolerant solutions () \\
+
 \section{Asynchronous Circuit and Synthesis}
@@
 Our fault tolerant transformation procedure is for a class of circuits, semi-modular control circuits, which includes many circuits.
+
+\chapter{New Background}
+\section{Assumptions:  Boolean signals}
+We make the assumption that all signals are Boolean, that is, the signals are either `logic 0' or logic 1'.
+When the the gates and C-elements are excited, and their outputs transition, we assume that transition is instantaneous and that after the transition, the signals are still Boolean.
+Even in cases where the wires are affected by faults, we assume that the new value of the wires are Boolean, and if they are inputs into circuit elements, that the output of the circuit elements also remain Boolean.
+For each circuit, there is a finite set of wires, which we call $W$.
+An exact definition $W$ will be presented at a later section, but for now just think of $W$ as including all the wires of some circuit.
+
+\section{Notation for Logical Operation}
+We use the logical operator notation.  For example, the AND operation with two inputs $w_1$ and $w_2$ is $w_1\wedge w_2$.
+The OR operation with two inputs $w_1$ and $w_2$ is $w_1\vee w_2$.
+The NOT operation with input $w_1$ is $\neg w_1$.
+These are interchangeable with the Electical Engineering convention, which represent AND as $w_1\cdot w_2$, OR as $w_1+w_2$, and NOT as $\overline{w_1}$.
+
+\section{Circuit Elements}
+Gates and elements (C-elements) are components that we allow in our circuit.
+In general, we call them elements.
+Each element has 2 input wires and 1 output wire.
+The elements can be in two states, excited or stable.
+Examples of gates are AND, OR, NOT etc.
+
+For each element, there exists a function that maps the inputs into a binary value.
+This function is represented by $f:[I \to \{0,1\}] \to \{0,1\}$ where $I$ is the set of input wires of the element, a subset of $W$.
+If we assume a two input element, we name the input wires $w_1$ and $w_2$.
+The function models the designed operation of the element such that if the element had no delay, $f(w_1,w_2)$ is the output value of the element.
+With asynchronous delay, if the inputs remain constant, then the output will eventually take the value of $f(w_1,w_2)$.
+For gates, such a function is easily defined.
+For example, an AND gate such as in figure \ref{fig:gates0} with two inputs $w_1$ and $w_2$ is modeled by the function
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.4\textwidth]{gates0}
+\captionof{figure}{AND gate}
+\end{figure}
+\[
+f_{AND}(w_1,w_2)= w_1\wedge w_2
+\]
+
+For C-elements, these are memory holding devices so the function also requires the previous output.
+For example, the C-element in figure \ref{fig:element0} with two input wires $w_1$ and $w_2$ is modeled by the function\\
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.3\textwidth]{element0}
+\captionof{figure}{C-element}
+\end{figure}
+\[
+f_{C-E}(w_1,w_2) =\left\{
+  \begin{array}{@{}ll@{}}
+    0, & \text{if}\ w_1=0 \wedge w_2=0\\
+    1, & \text{if}\ w_1=1 \wedge w_2=1\\
+    v, & \text{otherwise}
+
+  \end{array}\right. 
+\]
+
+Each element is in one of two states, excited or stable.  
+\begin{definition}
+An element with inputs $w_1$, $w_2$, output $v$ and function $f$ is {\em excited} if $v\neq f(w_1,w_2)$.  
+\end{definition}
+This definition can be extended to include elements with any number of inputs by replacing $w_1$ and $w_2$ with the inputs of a specific element.
+A natural extension to an excited element is to consider an element that is not excited.
+\begin{definition} 
+An element is stable if the element is not excited.
+\end{definition}
+Then, a stable element must satisfy $v= f(w_1,w_2)$.
+An example of an excited and stable AND gate is shown in figure \ref{fig:gates1}.
+An example of an excited and stable C-element is shown in figure \ref{fig:element1}.
+For C-elements, there are two situations in which the element is stable.
+One is where the output is being actively driven to its function value, i.e.
+when both inputs are 0 or both inputs are 1.
+The second is where the inputs are mismatched and the C-element is holding the previous output.
+In the second case, the C-element is stable regardless of the output's value.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\textwidth]{gates1}
+\captionof{figure}{a) the AND element is excited  b) an excited element fires to become stable}
+\end{figure}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.9\textwidth]{element1}
+\captionof{figure}{a) the C-element is excited  b) two types of stable C-elements}
+\end{figure}
+
+The states described above are static descriptions of the element, but we must also consider the dynamic behavior.  
+That is, when the input or output wires change.
+Because we focus on asynchronous circuits, we view these wire changes as happening one at a time with some delay in between.
+For example, we do not allow an input wire and output wire to change at the same time.
+With this assumption, it is easy to consider all cases for the dynamic behavior of the element.
+When the element is stable, the output wire does not change.
+A stable element can have input wire changes, and the input changes may cause the element to become excited.
+A small point to note is that not all input changes cause the element to become excited, .
+When the element is excited, there are two possibilities for the element to become stable again.
+Either the input changes such that the element is stable, or the output changes.
+Again, not all input changes will cause the element to become stable.
+In fact, semi-modular circuits utilizes input changes that allow the element to stay excited.
+If the output changes in an excited state, the element becomes stable and we call this action a {\em firing} of the element.
+
+\section{Circuits}
+A circuit is a network of elements.
+These elements are connected when they share a wire.
+For an element, each input is connected to either a primary input or the output of a different element.
+Other than elements, a circuit also consists of primary inputs and primary outputs.
+Primary inputs are all inputs that are not the output of an element in the circuit.
+Primary outputs are outputs of an element in the circuit that connects to another device or element outside of the circuit.
+Primary inputs and outputs can be thought of as the interface with outside of the circuit.
+They can be the outputs and inputs of a different circuit, or connected to physical mechanisms such as a user pushing a button.
+An example of a circuit with primary inputs and outputs is:  .
+
+\section{States}
+Let $W$ be the set denoting the union of all wires of elements and the primary inputs of a circuit, then $S$ is the set of functions $[W\to \{0,1\}]$ which maps each element of $W$ to a boolean value.
+An element of $S$ is called a {\em state}.
+
+Assigning values to all wires of a circuit names a state.
+An example of a state for a circuit containing 3 wires is `101'.
+From the set definition, states are unique and no two states share the same values.
+
+\section{Behavior of a circuit}    
+Circuits respond to input changes and produces outputs that accomplish some specified task.
+Thus the function of a circuit depends on its dynamic behavior and how its state changes over time.
+Under the state representation of a circuit, if the value of a wire changes, the state also changes.
+If the wire changes from a previous state $s$ to a new state $s'$, then there is a transition relation between the two states.
+Defined more formally with $s(w)$ denoting the value of wire $w$ in state $s$:
+\begin{definition}
+For all $s$ and $s'$ in S, the \emph{transition relation} $T(s,s')$ holds when there is exactly one wire $w \in W$ such that $s(w)\neq s'(w)$, and wire $w$ must be either the output of an excited element in state $s$, or $w$ is a primary input.
+\end{definition}
+%from state graph, T(s,s') must satisfy...
+but we can define ourselves which are the transitions (ie arrows in a state graph).
+Going from the circuit, there is a transition if the circuit state allows for a transition, either something excited fires or the primary input changes
+There may be multiple transitions from a state $s$.
+
+We define a {\em trace} to describe a path the circuit can take.
+Different paths can occur because there may be multiple transitions from each state.
+We call the succession of states the trace, which is formally defined as follows:
+\begin{definition}A {\em trace} $\sigma=(s_1, s_2, ...)$ of a circuit is a sequence of states of finite or infinite length.  
+%Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
+ Every pair of consecutive states in a trace are in a transition relation $T(s_i,s_{i+1})$, where state $s_i$ represents the $i^{th}$ term of the sequence.
+.
+% such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$
+\end{definition} 
+We also use $\sigma_n$ as shorthand to denote the sequence of the first $n$ states of $\sigma$.
+Taking different paths form different traces so a circuit has a set of traces.
+% A circuit also has a set of initial states where the traces can begin in.
+The set of initial states are the same as the set of states in the state graph.
+The set of traces that can occur depends on the {\em initial} state of the wires in the circuit and the primary inputs.  When we specify a circuit, we must also specify the initial state.  
+There are some additional properties that a trace can have and we define them here.
+\begin{definition}
+A {\em stopping state} is a state where there are no excited elements in the circuit. 
+\end{definition} 
+ The circuit may be waiting for a primary input change.
+%Thus, the only possible transitions from a stopping state are from changes in the primary inputs.  In other words, in a stopping state, the circuit is waiting for the primary inputs to changes.\\
+\begin{definition}
+A {\em complete trace} is either a finite length trace that ends in a stopping state, or an infinite trace.
+\end{definition}
+A complete trace of finite length must end in a stopping state where the primary inputs never change and the circuit is stopped.
+In other words, for any state of a complete trace, if there are excited elements, one of them must fire, causing the circuit to transition to another state.
+\begin{definition}
+A {\em fair trace} is a trace of a circuit where if an element is excited in any state, it becomes stable in a finite number of transitions.
+\end{definition}
+In other words, every circuit element must be stable infinitely often in a fair trace.
+This fits with the physical properties of circuits because the elements are not arbitrarily slow and if excited, they will eventually change.
+A set of traces can describe a circuit completely, in addition we may be interested in the states that the circuit visits in these traces. 
+A {\em reachable state} is defined in this way.
+\begin{definition}
+A state is {\em reachable} if it is in some trace, of a set of traces.
+%A {\em reachable state} is an element of the set of all states in some trace, of a set of traces.  
+\end{definition}
+Thus, unreachable states are states that are not in any of the traces, of a set of traces.
+Since all functionality of a circuit can be described by a set of traces, then the circuit will never enter such a state, hence termed unreachable.
+
+\section{Semi-modularity}
+Semi-modular circuits are a subset of speed independent circuits and is a large enough class to include circuits used in real applications.
+Also, they have been extensively studied, with algorithms to synthesize and analyze them.
+A simple explanation of semi-modularity is that once an element is excited, it stays excited until it fires and its output changes.
+Formally this can be defined as follows: %proof that semi-modular circuits are also speed independent
+\begin{definition}
+An asynchronous circuit is {\em semi-modular} if for every pair of successive states in its set of traces $s_{i}$ and $s_{i+1}$, if element $j$ is excited in state $s_i$ and did not fire, then $j$ is also excited in state $s_{i+1}$.
+%An asynchronous circuit is {\em semi-modular} if for every pair of successive states in its set of traces $s_{i}$ and $s_{i+1}$, and let $v$ and $w$ be output wires such that $s_i(w) \neq s_{i+1}(w)$ (wire $w$ transitions) and $w\neq v$, then if $v$ is excited in state $s_i$, $v$ is also excited in state $s_{i+1}$
+\end{definition}
+In a circuit with primary inputs, the changes in the primary inputs are constrained not to violate semi-modularity, for example through a protocol using the primary outputs from the circuit to signal when the circuit is ready for a primary input change.
+
+Combining semi-modularity and fair traces, since excited elements in semi-modular circuits can only become stable from the element firing, then a fair infinite trace of the circuit has the property that if an element is excited infinitely often, then it fires infinitely often.
 
@@
 The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
-The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault tolerant circuit does not deadlock under a single transient fault.
+The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault tolerant circuit does not deadlock under a single transient fault.\\
+
+Returning to the condition of deadlock, where the circuit has no further transitions and is also not in a stopping state, we can make the following conclusion about the inputs and outputs of C-elements.
+\begin{lemma}[5]
+If the circuit is in deadlock, and the two inputs into a C-element is the same value $v$, then the output of the C-element is also $v$.
+\end{lemma}
+\begin{proof}
+For a circuit in deadlock, there are no excited elements.  If a C-element has two inputs with value $v$, then the output must also be $v$ for the C-element to be unexcited.
+\end{proof}
+Then for each layer of C-elements in the wire block, if say the wires $c2^A$ and $c2^B$ are equal to $v$, then at deadlock the wires $c3^A$ and $c3^B$ are also equal to $v$.
+Then by extending this to successive layers of C-elements, all outputs of these C-elements must also hold the value $v$.
+This example is illustrated in Figure \ref{fig:t2}.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=\textwidth]{lemma4help}
+  \caption{a) If $c2^A=c2^B$, for example both are 0  b) At deadlock (no excitations) and $c2^A=c2^B$, then the two subsequent layers of C-elements must also be at 0. }
+  \label{fig:t2}
+\end{figure}
 
@@
 Without loss of generality, we can assume the fault occurs in the B half of the circuit.
-First by Lemma 3, we know that if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires.
-Thus we look at when the fault occurs on the remaining wires.
-Next, we prove that a deadlocked circuit in this scheme must have at least one pair of output wires which have different values.  That is $w^A\neq w^B$ for some wire $w$.
-This is shown by contradiction.
-Assume that the circuit is deadlocked at state $s$ and $v^A = v^B$ for all wires $v$ from the original circuit.
-If a transient occurs, one can wait until that wire is free to transition.
-There
- must exist a wire $w$ that is excited in the state $h^A(s)$ in the original circuit and for that wire block in the duplicated circuit, by Lemma 4 it must also be in a case in Figure \ref{fig:l4}.
-We examine each case in turn.
-\begin{itemize}
-	\item
-	Case 1: Since wire $w$ in the original circuit is excited, then by Lemma 1, the wire block $w$ is in case a or d in Figure \ref{fig:l1helper} and wires $c1^A$ or $w^A$ can transition.
-\item
-Case 2:  Wire $c1^B$ may be 0 or 1.
-If $c1^B=0$, since the inputs to A half and B half are equal then $c1^B$ must be excited and can transition to 1.
-If $c1^A=1$ then the wire block can transition to case 3a or 3b.
-\item
-Case 3a/3b:  Wire $c1^B$ may be 0 or 1.  If $c1^B=0$, again $c1^B$ can transition to 1.  If $c1^B=1$ then it can transition to case 4.
-\item
-Case 4/5a/5b:  Wire $c3$ is excited and can transition. 
-\end{itemize}
-Thus a transition can always occur and the circuit is not deadlocked which leads to a contradiction.
-To remain deadlocked, it must be true that there exists a wire where $w^A\neq w^B$, which implies its $c1^A\neq c1^B$ and $c2^A\neq c2^B$ and $c3^A\neq c3^B$.
-But this is not a possible case by Lemma 4.
-Thus deadlock is not possible when there is a single transient fault.
-And by Lemma 1, $h^A(\sigma_n)$ is a prefix of a trace in the original circuit.
+First by Lemma 3, we know that if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires and the circuit does not deadlock.
+Thus we look at when the fault occurs on the remaining wires.\\
+
+We show there exists a contradiction when the fault occurs on the remaining wires and we assume that the circuit is in deadlock.
+We first show that the output wires $w^A = w^B$ for all wire blocks.
+For each wire block $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
+For both cases, since the circuit is in deadlock, then by Lemma 5 all wire blocks have output wires with the property $w^A = w^B$.
+\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
+
+Next, with this new property, we show that there exists a contradiction and the circuit must not be in deadlock.
+Let the circuit be in some deadlocked state $s$.
+By Lemma 1, $h^A(s)$ is a state in the original circuit.
+By definition of deadlocked state, the state $h^A(s)$ is not a stopping state, so there must exist a wire $v$ that is excited.
+In the duplicated circuit, for the circuit to be in deadlock in wire block $v$, the $c1^A$ wire must have value $\neg{v}$, because otherwise the logic block in the A half is excited.
+Since $w^A = w^B$ for all wires then $h^A(s)=h^B(s)$ and the $c1^B$ wire must also have value $\neg{v}$ or the logic block in the B half is excited.
+By Lemma 5, $v^A$ and $v^B$ wires must have the same value as the $c1$ wires.
+However this results in $v^A= \neg{v}$ which is a contradiction, therefore the initial assumption is wrong and the circuit is not in deadlock.
+%excited blocks, and stopping states
+%the fallible part of the logic is that if inputs to B is the same it may not be excited (it is in our case because I know the structure of the logic block) but in a general implementation it could not be, ie if it depends on previous inputs etc
+
+Thus deadlock is not possible when there is a single transient fault.  And by Lemma 1, $h^A(\sigma_n)$ is a prefix of a trace in the original circuit. 
 \end{proof}

### 2019-09-03 draft_together3.tex
before remove SM consistent

@@
 \usepackage[font=small,labelfont=bf]{caption}
+\usepackage{comment}
 
@@
 The end result is a hazard-free and speed independent asynchronous circuit.
+We assume that the previous steps are hidden, and are presented with a semi-modular circuit to make fault tolerant.
 There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.
@@
 \subsection{Speed Independent Circuits}
-As mentioned in the introduction, the unbounded gate delay model assumes an arbitrary delay on all the gates and ignores any delay on wires.
+As mentioned in the introduction, circuits are composed of gates and wires.
+The unbounded gate delay model assumes an arbitrary delay on all the gates and no delay on wires.
 This delay model is the basis for Muller circuits \cite{Muller_59}.
+Circuits that operate correctly regardless of the delay are called Speed Independent Circuits.
+The correct operation is specified when designing the circuit, for example, given some input values the circuit will return specified output values.
+There are many ways to represent specifications such as petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.
+We won't go into these representations and methods in detail, other than the aspects that are relevant to this work.
+We consider circuits which has wires that take on Boolean values of either `1' or `0'.\\
+%Wires in the circuits take on Boolean values of either `1' or `0'.
+A state is defined by assigning a Boolean value to each wire of the circuit.
+States are unique in that no two states share the same wire values.
+There will be a formal definition of wires and states in the next chapter.
+
+\begin{comment}
 State graphs describe how we would like the circuit to function.  
@@
 We next look at how such a gate logic can be made.\\
+\end{comment}
 
@@
 The two specific Muller circuit implementations that we consider are the generalized C-element and standard C-implementations.
-We assume that the circuits we want to make fault tolerant follow these implementations.
-For each wire in the state graph there is a gate logic that controls the value of the wire.
-We look at two conditions, set, the condition for the wire to transition to a high value; and reset, the condition for the wire to transition to a low value.
+We assume that the circuits we want to make fault tolerant are synthesized according to these two implementations.
+Each wire in the circuit is the output wire of a gate logic.
+The gate logic has a set of input wires and the output wire changes value according to the values of the inputs.
+We look at two conditions, set, the condition for the output wire to transition to a high value; and reset, the condition for the output wire to transition to a low value.
 The gate logic then implements the set and reset conditions.
-The details of how this is implemented is that we use the state graph to generate the set and reset conditions.
-For each set and reset there is an ON-set, OFF-set and Don't Care set.
-ON-set are all states in the state graph where the wire is excited and a transition will occur.
-That is for the set condition, it must evaluate to TRUE for these states so that the wire can transition to high.
-OFF-set includes all states where the set condition must evaluate to FALSE which is the states where the wire is excited but to the opposite value, which is low for set, as well as all states in the state graph where the wire value is at the opposite value, again low for set.
-The rest of the states are in the Don't Care set which includes states that are not included in the state diagram.
-It does not matter what the set condition evaluates to in these states as they do not disturb the function of the circuit.
-The same procedure applies as well in finding the ON-set, OFF-set and Don't Care set for reset except substituting in reset for set and flipping the value of the wire where needed.
-The set and reset conditions then must include all states in the ON-set and not include all states in the OFF-set so that the wire transitions according to the underlying state graph.
-The set and reset can be implemented separately with logic and the gate logic for the wire includes logic for both set and reset and also the combination of them into the output wire.
+We skim the details in finding the set and reset conditions from the circuit specifications.
+For each condition set and reset, there is an ON-set, OFF-set and Don't Care set.
+ON-set are all input values where the wire is excited and a transition will occur.
+The OFF-set includes all input values where the wire cannot be excited to some value per the circuit specifications.
+Input values that are neither in the ON-set or OFF-set are in the Don't Care set.
+So for the set condition, the ON-set are all input values where the wire must transition to high.
+The OFF-Set includes all input values where the wire is excited instead to low, as well as input values for which the output wire must remain low.
+The input values of the Don't Care set assign the output wire to be either high or low.
+It does not matter which value is assigned since it does not disturb the function of the circuit and only helps for circuit optimization.
+\\
+
+The same procedure applies as well in finding the ON-set, OFF-set and Don't Care set for reset except substituting in reset for set and flipping the value of the wire from high to low and vice versa.
+The set and reset conditions constructed this way then follows the desired circuit specification.
+The set and reset conditions are implemented using gates and are combined into the output wire through a C-element.
+This entire block of gates and C-element for the output wire is called the gate logic.
 \\   %Beerel and Myers....
@@
 For the standard C-implementation, we allow for more variation in delay.
-For the gate logic of each variable in the state graph, we look at the set and reset logic as composition of various gates (such as AND, OR, NOT).
+For each wire in the circuit with a corresponding gate logic, we look at the set and reset logic as composition of various gates (such as AND, OR, NOT).
 Each of these gates can have their own delay that is arbitrary in length that is instantized as an intermediate wire.
@@
 We also use $\sigma_n$ as shorthand to denote the sequence of the first $n$ states of $\sigma$.
-Taking different paths form different traces so a circuit has a set of traces.
-% A circuit also has a set of initial states where the traces can begin in.
-The set of initial states are the same as the set of states in the state graph.
-The set of traces that can occur depends on the {\em initial} state of the wires in the circuit and the primary inputs.  When we specify a circuit, we must also specify the initial state.  
+When there multiple transitions from a state, multiple traces exist depending on which wire transitions.
+Thus we want to define a set of traces for all the traces that form.
+In addition the initial state is important in naming a trace and by extension for a set of traces.
+The {\em initial state} specifies the state of the wires in the circuit as well as the primary inputs.
+Thus a set of traces is defined as follows:
+\begin{definition}
+A {\em set of traces} of a circuit with initial state $s_1$ is the set of all traces of the circuit starting in state $s_1$. 
+\end{definition}
+
+ % A circuit also has a set of initial states where the traces can begin in.  The set of initial states are the same as the set of states in the state graph.
+When we specify a circuit, we must also specify the initial state.  
 There are some additional properties that a trace can have and we define them here.
@@
 \begin{definition}
-A state is {\em reachable} if it is in some trace, of a set of traces.
+A state $s$ is {\em reachable} from $s_1$ if $s$ appears in some trace that begins with $s_1$.
 %A {\em reachable state} is an element of the set of all states in some trace, of a set of traces. 
+%still kind of weird oh well 
 \end{definition}
-Thus, unreachable states are states that are not in any of the traces, of a set of traces.
-Since all functionality of a circuit can be described by a set of traces, then the circuit will never enter such a state, hence termed unreachable.
+Thus, unreachable states are states that are not in any of the traces with initial state $s_1$.
+Since all functionality of a circuit can be described by a set of traces starting in a specified state, then the circuit will never enter those unreachable states.
 
@@
 \section{Traces and circuit equivalence}
-We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.
+We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all of its circuit elements.
 Due to the asynchronous nature of how signals are processed, corresponding wires in the resulting half circuits may have different values.
@@
 
+\begin{comment}
 Other than the basic terminology for asynchronous circuits, we also want terminology to compare two circuits based on their function.  
@@
 \begin{definition}A {\em stopping state} is a state where there are no excitations in the wires in the circuit and the circuit is waiting for the external inputs.\end{definition}
+
+In the previous chapter, we have introduced the trace of a circuit, stopping state and complete trace.
+
 A trace of finite length ends in a stopping state where the external inputs never arrive and the circuit is stopped.
 A related concept is a deadlocked state which is a state where the circuit prematurely stops and defined as follows:
-\begin{definition}A {\em deadlocked state} is a state where there are no excitations in the wires in the circuit and is not a stopping state.\end{definition}
+\begin{definition}A {\em deadlocked state} is a state where there are no excitations in the wires in the circuit and is not a stopping state.\end{definition} %but stopping state= no excitations, so either does not introduce new stopping states after the transformation or what....
 A deadlocked state does not appear in a well designed circuit, but may appear after a circuit transformation (i.e., the new circuit stops at states where the original circuit do not), or when there are faults.
 Thus we want to design a circuit transformation where there are no deadlocked states.\\ %end new
+
+\end{comment}
 %Note that our definition of trace also includes the case where there is only one transition from each state of a state graph, which results in a linear state graph.
@@
 The original circuit is semi-modular by design.
-But the design only covers cases where the wires are in a state in the state graph.
-That is, hazards may occur if the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.
-This does not happen in the fault-free case where the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.
-However when faults do occur, the circuit may become unpredictable which is a reason why we need to transform the circuit to protect against faults.
+But the design only covers traces when the circuit starts in a specified initial state.
+That is, hazards may occur if the circuit goes into an unreachable state of the traces and the circuit is no longer semi-modular and furthermore becomes unpredictable.
+This does not happen in the fault-free case and the circuit starts in a valid initial state.
+However when faults do occur, the circuit may become unpredictable, which is a reason why we need to transform the circuit to protect against faults.
 An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
@@
 Half of those bits are obviously from the A half and half are from the B half of the circuit.
-The state graph for a fault tolerant circuit is defined on this combined state.
+The trace of a fault tolerant circuit is defined on this combined set of wires.
 We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
@@
 Adding another layer of C-elements creates delays at the input to logic blocks and the isochronic fork assumption is violated.
-Thus the resulting circuit will not function according to the specified state graph.
+Thus the resulting circuit will not function according to the desired specifications.
 (an example can be provided but not sure if needed?)\\
@@
 Next we examine the traces of each half circuit.
-Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where each state is given a nominal name (state 0, state 1, ...
-etc) and each transition is labeled with the transitioning wire.
-Suppose we apply our fault tolerant transformation to such a circuit based on this state graph.
-Both halves in the fault tolerant circuit will transition based on this state graph, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
-Starting in {\em state 0}, it is possible for the A-half to transition to {\em state 1} ($a^A$ transitions) and for the B-half to transition to {\em state 2} ($c^A$ transitions).
+Assume that for the original circuit starting in state 0, both (state 0, state 1, state 3, state 6) and (state 0, state 2, state 5, state 6) are prefixes of valid traces.
+Then both halves in the fault tolerant circuit will transition based on the traces of the original circuit, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
+Since only one wire transitions at a time, it is possible for say $a^A$ to transition first and $a^B$ to transition later.
+Starting in {\em state 0}, it is possible for the A-half to transition to {\em state 1} ($a^A$ transitions) and for the B-half to transition to {\em state 2} ($c^B$ transitions).
 We assume that $a^B$ and $c^A$ do not complete their transitions yet.
-Immediately, in the A-half, $b^A$ is excited and in the B-half, $b^B$ is excited.
-Then, suppose the transition on wire $b^A$ and $b^B$ occurs.
+Immediately in the A-half, $b^A$ is excited, and in the B-half, $b^B$ is excited.
+Since $b$ is excited in both halves, wires $b^A$ and $b^B$ can transition.
 That is, the A-half transitions to {\em state 3} and the B-half transitions to {\em state 5}.
@@
 Now we will discuss the proper wire initializations before going into the Lemmas.
+Defining a set of traces of a circuit includes defining the initial state.
+For the original circuit, if the circuit starts from this initial state, then the synthesis method ensures semi-modularity in all traces.
+However, the proposed fault tolerant transformation adds logic, and the set of traces and initial state may be different from those of the original circuit, even after applying the half circuit mappings.
+Thus we need to ensure that after the transformation, the circuit behaves in a similar way to the original circuit.
+That is for an initial state of the fault tolerant circuit, which is related to the initial state of the original circuit, the resulting traces will behave similarly and have properties such as semi-modularity and the same stopping states as the original circuit.
+\\
+
+%the half circuits are still semi-modular, has the same transitions as the original circuit and does not stop in non-stopping states of the original circuit. 
+%This initial state consistent with semi-modularity also includes the initial values of internal wires.
+
+We show how to define the initial state for the fault tolerant circuit if given the initial state for the original circuit.
+The values for the internal wires must also be set.
+These internal wires are initialized to a semi-modularity consistent value.
+Given this, we pick the following convenient initializations for the fault tolerant circuit.
+The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
+%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
+The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s.
+The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.
+Given these we will show how to define a corresponding initial state in the duplicated circuit.
+%should I delete intermediate?
+\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed from the initial state of the original circuit.
+The wire values in the logic block and $w$ in the original circuit are copied to the corresponding wires in the A half.
+The additional wires from the C-element chain are also assigned the same value as $w$.
+That is, first assign the value of $w$ to $w^A$, then assign the value of $w$ to $c1^A$ $c2^A$ $c3^A$ as well.
+The same construction applies for the B half circuit as well.
+\end{definition}
+%\textbf{
+This definition is stronger than it needs to be but is convenient.\\
+
+\begin{comment}
+%dynamic properties of SM?  I don't think it's needed right now
+The input wire values must also satisfy dynamic properties.
+Static properties such as the input wire values must be from valid states of the trace is not enough.
+The order and the wire transitions also matter.
+The semi-modularity property must be preserved: if the logic block output is excited then it must remain excited until a transition on its output occurs.
+Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
+
 In normal operation, the fault tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.  
@@
 \\%newly added
-
-What values to initialize the wires of a circuit to is very important.
-We want certain properties to hold for all states that the circuit goes through, and such properties must also hold for the initial state.
-On one hand, the initial state $s$ must be a state in the underlying state graph.
-Thus the wire values is initialized to be consistent with that property.
-On the other hand, as mentioned previously, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.
-We assume that we can initialize the wire values of the original circuit to satisfy these two properties.
-Given this, we pick convenient initializations for the fault tolerant circuit.
-The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
-%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.
-The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s.
-The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.
-Given these we will show how to define a corresponding initial state in the duplicated circuit.
-%should I delete intermediate?
-\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed from an initial state of the original circuit.
-The wire values in the logic block and $w$ in the original circuit are copied to the corresponding wires in the A half.
-The additional wires from the C-element chain are also assigned the same value as $w$.
-That is, first assign to $w^A$ the value of $w$, then assign to $c1^A$ $c2^A$ $c3^A$ the value of $w^A$ as well.
-The same construction applies for the B half circuit as well.
-\end{definition}
-%\textbf{
-This definition is stronger than it needs to be but is convenient.\\
+\end{comment}
 
@@
 We show this through several Lemmas.
-Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.
-This is a strong result; it is true for arbitrary behavior of
-signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
-This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
+Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the set of traces of the
+%since it's a transition, then all previous transitions must also be in the set of traces, in fact they must all be a sequence of at least one trace (true because if excited, must be excited in all states of same name)
+ original circuit.  This is a strong result; it is true for arbitrary behavior of
+wires in the other half circuit, so long as those wire values are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
+This result is also significant later in proving fault tolerance under a single transient fault since at least one of the halves is always fault-free.
+%as long as it does not violate digital abstraction
 %One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
@@
 
-Note that Lemma 1 allows for the possiblity of deadlock.
-Lemma 2 shows deadlock does not occur during normal operation.
-Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
+Note that Lemma 1 allows for the possiblity of the fault tolerant circuit to stop at states that are not stopping states in the original circuit.
+This is an important point as we do not want our transformed circuit to stop prematurely.
+We call such premature stopping states, if they exist, as deadlocked states:
+\begin{definition}A {\em deadlocked state} is a stopping state of the fault tolerant circuit but not a stopping state of the original circuit.\end{definition}
+We use {\em deadlock} to mean the existence of such deadlocked states.  
+Then, Lemma 2 shows deadlock does not occur during normal operation.
+Combining these two Lemmas, we can show that all traces in the fault tolerant circuit can be mapped to a trace in the original circuit.\\
 % and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace

### 2019-10-12 draft_together3.tex
10-12 after first edits to Lemma1, before more changes

@@
 There is a variety of uses of asynchronous circuits because it has speedups over synchronous circuits and is also useful for synchronous systems where there is significant clock skew or combining components with different clock cycles and/or interfacing with the real world.
-There are some previous work that has been done to make asynchronous circuits fault tolerant to soft errors.
+There are some previous work that has been done to make asynchronous circuits fault-tolerant to soft errors.
 The design is based on duplicating the circuit and only works for quasi-delay-insensitive circuits which requires a lot of assumptions about how the delays in the underlying transistors function.
 The main contributions of this work are that it extends the previous work by proposing a new design.
-The new design also follows the duplication strategy but makes fault tolerant the class of semi-modular speed independent circuits (a class of circuits about the same size as QDI circuits) with looser assumptions on the delay and without significant overhead.
+The new design also follows the duplication strategy but makes fault-tolerant the class of semi-modular speed independent circuits (a class of circuits about the same size as QDI circuits) with looser assumptions on the delay and without significant overhead.
 Namely the only assumption is that the combinational logic components are composed of gates and that each gate is allowed to have arbitrary delay, instead of assuming that there is no delay in these components.
 Previous designs do not work for this more generalized case of circuits.
-This work also proves that such a fault tolerant model will always work and correct transient faults.
+This work also proves that such a fault-tolerant model will always work and correct transient faults.
 This allows for circuits to be more robust to different types of errors that may occur and prolong the lifetime and types of environments this circuit can be used for.
@@
 The end result is a hazard-free and speed independent asynchronous circuit.
-We assume that the previous steps are hidden, and are presented with a semi-modular circuit to make fault tolerant.
+We assume that the previous steps are hidden, and are presented with a semi-modular circuit to make fault-tolerant.
 There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.
@@
 %why are async circuits important, timing delay etc
-Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work put into making digital circuits fault tolerant.
-Most of the fault tolerant solutions has been investigated for synchronous digital circuits.
+Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work put into making digital circuits fault-tolerant.
+Most of the fault-tolerant solutions has been investigated for synchronous digital circuits.
 Because the timing difference between different signals arriving do not have to be considered for synchronous circuits, they can use error correcting codes and redundancy techniques such as triple modular redundancy (TMR).
@@
 
-In this work, we propose a new fault tolerant circuit transformation on asynchronous semi-modular control circuits.
-We also propose a method of comparing the fault tolerant circuit with the original circuit, by comparing traces with the half circuit.
-The fault free half of the fault tolerant circuit behaves like the original circuit under single transient faults.
+In this work, we propose a new fault-tolerant circuit transformation on asynchronous semi-modular control circuits.
+We also propose a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.
+The fault free half of the fault-tolerant circuit behaves like the original circuit under single transient faults.
 In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\
@@
 Then I will go into depth about the asynchronous circuit models that are relevant to this work.
-I will then go through the existing body of work on fault tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.
-In chapter three, I will show why the existing fault tolerant methods are insufficient and propose a new fault free method for asynchronous transient faults.
+I will then go through the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.
+In chapter three, I will show why the existing fault-tolerant methods are insufficient and propose a new fault free method for asynchronous transient faults.
 I will prove using logical proofs as well as formal verification methods to show why my new method always works.
@@
 Radiation from cosmic rays become more severe at higher elevations while the latent source in packaging is difficult to eliminate.
-Thus initially a lot of the work in fault tolerant design was done for aviation and space flight.
+Thus initially a lot of the work in fault-tolerant design was done for aviation and space flight.
 
@@
 %Asynchronous circuits (different types) possibly synchronous too? (and our circuit model based on Meyer) \\
-%Then talk about the fault tolerant solutions () \\
+%Then talk about the fault-tolerant solutions () \\
 
@@
 The two specific Muller circuit implementations that we consider are the generalized C-element and standard C-implementations.
-We assume that the circuits we want to make fault tolerant are synthesized according to these two implementations.
+We assume that the circuits we want to make fault-tolerant are synthesized according to these two implementations.
 Each wire in the circuit is the output wire of a gate logic.
@@
 %soft error protection <- error correcting codes for SRAM memory
-Because faults cannot be eliminated in digital circuits, different methodologies have been used to make the circuits fault tolerant.
+Because faults cannot be eliminated in digital circuits, different methodologies have been used to make the circuits fault-tolerant.
 Much of the research done in this area are for synchronous circuits.
@@
 First we present an overview of some common techniques for synchronous circuits, then introduce the current techniques for asynchronous circuits.
-Some of the techniques in asynchronous design borrows or are inspired by the much more developed fault tolerant synchronous circuits field.
+Some of the techniques in asynchronous design borrows or are inspired by the much more developed fault-tolerant synchronous circuits field.
 However due to the difference in timing assumptions of the two types of circuits the techniques are not completely transferable.
@@
 The faults that they consider are fabrication defects, permanent faults and unrecoverable failures.
-New nodes and edges are added to make it k fault tolerant.
+New nodes and edges are added to make it k fault-tolerant.
 They detect when there is a deadlock at which time it reconfigures the circuit by trial and error of all the possible combinations until the circuit is no longer deadlocked.
@@
 
-The approach that we use to make circuits fault tolerant will be described in the next chaper.
+The approach that we use to make circuits fault-tolerant will be described in the next chaper.
 Some of the previous works makes additional assumptions such as the checking circuit is fault free or that only one fault can occur on an arbitrarily large transistor gate.
 We allow for standard two-input gates and assume that all gates in our model are subject to faults.
-Our fault tolerant transformation procedure is for a class of circuits, semi-modular control circuits, which includes many circuits.
+Our fault-tolerant transformation procedure is for a class of circuits, semi-modular control circuits, which includes many circuits.
 
@@
 In the rest of this chapter we define a way to compare two circuits and to show their equivalence.
-Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.
-Finally we show that if a single transient fault occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
+Then we propose our transformation method and show that under normal operation (no faults), the fault-tolerant circuit is equivalent to the original.
+Finally we show that if a single transient fault occurs, one side of the fault-tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
 \begin{figure}
@@
     \includegraphics[width=.9\textwidth]{transf3Csimp}
-  \caption{a) original circuit b) after the fault tolerant transformation}
+  \caption{a) original circuit b) after the fault-tolerant transformation}
   \label{fig:dupschemeex}
@@
 
-We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in figure \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
+We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in figure \ref{fig:dupscheme}: we make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
 We also label the duplicated logic blocks as belonging to circuit A or circuit B in agreement to the wire naming.
@@
 These then connect to other logic blocks in circuit A and circuit B respectively.
+\\
 Note that when labelling the C-elements and its outputs, which side is A and B can be somewhat arbitrary because the output pairs are symmetric.
@@
     \includegraphics[width=\textwidth]{circuitforproof3}
-  \caption{Fault tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
+  \caption{Fault-tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
   \label{fig:dupscheme}
@@
 
-We want to show that a half circuit from the fault tolerant circuit has correct function.
-To do this, we define a correspondence between states of the original circuit and states of the fault tolerant circuit.
-As a result of the circuit transformation, a state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
+We want to show that a half circuit from the fault-tolerant circuit has correct function.
+To do this, we define a correspondence between states of the original circuit and states of the fault-tolerant circuit.
+As a result of the circuit transformation, a state of the fault-tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
 Half of those bits are obviously from the A half and half are from the B half of the circuit.
-The trace of a fault tolerant circuit is defined on this combined set of wires.
-We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
-The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.
-The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are hidden by $h^A$ or $h^B$.
-We extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.
+The trace of a fault-tolerant circuit is defined on this combined set of wires.
+We first  define the half-circuit mapping $h^B$ for the A half, the half-circuit mapping $h^B$ is similarly defined for the B half.
+The half-circuit mapping $h^A: s^{\textit{full}} \to s^A$ where $s^{\textit{full}}$ is the combined state of a fault-tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
+The added wires such as $c1^A$, $c2^A$, $c3^A$ from the duplication procedure is hidden by $h^A$.
+We can extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$.
 %not sure if I want the mapping to be from variable to variable or specific state to state
-%For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
+%For a trace in the fault-tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
 The resulting trace may have successive repeated states.
-So next we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.
-The result should be a trace from the original circuit.
-Using this mapping we will show that the original circuit is equivalent to half of the fault tolerant circuit in both the absence and presence of a single transient fault.
+So next we delete all but one of the neighboring repeats, to obtain a valid trace on the shortened list of wires.
+Theorem 1 in the upcoming section shows that $h^A(\sigma)$ will be a trace from the original circuit.
+Using this mapping we will show that the original circuit is equivalent to half of the fault-tolerant circuit in both the absence and presence of a single transient fault.
 %do I need to define all the new transitions in duplicated circuit?  maybe
@@
     \includegraphics[width=.8\textwidth]{counterexhalf}
-  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault tolerant circuit}
+  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault-tolerant circuit}
   \label{fig:counterexhalf}
@@
 Assume that for the original circuit starting in state 0, both (state 0, state 1, state 3, state 6) and (state 0, state 2, state 5, state 6) are prefixes of valid traces.
-Then both halves in the fault tolerant circuit will transition based on the traces of the original circuit, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
+Then both halves in the fault-tolerant circuit will transition based on the traces of the original circuit, with the added caveat that for a wire to transition at some state, it must be excited in both halves.
 Since only one wire transitions at a time, it is possible for say $a^A$ to transition first and $a^B$ to transition later.
@@
 Thus the two halves need not have the same trace.
-One criticism may be that the current fault tolerant transformation synchronizes at the outputs of the logic blocks.
+One criticism may be that the current fault-tolerant transformation synchronizes at the outputs of the logic blocks.
 If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
@@
 
-Another wrong approach for the fault tolerant transformation is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.
+Another wrong approach for the fault-tolerant transformation is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault-tolerant circuit, then some signals may transition out of order.
 We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.
@@
 Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined trace no longer maps back to a valid trace in the original state graph.
-Another approach we may take is to record the first transition of a wire in either half of the fault tolerant circuit.
+Another approach we may take is to record the first transition of a wire in either half of the fault-tolerant circuit.
 For example, if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.
@@
 For the original circuit, if the circuit starts from this initial state, then the synthesis method ensures semi-modularity in all traces.
-However, the proposed fault tolerant transformation adds logic, and the set of traces and initial state may be different from those of the original circuit, even after applying the half circuit mappings.
+However, the proposed fault-tolerant transformation adds logic, and the set of traces and initial state may be different from those of the original circuit, even after applying the half circuit mappings.
 Thus we need to ensure that after the transformation, the circuit behaves in a similar way to the original circuit.
-That is for an initial state of the fault tolerant circuit, which is related to the initial state of the original circuit, the resulting traces will behave similarly and have properties such as semi-modularity and the same stopping states as the original circuit.
+That is for an initial state of the fault-tolerant circuit, which is related to the initial state of the original circuit, the resulting traces will behave similarly and have properties such as semi-modularity and the same stopping states as the original circuit.
 \\
@@
 
-We show how to define the initial state for the fault tolerant circuit if given the initial state for the original circuit.
+We show how to define the initial state for the fault-tolerant circuit if given the initial state for the original circuit.
 The values for the internal wires must also be set.
 These internal wires are initialized to a semi-modularity consistent value.
-Given this, we pick the following convenient initializations for the fault tolerant circuit.
+Given this, we pick the following convenient initializations for the fault-tolerant circuit.
 The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
@@
 %should I delete intermediate?
-\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed from the initial state of the original circuit.
-The wire values in the logic block and $w$ in the original circuit are copied to the corresponding wires in the A half.
+\begin{definition} A {\em valid initial state} $s'$ for the A-half of the fault-tolerant circuit is constructed from the initial state $s$ of the original circuit.  
+For the $w$ logic block and output wire $w$ in the original circuit, the wire values are copied to the corresponding logic block and output wire $w^A$ in the A-half.
 The additional wires from the C-element chain are also assigned the same value as $w$.
-That is, first assign the value of $w$ to $w^A$, then assign the value of $w$ to $c1^A$ $c2^A$ $c3^A$ as well.
-The same construction applies for the B half circuit as well.
+That is, $s(w)=s'(w^A)=s'(c1^A)=s'(c2^A)=s'(c3^A)$.
+This is repeated for all output wires in the original circuit.
+%This completes the construction for the {\em valid initial state} of the A-half circuit.
 \end{definition}
 %\textbf{
-This definition is stronger than it needs to be but is convenient.\\
+The same construction applies for the B-half circuit as well.  Given this definition, both the A-half and B-half initial states are constructed from the same initial state of the original circuit.  
+There is a larger set of states that could serve as initial states of the fault-tolerant circuit, but this definition is sufficient for our purposes.\\
 
@@
 
-In normal operation, the fault tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.  
-This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault tolerant circuit.
+In normal operation, the fault-tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.  
+This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault-tolerant circuit.
 The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.
@@
 
-%To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
+%To avoid overly clunky sentences, we will assume that fault-tolerant circuits start from the same valid intial state in both halves.
 One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.\\
-%For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.
+%For all subsequent discussion in this document, when we talk about the trace of a fault-tolerant circuit we assume that both half circuits start from the same valid initial state.
 I will not include this assumption in the following lemma definitions to avoid complicated wording.
@@
 To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.
-That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
-And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.
+That is, the set of traces of the fault-tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
+And likewise after applying a mapping of $h^B$ to the fault-tolerant circuit.
 We show this through several Lemmas.
@@
 %since it's a transition, then all previous transitions must also be in the set of traces, in fact they must all be a sequence of at least one trace (true because if excited, must be excited in all states of same name)
- original circuit.  This is a strong result; it is true for arbitrary behavior of
-wires in the other half circuit, so long as those wire values are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
+ original circuit.  This is a strong result; it is true for  {\em arbitrary behavior} of
+wires in the other half circuit, so long as those wire values are well-formed Boolean values and also does not cause the fault-free half to deviate from well-formed Boolean values.  
 This result is also significant later in proving fault tolerance under a single transient fault since at least one of the halves is always fault-free.
@@
 
-Note that Lemma 1 allows for the possiblity of the fault tolerant circuit to stop at states that are not stopping states in the original circuit.
+Note that Lemma 1 allows for the possiblity of the fault-tolerant circuit to stop at states that are not stopping states in the original circuit.
 This is an important point as we do not want our transformed circuit to stop prematurely.
 We call such premature stopping states, if they exist, as deadlocked states:
-\begin{definition}A {\em deadlocked state} is a stopping state of the fault tolerant circuit but not a stopping state of the original circuit.\end{definition}
+\begin{definition}A {\em deadlocked state} is a stopping state of the fault-tolerant circuit but not a stopping state of the original circuit.\end{definition}
 We use {\em deadlock} to mean the existence of such deadlocked states.  
 Then, Lemma 2 shows deadlock does not occur during normal operation.
-Combining these two Lemmas, we can show that all traces in the fault tolerant circuit can be mapped to a trace in the original circuit.\\
+Combining these two Lemmas, we can show that all traces in the fault-tolerant circuit can be mapped to a trace in the original circuit.\\
 % and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
@@
 \begin{lemma}[1]
-If $\sigma$ is the trace of the fault tolerant circuit where the A half begins in a valid initial state and is fault free, then the following three properties are true:
+For every trace $\sigma$ of the fault-tolerant circuit which is fault free and the A half begins in a valid initial state, the following three properties hold: %still kind of weird wording
 \begin{itemize}
-\item P1: The half-circuit mapping of a prefix of $\sigma$, $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit, regardless of the wire values in the B half.
-\item P2: The logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
-\item P3: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
-We also call this condition: wireblock $w$ is excited.
-(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
+\item P1: The half-circuit mapping of a prefix of $\sigma$, written as $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit, regardless of the wire values in the B half.
+%\item P2: The logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
+\item P2: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault-tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
+When one of these conditions holds, we say “the wireblock $w$ is excited.”  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault-tolerant circuit.
+(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)
 \end{itemize}
 
-%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).
+%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault-tolerant circuit (the trace is possibly finite).
 
@@
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of the fault tolerant circuit.
-We will show that for any prefix of the trace $\sigma_n$, where $n$ is any value from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit, by induction on $n$.
+Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ 
+that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show the induction hypotheses hold in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state.
+We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state.
 \begin{itemize}
@@
 Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and P1 holds.
-\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state and P2 holds.
+%\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state so P2 holds.
 \item 
@@
 Thus any excitations must be on $c1^A$.
-Since all output/input wires have the same values in the original and fault tolerant circuit and the logic blocks are in semi-modularity consistent states, then if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault tolerant circuit.
-Similarly if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault tolerant circuit.
-This shows the valid initial state satisfies P3.    %is this enough.... that the existing states follow that iff statement?
+Since all output/input wires have the same values in the original and fault-tolerant circuit, if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault-tolerant circuit.
+If wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.
+This shows the valid initial state satisfies P2.
+%is this enough....
+that the existing states follow that iff statement?
 \end{itemize}
 
-The induction step is to assume that the induction hypotheses is true for a length k prefix of the trace $\sigma_k$.
-We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.
-In particular for all possible next states from the current state $s_k$, we show that either the output wires have not transitioned, or in the case of a transition that it is also a transition of the original circuit.
-Then we show that the logic blocks in all possible next states remain in a semi-modularity consistent state.
-And finally that P3 is true and all wire blocks in the next states are in one of the cases in Figure \ref{fig:l1helper}.\\
-
+The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of the trace.
+We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist.
+First, in the fault-tolerant circuit, for all possible transitions from current state $s_k$, we show that after applying the half circuit mapping there is either no transitions in the original circuit or it is also a transition of the original circuit, and thus P1 is true.
+%(very long, very badly worded sentence, need to fix it)  
+Second, we show for all possible next states $s_{k+1}$ that P2 is true and all wire blocks in $s_{k+1}$ are in one of the cases in Figure \ref{fig:l1helper}.\\
+
+Since P1 and P2 are true for all states in $\sigma_k$, they must also be true for the current state $s_k$.
 From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.
-Transitions in the B-half do not change wire values in the A-half and can be ignored.
+We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.
 Wire blocks in the A-half are in one of the cases in Figure \ref{fig:l1helper}, thus transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.
-By P3, if a wire block $w$ is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$..
+(By P2, if a wire block $w$
+%(is wire block defined?) 
+is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.
 To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.
+)
 
 % which by P3 applied to state $s_k$, implies that the corresponding wire is also excited in the original circuit.
-%By P3, wires in the fault tolerant circuit may change only if the wire block is excited, which implies wire $w$ is also excited in the original circuit in state $h^A(s_k)$.
+%By P3, wires in the fault-tolerant circuit may change only if the wire block is excited, which implies wire $w$ is also excited in the original circuit in state $h^A(s_k)$.
 
@@
   \centering
-    \includegraphics[width=\textwidth]{gatewl1}
-  \caption{Different cases of P3 for a wireblock a-d are excited and e is unexcited.  a) case 1, b) case 2, c) case 3, d) case 4, e) case 5}
+    \includegraphics[width=\textwidth]{gatewl2}
+  \caption{Different cases of P2 for a wireblock, a-d correspond to excited wire in the original circuit and e is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
   \label{fig:l1helper}
@@
 
+We first show that P1 is true for $\sigma_{k+1}$.
+We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).
+%(maybe still need to be more clear about wire block vs transitions)
+If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.
+Thus in the new state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.
+For all 3 cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
+This is a repeated state under the half circuit mapping and is deleted in the resulting trace.
+Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit.
+\\
+Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.
+Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.
+Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit.
+\\
+
+Next, we show that P2 is true for $\sigma_{k+1}$.
+Again we consider all possible transitions that lead to the new state $s_{k+1}$.
+The wireblock which transitions, which we again name $w$, is in one of cases 1-4.
+
 \begin{itemize}
-\item We consider cases 1-3 together (a-c in Figure \ref{fig:l1helper}) for some excited wire block $w$.
-For each case, it is clear that in the fault tolerant circuit, the transition propagates down the C-element chain as shown in the figure.
-The transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
+\item Again, we consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).
+We use the following fact from the P1 proof: in the new state $s_{k+1}$, the wireblock $w$ is in cases 2-4 respectively and $h^A(s_{k+1})=h^A(s_{k})$.
+Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A{s_{k+1}}$.
+Then $w$ in the original circuit remains excited in state $h^A{s_{k+1}}$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.
+Thus, wireblock $w$ satisfies P2.
+All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.
+%(explain why?
+does it involve `P2')
+Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2, so P2 is true for the trace $\sigma_{k+1}$.
+
+%The transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
 The wire $w$, in the original circuit, is then excited in state $h^A(s_{k+1})$ and P3 holds for wire $w$.
 For the remaining output wires, P3 holds because again $h^A(s_{k+1})=h^A(s_{k})$, so the excitation of all output wires in the original circuit do not change in state $h^A(s_{k+1})$.
-The wire blocks in the fault tolerant circuit also remain in the same case of Figure \ref{fig:l1helper} in $s_{k+1}$.
+The wire blocks in the fault-tolerant circuit also remain in the same case of Figure \ref{fig:l1helper} in $s_{k+1}$.
 Thus P3 holds for all wires in state $s_{k+1}$.
@@
 %\item The first case is for an excited wire $w$.
-In the fault tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
+In the fault-tolerant circuit, wire $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.
 Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.
@@
 
-\item Case 4 is when $w^A$ transitions in the fault tolerant circuit, shown in case d of Figure \ref{fig:l1helper}.
+\item The last case is when a transition occurs from case 4.
+That is, $w^A$ transitions in the fault-tolerant circuit from case d of Figure \ref{fig:l1helper}.
 %The original circuit transitions to state $h^A(s_{k+1})$ where wire $w$ transitions.
-Thus $w$ transitions in the original circuit as seen by comparing $h^A(s_k)$ and $h^A(s_{k+1})$.  
+As mentioned in the P1 proof, applying the half circuit mapping results in wire $w$ transitioning in the original circuit.  
 %applying the $h^A$ mapping to state $s_{k+1}$ indicates that $w$ transitions in the original circuit.  
-Because $w$ is excited in state $h^A(s_k)$, then the transition to the next state is a valid transition of the state graph (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and P1 holds.
-Because $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, then inputs to all logic blocks in the A-half are also semi-modularity consistent in state $s_{k+1}$ and P2 holds.
-Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.
-A change in wire $w$ fanouts to other logic blocks which may change their excitations in response.
+We show this transition affects the excitation state of wire blocks/wires in both the fault-tolerant circuit and the original circuit such that P2 is satisfied for $s_{k+1}$.
+By P2 of state $s_k$, we partition the wire blocks in the fault-tolerant circuit in state $s_k$ into five cases, as described in Figure \ref{fig:l1helper}.
+Note that because wire $w^A$ transitions, wireblock $w$ is a special case of case 4 which we deal with separately from other wireblocks in case 4.
+%Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.
+A change in wire $w$ fans out to other logic blocks which may change their excitations in response.
 Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
@@
 \item
-For wires $v$ that are excited in state $h^A(s_k)$ and excited in state $h^A(s_{k+1})$ in the original circuit, the wire block $v$ must be in cases 1-4 of Figure \ref{fig:l1helper} at state $s_k$.
+For wireblocks in cases 1-4 (not including wireblock $w$), we show that these wireblocks remain in the same case in state $s_{k+1}$.
+Let us call a wireblock in one of these states as $v$.
+By P2 of state $s_k$, wire $v$ of the original circuit is excited in state $h^A(s_{k})$.
+Since the original circuit is semi-modular and $v$ does not transition, then $v$ must remain excited in state $h^A(s_{k+1})$.
+In the fault tolerant circuit, we only need to examine the logic block portion of the wireblock since the transition is not in $v$.
+\\
+state $s_{k+1}$ Case 1 is straight forward since the inputs of $c1^A$ in the fault-tolerant circuit and $v$ in the original circuit are equal under the half circuit mapping and the wire values $c1^A$ and $v$ are equal as well.
+Therefore $c1^A$ must have the same excitation as $v$, that is, excited.
+If $v$ is in case 1 in state $s_k$, then $c1^A$ remains excited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 1 in state $s_{k+1}$.
+\\
+In Cases 2-4, the logic block of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.
+The logic block of the fault-tolerant circuit remains unexcited in state $s_{k+1}$, which is by contradiction.
+Suppose that there is some $v$ where the logic block becomes excited in state $s_{k+1}$, then $v$ in the original circuit and $c1^A$ in the fault tolerant circuit are excited in opposite directions.
+Since the logic blocks for $v$ and $c1^A$ are identical and one of gates or C-element, the excitation is determined purely by its inputs.
+Again the inputs to $c1^A$ and $v$ are equal so these input values cause the logic block to excite to both 1 and 0 at the same time.
+This cannot happen in any of the elements that we build are circuit from and is therefore a contradiction.
+%(change this into a new lemma?)
+Thus, if $v$ is in case 2-4 in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 2-4 in state $s_{k+1}$.  
+Combined with $v$ staying excited in the original circuit in state $h^A(s_{k+1})$, any wireblocks in these 4 cases satisfy P2 in state $s_{k+1}$.
+
+%For wires $v$ that are excited in state $h^A(s_k)$ and excited in state $h^A(s_{k+1})$ in the original circuit, the wire block $v$ must be in cases 1-4 of Figure \ref{fig:l1helper} at state $s_k$.
 If $w^A$ does not feed into wire block $v$ then wire block $v$ stays in the same case in state $s_{k+1}$.
-Furthermore, if wire block $v$ is in case 1, then the inputs and $c1^A$ and $v$ wires match in the fault tolerant and original circuits, thus $c1^A$ is also excited in state $s_{k+1}$ and wire block $v$ remains in case 1.
+Furthermore, if wire block $v$ is in case 1, then the inputs and $c1^A$ and $v$ wires match in the fault-tolerant and original circuits, thus $c1^A$ is also excited in state $s_{k+1}$ and wire block $v$ remains in case 1.
 If wire block $v$ is in cases 2-4, then $c1^A\neq v$ and we cannot apply the same logic.
 The correct reasoning is outlined in Figure \ref{fig:sml1} and described as follows.
-Since $v$ is excited in state $h^A(s_{k+1})$, then $v$ can transition to a state $h^A(s_{k+2})$.
-Now we compare the original circuit in state $h^A(s_{k+2})$ and the fault tolerant circuit in state $s_{k+1}$.
-  The inputs of $v$ in state $h^A(s_{k+2})$ are equal to the inputs to wireblock $v$ in state $s_{k+1}$ (since $v$ is not its own input) and $c1^A=v$, therefore $c1^A$ must be unexcited in state $s_{k+1}$.
+%Since $v$ is excited in state $h^A(s_{k+1})$, then $v$ can transition to a state $h^A(s_{k+2})$.
+Now we compare the original circuit in state $h^A(s_{k+2})$ and the fault-tolerant circuit in state $s_{k+1}$.
+%  The inputs of $v$ in state $h^A(s_{k+2})$ are equal to the inputs to wireblock $v$ in state $s_{k+1}$ (since $v$ is not its own input) and $c1^A=v$, therefore $c1^A$ must be unexcited in state $s_{k+1}$.
 Thus wire block $v$ stays in the same case for cases 2-4.
-We have shown for all such wires $v$, the corresponding wire block stays in the same case in the fault tolerant circuit, so P3 holds for wires of this type.
+We have shown for all such wires $v$, the corresponding wire block stays in the same case in the fault-tolerant circuit, so P3 holds for wires of this type.
+
 %by semi-modularity $c1^A$ of $v$ in the A-half circuit will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy P3.
 %semi-modularity part still needs to be fixed
-\begin{figure}
-  \centering
-    \includegraphics[width=\textwidth]{sml1}
-  \caption{An example of wire block $v$ in case 2.
-The firgure shows wire block $v$ in the fault tolerant circuit and wire $v$ in the original circuit in states $s_k$ and $s_{k+1}$.
+
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=\textwidth]{sml1}
+%  \caption{An example of wire block $v$ in case 2.
+The figure shows wire block $v$ in the fault-tolerant circuit and wire $v$ in the original circuit in states $s_k$ and $s_{k+1}$.
 Each arrow denotes a transition}
-  \label{fig:sml1}
-\end{figure}
+%  \label{fig:sml1}
+%\end{figure}
 \item
-By semi-modularity, if a wire is excited in state $h^A(s_{k})$ and does not transition, then it remains excited in state $h^A(s_{k+1})$.  
-Thus, the only wire that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (since $w$ is not its own input).
-  In state $s_{k+1}$, $w^A$ transitions and since $c1^A=w$, $c1^A$ remains unexcited, so wire block $w$ is in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wire $w$.  
+Wireblock $w$ is a case of its own.
+Wire $w$ in the original circuit in state $h^A(s_{k+1})$ has just transitioned and is unexcited since $w$, (this explanation is still a bit weird) the only wire value that changed, is not an input to itself.
+In the fault-tolerant circuit, $w^A$ just transitioned and none of the C-element down the chain is excited.
+$c1^A$ must remain unexcited since $w$ is unexcited in the original circuit.
+Thus wireblock $w$ in state $s_{k+1}$ is in case 5 of Figure \ref{fig:l1helper}.
+And as previously mentioned, wire $w$ is unexcited in state $h^A(s_{k+1})$ and thus P2 holds for wire block $w$.
+
+%By semi-modularity, if a wire is excited in state $h^A(s_{k})$ and does not transition, then it remains excited in state $h^A(s_{k+1})$.  
+%Thus, the only wire that is excited in state $h^A(s_{k})$ and unexcited in state $h^A(s_{k+1})$ is the transitioning wire $w$ (since $w$ is not its own input).
+%  In state $s_{k+1}$, $w^A$ transitions and since $c1^A=w$, $c1^A$ remains unexcited, so wire block $w$ is in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wire $w$.  
 \item
-For wires $u$ that are unexcited in state $h^A(s_{k})$ and transition to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in case 5 of Figure \ref{fig:l1helper}.
+For wires in case 5 in state $s_k$, we name such a wire $u$.
+$u$ is unexcited in the original circuit in state $h^A(s_{k})$ by P2.
+There are two possibilities: if $u$ is excited in state $h^A(s_{k+1})$, then logic block $u$ in the fault-tolerant circuit is also excited in state $s_{k+1}$.
+This is because the inputs to $u$ and $c1^A$ of wireblock $u$ are the same in the original circuit and fault-tolerant circuit by the half circuit mapping, and $c1^A=u$, then $c1^A$ is also excited in state $s_{k+1}$.
+Wire block $u$ is in case 1 of Figure \ref{fig:l1helper} in state $s_{k+1}$.
+Thus P2 holds for wires of this type in state $s_{k+1}$.\\
+The second possibility is if $u$ remains unexcited in state $h^A(s_{k+1})$.
+By similar reasoning as above $c1^A$ of wireblock $u$ is unexcited in state $s_{k+1}$ and the wireblock stays in case 5 of Figure \ref{fig:l1helper}.
+Thus P2 holds for wires of this type.
+%$u$ that are unexcited in state $h^A(s_{k})$ and transition to excited in state $h^A(s_{k+1})$, in state $s_{k}$ the wire block $u$ is in case 5 of Figure \ref{fig:l1helper}.
 But since wire $u$ in the original circuit is excited in state $h^A(s_{k})$ and $c1^A=u$, then $c1^A$ is also excited in state $s_{k+1}$ and the wire block $u$ is in case 1 of Figure \ref{fig:l1helper}.
 Thus P3 holds for wires of this type.
-\item
-Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, $c1^A$ is unexcited and the wire block stays in case 5 of Figure \ref{fig:l1helper}.  Thus P3 holds for wires of this type. 
+%\item
+%Finally for wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, $c1^A$ is unexcited and the wire block stays in case 5 of Figure \ref{fig:l1helper}.
+Thus P3 holds for wires of this type.
 \end{itemize}
-Then the induction hypotheses are true for any transition from this case. 
+We have covered all possible wire cases in the circuit.   
+Then P2 is true for any transition from case 4. 
 \end{itemize}
@@
 This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transition in a completely predictable pattern and thus deadlock does not occur.
-To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.
+To avoid overly clunky sentences, we will assume that fault-tolerant circuits start from the same valid intial state in both halves.
 One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.
@@
 \begin{lemma}[2.1]
-For any trace of the fault tolerant circuit, each wire block follow the state diagram in Figure \ref{fig:l21} (up to 0 and 1 inversion).
+For any trace of the fault-tolerant circuit, each wire block follow the state diagram in Figure \ref{fig:l21} (up to 0 and 1 inversion).
 \end{lemma}
@@
 We look at the base case of $\sigma_1$ which is also $s_1$ initialized as a valid initial state.
-For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
-Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault tolerant circuit are in case 3b of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
+For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault-tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
+Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault-tolerant circuit are in case 3b of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
 Thus the lemma property holds for the base case.
@@
 This shows that all wire blocks in all possible $s_{k+1}$ follow the state diagram, and the induction step is complete.\\
-By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit follow the state diagram in Figure \ref{fig:l21} for all traces. \\
+By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault-tolerant circuit follow the state diagram in Figure \ref{fig:l21} for all traces. \\
 \end{proof}
@@
 \begin{lemma}[2.2]
-For all traces $\sigma$ in the fault tolerant circuit, deadlock does not occur.
+For all traces $\sigma$ in the fault-tolerant circuit, deadlock does not occur.
 \end{lemma}
 \begin{proof}
-To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the fault tolerant circuit.
+To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the fault-tolerant circuit.
 The state $s_k$ can be split into two cases, one is that all output wire pairs in the A half and B half are equal, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.
@@
 
-Combining the results of the previous Lemmas shows that the fault tolerant circuit is equivalent to the original circuit under normal operation.  This is defined formally in a theorem as follows:
+Combining the results of the previous Lemmas shows that the fault-tolerant circuit is equivalent to the original circuit under normal operation.  This is defined formally in a theorem as follows:
 \begin{theorem}[1]
-For all traces $\sigma$ in the fault tolerant circuit, $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For all traces $\sigma$ in the fault-tolerant circuit, $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
@@
 %fix this
-Next we consider what happens to the fault tolerant circuit under a single transient fault which is defined as follows:
+Next we consider what happens to the fault-tolerant circuit under a single transient fault which is defined as follows:
 \begin{definition}A {\em transient fault} on a wire $w$ causes a transition $w= \lnot w^{prev}$.
@@
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
+For all traces $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
 \end{lemma}
@@
 The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
-The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault tolerant circuit does not deadlock under a single transient fault.\\
+The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
 
@@
 \begin{theorem}[2]
-When a single transient fault occurs, if $\sigma$ is a trace in the fault tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) for all $n \in \mathbb{N}$ is a prefix of a trace in the original circuit.
+When a single transient fault occurs, if $\sigma$ is a trace in the fault-tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) for all $n \in \mathbb{N}$ is a prefix of a trace in the original circuit.
 And the circuit does not deadlock.
@@
 
-Thus we have shown that under a single transient fault that the transformed circuit has a half that behaves like the original circuit and the transformation is a fault tolerant transformation.
+Thus we have shown that under a single transient fault that the transformed circuit has a half that behaves like the original circuit and the transformation is a fault-tolerant transformation.
 
 \chapter{Conclusions}
-In this work, we have proposed a fault tolerant circuit transformation of asynchronous control circuits using duplication and a chain of C-elements.
+In this work, we have proposed a fault-tolerant circuit transformation of asynchronous control circuits using duplication and a chain of C-elements.
 This is more transistor efficient than TMR and the doubled inputs duplication approaches.
-We also proposed a method of comparing the fault tolerant circuit with the original circuit, by comparing traces with the half circuit.
+We also proposed a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.
 And finally we showed the transformation of the circuit makes it fault tolerat to transient faults at the gate level implementation of the asynchronous circuit\\
@@
 
-Some future work to extend this model would be to allow for arbiters, mutual exclusion elements by making them transient fault tolerant as well.
+Some future work to extend this model would be to allow for arbiters, mutual exclusion elements by making them transient fault-tolerant as well.
 We can also extend fault tolerance to permanent faults, we have an initial idea of adding a timer and restart mechanism to get past the deadlock that accompanies permanent faults.

### 2019-10-12 draft_together3.tex
10-12 after restructuring Lemma1 to FT cases

@@
 First, in the fault-tolerant circuit, for all possible transitions from current state $s_k$, we show that after applying the half circuit mapping there is either no transitions in the original circuit or it is also a transition of the original circuit, and thus P1 is true.
-%(very long, very badly worded sentence, need to fix it)  
+(very long, very badly worded sentence, need to fix it)
 Second, we show for all possible next states $s_{k+1}$ that P2 is true and all wire blocks in $s_{k+1}$ are in one of the cases in Figure \ref{fig:l1helper}.\\
@@
 (By P2, if a wire block $w$
-%(is wire block defined?) 
+(is wire block defined?) 
 is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.
@@
 We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).
-%(maybe still need to be more clear about wire block vs transitions)
+(maybe still need to be more clear about wire block vs transitions)
 If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.
@@
 All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.
-%(explain why?
+(explain why?
 does it involve `P2')
@@
 This cannot happen in any of the elements that we build are circuit from and is therefore a contradiction.
-%(change this into a new lemma?)
+(change this into a new lemma?)
 Thus, if $v$ is in case 2-4 in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 2-4 in state $s_{k+1}$.  

### 2019-10-22 draft_together3.tex
in progress with comments

@@
 \begin{lemma}[1]
-For every trace $\sigma$ of the fault-tolerant circuit which is fault free and the A half begins in a valid initial state, the following three properties hold: %still kind of weird wording
+Consider a fault-tolerant circuit that is fault free and its A half begins in a valid initial state.
+For every trace $\sigma$ of this circuit, the following two properties hold: %still kind of weird wording
 \begin{itemize}
@@
 \item P2: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault-tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
-When one of these conditions holds, we say “the wireblock $w$ is excited.”  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault-tolerant circuit.
+When one of these conditions holds, we say “the wireblock $w^A$ is excited.”  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault-tolerant circuit.
 (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)
@@
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ 
-that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
+Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.
+We will show by induction on $n$ that Lemma 1 is true for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace.
+%We will show by induction on $n$ that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state.
+We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
 \begin{itemize}
-\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction.
+\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction. %how to compare with OG circuit NEED TO FIX!!
  Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and P1 holds.
@@
 \item 
-For any wire, $c1^A$, $c2^A$, $c3^A$ and $w^A$ are assigned the same values by the valid initial state.
-Thus any excitations must be on $c1^A$.
+For any wire, the valid initial state (definition) assigns wires $c1^A$, $c2^A$, $c3^A$ and $w^A$ the same values.
+Therefore only wire $c1^A$ may be excited.
 Since all output/input wires have the same values in the original and fault-tolerant circuit, if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault-tolerant circuit.
+%ANOTHER INSTANCE OF MAY BE USING ANOTHER LEMMA, observation?
 If wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.
@@
 
-The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of the trace.
-We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist.
-First, in the fault-tolerant circuit, for all possible transitions from current state $s_k$, we show that after applying the half circuit mapping there is either no transitions in the original circuit or it is also a transition of the original circuit, and thus P1 is true.
-(very long, very badly worded sentence, need to fix it)
-Second, we show for all possible next states $s_{k+1}$ that P2 is true and all wire blocks in $s_{k+1}$ are in one of the cases in Figure \ref{fig:l1helper}.\\
-
-Since P1 and P2 are true for all states in $\sigma_k$, they must also be true for the current state $s_k$.
+The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of a given trace.
+We will prove that the induction hypothesis is true for $\sigma_{k+1}$ by first proving it for the set of all possible traces of length $k+1$ (including prefix of traces longer than $k+1$) with $\sigma_k$ as their first $k$ terms.
+%/length $k$ prefix
+The trace $\sigma_{k+1}$ is an element in this set and consequently the induction hypothesis is true for $\sigma_{k+1}$ as well.  
+%We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist. 
+To show the hypothesis is true for all such length $k+1$ traces, it is equivalent to considering all possible transitions from the state $s_k$ and showing the hypothesis is true for the new state $s_{k+1}$ in the fault-tolerant circuit.\\
+
+In fact, the possible transitions can be neatly partitioned into the cases in Figure \ref{fig:l1helper}.
 From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.
 We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.
-Wire blocks in the A-half are in one of the cases in Figure \ref{fig:l1helper}, thus transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.
+In addition, from the induction hypothesis, P1 and P2 are true for the current state $s_k$.
+Thus wire blocks in the A-half in state $s_k$ are in one of the cases in Figure \ref{fig:l1helper}, and the transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.
 (By P2, if a wire block $w$
-(is wire block defined?) 
 is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.
 To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.
-)
+) \\
 
@@
 
+We prove P1 and P2 sequentially for $s_{k+1}$.  The proof for P1 only relies on the induction hypothesis being true in state $s_k$ and is as follows: \\
+
+\begin{itemize}
 We first show that P1 is true for $\sigma_{k+1}$.  
-We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).
-(maybe still need to be more clear about wire block vs transitions)
+\item We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}). (maybe still need to be more clear about wire block vs transitions) 
 If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.
@@
 Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit.
-\\
-Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.
+\item Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.
 Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.
 Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit.
-\\
-
-Next, we show that P2 is true for $\sigma_{k+1}$.
+\end{itemize}
+
+Next, we show that P2 is true for $s_{k+1}$.
 Again we consider all possible transitions that lead to the new state $s_{k+1}$.

### 2019-11-23 draft_final.tex
final

--- 2019-10-22 draft_together3.tex
@@
 \chapter{Introduction}
-Digital circuits is the basis of many of present day electronics.
+
+Faults in digital circuits arise from sources such as fabrication defects and radiation.
+These faults can ultimately lead to failures of the component.
+Thus fault tolerant designs are crucial especially in applications where errors can have disastrous consequences such as in aviation or banking.
+Moreover, due to new technology and shrinking transistor sizes for MOSFETs, radiation effects become more prominent.
+Because designing fault-tolerant circuits is such an important problem, there has been significant previous work done on fault-tolerance for synchronous circuits.
+However there are less work done on fault-tolerant asynchronous circuits.
+The research described here aims to fill that gap.\\
+
+Asynchronous circuits differ from synchronous circuits in that the gates have arbitrary delays so asynchronous designs must be more meticulous to account for these delays.
+The arbitrary delays also make fault-tolerance a harder problem.
+For example, the classic solution of Triple Modular Redundancy (TMR) does not work for asynchronous circuits.
+The main contribution of this work is proposing a new fault-tolerant design for asynchronous circuits.
+The new design expands fault-tolerance to semi-modular speed independent circuits composed of two-input gates and C-elements.
+This work also proves that the proposed fault-tolerant design is tolerant to transient faults.
+With this new design, circuits can be more robust to different types of errors, allowing the circuits to be used in a greater variety of environments.
+
+%Digital circuits is the basis of many of present day electronics.
 Digital circuits has signals which are represented as discrete values.
@@
 
-Although digital circuits are less sensitive to errors due to noise, it can experience other faults in its electronics which ultimately may lead to failure of the component.
+%Although digital circuits are less sensitive to errors due to noise, it can experience other faults in its electronics which ultimately may lead to failure of the component.
 Faults may arise due to fabrication defects and radiation such as from space.
@@
 
-This work focuses on a class of digital circuits known as asynchronous circuits.
+%This work focuses on a class of digital circuits known as asynchronous circuits.
 There is an arbitrary delay on the gates of asynchronous circuits so that each design must be additionally verified to operate correctly under such delays.
@@
 The time it takes for gates to process input signals and then propagate the output to the next gates in a digital circuit may vary widely.
-If the timing is somehow off, it is possible for the outputs to be different from the desired value and may cause harm.
+If the timing is somehow off, it is possible for the outputs to be different from the desired value resulting in incorrect computation.
 In synchronous systems this timing variation is dealt with by using a global clock.
@@
 \\
+\begin{figure}
 \includegraphics[width=\textwidth]{syncex}
 \captionof{figure}{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
+\end{figure}
 %possible picture of clock and flip flops?.... redraw as my own
@@
 Asynchronous circuits, as the name suggests, do not depend on a clock.
-As a result there are varying time delays in its components.
-The goal of designing asynchronous circuits is to make circuits that achieves some specification in spite of the time delays.
-That is, irrespective of the time delays, the circuit behaves the same way.
-One main reason that asynchronous circuits are used is that because it does not require clocks to propagate signals, instead as soon as one logic element finishes the signal goes directly to the next element.
+As a result there are varying time delays in their components.
+The goal of designing asynchronous circuits is to make circuits that achieve some specification in spite of the time delays.
+That is, irrespective of the time delays, the circuit meets its specification.
+One main reason that asynchronous circuits are used is that they do not require clocks to propagate signals; instead as soon as one logic element finishes the signal goes directly to the next element.
 This can allow the circuits to have speedups as it is not waiting for the slowest element for each clock cycle.
@@
 Additionally even in synchronous systems, small asynchronous circuits are needed to match the inputs coming in from different circuits with different clock frequencies or from the outside world.
-For large synchronous circuits clock skew from different parts of the system is also an issue and may be solved with asynchronous methods.
+For large synchronous circuits, clock skew from different parts of the system is also an issue and may be solved with asynchronous methods.
 \\ %Martin did not give references for these....prob ok then
@@
 
-Muller circuits is the approach that D.
+D.
 E.
-Muller originally proposed based on this delay model \cite{Muller_59}.
+Muller proposed essentially this class of speed independent circuits, which are sometimes called Muller circuits \cite{Muller_59}.
 Since then a number of synthesis methods following this design has been produced.
-Usually the synethsis methods begin with some higher-level specification such as signal transition graph or petri nets and translate into a state graph.
-State graphs describes the progression of changes of a finite number of signals.
-(The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allows the circuit to function according to the state graph is synthesized.
+Usually the synthesis methods begin with some higher-level specification such as signal transition graph or Petri nets and translate into a state graph.
+A state graph describes all the possible sequences of changes in a finite number of signals.
+(The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allow the circuit to function according to the state graph is synthesized.
 The end result is a hazard-free and speed independent asynchronous circuit.
-We assume that the previous steps are hidden, and are presented with a semi-modular circuit to make fault-tolerant.
-There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.
+The construction we describe begins with a semi-modular circuit, possibly resulting from the previously described process, and transforms it into a circuit that can tolerate any single transient fault.
+
+%There are other types of delay models and asynchronous circuit synthesis methods such as Quasi Delay Insensitive circuits and the relevant types for this work are described in more detail in the literature review.
 \\  %add refs to gen C etc
@@
 %why are async circuits important, timing delay etc
-Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work put into making digital circuits fault-tolerant.
-Most of the fault-tolerant solutions has been investigated for synchronous digital circuits.
+Because these various faults can interfere with the function of the circuit and even result in harmful operations (catastrophic failures), there has been a lot of work on making digital circuits fault-tolerant.
+Most of the fault-tolerant solutions have been investigated for synchronous digital circuits.
 Because the timing difference between different signals arriving do not have to be considered for synchronous circuits, they can use error correcting codes and redundancy techniques such as triple modular redundancy (TMR).
-Unfortunately many of these techniques have problems if directly implemented in asynchronous circuits.\\
+Unfortunately most of these techniques are not applicable to asynchronous circuits.\\
 
@@
 We also propose a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.
-The fault free half of the fault-tolerant circuit behaves like the original circuit under single transient faults.
-In addition, we assume a gate level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\
-
-In the rest of this work, in chapter two, I will first introduce the different types of common faults and their causes, as well as the common fault models that researchers use when investigating these faults.
-Then I will go into depth about the asynchronous circuit models that are relevant to this work.
-I will then go through the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.
-In chapter three, I will show why the existing fault-tolerant methods are insufficient and propose a new fault free method for asynchronous transient faults.
-I will prove using logical proofs as well as formal verification methods to show why my new method always works.
-In the final chapter, chapter four, I will conclude on how to better build fault free asynchronous circuits and suggest some possible new research directions.
+The fault-free half of the fault-tolerant circuit behaves like the original circuit under single transient faults.
+In addition, we assume a gate-level model of the circuit and allow the transient to occur on any of the wires thus solving the transient fault problem for a bigger class of circuits than the current state-of-the-art.\\
+
+The rest of this work is organized as follows.
+Chapter two introduces the different types of common faults and their causes, as well as the common fault models that researchers use when investigating these faults.
+Also included in chapter two are the asynchronous circuit models that are relevant to this work.
+In addition, there is discussion about the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.
+Chapter three provides the background terminology and definitions for asynchronous circuits.
+Chapter four shows why the existing fault-tolerant methods are insufficient and propose a new fault-tolerant method for asynchronous transient faults.
+We prove the correctness of the method using a combination of automated formal verification and manual methods.
+And finally chapter five discusses how to better build fault-tolerant asynchronous circuits and suggests some possible new research directions.
 %Overview:  why is the problem important  \\  maybe I can extend the Introduction a bit more
@@
 The correct operation is specified when designing the circuit, for example, given some input values the circuit will return specified output values.
-There are many ways to represent specifications such as petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.
+There are many ways to represent specifications such as Petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.
 We won't go into these representations and methods in detail, other than the aspects that are relevant to this work.
@@
 
+\begin{lemma}[0]
+Given two identical logic blocks $f$ and $g$, if the inputs into $f$ and $g$ have the same values then:\\
+i)  if the outputs are the same value and $f$ is excited then $g$ is also excited.\\
+ii)  if the outputs are the same value and $f$ is unexcited then $g$ is also unexcited.\\
+iii)  if the outputs are different values and $f$ is excited then $g$ is unexcited.
+\end{lemma}
+\begin{proof}
+i) \& ii)  Since $f$ and $g$ are identical gates or C-elements then if the inputs and output are the same values, $f$ and $g$ must be both excited or both unexcited. \\
+
+iii)  We prove this by contradiction.
+Suppose that inputs to $f$ and $g$ are the same and the outputs are different values and both $f$ and $g$ are excited.
+This means that for some circuit element that these input values both cause the element to excite to 1 and 0 at the same time.
+This cannot happen in any of the elements that we build our circuit from and is therefore a contradiction.
+\end{proof}
+
+%MAPPING PROPERTY?
+In the following lemmas and theorems we compare a state $s$ in the fault-tolerant circuit with its mapped state $h^A(s)$ in the original circuit.
+Due to the mapping and architecture of the circuits, for any wire block $w$, the inputs to the logic block of $w^A$ in the fault-tolerant circuit has the same value as the inputs to the logic block of $w$ in the original circuit.
+This fact is used extensively in combination with Lemma 0.
+The excitation on $w$ in the original circuit can sometimes be deduced from semi-modularity, then by applying Lemma 0 we can also derive the excitation on $w^A$.
+\\
+%compare with original circuit: logic block with same inputs.....if input cause block to be excited... if output is same too then the state of logic block is identical.
+
 This leads to the definition and proof of Lemma 1 as follows:
@@
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.
-We will show by induction on $n$ that Lemma 1 is true for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace.
+Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ that Lemma 1 is true for the length $n$ prefix of the trace $\sigma_n$.  
 %We will show by induction on $n$ that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
+We first show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
 \begin{itemize}
-\item For every $s_1$ that is a valid initial state, we have that $h^A(s_1)$ is some state in the original circuit by construction. %how to compare with OG circuit NEED TO FIX!!
- Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and P1 holds.
+\item State $s_1$ is a valid initial state so $h^A(s_1)$ is a state in the original circuit by construction. %how to compare with OG circuit NEED TO FIX!!
+ Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and satisfies P1.
 %\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state so P2 holds.
 \item 
-For any wire, the valid initial state (definition) assigns wires $c1^A$, $c2^A$, $c3^A$ and $w^A$ the same values.
+For each wireblock, the valid initial state initializes wires $c1^A$, $c2^A$, $c3^A$ and $w^A$ to the same value.
 Therefore only wire $c1^A$ may be excited.
-Since all output/input wires have the same values in the original and fault-tolerant circuit, if wire $w$ is excited in the original circuit, then $c1^A$ must be excited in the fault-tolerant circuit.
-%ANOTHER INSTANCE OF MAY BE USING ANOTHER LEMMA, observation?
-If wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.
-This shows the valid initial state satisfies P2.
+Since the mapping gives identical inputs then by Lemma 0 i) ii) if wire $w$ is excited in the original circuit, $c1^A$ is also excited in the fault-tolerant circuit.
+And if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.
+This shows that state $s_1$ satisfies P2.
 %is this enough....
@@
 
-The induction step is to assume that the induction hypothesis is true for a length $k$ prefix $\sigma_k$ of a given trace.
-We will prove that the induction hypothesis is true for $\sigma_{k+1}$ by first proving it for the set of all possible traces of length $k+1$ (including prefix of traces longer than $k+1$) with $\sigma_k$ as their first $k$ terms.
+The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of traces of the fault-tolerant circuit.
+We will prove that the induction hypothesis is true for all length $k+1$ prefixes.
 %/length $k$ prefix
-The trace $\sigma_{k+1}$ is an element in this set and consequently the induction hypothesis is true for $\sigma_{k+1}$ as well.  
 %We will prove that the induction hypothesis is also true for all $\sigma_{k+1}$ that exist. 
-To show the hypothesis is true for all such length $k+1$ traces, it is equivalent to considering all possible transitions from the state $s_k$ and showing the hypothesis is true for the new state $s_{k+1}$ in the fault-tolerant circuit.\\
-
-In fact, the possible transitions can be neatly partitioned into the cases in Figure \ref{fig:l1helper}.
-From state $s_k$, we examine all possible transitions that change wire values in the A-half; a transition may occur on excited gates or C-elements.
-We ignore transitions in the B-half because those transitions do not change wire values in the A-half and the resulting states are deleted during the half circuit mapping.
-In addition, from the induction hypothesis, P1 and P2 are true for the current state $s_k$.
-Thus wire blocks in the A-half in state $s_k$ are in one of the cases in Figure \ref{fig:l1helper}, and the transitions in the A-half can only occur in wire blocks that are in cases 1-4 of the figure.
-(By P2, if a wire block $w$
-is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.
+Let $\sigma_k$ be an arbitrary length $k$ prefix and $s_k$ its $k$-th state.  
+To show the hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.\\
+
+In fact, the possible next states can be partitioned into transitions from each of the cases in Figure \ref{fig:l1helper}.
+To see this, we first note that examining the transitions in only the A-half is sufficient.
+Transitions in the B-half can be ignored under the $h^A$ mapping because such transitions do not change wire values in the A-half and the resulting states are deleted by the mapping.
+We know by the induction hypothesis that P1 and P2 are true for the current state $s_k$.
+In particular, P2 states that all wire blocks in state $s_k$ are in one of the cases in Figure \ref{fig:l1helper}.
+Only cases 1-4 have excited gates or C-elements that are capable of a transition.
+Thus, to cover all possible transitions, it suffices to examine transitions in an excited wire block from cases 1-4.
+\\
+%(By P2, if a wire block $w$ is excited in state $s_k$, then the corresponding wire $w$ is excited in the original circuit in state $h^A(s_k)$.
 To cover all transitions, it suffices to examine transitions in an excited wire block from cases 1-4.
-) \\
+)
 
@@
     \includegraphics[width=\textwidth]{gatewl2}
-  \caption{Different cases of P2 for a wireblock, a-d correspond to excited wire in the original circuit and e is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
+  \caption{Different cases of P2 for a wireblock, 1-4 correspond to excited wire in the original circuit and 5 is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
   \label{fig:l1helper}
@@
 
-We prove P1 and P2 sequentially for $s_{k+1}$.  The proof for P1 only relies on the induction hypothesis being true in state $s_k$ and is as follows: \\
-
+We first prove P1 and then P2 for the length $k+1$ prefix.
+To show P1 is true for state $s_{k+1}$, we must show that $h^A(s_{k+1})$ is a reachable state and that ($h^A(s_{k})$,$h^A(s_{k+1})$) is a transition in the original circuit.
+The proof for P1 relies only on the induction hypothesis being true for state $s_k$ and is as follows: \\
+
+Let the transitioning wire block from state $s_k$ be called $w$.  There are four cases that $w$ can be in.  % A transition occurs on a wire block that is in cases 1-4. 
 \begin{itemize}  
-We first show that P1 is true for $\sigma_{k+1}$.  
-\item We consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}). (maybe still need to be more clear about wire block vs transitions) 
-If an excited wire block $w$ is in any of these 3 cases, there is only one possible transition for each case: the new value of the signal propagates down the C-element chain.
-Thus in the new state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.
-For all 3 cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
-This is a repeated state under the half circuit mapping and is deleted in the resulting trace.
-Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and therefore $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit.
-\item Case 4 is when $w^A$ transitions in the fault-tolerant circuit, as shown in case d of Figure \ref{fig:l1helper}.
-Then in the original circuit, the transition from state $h^A(s_k)$ to state $h^A(s_{k+1})$ is on wire $w$.
-Because wire $w$ is excited in state $h^A(s_k)$, this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$) and $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit.
+\item Cases 1-3 (Figure \ref{fig:l1helper}) are considered together.  
+If an excited wire block $w$ is in any of these three cases, there is only one possible transition for each case: the new wire value propagates down the C-element chain.
+That is, in state $s_{k+1}$, wire block $w$ is in cases 2-4 respectively.
+For all three cases, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
+This is a repeated state under the half circuit mapping applied to the trace and is deleted.
+Thus $h^{A}(\sigma_{k+1})=h^{A}(\sigma_k)$ and $h^{A}(\sigma_{k+1})$ must also be a prefix of a trace of the original circuit.
+\item Case 4 (Figure \ref{fig:l1helper}) has only one possible transition which is on wire $w^A$.
+Then under the half circuit mapping, wire $w$ transitions from state $h^A(s_k)$ to state $h^A(s_{k+1})$.
+By P2, wire $w$ is also excited in state $h^A(s_k)$ and this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$).
+Therefore $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit.
 \end{itemize}
 
-Next, we show that P2 is true for $s_{k+1}$.
-Again we consider all possible transitions that lead to the new state $s_{k+1}$.
-The wireblock which transitions, which we again name $w$, is in one of cases 1-4.
+That concludes the proof for P1.
+Next, we show that P2 is true for all possible $s_{k+1}$ by showing that $s_{k+1}$ in the fault-tolerant circuit corresponds to $h^A(s_{k+1})$ in the original circuit with certain properties of the wireblocks preserved.
+Again, there are four cases that the transitioning wireblock $w$, can be in.
 
 \begin{itemize}
-\item Again, we consider transitions from cases 1-3 together (1-3 in Figure \ref{fig:l1helper}).
-We use the following fact from the P1 proof: in the new state $s_{k+1}$, the wireblock $w$ is in cases 2-4 respectively and $h^A(s_{k+1})=h^A(s_{k})$.
-Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A{s_{k+1}}$.
-Then $w$ in the original circuit remains excited in state $h^A{s_{k+1}}$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.
-Thus, wireblock $w$ satisfies P2.
+\item Cases 1-3 (Figure \ref{fig:l1helper}) are considered together.
+As mentioned in the P1 proof, the transition occurs on an intermediate wire and $h^A(s_{k+1})=h^A(s_{k})$.
+Since $h^A(s_{k+1})=h^A(s_{k})$, then all wires in the original circuit do not change excitations in the new state $h^A(s_{k+1})$.
+Then $w$ in the original circuit remains excited in state $h^A(s_{k+1})$, while wireblock $w$ in the fault tolerant circuit is in one of cases 2-4 in state $s_{k+1}$.
+Wireblock $w$ satisfies P2.
 All other wireblocks in the fault-tolerant circuit do not change cases in the new state $s_{k+1}$.
-(explain why?
-does it involve `P2')
-Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2, so P2 is true for the trace $\sigma_{k+1}$.
+Thus all wireblocks of the fault-tolerant circuit in state $s_{k+1}$ satisfy P2.
 
@@
 \item The last case is when a transition occurs from case 4.
-That is, $w^A$ transitions in the fault-tolerant circuit from case d of Figure \ref{fig:l1helper}.
+That is, $w^A$ transitions in the fault-tolerant circuit from case 4 of Figure \ref{fig:l1helper}.
 %The original circuit transitions to state $h^A(s_{k+1})$ where wire $w$ transitions.
-As mentioned in the P1 proof, applying the half circuit mapping results in wire $w$ transitioning in the original circuit.  
+As mentioned in the P1 proof, applying the half circuit mapping results in a corresponding transition of wire $w$ in the original circuit.  
 %applying the $h^A$ mapping to state $s_{k+1}$ indicates that $w$ transitions in the original circuit.  
-We show this transition affects the excitation state of wire blocks/wires in both the fault-tolerant circuit and the original circuit such that P2 is satisfied for $s_{k+1}$.
-By P2 of state $s_k$, we partition the wire blocks in the fault-tolerant circuit in state $s_k$ into five cases, as described in Figure \ref{fig:l1helper}.
-Note that because wire $w^A$ transitions, wireblock $w$ is a special case of case 4 which we deal with separately from other wireblocks in case 4.
+These two transitions can change the excitation state of wireblocks/wires in the fault-tolerant circuit and the original circuit respectively.
+By P2, the wireblocks in state $s_k$ are partitioned into five cases (Figure \ref{fig:l1helper}).
+We examine the changes to a wireblock in each of the five cases due to the $w^A$ transition.
+Note that because wire $w^A$ transitions, wireblock $w$ is a special case of case 4 which we deal with separately.
 %Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.
@@
 \item
-For wireblocks in cases 1-4 (not including wireblock $w$), we show that these wireblocks remain in the same case in state $s_{k+1}$.
-Let us call a wireblock in one of these states as $v$.
-By P2 of state $s_k$, wire $v$ of the original circuit is excited in state $h^A(s_{k})$.
-Since the original circuit is semi-modular and $v$ does not transition, then $v$ must remain excited in state $h^A(s_{k+1})$.
-In the fault tolerant circuit, we only need to examine the logic block portion of the wireblock since the transition is not in $v$.
-\\
-state $s_{k+1}$ Case 1 is straight forward since the inputs of $c1^A$ in the fault-tolerant circuit and $v$ in the original circuit are equal under the half circuit mapping and the wire values $c1^A$ and $v$ are equal as well.
-Therefore $c1^A$ must have the same excitation as $v$, that is, excited.
+For wireblocks in cases 1-4 in state $s_k$ (excluding wireblock $w$), we show that these wireblocks remain in the same case in state $s_{k+1}$.
+Let us call such a wireblock $v$.
+By P2, wire $v$ of the original circuit is excited in state $h^A(s_{k})$.
+Since $h^A(\sigma_{k+1})$ is a prefix of a trace (by P1) in a semi-modular circuit and $v$ does not transition, then $v$ must remain excited in state $h^A(s_{k+1})$.
+For P2 to be true in state $s_{k+1}$, we must show that wireblock $v$ in the fault-tolerant circuit remains in cases 1-4.
+A transition on $w^A$ can only affect the logic block portion of the wireblock.
+\\
+Case 1 is straight forward since the inputs and output of $c1^A$ in the fault-tolerant circuit and $v$ in the original circuit are the same values, then by Lemma 0 i) wire $c1^A$ must have the same excitation as $v$, that is, excited.
 If $v$ is in case 1 in state $s_k$, then $c1^A$ remains excited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 1 in state $s_{k+1}$.
@@
 In Cases 2-4, the logic block of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.
-The logic block of the fault-tolerant circuit remains unexcited in state $s_{k+1}$, which is by contradiction.
-Suppose that there is some $v$ where the logic block becomes excited in state $s_{k+1}$, then $v$ in the original circuit and $c1^A$ in the fault tolerant circuit are excited in opposite directions.
-Since the logic blocks for $v$ and $c1^A$ are identical and one of gates or C-element, the excitation is determined purely by its inputs.
-Again the inputs to $c1^A$ and $v$ are equal so these input values cause the logic block to excite to both 1 and 0 at the same time.
-This cannot happen in any of the elements that we build are circuit from and is therefore a contradiction.
-(change this into a new lemma?)
-Thus, if $v$ is in case 2-4 in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ with no other transitions in $v$, thus $v$ is in case 2-4 in state $s_{k+1}$.  
-Combined with $v$ staying excited in the original circuit in state $h^A(s_{k+1})$, any wireblocks in these 4 cases satisfy P2 in state $s_{k+1}$.
+By semi-modularity, wire $v$ remains excited in state $h^A(s_{k+1})$.
+In state $s_{k+1}$ and state $h^A(s_{k+1})$, the inputs to $c1^A$ and $v$ are equal but $c1^A$ and $v$ have different values.
+By Lemma 0 iii), since $v$ is excited then $c1^A$ is unexcited.
+Thus, if wireblock $v$ is in case 2 (or 3 or 4) in state $s_k$, then $c1^A$ remains unexcited in state $s_{k+1}$ and wireblock $v$ remains in case 2 (or 3 or 4) in state $s_{k+1}$.
+Since $v$ stays excited in the original circuit in state $h^A(s_{k+1})$, any wireblocks in these 4 cases satisfy P2 in state $s_{k+1}$.
 
@@
 \item
-Wireblock $w$ is a case of its own.
-Wire $w$ in the original circuit in state $h^A(s_{k+1})$ has just transitioned and is unexcited since $w$, (this explanation is still a bit weird) the only wire value that changed, is not an input to itself.
-In the fault-tolerant circuit, $w^A$ just transitioned and none of the C-element down the chain is excited.
-$c1^A$ must remain unexcited since $w$ is unexcited in the original circuit.
-Thus wireblock $w$ in state $s_{k+1}$ is in case 5 of Figure \ref{fig:l1helper}.
-And as previously mentioned, wire $w$ is unexcited in state $h^A(s_{k+1})$ and thus P2 holds for wire block $w$.
+Wireblock $w$ is a special case of case 4.
+Wire $w$ of the original circuit has just transitioned in state $h^A(s_{k+1})$.
+Since $w$, the only wire value that changed, is not an input to itself, $w$ is unexcited in state $h^A(s_{k+1})$.
+In the fault-tolerant circuit, $w^A$ just transitioned so the wireblock $w$ is in either case 1 or case 5.
+By Lemma 0 ii), since $w$ is unexcited in the original circuit $c1^A$ is also unexcited.
+Thus wireblock $w$ in state $s_{k+1}$ is in case 5 while wire $w$ in state $h^A(s_{k+1})$ is unexcited.
+Thus P2 holds for wire block $w$ in state $s_{k+1}$.
 
@@
 \item
-For wires in case 5 in state $s_k$, we name such a wire $u$.
-$u$ is unexcited in the original circuit in state $h^A(s_{k})$ by P2.
-There are two possibilities: if $u$ is excited in state $h^A(s_{k+1})$, then logic block $u$ in the fault-tolerant circuit is also excited in state $s_{k+1}$.
-This is because the inputs to $u$ and $c1^A$ of wireblock $u$ are the same in the original circuit and fault-tolerant circuit by the half circuit mapping, and $c1^A=u$, then $c1^A$ is also excited in state $s_{k+1}$.
-Wire block $u$ is in case 1 of Figure \ref{fig:l1helper} in state $s_{k+1}$.
+For wireblocks in case 5 in state $s_k$, we show that these wires stay in case 5 or transition to case 1 in state $s_{k+1}$.
+Let us call such a wireblock $u$.
+By P2, $u$ is unexcited in the original circuit in state $h^A(s_{k})$.
+There are two possibilities in the next state: $u$ can be excited or unexcited in state $h^A(s_{k+1})$.
+We first note that by the half circuit mapping on $s_{k+1}$, the inputs to $u$ in the original circuit and $c1^A$ of wireblock $u$ in the fault-tolerant circuit have the same values, and also $c1^A=u$.
+\\
+If $u$ is excited, then by Lemma 0 i) $c1^A$ in the fault-tolerant circuit is also excited in state $s_{k+1}$.
+Then wireblock $u$ is in case 1 (Figure \ref{fig:l1helper}) in state $s_{k+1}$.
 Thus P2 holds for wires of this type in state $s_{k+1}$.\\
-The second possibility is if $u$ remains unexcited in state $h^A(s_{k+1})$.
-By similar reasoning as above $c1^A$ of wireblock $u$ is unexcited in state $s_{k+1}$ and the wireblock stays in case 5 of Figure \ref{fig:l1helper}.
+And if $u$ remains unexcited in state $h^A(s_{k+1})$, by Lemma 0 ii) $c1^A$ of wireblock $u$ is unexcited in state $s_{k+1}$.
+Then wireblock $u$ stays in case 5 of Figure \ref{fig:l1helper}.
 Thus P2 holds for wires of this type.
@@
 \end{itemize}
-So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
+So the induction hypothesis holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
 By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
@@
 %fix this
-Next we consider what happens to the fault-tolerant circuit under a single transient fault which is defined as follows:
-\begin{definition}A {\em transient fault} on a wire $w$ causes a transition $w= \lnot w^{prev}$.
-After this event, the wire can freely transition based on its inputs.
+Next we consider what happens to the fault-tolerant circuit under a single transient fault.
+A {\em transient fault} on a wire $w$ causes a transition i.e.
+flips the bit of $w$.
+After the transient event, the affected wire transitions based on its inputs.
 %do I need to talk about when transient is not ~x?
@@
 That's the same as a longer delay
-\end{definition}
 \begin{figure}
@@
 \begin{definition}
-A {\em faulty trace} is a trace of the circuit where at some state $n$, a transient fault replaces the transition from $s_n$ to $s_{n+1}$.  The circuit continues to transition from $s_{n+1}$.   
+A {\em faulty trace} is a trace of the circuit where for all $k$, a transition from $s_k$ to $s_{k+1}$ is either a transition as defined in the fault-free case, or a transition through a transient fault.
 %there exists an $n$ where $\sigma_n$ is a prefix of a trace of the fault free circuit, then the $n+1$st transition is a transient fault.  After the fault occurs, the circuit continues to transition .
@@
 Then these lemmas combine to show that there is no deadlock.
+A complete trace is defined similarly for the fault-tolerant circuit.
+That is, the trace after mapping must be a complete trace in the original circuit.
+The completeness property must be treated separately because there are two halfs in the fault-tolerant circuit and one side needs the other to transition.
+Thus, we need to show that even in the presence of a transient fault, each wireblock will eventually transition.
 
@@
 \begin{lemma}[3]
-For any trace $\sigma$ in the duplicated circuit, if a single transient fault occur on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{A}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For any trace $\sigma$ in the fault-tolerant circuit, if a single transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
 \end{lemma}
@@
 \begin{lemma}[4]
-For all traces $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
+For every trace $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
 \end{lemma}
 \begin{proof}
-The fault is in the B-half so Lemma 1 applies for the A-half.
-We show by induction that when the fault is not in $c2^B$ and $c3^B$, in the resulting trace, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in Figure \ref{fig:l4}.
-We only analyze for cases 1-5 because transitions from case 6 is symmetric to transitions from case 1 with 0's and 1's inverted until the state ends back in case 1.\\
-
-The base case of $\sigma_1$ consists of state $s_1$ which is the valid initial state with no faults.
-As noted in Lemma 2.1, the state of each of the wire blocks must be in case 1 or case 3b of Figure \ref{fig:l21}.
-Projecting these states onto the $c1$, $c2$ and $c3$ wires results in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
-
-In the induction step we assume that $\sigma_k$ follows Figure \ref{fig:l4} and in particular, each wire block at state $s_k$ is in a case of the figure.
-For each case that a wire block may be in, we then investigate the case changes in all possible next states $s_{k+1}$.
-It is possible that a fault has already been introduced in the B-half on wires other than $c2$ and $c3$, so that $c1^B$ may be affected by the fault.
-Despite the possibility of a fault, we assume that wire $c1^B$ has value of either 0 or 1 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.
-The possibly faulty wire value $c1^B$ is represented by the symbol X.
-In all the cases below we do not consider if $c1^B$ transitions because that will result in the wire block staying in the same case.
+The fault is in the B-half while the A-half is fault-free so Lemma 1 applies for the A-half.
+We will show by induction on $n$ that Lemma 4 is true for each prefix of the trace, $\sigma_n$.
+%how to make it seem like prefix not trace modifies sigma_n
+We only analyze cases 1-5 because transitions from case 6 onwards is symmetric to transitions from case 1 onwards with 0's and 1's inverted, until the state eventually loops back to case 1.
+For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7, which is symmetric to case 2 with corresponding transitions and so on.\\
+
+We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state with no faults.
+As noted in Lemma 2.1, each wireblock must be in case 1 or case 3b of Figure \ref{fig:l21}.
+Projecting these states onto the $c1$, $c2$ and $c3$ wires result in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
+
+The induction step is to assume that the induction hypothesis is true for a length $k$ prefix of a given trace, $\sigma_k$.  
+To show the induction hypothesis is true for the length $k+1$ prefix $\sigma_{k+1}$, we show the hypothesis is true for all possible (transitions) next states from state $s_k$.  
+By the induction hypothesis, a wireblock in state $s_k$ may be in any of the seven cases, so we check for each case that the wire block transitions according to Figure \ref{fig:l4}.  
+%so we observe the effects of the next transition on such a wire block.    
+%we then observe how the case may change for that wire block in the next state $s_{k+1}$.      
+%For each case that a wire block may be in, we then investigate the case changes in all possible next states $s_{k+1}$.  
+The wire value of $c1^B$ is denoted by X in the figure because it is possible that a fault (satisfying the criteria of this lemma) has already occurred in the trace, so the value of wire $c1^B$ may be affected by that fault.
+We do not know the value of X except that it is either 0 or 1.
+%(Despite the possibility of a fault, we assume that wire $c1^B$ has value of either 0 or 1 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.<-should already be covered)
+Therefore we do not consider $c1^B$ transitions because the transition is covered by X. %X covers both cases when $c1^B$ is 0 or 1.
+  The possible next transitions from each of the seven cases are as follows:
+%the cases do not depend on the wire value of $c1^B$
+%that will result in the wire block staying in the same case.
 \begin{itemize}
 	\item
-Case 1:  $c2$, $c3$ are not excited.  $c1^A$ can be excited depending on the inputs to the logic block.  Therefore, a transition from this case must be to case 2.
+Case 1:  If the wireblock is in case 1, its $c2$ and $c3$ wires are not excited.
+Depending on the inputs to the wireblock, wire $c1^A$ may be excited.
+Therefore the wireblock either stays in this case or transitions to case 2 in state $s_{k+1}$.
+%(must prove both the state, and the transition, if there is any...
+follows the state graph)
 \item
-Case 2/3a/3b:  $c2$ can be excited depending on $c1^B$.
-$c1^A$ cannot be excited to 0 due to semi-modularity of wire $w$ and Lemma 1.
-Therefore, a transition from case 2 must be to case 3a or 3b, and from case 3a or 3b to case 4.
+Case 2/3a/3b:   If the wireblock is in one of these cases, wire $c1^A$ cannot be excited due to Lemma 1 as it would violate semi-modularity for wire-blocks.
+The $c3$ wires are not excited.
+Depending on the wire value of $c1^B$ and the current case of the wireblock, one or both of the $c2$ wires may be excited.
+Therefore if the wireblock is in case 2, it either stays in case 2 or transitions to case 3a or 3b in state $s_{k+1}$.
+And if the wireblock is in case 3a or 3b, it either stays in the current case or transitions to case 4 in state $s_{k+1}$.
+(Do I need to say explicity it can stay in the current case?)
 %I might need to show the excited ness of the good logic gate
 \item
-Cases 4/5a/5b:  $c1^A$ cannot be excited to 0 due to the same reasoning above.
-The $c2$ wires are not excited but the $c3$ wires are excited.
-Therefore, a transition from case 4 must be to case 5a or 5b, and from case 5a or 5b to 6.
+Cases 4/5a/5b:   If the wireblock is in one of these cases, again, wire $c1^A$ cannot be excited due to Lemma 1.
+The $c2$ wires are not excited.
+The $c3$ wires are excited.
+Therefore, if the wireblock is in case 4, it may transition to case 5a or 5b; and if the wireblock is in case 5a or 5b, it may transition to case 6.
 \end{itemize}
-Thus, in the next state $s_{k+1}$, all wire blocks either stay in the same case or transition according to Figure \ref{fig:l4}.  
-By induction, the trace $\sigma$ also follows Figure \ref{fig:l4}.  
+Thus, in all possible next states $s_{k+1}$, the wire block transitions according to Figure \ref{fig:l4}.
+This is true for each wireblock in the circuit, so the induction hypothesis holds for all length $k+1$ prefixes of traces and the induction step is complete.
+By induction on the length of the trace, the trace $\sigma$ also transitions according to Figure \ref{fig:l4}.  
 \end{proof}
-By symmetry, this is also true if the fault occurs in the A half.  
-The importance of this Lemma is that at most one of $c2$ or $c3$ pairs can be mismatched.
-The next theorem shows that this property implies all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
-
-Returning to the condition of deadlock, where the circuit has no further transitions and is also not in a stopping state, we can make the following conclusion about the inputs and outputs of C-elements.
+By symmetry, this is also true if the fault occurs in the A half and the A and B labels in Figure \ref{fig:l4} are switched.  
+The importance of this Lemma is that at most one of the following happens: $c2^A\neq c2^B$ or $c3^A\neq c3^B$.
+This property can also be described as at most one of the $c2$ or $c3$ wire pairs can have different values.
+The next theorem uses this property to show that the fault-tolerant circuit does not deadlock under a single transient fault.\\
+%all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
+
+For a circuit under deadlock, where the circuit has no further transitions and is also not in a stopping state, we can make the following conclusion about the inputs and outputs of C-elements in that circuit.
 \begin{lemma}[5]
-If the circuit is in deadlock, and the two inputs into a C-element is the same value $v$, then the output of the C-element is also $v$.
+If the circuit is under deadlock, and the two input wires into a C-element have the same value $p$, then the output of the C-element is also $p$.
 \end{lemma}
 \begin{proof}
-For a circuit in deadlock, there are no excited elements.  If a C-element has two inputs with value $v$, then the output must also be $v$ for the C-element to be unexcited.
+For a circuit under deadlock, there are no excited elements.  If a C-element has two inputs with value $p$ and is unexcited, then the output must also be $p$.
 \end{proof}
-Then for each layer of C-elements in the wire block, if say the wires $c2^A$ and $c2^B$ are equal to $v$, then at deadlock the wires $c3^A$ and $c3^B$ are also equal to $v$.
-Then by extending this to successive layers of C-elements, all outputs of these C-elements must also hold the value $v$.
+This lemma can be extended to the three successive layers of C-elements of a wireblock.
+For example, for the second layer of C-elements, if the wires $c2^A$ and $c2^B$ have the same value $p$, then under deadlock the wires $c3^A$ and $c3^B$ also have the value $p$.
+Then by extending this to successive layers of the C-elements, all outputs of the C-elements after this layer must also have the value $p$.
 This example is illustrated in Figure \ref{fig:t2}.
@@
 
-\begin{theorem}[2]
-When a single transient fault occurs, if $\sigma$ is a trace in the fault-tolerant circuit, then one of $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ (the non faulty half) for all $n \in \mathbb{N}$ is a prefix of a trace in the original circuit.
-And the circuit does not deadlock.
+\begin{theorem}[2.1]
+Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
+For every trace $\sigma$ of this circuit, the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
+And the fault-tolerant circuit does not deadlock.
 \end{theorem}
 \begin{proof}
-Without loss of generality, we can assume the fault occurs in the B half of the circuit.
-First by Lemma 3, we know that if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires and the circuit does not deadlock.
-Thus we look at when the fault occurs on the remaining wires.\\
-
-We show there exists a contradiction when the fault occurs on the remaining wires and we assume that the circuit is in deadlock.
-We first show that the output wires $w^A = w^B$ for all wire blocks.
-For each wire block $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
-For both cases, since the circuit is in deadlock, then by Lemma 5 all wire blocks have output wires with the property $w^A = w^B$.
-\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
-
-Next, with this new property, we show that there exists a contradiction and the circuit must not be in deadlock.
-Let the circuit be in some deadlocked state $s$.
+By Lemma 1, it is clear that the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
+Thus we need only to show that the circuit does not deadlock.\\
+
+First by Lemma 3, if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires and the circuit does not deadlock.\\
+
+If the fault occurs on the remaining wires, we prove by contradiction that the circuit does not deadlock.
+We first show that the output wire pairs have the same values $w^A = w^B$ for all wireblocks.
+For a wireblock $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
+In either case, since the circuit is in deadlock, then by Lemma 5 the output wires of the wireblock have the property $w^A = w^B$.
+This is true for all wireblocks of the circuit.\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
+
+Next, we begin the proof by contradiction.
+Assume that the circuit is in a deadlocked state $s$.
 By Lemma 1, $h^A(s)$ is a state in the original circuit.
-By definition of deadlocked state, the state $h^A(s)$ is not a stopping state, so there must exist a wire $v$ that is excited.
-In the duplicated circuit, for the circuit to be in deadlock in wire block $v$, the $c1^A$ wire must have value $\neg{v}$, because otherwise the logic block in the A half is excited.
-Since $w^A = w^B$ for all wires then $h^A(s)=h^B(s)$ and the $c1^B$ wire must also have value $\neg{v}$ or the logic block in the B half is excited.
-By Lemma 5, $v^A$ and $v^B$ wires must have the same value as the $c1$ wires.
-However this results in $v^A= \neg{v}$ which is a contradiction, therefore the initial assumption is wrong and the circuit is not in deadlock.
+By the definition of deadlock, the state $h^A(s)$ is not a stopping state so there must exist a wire $v$ with value $p$ that is excited.
+In the fault-tolerant circuit, the inputs to the $v^A$ logic block have the same values as the inputs to the $v$ logic block in the original circuit.
+However we assumed that the fault-tolerant circuit is deadlocked so wire $c1^A$ must have value $\neg{p}$.
+Using the property above where $w^A = w^B$ for all wireblocks, then by the same reasoning wire $c1^B$ must also have value $\neg{p}$.
+Since $c1^A=c1^B$, then by Lemma 5 wires $v^A$ and $v^B$ must have the same value as the $c1$ wires.
+%However in the original circuit wire $v$ has value $p$ which implies wire $v^A$ in the fault-tolerant circuit also has value $p$.
+However this results in wires $v^A$ and $v^B$ taking on values of both $p$ and $\neg{p}$, which is a contradiction.  Therefore the initial assumption is wrong and the circuit cannot be under deadlock.
 %excited blocks, and stopping states
@@
 
-Thus deadlock is not possible when there is a single transient fault.  And by Lemma 1, $h^A(\sigma_n)$ is a prefix of a trace in the original circuit. 
+\end{proof}
+
+\begin{theorem}[2.2]
+Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
+For every infinite trace $\sigma$ of this circuit, the half-circuit mapping of the trace $h^{A}(\sigma)$ is also complete.
+\end{theorem}
+\begin{proof}
+Given the mapped trace must be complete, we must verify that if a wireblock $w$ in the fault-tolerant circuit is excited, it must eventually transition.
+The proof is by contradiction.
+Assume that there is an infinite trace with a wireblock in the A-half that is excited but never transitions.
+We apply Lemma 3.2 from Beerel & Meng that all cycles of states in live semi-modular circuits must contain all signal transitions.
+Thus the A-half is not in a cycle and eventually stops at some state.
+We look at some state $s_k$ in the trace where the A-half is stopped.
+Excitations on the $c1^A$ wires always transition because its inputs are all A-half wires, and by Lemma 1 and Lemma 0, if the logic block is excited it stays excited until it transitions.
+In fact, only excitations on wire $c2^A$ can halt because it is waiting for inputs from the A and B-half to have the same value.
+Once both $c2$ wires transition to the new value, faulty $c1^B$ values can not prevent the wireblock from completing its transition.
+This fact also extends to the property that once the A-half is stopped, the wireblock outputs in the B-half can change at most once.
+Then from state $s_k$, there are at most $O(n)$ transitions where $n$ is the number of wireblocks.
+Thus the trace is finite and contradicts the initial assumption.
+
 \end{proof}

### 2019-11-23 draft_final.tex
ran spellcheck on ch 2

@@
 Since then a number of synthesis methods following this design has been produced.
-Usually the synthesis methods begin with some higher-level specification such as signal transition graph or Petri nets and translate into a state graph.
+Usually the synthesis methods begin with some higher-level specification such as a signal transition graph or Petri net and translate into a state graph.
 A state graph describes all the possible sequences of changes in a finite number of signals.
@@
 In addition, there is discussion about the existing body of work on fault-tolerant solutions for both types of circuits with an emphasis on asynchronous circuits.
-Chapter three provides the background terminology and definitions for asynchronous circuits.
+Chapter three provides the background concepts and definitions for asynchronous circuits.
 Chapter four shows why the existing fault-tolerant methods are insufficient and propose a new fault-tolerant method for asynchronous transient faults.
@@
 
-\chapter{Background}
+\chapter{Related Works}
 \section{Faults}
@@
 Most permanent faults occur during fabrication.
-There are many existing literature that cover permanent faults and the different tests at production time that can uncover the presence and location of these faults.
+There are many existing literatures that cover permanent faults and the different tests at production time that can uncover the presence and location of these faults.
 \cite{jha_gupta_2003} \cite{giz_book_2006}.
@@
 
-Non-permanent faults is defined as faults that affect the system's functional behavior for a finite but unknown period of time.
+Non-permanent faults are defined as faults that affect the system's functional behavior for a finite but unknown period of time.
 They can occur at random moments and are categorized into two types, intermittent and transient faults.
 Intermittent faults are caused by non-environmental conditions such as loose connections, deteriorating or aging components, critical timing (hazards and race conditions), resistance and capacitance variations (which may lead to timing faults), physical irregularities, and noise.
-Intermittent faults usually affects the system for a shorter time period than the application time of a test developed for permanent faults and thus may not be detected using such a test.
+Intermittent faults usually affect the system for a shorter time period than the application time of a test developed for permanent faults and thus may not be detected using such a test.
 Intermittent faults can transition into permanent faults naturally but may take a long time from hours up to months.
@@
 Radiation from cosmic rays become more severe at higher elevations while the latent source in packaging is difficult to eliminate.
-Thus initially a lot of the work in fault-tolerant design was done for aviation and space flight.
+Thus, initially a lot of the work in fault-tolerant design was done for aviation and space flight.
 
@@
 \section{Asynchronous Circuit and Synthesis}
-In the previous chapter we described how an asynchronous circuit works from a higher level perspective and in particular that it should work under varying delays.
-In this section we will cover some definitions and properties of the circuit and also how we can synthesize the circuit from a higher level specification.
+In the previous chapter we described how an asynchronous circuit works from a higher-level perspective and in particular that it should work under varying delays.
+In this section we will cover some definitions and properties of the circuit and also how we can synthesize the circuit from a higher-level specification.
 Both Speed Independent and Delay Insensitive technologies will be introduced.
@@
 
-Next we describe the set of {\em transitions} of a circuit where only one signal value changes more formally.  
+Next, we describe the set of {\em transitions} of a circuit where only one signal value changes more formally. 
 We write $s(w)$ for the value of signal $w$ in state $s$, and write $T(s, s')$ when there is a transition from $s$ to $s'$.
@@
 %ADD SPECIFIC CONDITIONS THAT ALLOW SYNTHESIS
-When the state graph have the following properties, it is possible to synthesize a hazard free and speed independent asynchronous circuit following the state graph.
+When the state graph has the following properties, it is possible to synthesize a hazard free and speed independent asynchronous circuit following the state graph.
 Each variable from the state graph is implemented as a gate logic that takes other variables/wires as inputs and outputs a variable/wire.
@@
 When both inputs are low, the C-element output goes low, and when both inputs are high the C-element output goes high.
-However when the inputs are mismatched then the output gets held at its previous value.
+However, when the inputs are mismatched then the output gets held at its previous value.
 This can be achieved in a number of ways such as a gate implementation as well as a transistor level implementation with feedback using a weak transistor, other implementations use capacitance to achieve this weak feedback.
 \includegraphics[width=\textwidth]{celement}
-\captionof{figure}{ a. logic of the C-element. A, B are inputs, C is the output \\  b. diagram of a C-element at the gate level   c. transistor-level implementation}
+\captionof{figure}{a. logic of the C-element. A, B are inputs, C is the output \\ b. diagram of a C-element at the gate level c. transistor-level implementation}
 
@@
 Input values that are neither in the ON-set or OFF-set are in the Don't Care set.
-So for the set condition, the ON-set are all input values where the wire must transition to high.
+So, for the set condition, the ON-set are all input values where the wire must transition to high.
 The OFF-Set includes all input values where the wire is excited instead to low, as well as input values for which the output wire must remain low.
@@
 We assume a transistor level implementation of the set and reset combined with the C-element so that there is only one delay for the entire logic block.
-In addition this is not a normal C-element because set is used exclusively for the pull-up logic and reset is used for the pull-down logic.
+In addition, this is not a normal C-element because set is used exclusively for the pull-up logic and reset is used for the pull-down logic.
 In a normal C-element we allow for any four combinations of the values of the set and reset input wires.
-However using the pull-up and pull-down logic setup, we do not allow for when both set and reset is `ON' as the output wire would simultaneously be connected to the high voltage and ground.
+However, using the pull-up and pull-down logic setup, we do not allow for when both set and reset is `ON' as the output wire would simultaneously be connected to the high voltage and ground.
 Such an output would have indeterminable voltage values and violate the digital assumptions.
@@
 Each of these gates can have their own delay that is arbitrary in length that is instantized as an intermediate wire.
-Thus the logic must be synthesized more carefully to eliminate hazards that can occur in these intermediate wires.
+Thus, the logic must be synthesized more carefully to eliminate hazards that can occur in these intermediate wires.
 In particular the set and reset must be activated at states only when the wire is appropriately excited.
@@
 This implementation uses the standard C-element so that if the set and reset inputs are mismatched, the output is held.
-In general the synthesis can be changed so that there is a hazard-free implementation using only two-input gates.
-
+In general, the synthesis can be changed so that there is a hazard-free implementation using only two-input gates.
 %explain sop?
-
 \subsection{Quasi Delay Insensitive Circuits}
@@
 \\
-
 The gates of a QDI circuit is formed from Production Rules (PRs).
 For the single output case, a gate takes a set of variables as inputs and outputs a variable.
-Again a transition on the variable $x$ is denoted as $x\uparrow$, a transition from $x=0$ to $x=1$; and $x\downarrow$, a transition from $x=1$ to $x=0$.
+Again, a transition on the variable $x$ is denoted as $x\uparrow$, a transition from $x=0$ to $x=1$; and $x\downarrow$, a transition from $x=1$ to $x=0$.
 Then the two PRs associated with the gate with output $x$ is :
@@
 Note that similar to the generalized C-elements, both guards cannot be active at the same time.
-In addition it is assumed that each guard is in a sum of products of the input variables.
+In addition, it is assumed that each guard is in a sum of products of the input variables.
 The PRs of a circuit are evaluated all at the same time.
@@
 This is due to the assumption of the arbitrary delay of a gate.
-Note that again, like the generalized C-element implementation, we assume that the transistor level implementation of a PR allow any arbitrary sum of products to be made where there are no delays within the logic of the sum of products.\\
+Note that again, like the generalized C-element implementation, we assume that the transistor level implementation of a PR allows any arbitrary sum of products to be made where there are no delays within the logic of the sum of products.\\
 
@@
 There has also been some research for asynchronous circuits using some similar techniques.
-First we present an overview of some common techniques for synchronous circuits, then introduce the current techniques for asynchronous circuits.
+First, we present an overview of some common techniques for synchronous circuits, then introduce the current techniques for asynchronous circuits.
 Some of the techniques in asynchronous design borrows or are inspired by the much more developed fault-tolerant synchronous circuits field.
@@
 These include space and aviation control systems where due to the altitude there are more radiation and thus more faults.
-In addition faults that cause error is very detrimental to these systems and may cause failures leading to loss of life.
+In addition, faults that cause error is very detrimental to these systems and may cause failures leading to loss of life.
 Other examples of systems requiring reliable circuits include banking and stock market applications where the system must function without error for hours at a time and in case of any error may have devastating consequences, such as a bit flip of the most significant bit in a money transaction.
@@
 
-Solutions for eliminating these transient fault induced errors include physical, hardware, software or a mix of the previous.
+Solutions for eliminating these transient fault-induced errors include physical, hardware, software or a mix of the previous.
 Some commonly used techniques are transistor sizing, circuit hardening, hardware duplication, and time redundancy \cite{Mitra_08_softerrors}.
-Transistor sizing is a physics based technique and does not reduce as much soft errors as the other techniques.
+Transistor sizing is a physics-based technique and does not reduce as much soft errors as the other techniques.
 Circuit hardening is on the physics level, where it uses intrinsic properties such as resistive or capacitive hardening, or combining the transistors differently to have less effects from transient faults.
@@
 This is achieved by having multiple duplicates of a circuit and often comparing the value from each duplicate to find and eliminate errors.
-For example Triple Modular Redundancy (TMR) has been used since the beginning of the field and is still a good solution for eliminating single soft errors.
+For example, Triple Modular Redundancy (TMR) has been used since the beginning of the field and is still a good solution for eliminating single soft errors.
 The advantages are that it is able to eliminate nearly all soft errors but also due to the duplication, the area for each circuit and additional power increases substantially (correlates to the number of additional duplicates).
@@
 There is also the additional distinction between error detection versus error correction.
-In general it is easier to detect an error than to correct it.
-For example using hardware duplication, only 2 copies are required to detect an error but 3 copies (TMR) to correct the error.
+In general, it is easier to detect an error than to correct it.
+For example, using hardware duplication, only 2 copies are required to detect an error but 3 copies (TMR) to correct the error.
 For different parts of the system there are also different strategies.
-For example in memory components such as SRAM, soft error correction is usually done using error-correction codes.
+For example, in memory components such as SRAM, soft error correction is usually done using error-correction codes.
 These codes are compared to the bits that are stored to ensure that there are no errors.
 They are designed to handle a predefined maximum number of errors.
-For example Hamming codes where each codeword are at least a distance of 3 apart can handle one error.
-This method is not purely hardware based and a controller system and software is used to match the codes and detect and correct any errors.
+For example, Hamming codes where each codeword are at least a distance of 3 apart can handle one error.
+This method is not purely hardware based and a controller system and software are used to match the codes and detect and correct any errors.
 For a control circuit, there are also a variety of strategies.
@@
 \\
-%However these cannot be used for latches or flip flops.  In these circuits,    Some of these techniques only detect errors but do not correct them.\\
+%However these cannot be used for latches or flip flops. In these circuits, some of these techniques only detect errors but do not correct them.\\
 
@@
 That is, if at least 2 out of the 3 signals agree on a value, the output becomes that value.
-Additionally, to counter possible faults on the single output wire, the majority vote unit can also be copied three times and it's output wire fed appropriately as input to the three copies of the downstream combinational logic.
+Additionally, to counter possible faults on the single output wire, the majority vote unit can also be copied three times and its output wire fed appropriately as input to the three copies of the downstream combinational logic.
 This would resolve both transient and permanent single faults.
-However the downside is that the circuit needs to be copied three times so the area is three times larger and the power consumption as well.
-In addition there must be many adaptations for this to work in asynchronous circuits as the signals can arrive in different orders.
+However, the downside is that the circuit needs to be copied three times so the area is three times larger and the power consumption as well.
+In addition, there must be many adaptations for this to work in asynchronous circuits as the signals can arrive in different orders.
 We give an example of why TMR does not work in an asynchronous circuit as it does in a synchronous circuit below.
@@
 The majority voter would then transition to a `1'.
-However the upset from transient faults usually happen within a short time period and the old inputs eventually force the output of the second logic block back to `0'.
+However, the upset from transient faults usually happen within a short time period and the old inputs eventually force the output of the second logic block back to `0'.
 Then the majority voter would transition to a `0' so that causes a hazard on the output of the majority voter.
@@
 That both copies should output the same value within a certain time determined by a pre-set delay element.
-Everytime one of the signals transitions to a new value, and the duplicates are mismatched the timer starts and if they stays mismatched when the timer ends an error is detected.
+Everytime one of the signals transitions to a new value, and the duplicates are mismatched the timer starts and if they stay mismatched when the timer ends an error is detected.
 They look at stuck-at-faults and premature firing faults.
-There are also cases when the timer detection does not work and for those cases they propose using additional hardware to look at the states of all the wires to see if an illegal state was reached.
+There are also cases when the timer detection does not work and for those cases, they propose using additional hardware to look at the states of all the wires to see if an illegal state was reached.
 They present an example of a control circuit for data computations.
-The main restrictions of this method is the additional timing assumptions they make about two copies of a circuit, and that the extra hardware components are assumed to be fault-free.
-Also it requires an additional comparison unit for each pair of signals which may be costly.
-Only one copy of the duplicates produce output signals that interfaces with the other units so that if there is an error on that signal it is not detected until some time after the error has propagated.
+The main restrictions of this method are the additional timing assumptions they make about two copies of a circuit, and that the extra hardware components are assumed to be fault-free.
+Also, it requires an additional comparison unit for each pair of signals which may be costly.
+Only one copy of the duplicates produces output signals that interfaces with the other units so that if there is an error on that signal it is not detected until some time after the error has propagated.
 \\
@@
 In the original functioning circuit, an SEU may cause a) a transition to a deadlocked state, an illegal state with no further possible transitions, b) abnormal, a transition to another state in the state graph and skip or adds certain transitions/signalling, c) tolerant where it transitions to an illegal state but the PRs are unaffected and eventually resumes to a valid state in the state graph.
-They solve this problem by duplicating the circuit and appending C-elements to the end of each of the original wires .
+They solve this problem by duplicating the circuit and appending C-elements to the end of each of the original wires.
 In addition to duplicating the circuit they change the production rule set so that if the rule is about wire $X$ is true in the original circuit, in the new circuit the rule is $X^1$ and $X^2$ both have to be true.
@@
 Given the transistor-based QDI assumptions, any changes to the production rules are implemented at the transistor level and assumed to not add any delays.
-In addition QDI logic is implemented in sum-of-products form and the production rules are excited only in the appropriate non-illegal states.
+In addition, QDI logic is implemented in sum-of-products form and the production rules are excited only in the appropriate non-illegal states.
 Faults are assumed to occur on the input/output wires as well as the new wires that feed into the C-elements.
@@
 
-The circuit transformation that Jang and Martin proposes work for their assumptions and specific implementation of QDI circuits at the transistor level.
-However it is not reasonable to assume that any PR can be implementation with transistors with no delay.
-Also for a simple 2-element inverter circuit their transformation also can end up in a deadlocked state after an SEU.
+The circuit transformation that Jang and Martin propose work for their assumptions and specific implementation of QDI circuits at the transistor level.
+However, it is not reasonable to assume that any PR can be implementation with transistors with no delay.
+Also, for a simple 2-element inverter circuit their transformation also can end up in a deadlocked state after an SEU.
 After the duplication and addition of C-element.
@@
 
-\chapter{New Background}
+\chapter{Asynchronous Circuit Concepts \& Definitions}
 \section{Assumptions:  Boolean signals}
@@
 Assume that there is an infinite trace with a wireblock in the A-half that is excited but never transitions.
-We apply Lemma 3.2 from Beerel & Meng that all cycles of states in live semi-modular circuits must contain all signal transitions.
+We apply Lemma 3.2 from Beerel \& Meng that all cycles of states in live semi-modular circuits must contain all signal transitions.
 Thus the A-half is not in a cycle and eventually stops at some state.

### 2019-11-24 draft_final.tex
Lemma 3 1st change

@@
 
-Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
+The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.
+To prove this, we need to show that if a wireblock in the fault-tolerant circuit is excited, it will eventually transition.
+We assume the fault happens only in the B-half and in some wireblock $v$.
+By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.
+The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\
+
+We first take note of some properites of semi-modular and fault-tolerant circuits.  \\
+
+Lemma 3.2 from Beerel \& Meng states that all cycles of states in live semi-modular circuits must contain all signal transitions.\\
+
+Thus, if the theorem that we want to prove is false, then there exists some excited wireblock that does not transition.
+B\&M's lemma implies that after the mapping, the original circuit stops in some state.
+This also implies that the A-half of the fault-tolerant circuit also stops.
+Assuming the A-half stops, we prove that the output pairs eventually have the same value, that is, $w^A=w^B$ for each wireblock $w$.
+This is split into two cases, when the fault occurs on the $c2^B$ or $c3^B$ wires of $v$, and when the fault occurs on the remaining wires $c1^B$ or $v^B$.
+%Lemma 3 shows that if the A-half stops and the single fault occurs on the $c2^B$ or $c3^B$ wires of $v$, .
+
+%Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.
 Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.
@@
 \begin{lemma}[3]
-For any trace $\sigma$ in the fault-tolerant circuit, if a single transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For any faulty trace $\sigma$ in the fault-tolerant circuit where the A-half stops, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $v$, then the circuit stops and for each wireblock $w$, wire values $w^A=w^B$.
 \end{lemma}
@@
 \begin{lemma}[4]
-For every trace $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
+For any faulty trace $\sigma$ in the fault-tolerant circuit where the A-half stops, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then the circuit stops and for each wireblock $w$, wire values $w^A=w^B$.
 \end{lemma}
+
 \begin{proof}

### 2019-11-29 draft_final.tex
before ch1 and 2 changes

--- 2019-11-23 draft_final.tex
@@
 
-\includegraphics[width=\textwidth]{asyncex}
+\includegraphics[width=\textwidth]{}
 \captionof{figure}{Example of a simple asynchronous circuit.  Note that there are no clocks and the signals can propagate at any time}
@@
 Let $\sigma_k$ be an arbitrary length $k$ prefix and $s_k$ its $k$-th state.  
-To show the hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.\\
+To show the induction hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.\\
 
@@
 
-Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
+It is useful to extend the concept of excited wireblocks to include wireblocks from faulty traces.
+Since we assume the fault is in the B-half, the A-half is fault-free and by Lemma 1, the wireblock in one of cases 1-5 of Figure \ref{fig:l1helper}.
+\begin{definition}
+An {\em excited wireblock} is any wireblock that is in cases 1-4 of Figure \ref{fig:l1helper}.  
+\end{definition}
+Also by Lemma 1, a wireblock is excited if and only if the corresponding wire in the original circuit is also excited.\\
+
+The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.
+To prove this, we need to show that if a wire $w$ in the original circuit is excited, it will eventually transition.
+Equivalently, if a wireblock $w$ in the fault-tolerant circuit is excited, it will eventually transition.
+We assume that the fault happens only in the B-half and in some wireblock $v$.
+By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.
+The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\
+
+The transient fault can be split into two cases: the fault occurs on the $c2^B$ or $c3^B$ wires of $v$, or the fault occurs on the remaining wires $c1^B$ or $v^B$.
+For the first case, if the fault occurs on the $c2^B$ or $c3^B$ wires, we can directly show that if a wireblock is excited, then it will eventually transition.
+The result is shown in Lemma 3.
+However, if the fault occurs on $c1^B$ or $v^B$, the reasoning is more complex.
+The result is shown in Lemma 4 and 5.\\
+
+We also use the following lemma from Beerel \& Meng (1991).
+\begin{lemma}[3.2]Given a live semi-modular speed-independent asynchronous control circuit, all cycles of states in the valid ESG (fault-free traces) must contain all signal (wire) transitions.\\
+\end{lemma}
+%The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.
+To prove this, we need to show that if a wireblock in the fault-tolerant circuit is excited, it will eventually transition.
+We assume the fault happens only in the B-half and in some wireblock $v$.
+By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.
+The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\
+%
+%We first take note of some properties of semi-modular and fault-tolerant circuits. \\
+%
+%Lemma 3.2 from Beerel \& Meng states that all cycles of states in live semi-modular circuits must contain all signal transitions.\\
+%
+%Thus, if the theorem that we want to prove is false, then there exists some excited wireblock that does not transition.
+B\&M's lemma implies that after the mapping, the original circuit stops in some state.
+This also implies that the A-half of the fault-tolerant circuit also stops.
+Assuming the A-half stops, we prove that the output pairs eventually have the same value, that is, $w^A=w^B$ for each wireblock $w$.
+This is split into two cases, when the fault occurs on the $c2^B$ or $c3^B$ wires of $v$, and when the fault occurs on the remaining wires $c1^B$ or $v^B$.
+%end first attempt
+
+%Lemma 3 shows that if the A-half stops and the single fault occurs on the $c2^B$ or $c3^B$ wires of $v$, .
+
+%Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.
 Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.
@@
 That is, the trace after mapping must be a complete trace in the original circuit.
-The completeness property must be treated separately because there are two halfs in the fault-tolerant circuit and one side needs the other to transition.
+The completeness property must be treated separately because there are two halves in the fault-tolerant circuit and one side needs the other to transition.
 Thus, we need to show that even in the presence of a transient fault, each wireblock will eventually transition.
@@
 \begin{lemma}[3]
-For any trace $\sigma$ in the fault-tolerant circuit, if a single transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wireblock $v$, then if $w$ is an excited wireblock, $w^A$ will transition.
+
+%For any faulty trace $\sigma$ in the fault-tolerant circuit where the A-half stops, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $v$, then the circuit stops and for each wireblock $w$, wire values $w^A=w^B$.
 \end{lemma}
@@
 \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
-This forms the input and output characteristic of a wire block under normal operation.}
+This forms the input and output characteristic of a wire block of a fault-free trace.}
 \label{fig:l3helper}
@@
 \begin{proof}
-We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain does not change.
+We use NuSMV to prove this.
+For each wireblock $w$, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) of a fault-free trace follow the state diagram shown in Figure \ref{fig:l3helper}.
+We can view the circuit as composed of two components, the faulty wireblock $v$ and the rest of the circuit.
+The faulty wireblock $v$ takes inputs from the rest of the circuit and has logic blocks that converts the inputs into wire values $c1^A$ and $c1^B$.
+Wireblock $v$ produces outputs $v^A$ and $v^B$, which the rest of the circuit takes as inputs.
+Thus, if we can prove that the outputs $v^A$ and $v^B$ follow the state diagram, then the rest of the circuit cannot tell the difference between this faulty trace and a fault-free trace.
+\\
+
+The strategy of the proof focuses on interactions between wireblock $v$ and the rest of the circuit.
+Assume $c1^A$ and $c1^B$ transition as in the fault-free trace, then if $v^A$ and $v^B$ follow the state diagram (Figure \ref{fig:l3helper}), this validates our assumptions for $c1^A$ and $c1^B$ and at the same time shows $v^A$ and $v^B$ follow the state diagram.
+\\
+
+Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: Lemma 3.2 (Beerel \& Meng) states that wires $c1^A$ and $c1^B$ become excited and transition an infinite number of times.
+In NuSMV, we model $c1^A$ and $c1^B$ as being excited infinitely often and excited only after the previous $v^A$ and $v^B$ transitions complete.
+We also model the rest of wireblock $v$, that is, the $c2^A$, $c2^B$, $c3^A$, $c3^B$, $v^A$ and $v^B$ wires.
+A transient fault occurs on wires $c2^B$ or $c3^B$ anytime during the trace.
+The specifications that are checked using NuSMV are that $v^A$ and $v^B$ transition according to the state diagram (Figure \ref{fig:l3helper}).
+\\
+
+Running the NuSMV model show that these properties are indeed true.
+Then for wireblock $v$, once it is excited $v^A$ will transition.
+For all other wireblocks $u$, since they don't have faults then Lemma 2.1 apply and if $u$ is excited, $u^A$ will transition.
+%We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain does not change.
 Under normal operation, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) follow the state diagram shown in Figure \ref{fig:l3helper}.
-Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2^B$ or $c3^B$, the transitions follow the state diagram in the figure.
+Thus, the property verified in NuSMV is that when a single transient fault occurs on wires $c2^B$ or $c3^B$, the transitions follow the state diagram in the figure.
 The fault is masked when this happens.
@@
 %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.
-We go through an example of a transient fault on $c3^B$ to demonstrate why the resulting trace follows the state diagram.
-By Lemma 2.1, the normal circuit is in a state in Figure \ref{fig:l21}, so we observe all possible transient induced traces by placing a transient starting at each state in Figure \ref{fig:l21}.
-\begin{itemize}
-	\item
-If the current state is 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b, 5, 6a, or 6b in Figure \ref{fig:l21}, the transient does not change excitations in the local circuit.
-In particular, since $w^A$ and $w^B$ do not change, then by semi-modularity the excitation of logic blocks do not change.
-So the transient fault induced state graph is a copy of Figure \ref{fig:l21} containing states 1, 2a, 2b, 3a, 3b, 3c, 4a, 4b only with $c3^B$ value flipped.
-Eventually all fault states transition to state 8b and proceed from there as usual.
-	\item
-If the current state is 7, then the transient changes the state to 8b, a valid transition.	
-      \item
-If the current state is 8a, then the transient changes the state to 9, a valid transition.	
-	\item
-      If the current state is 8b, then the transient reverts the state back to state 7.  It will then proceed from state 7 as usual.   
-	\item
-If the current state is 9, then the transient reverts the state back to state 8a.  Again, it will proceed from state 8a as usual.  
-	\item
-If the current state is 10a, then when the transient occurs, $w_B$ changes from excited to non excited; and if the current state is 10b, $w_A$ changes.
-In both cases, wire $c3^B$ is excited but there are no other excitations in the wire block.
-Thus $w^A$ and $w^B$ stay mismatched and by semi-modularity, the logic blocks in these wire blocks cannot be excited in any subsequent states (by the same argument as in Lemma 2.1 for cases 10a/10b).
-Then the wire block will stay in this transient induced state until $c3^B$ finally transitions and the wire block returns to either 10a or 10b.
-\end{itemize}
-%c3
-Similar reasoning would then apply if a transient fault occurs in $c2^B$.  
+
+%We go through some examples of a transient fault on $c3^B$ to demonstrate why the resulting trace follows the state diagram.
+We look at the trace when a transient occurs for $v$ in a state in Figure \ref{fig:l21}
+% By Lemma 2.1, the normal circuit is in a state in Figure \ref{fig:l21}, so we observe all possible transient induced traces by placing a transient starting at each state in Figure \ref{fig:l21}.
 \end{proof}
-By symmetry this is also true for transients in the A half if we exchange A and B in the statement of Lemma 3.\\
+%By symmetry this is also true for transients in the A half if we exchange A and B in the statement of Lemma 3.\\
 
@@
 \centering
-    \includegraphics{flowl4c3a}
+\includegraphics{flowl4c3full}
 \caption{The wires in each row are in order of $c1$, $c2$ and $c3$.
-Each row represents half of the duplicated circuit, ie.
+Each row represents half of the duplicated circuit, i.e.
 top row are A half wires and bottom row are B half wires.
 Note that case 5 transitions according to case 1 except with the 0's and 1's inverted.
-The states transitions after that are inverted versions of state 2-4 until it transitions back to state 1 (uninverted).}
+The states transition after that are inverted versions of state 2-4 until it transitions back to state 1 (uninverted).}
 \label{fig:l4}
@@
 
-We showed that if a fault occurs on the $c2$ or $c3$ wires then there are no observable differences in the output wires between the faulty circuit and the fault free circuit.  
-Next we show that if a fault occurs on the remaining wires, then the $c2$ or $c3$ wires of each wire block of the circuit transition according to Figure \ref{fig:l4}.
+We showed that if a fault occurs on the $c2^B$ or $c3^B$ wires, then if a wireblock is excited, it will eventually transition. 
+Next, we show the same result for when the fault occurs on $c1^B$ or $v^B$ wires.
+
+The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.
+
+%then the $c2$ or $c3$ wires of each wire block of the circuit transition according to Figure \ref{fig:l4}.
 The state graph of Figure \ref{fig:l4} is similar to projecting the state graph of Figure \ref{fig:l21} onto the $c1$, $c2$ and $c3$ wires, with the exception that the $c1$ wire value is not known in the faulty half.
@@
 \begin{lemma}[4]
-For every trace $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
-\end{lemma}
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then for each wireblock $u$, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true.\end{lemma}
 \begin{proof}
-The fault is in the B-half while the A-half is fault-free so Lemma 1 applies for the A-half.
-We will show by induction on $n$ that Lemma 4 is true for each prefix of the trace, $\sigma_n$.
-%how to make it seem like prefix not trace modifies sigma_n
-We only analyze cases 1-5 because transitions from case 6 onwards is symmetric to transitions from case 1 onwards with 0's and 1's inverted, until the state eventually loops back to case 1.
-For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7, which is symmetric to case 2 with corresponding transitions and so on.\\
+We first show that each wireblock $u$ follow the state graph of Figure \ref{fig:l4}. 
+We will show by induction on $n$ that this is true for the length $n$ prefix of the trace $\sigma_n$.\\ %how to make it seem like prefix not trace modifies sigma_n
 
@@
 As noted in Lemma 2.1, each wireblock must be in case 1 or case 3b of Figure \ref{fig:l21}.
-Projecting these states onto the $c1$, $c2$ and $c3$ wires result in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
-
-The induction step is to assume that the induction hypothesis is true for a length $k$ prefix of a given trace, $\sigma_k$.  
-To show the induction hypothesis is true for the length $k+1$ prefix $\sigma_{k+1}$, we show the hypothesis is true for all possible (transitions) next states from state $s_k$.  
-By the induction hypothesis, a wireblock in state $s_k$ may be in any of the seven cases, so we check for each case that the wire block transitions according to Figure \ref{fig:l4}.  
+Projecting these wireblocks onto its $c1$, $c2$ and $c3$ wires result in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
+
+The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of traces of the fault-tolerant circuit. 
+To show the induction hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.
+Let the transitioning wireblock from state $s_k$ be called $w$.
+By the induction hypothesis, $w$ in state $s_k$ may be in any one of the cases in Figure \ref{fig:l4}, so we check for each case that the wire block transitions according to Figure \ref{fig:l4}.
+We make a further simplification and only analyze when $w$ is in cases 1-5 because transitions from case 6-10 is symmetric to transitions from case 1-5 with 0's and 1's inverted.
+For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7 as case 1 has to case 2, and so on.\\
+
 %so we observe the effects of the next transition on such a wire block. 
@@
 %For each case that a wire block may be in, we then investigate the case changes in all possible next states $s_{k+1}$. 
-The wire value of $c1^B$ is denoted by X in the figure because it is possible that a fault (satisfying the criteria of this lemma) has already occurred in the trace, so the value of wire $c1^B$ may be affected by that fault.
-We do not know the value of X except that it is either 0 or 1.
+The wire value of $c1^B$ is denoted by $X$ in the figure because it is possible that a fault on $c1^B$ or $v^B$ of wireblock $v$ has already occurred in the trace, so the value of wire $c1^B$ of other wireblocks may be affected by that fault.
+We do not know the value of $X$ except that it is either 0 or 1.
+Although we don't show the values for $w^B$, we also denote $w^B$ by $X$.
+Note that this representation also works for the wireblock $v$ when there is a fault on either $c1^B$ or $v^B$ so it encompasses all wireblocks of the circuit.
 %(Despite the possibility of a fault, we assume that wire $c1^B$ has value of either 0 or 1 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.<-should already be covered)
-Therefore we do not consider $c1^B$ transitions because the transition is covered by X. %X covers both cases when $c1^B$ is 0 or 1.
-  The possible next transitions from each of the seven cases are as follows:
+Also, we do not consider a $c1^B$ or $w^B$ transition because such a transition is covered by $X$. %X covers both cases when $c1^B$ is 0 or 1.
+The possible next transitions from each of the cases is as follows:
 %the cases do not depend on the wire value of $c1^B$
@@
 \item
-Case 1:  If the wireblock is in case 1, its $c2$ and $c3$ wires are not excited.
-Depending on the inputs to the wireblock, wire $c1^A$ may be excited.
-Therefore the wireblock either stays in this case or transitions to case 2 in state $s_{k+1}$.
+Case 1: If the transitioning wireblock is in case 1, its $c2$ and $c3$ wires are not excited and only the $c1^A$ and $w^A$ wires may be excited.
+Therefore, the wireblock either stays in this case or transitions to case 2 in state $s_{k+1}$.
 %(must prove both the state, and the transition, if there is any...
@@
 \item
-Case 2/3a/3b:   If the wireblock is in one of these cases, wire $c1^A$ cannot be excited due to Lemma 1 as it would violate semi-modularity for wire-blocks.
-The $c3$ wires are not excited.
-Depending on the wire value of $c1^B$ and the current case of the wireblock, one or both of the $c2$ wires may be excited.
-Therefore if the wireblock is in case 2, it either stays in case 2 or transitions to case 3a or 3b in state $s_{k+1}$.
-And if the wireblock is in case 3a or 3b, it either stays in the current case or transitions to case 4 in state $s_{k+1}$.
-(Do I need to say explicity it can stay in the current case?)
+Case 2/3a/3b: If the transitioning wireblock is in one of these cases, by Lemma 1, wire $w^A$ must be 0.
+Also, by Lemma 1, $c1^A$ cannot be excited as it would violate semi-modularity.
+Thus, the only excited wires are the $c2$ wires.
+Therefore, if the wireblock is in case 2, it transitions to case 3a or 3b in state $s_{k+1}$. And if the wireblock is in case 3a or 3b, it transitions to case 4 in state $s_{k+1}$.
 %I might need to show the excited ness of the good logic gate
 \item
-Cases 4/5a/5b:   If the wireblock is in one of these cases, again, wire $c1^A$ cannot be excited due to Lemma 1.
-The $c2$ wires are not excited.
-The $c3$ wires are excited.
-Therefore, if the wireblock is in case 4, it may transition to case 5a or 5b; and if the wireblock is in case 5a or 5b, it may transition to case 6.
+Cases 4/5a/5b: If the transitioning wireblock is in one of these cases, again, by Lemma 1, wire $w^A$ must be 0.
+And again, by Lemma 1, wire $c1^A$ cannot be excited as it would violate semi-modularity.
+Thus, the only excited wires are the $c3$ wires.
+Therefore, if the wireblock is in case 4, it transitions to case 5a or 5b; and if the wireblock is in case 5a or 5b, it transitions to case 6.
 \end{itemize}
-Thus, in all possible next states $s_{k+1}$, the wire block transitions according to Figure \ref{fig:l4}.
-This is true for each wireblock in the circuit, so the induction hypothesis holds for all length $k+1$ prefixes of traces and the induction step is complete.
-By induction on the length of the trace, the trace $\sigma$ also transitions according to Figure \ref{fig:l4}.  
+Thus, in all possible next states $s_{k+1}$, wireblock $w$ transitions according to Figure \ref{fig:l4}.
+For all other wireblocks, since they do not transition, they stay in the same cases as in state $s_k$.
+So, the induction hypothesis holds for all length $k+1$ prefixes of traces and the induction step is complete.
+By induction on the length of the trace, in each trace $\sigma$, each wireblock $u$ transitions according to Figure \ref{fig:l4}. \\ 
+For all states in Figure \ref{fig:l4}, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true. It follows that for each wireblock $u$, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true.
 \end{proof}
-By symmetry, this is also true if the fault occurs in the A half and the A and B labels in Figure \ref{fig:l4} are switched.  
-The importance of this Lemma is that at most one of the following happens: $c2^A\neq c2^B$ or $c3^A\neq c3^B$.
-This property can also be described as at most one of the $c2$ or $c3$ wire pairs can have different values.
-The next theorem uses this property to show that the fault-tolerant circuit does not deadlock under a single transient fault.\\
+Lemma 4 shows that at least one of the $c2$ or $c3$ wire pairs have the same values.
+The next theorem uses this property to show that an excited wireblock will transition when the transient fault is on the $c1^B$ or $v^B$ wires.\\
 %all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
 
-For a circuit under deadlock, where the circuit has no further transitions and is also not in a stopping state, we can make the following conclusion about the inputs and outputs of C-elements in that circuit.
 \begin{lemma}[5]
-If the circuit is under deadlock, and the two input wires into a C-element have the same value $p$, then the output of the C-element is also $p$.
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then if $w$ is an excited wireblock, $w^A$ will transition.
 \end{lemma}
 \begin{proof}
-For a circuit under deadlock, there are no excited elements.  If a C-element has two inputs with value $p$ and is unexcited, then the output must also be $p$.
+We prove by contradiction.
+Suppose that there is some wireblock $w$ in the fault-tolerant circuit that is excited but $w^A$ never transitions.
+Beerel \& Meng's lemma implies that after the mapping, $w$ doesn't transition in the original circuit and the circuit stops eventually in some state.
+Thus, the A-half of the fault-tolerant circuit also eventually stops and has no excited wires.
+By Lemma 4, since at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true for all wireblocks, then $c3^A=c3^B$ and subsequently $u^A=u^B$ are true for each wireblock $u$ when the A-half stops.
+This is illustrated in Figure \ref{fig:t2}.
+Furthermore $u^B$ cannot transition again since the A-half is stopped.
+Then the inputs to the A-half and B-half of wireblock $w$ have the same values.
+By the $h^A()$ mapping, the inputs to the $w$ logic block in the original circuit also have the same values.
+By Lemma 0 i), since wire $w$ is excited in the original circuit, then wire $c1^B$ is also excited.
+Since the inputs to $c1^B$ do not change, $c1^B$ eventually transitions.
+By similar reasoning, $c1^A$ must have transitioned as well and so $c1^A=c1^B$ which forces $c2^{A,B}$ then $c3^{A,B}$ then $w^{A,B}$ to the new value.
+This violates our initial assumption that $w^A$ does not transition.
+Thus, for an excited wireblock $w$, $w^A$ will transition.
 \end{proof}
-This lemma can be extended to the three successive layers of C-elements of a wireblock.
-For example, for the second layer of C-elements, if the wires $c2^A$ and $c2^B$ have the same value $p$, then under deadlock the wires $c3^A$ and $c3^B$ also have the value $p$.
-Then by extending this to successive layers of the C-elements, all outputs of the C-elements after this layer must also have the value $p$.
-This example is illustrated in Figure \ref{fig:t2}.
 
@@
 \includegraphics[width=\textwidth]{lemma4help}
-  \caption{a) If $c2^A=c2^B$, for example both are 0  b) At deadlock (no excitations) and $c2^A=c2^B$, then the two subsequent layers of C-elements must also be at 0. }
+\caption{a) If $c2^A=c2^B$, for example both are 0 b) If A-half stops (no excitations) and $c2^A=c2^B$, then the two subsequent layers of C-elements must also be at 0. }
 \label{fig:t2}
@@
 
-\begin{theorem}[2.1]
+\begin{theorem}[2]
 Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
-For every trace $\sigma$ of this circuit, the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
-And the fault-tolerant circuit does not deadlock.
+For every trace $\sigma$ of this circuit, the half-circuit mapping of the trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
 \end{theorem}
@@
 By Lemma 1, it is clear that the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
-Thus we need only to show that the circuit does not deadlock.\\
-
-First by Lemma 3, if the fault occurs on the $c2$ or $c3$ wires, then there is no observable differences on the output wires and the circuit does not deadlock.\\
-
-If the fault occurs on the remaining wires, we prove by contradiction that the circuit does not deadlock.
-We first show that the output wire pairs have the same values $w^A = w^B$ for all wireblocks.
-For a wireblock $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
-In either case, since the circuit is in deadlock, then by Lemma 5 the output wires of the wireblock have the property $w^A = w^B$.
-This is true for all wireblocks of the circuit.\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
-
-Next, we begin the proof by contradiction.
-Assume that the circuit is in a deadlocked state $s$.
-By Lemma 1, $h^A(s)$ is a state in the original circuit.
-By the definition of deadlock, the state $h^A(s)$ is not a stopping state so there must exist a wire $v$ with value $p$ that is excited.
-In the fault-tolerant circuit, the inputs to the $v^A$ logic block have the same values as the inputs to the $v$ logic block in the original circuit.
-However we assumed that the fault-tolerant circuit is deadlocked so wire $c1^A$ must have value $\neg{p}$.
-Using the property above where $w^A = w^B$ for all wireblocks, then by the same reasoning wire $c1^B$ must also have value $\neg{p}$.
-Since $c1^A=c1^B$, then by Lemma 5 wires $v^A$ and $v^B$ must have the same value as the $c1$ wires.
-%However in the original circuit wire $v$ has value $p$ which implies wire $v^A$ in the fault-tolerant circuit also has value $p$.
-However this results in wires $v^A$ and $v^B$ taking on values of both $p$ and $\neg{p}$, which is a contradiction.  Therefore the initial assumption is wrong and the circuit cannot be under deadlock.
-%excited blocks, and stopping states
-%the fallible part of the logic is that if inputs to B is the same it may not be excited (it is in our case because I know the structure of the logic block) but in a general implementation it could not be, ie if it depends on previous inputs etc
-
-\end{proof}
-
-\begin{theorem}[2.2]
-Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
-For every infinite trace $\sigma$ of this circuit, the half-circuit mapping of the trace $h^{A}(\sigma)$ is also complete.
-\end{theorem}
-\begin{proof}
-Given the mapped trace must be complete, we must verify that if a wireblock $w$ in the fault-tolerant circuit is excited, it must eventually transition.
-The proof is by contradiction.
-Assume that there is an infinite trace with a wireblock in the A-half that is excited but never transitions.
-We apply Lemma 3.2 from Beerel \& Meng that all cycles of states in live semi-modular circuits must contain all signal transitions.
-Thus the A-half is not in a cycle and eventually stops at some state.
-We look at some state $s_k$ in the trace where the A-half is stopped.
-Excitations on the $c1^A$ wires always transition because its inputs are all A-half wires, and by Lemma 1 and Lemma 0, if the logic block is excited it stays excited until it transitions.
-In fact, only excitations on wire $c2^A$ can halt because it is waiting for inputs from the A and B-half to have the same value.
-Once both $c2$ wires transition to the new value, faulty $c1^B$ values can not prevent the wireblock from completing its transition.
-This fact also extends to the property that once the A-half is stopped, the wireblock outputs in the B-half can change at most once.
-Then from state $s_k$, there are at most $O(n)$ transitions where $n$ is the number of wireblocks.
-Thus the trace is finite and contradicts the initial assumption.
-
+Thus, we need only to show that the resulting trace is also fair.\\
+
+Let the wireblock with the transient fault be called $v$.
+The fault can occur on wires $c1^B$, $c2^B$, $c3^B$ or $v^B$.
+If the fault occurs on wires $c2^B$ or $c3^B$, Lemma 3 shows that if a wireblock is excited, it will eventually transition.
+And if the fault occurs on wires $c1^B$ or $v^B$, Lemma 5 shows that if a wireblock is excited, it will eventually transition.
+
+And by Lemma 1, an excited wireblock in the fault-tolerant circuit corresponds to an excited wire in the original circuit, thus the mapped trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
 \end{proof}

### 2019-12-04 draft_final.tex
last fair traces version
edited ch 4, changed L3

@@
 
-\title{Background for transient faults in asynchronous circuits}
-\author{Zoey Zhou}
-\date{\today}  
 \usepackage{graphicx}
@@
 
+    \title{Fault-tolerant Asynchronous Circuits}
+    \author{Zoey Zhou}
+    \dept{Electrical Engineering}
+    \principaladviser{David Dill}
+    \firstreader{Subhasish Mitra}
+    \secondreader{Clark Barrett\\(Computer Science)}
+
+%\title{Background for transient faults in asynchronous circuits}
+%\author{Zoey Zhou}
+%\date{\today}
+
 \begin{document}
+
+\beforepreface
+
+\prefacesection{Abstract}
+
+\newpage
+
+%% one can also have a prefacesection that is a Preface instead of
+%% Acknowledgements.   The thematic purpose is the same (thanks).
+    \prefacesection{Acknowledgements}
+        I would like to thank Professor David Dill.
+
+%% afterpreface produces a table of contents and any other tables
+%% wanted. At the end pagenumbering changes from roman to arabic and
+%% is restarted
+    \afterpreface
+
 \chapter{Introduction}
@@
 Digital circuits can be divided into two types, synchronous and asynchronous.
-The time it takes for gates to process input signals and then propagate the output to the next gates in a digital circuit may vary widely.
+In digital circuits, the time it takes for gates to process input signals into output signals and for these signals to reach the next gates vary widely.
 If the timing is somehow off, it is possible for the outputs to be different from the desired value resulting in incorrect computation.
@@
 \includegraphics[width=\textwidth]{syncex}
-\captionof{figure}{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
+\captionof{figure}[Example of a synchronous digital circuit]{Example of a synchronous digital circuit.  Each output is gated by a flip flop that is controlled by the clock}
 \end{figure}
@@
 
-\includegraphics[width=\textwidth]{}
-\captionof{figure}{Example of a simple asynchronous circuit.  Note that there are no clocks and the signals can propagate at any time}
+%\includegraphics[width=\textwidth]{}
+%\captionof{figure}{Example of a simple asynchronous circuit.  Note that there are no clocks and the signals can propagate at any time}
 
@@
 This can be achieved in a number of ways such as a gate implementation as well as a transistor level implementation with feedback using a weak transistor, other implementations use capacitance to achieve this weak feedback.
+\begin{figure}
 \includegraphics[width=\textwidth]{celement}
-\captionof{figure}{a. logic of the C-element. A, B are inputs, C is the output \\ b. diagram of a C-element at the gate level c. transistor-level implementation}
+\captionof{figure}[C-element: logic and implementation]{a. logic of the C-element. A, B are inputs, C is the output \\ b. diagram of a C-element at the gate level c. transistor-level implementation}
+\end{figure}
 
@@
 \end{center}
-\captionof{figure}{transistor level implementation of a generalized C-element.
+\captionof{figure}[Generalized C-element implementation]{Transistor level implementation of a generalized C-element.
 The + signs are the set logic inputs and - signs are the reset logic inputs.
@@
 \end{center}
-\captionof{figure}{An example of an error if a fault occurs in an asynchronous TMR circuit}
+\captionof{figure}{TMR asynchronous circuit example with fault}
 Initially all output wire values are `0's.
@@
 \includegraphics[width=0.8\textwidth]{gates1}
-\captionof{figure}{a) the AND element is excited  b) an excited element fires to become stable}
+\captionof{figure}[AND excited and stable]{a) the AND element is excited  b) an excited element fires to become stable}
 \end{figure}
@@
 \includegraphics[width=0.9\textwidth]{element1}
-\captionof{figure}{a) the C-element is excited  b) two types of stable C-elements}
+\captionof{figure}[C-element excited and stable]{a) the C-element is excited  b) two types of stable C-elements}
 \end{figure}
@@
 In other words, for any state of a complete trace, if there are excited elements, one of them must fire, causing the circuit to transition to another state.
-\begin{definition}
-A {\em fair trace} is a trace of a circuit where if an element is excited in any state, it becomes stable in a finite number of transitions.
-\end{definition}
-In other words, every circuit element must be stable infinitely often in a fair trace.
+%\begin{definition}
+%A {\em fair trace} is a trace of a circuit where if an element is excited in any state, it becomes stable in a finite number of transitions.
+%\end{definition}
+I%n other words, every circuit element must be stable infinitely often in a fair trace.
 This fits with the physical properties of circuits because the elements are not arbitrarily slow and if excited, they will eventually change.
@@
 
-Combining semi-modularity and fair traces, since excited elements in semi-modular circuits can only become stable from the element firing, then a fair infinite trace of the circuit has the property that if an element is excited infinitely often, then it fires infinitely often.
+%Combining semi-modularity and fair traces, since excited elements in semi-modular circuits can only become stable from the element firing, then a fair infinite trace of the circuit has the property that if an element is excited infinitely often, then it fires infinitely often.
 
@@
     \includegraphics[width=.9\textwidth]{transf3Csimp}
-  \caption{a) original circuit b) after the fault-tolerant transformation}
+  \caption[Fault-tolerant transformation of an example circuit]{Fault-tolerant transformation of an example circuit: a) original circuit b) after the fault-tolerant transformation}
   \label{fig:dupschemeex}
@@
     \includegraphics[width=.6\textwidth]{sm_counter2}
-  \caption{a) original circuit for wire w b) an erroneous initialization}
+  \caption[Initializations]{Initializations: a) original circuit for wire w b) an erroneous initialization}
   \label{fig:sm_counter2}
@@
     \includegraphics[width=\textwidth]{circuitforproof3}
-  \caption{Fault-tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
+  \caption[Fault-tolerant transformation of each wire]{Fault-tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
   \label{fig:dupscheme}
@@
     \includegraphics[width=.8\textwidth]{counterexhalf}
-  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault-tolerant circuit}
+  \caption[State graph example of fault-tolerant circuit]{State graph example to show how b can transition before a or c finishes in both halves in the fault-tolerant circuit}
   \label{fig:counterexhalf}
@@
 ii)  if the outputs are the same value and $f$ is unexcited then $g$ is also unexcited.\\
-iii)  if the outputs are different values and $f$ is excited then $g$ is unexcited.
+iii)  if the outputs are different values and $f$ is excited then $g$ is unexcited.\\
+iv)  if $f$ is excited and $g$ is unexcited then the outputs have different values.
 \end{lemma}
@@
 i) \& ii)  Since $f$ and $g$ are identical gates or C-elements then if the inputs and output are the same values, $f$ and $g$ must be both excited or both unexcited. \\
-
 iii)  We prove this by contradiction.
@@
 This means that for some circuit element that these input values both cause the element to excite to 1 and 0 at the same time.
-This cannot happen in any of the elements that we build our circuit from and is therefore a contradiction.
+This cannot happen in any of the elements that we build our circuit from and is therefore a contradiction.\\
+iv)  We prove this by contradiction.
+Suppose that inputs to $f$ and $g$ are the same and the outputs are the same values but $f$ is excited and $g$ is unexcited.
+This violates i) and is therefore a contradiction.
 \end{proof}
@@
     \includegraphics[width=\textwidth]{gatewl2}
-  \caption{Different cases of P2 for a wireblock, 1-4 correspond to excited wire in the original circuit and 5 is unexcited.  1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
+  \caption[Different cases of a wireblock]{Different cases of P2 for a wireblock, 1-4 correspond to excited wire in the original circuit and 5 is unexcited.
+1) case 1, 2) case 2, 3) case 3, 4) case 4, 5) case 5}
   \label{fig:l1helper}
@@
     \includegraphics{flowl2c3}
-  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.
+  \caption[Lemma 2 transitions]{The wires in each row are in order of logic block, C1, C2, C3, W.
 Each row represents half of the duplicated circuit, ie.
@@
 which I think I need to show the signals propagating through??
-It is now easy to show that deadlock does not occur since each wire block must be in one of the configurations of figure \ref{fig:l21}.
+It is now easy to show that deadlock does not occur since each wire block must be in one of the configurations of Figure \ref{fig:l21}.
 \begin{lemma}[2.2]
@@
 %with these 3 properties show the original claim
+
 \section{Single transient fault analysis}
@@
 flips the bit of $w$.
-After the transient event, the affected wire transitions based on its inputs.
+In light of this, we have expanded the definition of a transition to include the case where the wire value changes due to the transient fault.
+After the transient event, the faulty wire transitions based on circuit rules.
 %do I need to talk about when transient is not ~x?
@@
     \includegraphics[width=\textwidth]{faultexes}
-  \caption{Effects of a transient fault.  The left most figure is the state right before a transient fault occurs.  The transition due to the transient fault is denoted by the red F and arrow.   \\
+  \caption[Effects of a transient fault]{Effects of a transient fault.
+The left most figure is the state right before a transient fault occurs.
+The transition due to the transient fault is denoted by the red F and arrow.
+\\
   a) An AND gate, the transient fault causes a transition in $w$ to 0 but the inputs resurrect it back to 1 sometime later.   \\
@@
 \end{figure}
-Examples of the transient fault occuring to gates in different states are shown in Figure \ref{fig:faultx}.
-Depending on the inputs and the specific gate, the transient fault can cause a transition to a faulty value and transition back to the previous value; or it can cause a transition that would happen anyway and thus do not affect the gate/ circuit; or the faulty value may be stored in memory elements like the C-element in the hold state.
+Examples of the transient fault occuring on elements in different states are shown in Figure \ref{fig:faultx}.
+Depending on the inputs and the element, the transient fault can cause a transition to a faulty value and transition back to the previous value; or it can cause a transition that would happen anyway and thus does not affect the element or circuit; or the faulty value may be stored in memory elements such as the C-element in the hold state.\\
 
@@
 \begin{definition}
-A {\em faulty trace} is a trace of the circuit where for all $k$, a transition from $s_k$ to $s_{k+1}$ is either a transition as defined in the fault-free case, or a transition through a transient fault.
+A {\em faulty trace} is a trace of the circuit where for all $k$, a transition from $s_k$ to $s_{k+1}$ is either a transition through an excited element or primary input, or a transition through a transient fault.
 %there exists an $n$ where $\sigma_n$ is a prefix of a trace of the fault free circuit, then the $n+1$st transition is a transient fault.  After the fault occurs, the circuit continues to transition .
 \end{definition}
-Transitions after the fault is based on circuit rules and not necessarily the state graph.
-To see this, note that the state graph does not necessarily include all possible states of the circuit.
-The circuit synthesis technique is designed such that if the circuit is in a state of the state graph, the circuit follows the state graph.
+Transitions after the fault is based on circuit rules and new transitions may occur.
+To see this, note that the fault-free traces do not necessarily include all possible states of the circuit.
+The circuit synthesis technique is designed such that if the circuit is in a state of the fault-free traces, the circuit follows the predefined transitions.
 However, a fault may cause $s_{n+1}$ to be in a previously unreachable state.
@@
 It is useful to extend the concept of excited wireblocks to include wireblocks from faulty traces.
-Since we assume the fault is in the B-half, the A-half is fault-free and by Lemma 1, the wireblock in one of cases 1-5 of Figure \ref{fig:l1helper}.
+Since we assume the fault is in the B-half, the A-half is fault-free, and by Lemma 1, the wireblock in one of cases 1-5 of Figure \ref{fig:l1helper}.
 \begin{definition}
@@
 \end{definition}
-Also by Lemma 1, a wireblock is excited if and only if the corresponding wire in the original circuit is also excited.\\
-
-The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.
-To prove this, we need to show that if a wire $w$ in the original circuit is excited, it will eventually transition.
-Equivalently, if a wireblock $w$ in the fault-tolerant circuit is excited, it will eventually transition.
-We assume that the fault happens only in the B-half and in some wireblock $v$.
-By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.
-The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\
-
-The transient fault can be split into two cases: the fault occurs on the $c2^B$ or $c3^B$ wires of $v$, or the fault occurs on the remaining wires $c1^B$ or $v^B$.
-For the first case, if the fault occurs on the $c2^B$ or $c3^B$ wires, we can directly show that if a wireblock is excited, then it will eventually transition.
-The result is shown in Lemma 3.
-However, if the fault occurs on $c1^B$ or $v^B$, the reasoning is more complex.
-The result is shown in Lemma 4 and 5.\\
-
-We also use the following lemma from Beerel \& Meng (1991).
-\begin{lemma}[3.2]Given a live semi-modular speed-independent asynchronous control circuit, all cycles of states in the valid ESG (fault-free traces) must contain all signal (wire) transitions.\\
-\end{lemma}
+Also, by Lemma 1, a wireblock is excited if and only if the corresponding wire in the original circuit is also excited.\\
+
+The next major theorem, Theorem 2, states that the prefix of a faulty trace in the fault-tolerant circuit maps to the prefix of a fault-free trace of the original circuit, and the fault-tolerant circuit does not deadlock.
+The first part is already covered by Lemma 1.
+The main contribution of Theorem 2 is to show that the fault-tolerant circuit does not deadlock.
+To prove this, we first assume that the transient fault occurs in a wireblock $v$.
+Then, the transient fault can be split into two cases: the fault occurs on the $c2^B$ or $c3^B$ wires of $v$; or the fault occurs on the remaining wires $c1^B$ or $v^B$.
+For the first case, if the fault occurs on the $c2^B$ or $c3^B$ wires, we directly show that each wireblock follows transitions similar to the fault-free case.
+This result is shown in Lemma 3.
+However, for the second case, if the fault occurs on $c1^B$ or $v^B$ wires, we show that at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true for each wireblock.
+This result is shown in Lemma 4.
+These lemmas are then used to show that deadlock cannot occur.\\
+
+%We also use the following lemma from Beerel \& Meng (1991).
+%\begin{lemma}[3.2]Given a live semi-modular speed-independent asynchronous control circuit, all cycles of states in the valid ESG (fault-free traces) must contain all signal (wire) transitions.\\
+%\end{lemma}
 %The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.
@@
 \begin{lemma}[3]
-For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wireblock $v$, then if $w$ is an excited wireblock, $w^A$ will transition.
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wireblock $v$, then for each wireblock $w$ (including $v$), at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
 
@@
 \includegraphics{L3helperfull}
-\caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
+\caption[Fault-free transitions of $c1$ and $w$ wires]{The projection of the states in Figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
 This forms the input and output characteristic of a wire block of a fault-free trace.}
@@
 \begin{proof}
+We first show that for each wireblock $w$, its $c1^A$, $c1^B$ and $w^A$, $w^B$ wires transition according to Figure \ref{fig:l3helper}.  
 We use NuSMV to prove this.
-For each wireblock $w$, by Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) of a fault-free trace follow the state diagram shown in Figure \ref{fig:l3helper}.
+For each wireblock $w$ of a fault-free trace, by projecting the states in Figure \ref{fig:l21} from Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) follow the state diagram shown in Figure \ref{fig:l3helper}.
+Next we consider a faulty trace.
 We can view the circuit as composed of two components, the faulty wireblock $v$ and the rest of the circuit.
@@
 
-The strategy of the proof focuses on interactions between wireblock $v$ and the rest of the circuit.
-Assume $c1^A$ and $c1^B$ transition as in the fault-free trace, then if $v^A$ and $v^B$ follow the state diagram (Figure \ref{fig:l3helper}), this validates our assumptions for $c1^A$ and $c1^B$ and at the same time shows $v^A$ and $v^B$ follow the state diagram.
-\\
-
-Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: Lemma 3.2 (Beerel \& Meng) states that wires $c1^A$ and $c1^B$ become excited and transition an infinite number of times.
-In NuSMV, we model $c1^A$ and $c1^B$ as being excited infinitely often and excited only after the previous $v^A$ and $v^B$ transitions complete.
-We also model the rest of wireblock $v$, that is, the $c2^A$, $c2^B$, $c3^A$, $c3^B$, $v^A$ and $v^B$ wires.
-A transient fault occurs on wires $c2^B$ or $c3^B$ anytime during the trace.
-The specifications that are checked using NuSMV are that $v^A$ and $v^B$ transition according to the state diagram (Figure \ref{fig:l3helper}).
+The strategy of the proof by NuSMV focuses on interactions between wireblock $v$ and the rest of the circuit.
+Assume $c1^A$ and $c1^B$ transition as in the fault-free trace, then if $v^A$ and $v^B$ follow the state diagram (Figure \ref{fig:l3helper}), this validates our assumptions for $c1^A$ and $c1^B$.
+At the same time, this shows $c1^A$, $c1^B$, $v^A$ and $v^B$ follow the state diagram.
+\\
+
+Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: $c1^A$ and $c1^B$, if they transition, can only be excited after the previous $v^A$ and $v^B$ transitions complete.
+(Note if figure \ref{fig:l3helper} is true when $c1^A$ and $c1^B$ are excited infinitely often, then it is also true for when one or both of $c1^A$ and $c1^B$ stop after a finite number of transitions.
+This is because in the finite case, the wireblock stops in one of the first 3 states in figure \ref{fig:l3helper} and does not violate the transitions in the figure.
+Thus, we only need to consider the case where both $c1^A$ and $c1^B$ are excited infinitely often)
+We model $c1^A$ and $c1^B$ in NuSMV as such.  
+%in NuSMV, we model $c1^A$ and $c1^B$ as being excited only after the previous $v^A$ and $v^B$ transitions complete. 
+We also model the rest of wireblock $v$, that is, the $c2^A$, $c2^B$, $c3^A$, $c3^B$, $v^A$ and $v^B$ wires and their circuit elements.
+These wires are initialized to a valid initial state and then the wires transition accordingly.
+Then, a transient fault occurs on wires $c2^B$ or $c3^B$ anytime during the trace.
+Under this scenario, NuSMV checks the specifications that the wires $v^A$ and $v^B$ transition according to the state diagram (Figure \ref{fig:l3helper}).
 \\
@@
 Running the NuSMV model show that these properties are indeed true.
-Then for wireblock $v$, once it is excited $v^A$ will transition.
-For all other wireblocks $u$, since they don't have faults then Lemma 2.1 apply and if $u$ is excited, $u^A$ will transition.
+Then, wireblock $v$ transitions according to Figure \ref{fig:l3helper}.
+For all other wireblocks, since the fault in wireblock $v$ does not affect them, then Lemma 2.1 still apply.
+Since Figure \ref{fig:l3helper} is a projection of the states in Figure \ref{fig:l21} from Lemma 2.1, then the remaining wireblocks also transition according to Figure \ref{fig:l3helper}.
+\\
+
+For all states in Figure \ref{fig:l3helper}, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true. It follows that for each wireblock $w$, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
+
 %We use NuSMV to verify that if a transient fault occurs on wire $c2^B$ or $c3^B$ of wire block $w$, the input-output characteristic of the local C-element chain does not change.
@@
 \includegraphics{flowl4c3full}
-\caption{The wires in each row are in order of $c1$, $c2$ and $c3$.
+\caption[Wireblock transitions with fault on $c1^B$ or $w^B$]{The wires in each row are in order of $c1$, $c2$, $c3$ and $w$.
 Each row represents half of the duplicated circuit, i.e.
 top row are A half wires and bottom row are B half wires.
-Note that case 5 transitions according to case 1 except with the 0's and 1's inverted.
-The states transition after that are inverted versions of state 2-4 until it transitions back to state 1 (uninverted).}
+Note that cases 6-10 are symmetric to cases 1-5 with the 0's and 1's inverted.}
 \label{fig:l4}
@@
 
-We showed that if a fault occurs on the $c2^B$ or $c3^B$ wires, then if a wireblock is excited, it will eventually transition. 
-Next, we show the same result for when the fault occurs on $c1^B$ or $v^B$ wires.
-
-The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.
+The importance of this result is that, if a fault occurs on the $c2^B$ or $c3^B$ wires of $v$, then at least one of $c1^A=c1^B$ or $w^A=w^B$ is true, for all wireblocks $w$.
+Next, we show a similar result for when the fault occurs on the $c1^B$ or $v^B$ wires.
 
@@
 To show the induction hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.
-Let the transitioning wireblock from state $s_k$ be called $w$.
-By the induction hypothesis, $w$ in state $s_k$ may be in any one of the cases in Figure \ref{fig:l4}, so we check for each case that the wire block transitions according to Figure \ref{fig:l4}.
+Let $w$ represent the transitioning wireblock from state $s_k$.
+By the induction hypothesis, $w$ in state $s_k$ may be in any one of the cases in Figure \ref{fig:l4}, so for each case, we check  that the wire block transitions accordingly.
 We make a further simplification and only analyze when $w$ is in cases 1-5 because transitions from case 6-10 is symmetric to transitions from case 1-5 with 0's and 1's inverted.
@@
 We do not know the value of $X$ except that it is either 0 or 1.
-Although we don't show the values for $w^B$, we also denote $w^B$ by $X$.
-Note that this representation also works for the wireblock $v$ when there is a fault on either $c1^B$ or $v^B$ so it encompasses all wireblocks of the circuit.
+The wire value of $w^B$ is also denoted by $X$.
+Note that this representation also works for the wireblock $v$ when there is a fault on either $c1^B$ or $v^B$, so it encompasses all wireblocks of the circuit.
 %(Despite the possibility of a fault, we assume that wire $c1^B$ has value of either 0 or 1 and that even with hazards on $c1^B$, the $c2$ wires transition to either 0 or 1.<-should already be covered)
-Also, we do not consider a $c1^B$ or $w^B$ transition because such a transition is covered by $X$. %X covers both cases when $c1^B$ is 0 or 1.
+The $X$ symbol further simplifies our analysis because we do not need to consider a $c1^B$ or $w^B$ transition since such a transition is masked by $X$.  %X covers both cases when $c1^B$ is 0 or 1.
 The possible next transitions from each of the cases is as follows:
@@
 By induction on the length of the trace, in each trace $\sigma$, each wireblock $u$ transitions according to Figure \ref{fig:l4}. \\
+
 For all states in Figure \ref{fig:l4}, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true. It follows that for each wireblock $u$, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true.
 \end{proof}
-Lemma 4 shows that at least one of the $c2$ or $c3$ wire pairs have the same values.
-The next theorem uses this property to show that an excited wireblock will transition when the transient fault is on the $c1^B$ or $v^B$ wires.\\
+Lemma 4 shows that at least one of the $c2$ or $c3$ wire pairs have the same values. \\
 %all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
 
-\begin{lemma}[5]
-For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then if $w$ is an excited wireblock, $w^A$ will transition.
-\end{lemma}
-\begin{proof}
-We prove by contradiction.
+%\begin{lemma}[5]
+%For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then if $w$ is an excited wireblock, $w^A$ will transition.
+%\end{lemma}
+%\begin{proof}
+%We prove by contradiction.
 Suppose that there is some wireblock $w$ in the fault-tolerant circuit that is excited but $w^A$ never transitions.
@@
 Thus, for an excited wireblock $w$, $w^A$ will transition.
+%\end{proof}
+
+For a circuit under deadlock, where the circuit has no excited elements, the C-elements in such a circuit have the following property.
+\begin{lemma}[5]
+If the circuit is under deadlock, and the two input wires into a C-element have the same value $p$, then the output of the C-element is also $p$.
+\end{lemma}
+\begin{proof}
+For a circuit under deadlock, there are no excited elements.  If a C-element has two inputs with value $p$ and is unexcited, then the output must also be $p$.
 \end{proof}
+This lemma can be extended to the three successive layers of C-elements of a wireblock.
+For example, if the wires $c2^A$ and $c2^B$ from the second layer of C-elements have the same value $p$, then under deadlock and by Lemma 5, the wires $c3^A$ and $c3^B$ also have the value $p$.
+Then, the next layer consisting of wires $w^A$ and $w^B$ must also have the value $p$.
+This example is illustrated in Figure \ref{fig:t2}.
 
@@
 \includegraphics[width=\textwidth]{lemma4help}
-\caption{a) If $c2^A=c2^B$, for example both are 0 b) If A-half stops (no excitations) and $c2^A=c2^B$, then the two subsequent layers of C-elements must also be at 0. }
+\caption[C-element under deadlock]{a) If $c2^A=c2^B$, for example both are 0 b) If A-half stops (no excitations) and $c2^A=c2^B$, then the two subsequent layers of C-elements must also be at 0. }
 \label{fig:t2}
@@
 
+The next theorem uses the previous lemmas to show that the fault-tolerant circuit does not deadlock under a single transient fault.
+
 \begin{theorem}[2]
-Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
-For every trace $\sigma$ of this circuit, the half-circuit mapping of the trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
+Consider a fault-tolerant circuit with a single transient fault in the B-half circuit.
+For every trace $\sigma$ of this circuit, the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
+And the fault-tolerant circuit does not deadlock.
 \end{theorem}
 \begin{proof}
-By Lemma 1, it is clear that the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
+By Lemma 1, the half-circuit mapping of a prefix $h^{A}(\sigma_n)$ is also a prefix of a trace of the original circuit.  Thus, we only need to show that the circuit does not deadlock.\\
+
+We first show at deadlock that for each wireblock $w$, its output wire pairs have the same values $w^A = w^B$.
+Let the wireblock with the transient fault be called $v$.
+The fault can occur on wires $c1^B$, $c2^B$, $c3^B$ or $v^B$.
+If the fault occurs on wires $c2^B$ or $c3^B$, Lemma 3 states that at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
+However, if $c1^A=c1^B$, then by Lemma 5, $w^A = w^B$ at deadlock.
+Thus, at deadlock, each wireblock $w$ has $w^A = w^B$.\\
+
+And if the fault occurs on wires $c1^B$ or $v^B$, we apply similar reasoning.
+For each wireblock $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
+In either case, since the circuit is in deadlock, then by Lemma 5 the output wires of the wireblock have the property $w^A = w^B$.
+\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
+
+Next, we prove that the circuit does not deadlock by contradiction.
+Assume that the circuit is deadlocked, that is, the circuit is stopped in a state $s$ where $h^A(s)$ is not a stopping state in the original circuit.
+By definition, there must exist a wire $v$ with value $p$ that is excited in state $h^A(s)$.
+In other words, wireblock $v$ is excited and $v^A$ also has value $p$.
+The inputs to $v$ in the original circuit and the inputs to $c1^A$ in the fault-tolerant circuit have the same values.
+In addition, since $w^A = w^B$ for all wireblocks, then the inputs to $c1^B$ also have the same values.
+By Lemma 0 iv), since wire $v$ is excited in the original circuit, then both wires $c1^A$ and $c1^B$ have value $\neg{p}$ in a deadlocked state.
+Then, by Lemma 5, wires $w^{A}$ and $w^B$ have value $\neg{p}$ as well.
+\\
+%However in the original circuit wire $v$ has value $p$ which implies wire $v^A$ in the fault-tolerant circuit also has value $p$.
+
+However, this shows wire $v^A$ does transition to $\neg{p}$ and wireblock $v$ is not excited, which is a contradiction.
+Therefore, the initial assumption is wrong and the circuit cannot be under deadlock.
+%taking on values of both $p$ and $\neg{p}$
+%excited blocks, and stopping states
+%the fallible part of the logic is that if inputs to B is the same it may not be excited (it is in our case because I know the structure of the logic block) but in a general implementation it could not be, ie if it depends on previous inputs etc
+
+\end{proof}
+
+%\begin{theorem}[2]
+%Consider a fault-tolerant circuit with a single transient fault in the B half circuit.
+For every trace $\sigma$ of this circuit, the half-circuit mapping of the trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
+%\end{theorem}
+%\begin{proof}
+%By Lemma 1, it is clear that the half-circuit mapping of a prefix $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit.
 Thus, we need only to show that the resulting trace is also fair.\\
-
-Let the wireblock with the transient fault be called $v$.
+%
+%Let the wireblock with the transient fault be called $v$.
 The fault can occur on wires $c1^B$, $c2^B$, $c3^B$ or $v^B$.
@@
 And if the fault occurs on wires $c1^B$ or $v^B$, Lemma 5 shows that if a wireblock is excited, it will eventually transition.
-
-And by Lemma 1, an excited wireblock in the fault-tolerant circuit corresponds to an excited wire in the original circuit, thus the mapped trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
-\end{proof}
-
-Thus we have shown that under a single transient fault that the transformed circuit has a half that behaves like the original circuit and the transformation is a fault-tolerant transformation.
+%
+%And by Lemma 1, an excited wireblock in the fault-tolerant circuit corresponds to an excited wire in the original circuit, thus the mapped trace $h^{A}(\sigma)$ is a fair trace of the original circuit.
+%\end{proof}
+
+Thus, we have shown that under a single transient fault that the transformed circuit has a half that behaves like the original circuit and also does not deadlock.
+The transformation is a fault-tolerant transformation.
 

### 2019-12-04 draft_final.tex
edited first half of ch 2, not lit review

@@
 \chapter{Related Works}
-\section{Faults}
-Faults can be split into permanent and non-permanent faults. Non-permanent faults are further split into transient and intermittent faults \cite{jha_gupta_2003}. %copied 
-A fault is defined as the physical difference between the good or correct system and the current system.
-An error may be caused by a fault, which is when the state of the system differs from the state of the good system and thus unable to perform some specified function.
-Hidden faults are also possible where the fault does not cause an error \cite{jha_gupta_2003}.
-\\
-
-Permanent faults refer to the presence of a fault that affects the functional behavior of a system(circuit) permanently.
-Some examples that may cause permanent faults are: incorrect connections between integrated circuits, broken components or parts of components, incorrect silicon and metal connections (manufacturing problem), and functional design errors.
+\section{Fault Model}
+A fault is defined as the physical difference between the good or correct system, and the current system.
+In this work, the system is the asynchronous circuit.
+An error, which is when the state of the system differs from the state of the good system and thus unable to perform some specified function, may be caused by a fault.
+Hidden faults, where the fault does not cause an error, are also possible \cite{jha_gupta_2003}.
+\\
+
+Faults can be split into permanent and non-permanent faults.
+Permanent faults are faults that affect the functional behavior of a system or circuit permanently.
+Non-permanent faults are faults that affect the system's functional behavior for a finite, but unknown period of time.
+Non-permanent faults can occur at random moments and are categorized into two types:  transient faults and intermittent faults \cite{jha_gupta_2003}.\\ %copied
+
+Transient faults are caused by many environmental sources such as cosmic rays, $\alpha$-particles, pollution, humidity, temperature, pressure, vibration, power supply fluctuations, electromagnetic interference, static electrical discharges, and ground loops.
+In particular, $\alpha$-particles are a major cause of transient faults.
+The $\alpha$-particles can interact with the semiconductor material which result in the generation of electron-hole pairs.
+When an $\alpha$-particle collides and interacts with the circuit, it can induce a voltage change on a wire.
+When the $\alpha$-particle causes a bit flip on a wire, this is called a single-event upset (SEU).
+When the SEU is on the output wire of a gate, that wire will eventually return to its previous value.
+If the SEU is on the output of a memory element, such as a flip flop, latch, or C-element, that faulty value is instead stored.
+SEUs include both single-bit and multi-bit upsets, but single-bit upsets, where a single wire is affected, are most common.
+There are other transient Single Event Effects (SEEs) such as the single-event transient (SET), where there is a voltage pulse on the wire.
+SEUs are the most abundant type of transient faults and we focus on SEUs in this work.
+\cite{jha_gupta_2003}\\
+
+Intermittent faults, another non-permanent fault, are caused by non-environmental conditions such as loose connections, deteriorating or aging components, critical timing (hazards and race conditions), resistance and capacitance variations (which may lead to timing faults), physical irregularities, and noise.
+Intermittent faults can transition into permanent faults naturally but may take a long time ranging from hours up to months.
+\\
+
+Permanent faults are caused by radiation, incorrect connections between integrated circuits, broken components or parts of components, incorrect silicon and metal connections (manufacturing problem), and functional design errors.
 Most permanent faults occur during fabrication.
-There are many existing literatures that cover permanent faults and the different tests at production time that can uncover the presence and location of these faults.
+Much work has been done on permanent faults and designing different tests at production time to uncover the presence and location of these faults.
 \cite{jha_gupta_2003} \cite{giz_book_2006}.
-We ignore the possible manufacturing problems and assume that the circuit is free from those problems.
-Instead we consider the permanent faults that develop during operation from radiation.
-For example, high energy ions can impact the transistors and the circuit causing short-circuiting, rupture of the gate oxide insulation and other permanent faults.\\ %copied from SEE eetimes article
-
-Non-permanent faults are defined as faults that affect the system's functional behavior for a finite but unknown period of time.
-They can occur at random moments and are categorized into two types, intermittent and transient faults.
-Intermittent faults are caused by non-environmental conditions such as loose connections, deteriorating or aging components, critical timing (hazards and race conditions), resistance and capacitance variations (which may lead to timing faults), physical irregularities, and noise.
-Intermittent faults usually affect the system for a shorter time period than the application time of a test developed for permanent faults and thus may not be detected using such a test.
-Intermittent faults can transition into permanent faults naturally but may take a long time from hours up to months.
-\\
-
-Transient faults are caused by environmental conditions such as cosmic rays, $\alpha$-particles, pollution, humidity, temperature, pressure, vibration, power supply fluctuations, electromagnetic interference, static electrical discharges, and ground loops.
-In particular $\alpha$-particles are a major cause of these faults.
-These $\alpha$-particles can interact with the semiconductor material which results in the generation of electron-hole pairs.
-When these $\alpha$-particles collide and interact with the circuit it can induce a voltage/current pulse.
-Also known as single-event transients (SETs), if the width of this pulse or transient is wide enough it may propagate through the circuit.
-$\alpha$-particles may also interact with a memory element (of which flip flops, latches and C-elements are most relevant to this work) and cause a bit flip in the state of the memory element.
-This is also known as single-event upsets (SEUs), SEUs include both single-bit and multi-bit upsets but single-bit upsets are most common and much work has been done to eradicate failures from SEUs.
-Transient faults may be hard to detect because it appears sporadically and may not affect the system during testing. \\
-
-In this work we will not be concerned with intermittent faults since it can be thought of as a transition between transient to permanent faults.
-Instead the two main fault modes we will look into are transient and permanent faults.
-In both radiation effects, also called single event effects (SEEs), figure prominently.
-SEEs are an umbrella term that covers the aforementioned SETs and SEUs as well as the single event effects causing permanent faults.
-There are two main sources of radiation, one is cosmic rays from space which interact with the atmosphere to produce high energy neutrons.
-Another is that $\alpha$-particles can be caused by trace impurities of radioactive elements present in the packaging material of the chip and the silicon substrate.
-Radiation from cosmic rays become more severe at higher elevations while the latent source in packaging is difficult to eliminate.
+Unfortunately, these methods do not work for non-permanent faults as these faults affect the system for a shorter time period and thus may not be detected at all.
+In addition to possible manufacturing problems, permanent faults can develop during operation due to radiation and aging effects.
+For example, high energy ions can impact the transistors and the circuit, causing short-circuiting, rupture of the gate oxide insulation and other permanent faults.\\ %copied from SEE eetimes article
+
+As mentioned before, we focus on SEUs as our main fault model because they are the most abundant transient faults.
+Transient faults happen sporadically so there are usually long intervals of time, such as days to months, between consecutive SEUs.
+Thus we model each fault as happening one at a time and call it a single transient fault.
+We will not be concerned with intermittent faults because they take a while to develop.
+We also ignore permanent faults because they are usually detected at production time.
+\\
+
+There are two main sources of radiation that cause SEUs: one is cosmic rays from space which interact with the atmosphere to produce high energy neutrons; another is the $\alpha$-particles caused by trace impurities of radioactive elements present in the packaging material of the chip and the silicon substrate.
+Radiation from cosmic rays become more severe at higher elevations.
 Thus, initially a lot of the work in fault-tolerant design was done for aviation and space flight.
+However, fault-tolerant design is becoming more important as radiation effects become more prominent in new circuit technology.
 
@@
 \section{Asynchronous Circuit and Synthesis}
-In the previous chapter we described how an asynchronous circuit works from a higher-level perspective and in particular that it should work under varying delays.
-In this section we will cover some definitions and properties of the circuit and also how we can synthesize the circuit from a higher-level specification.
-Both Speed Independent and Delay Insensitive technologies will be introduced.
+In the previous chapter, we described how an asynchronous circuit works from a higher-level perspective; that it should work under varying delays.
+In this section, we will cover some definitions and properties of such a circuit and how the circuit is synthesized from a higher-level specification.
+%Both Speed Independent and Delay Insensitive technologies will be introduced.
 There are differences but also many similarities between the two methods.
@@
 \subsection{Speed Independent Circuits}
-As mentioned in the introduction, circuits are composed of gates and wires.
-The unbounded gate delay model assumes an arbitrary delay on all the gates and no delay on wires.
+Circuits are composed of logic elements and wires.
+The unbounded gate delay model assumes an arbitrary delay on the logic elements and no delay on wires.
 This delay model is the basis for Muller circuits \cite{Muller_59}.
 Circuits that operate correctly regardless of the delay are called Speed Independent Circuits.
-The correct operation is specified when designing the circuit, for example, given some input values the circuit will return specified output values.
-There are many ways to represent specifications such as Petri nets and state graphs, and there are established methods to build asynchronous circuits to satisfy the specifications.
+The designer specifies the correct operation of the circuit.
+For example, given certain input values, the circuit will return specified output values.
+There are many ways to represent specifications such as with Petri nets and state graphs, and there are established methods to build asynchronous circuits that satisfy the specifications \cite{myers_book_2004}.
 We won't go into these representations and methods in detail, other than the aspects that are relevant to this work.
-We consider circuits which has wires that take on Boolean values of either `1' or `0'.\\
+We work with digital circuits, so the wires take on Boolean values of either `1' or `0'.\\
+
 %Wires in the circuits take on Boolean values of either `1' or `0'.
@@
 %C-elements
-The C-element proposed by Muller is an important building block for asynchronous circuits.
-It acts as a memory element in that it receives two inputs.
-When both inputs are low, the C-element output goes low, and when both inputs are high the C-element output goes high.
-However, when the inputs are mismatched then the output gets held at its previous value.
-This can be achieved in a number of ways such as a gate implementation as well as a transistor level implementation with feedback using a weak transistor, other implementations use capacitance to achieve this weak feedback.
+\subsection{C-elements}
+The C-element proposed by Muller, is an important building block for asynchronous circuits.
+It acts as a memory element because it can sometimes store a previous output value.
+A C-element has two inputs, when both inputs are low, the C-element output goes low, and when both inputs are high, the C-element output goes high.
+However, when the inputs are different Boolean values, the output gets held at its previous value.
+This can be achieved in a number of ways such as a gate-level implementation or a transistor-level implementation with feedback using a weak transistor, still other implementations use capacitance to achieve this weak feedback.
+C-elements are an essential component of Muller circuits and asynchronous circuit designs.
+\\
 \begin{figure}
@@
 \end{figure}
-
-C-elements can be used in various asynchronous circuit designs and is an essential component of Muller circuits. \\
-
-The two specific Muller circuit implementations that we consider are the generalized C-element and standard C-implementations.
-We assume that the circuits we want to make fault-tolerant are synthesized according to these two implementations.
-Each wire in the circuit is the output wire of a gate logic.
-The gate logic has a set of input wires and the output wire changes value according to the values of the inputs.
-We look at two conditions, set, the condition for the output wire to transition to a high value; and reset, the condition for the output wire to transition to a low value.
-The gate logic then implements the set and reset conditions.
-We skim the details in finding the set and reset conditions from the circuit specifications.
+%replace with figure from ...
+
+For a semi-modular state graph, there are many existing methods of implementing a Speed-Independent asynchronous circuits that satisfies the state graph.
+Generalized C-element implementation and standard C-implementation are two possible circuit implementations using C-elements.
+A generalized C-element directly implements switching logic and the C-element as one circuit element at the transistor-level \cite{myers_book_2004}.
+This means, for the purpose of the asynchronous circuit, there is only one delay for this logic block.
+The logic for the C-element component is as follows: there is a set condition, the condition for the output wire to transition to a high value; and a reset condition, the condition for the output wire to transition to a low value.
+The set and reset conditions are designed to be mutually exclusive so that they are never both true at the same time.
+The set and reset conditions are implemented with transistors and inserted into the C-element's pull-up and pull-down networks respectively.\\
+
+%We skim the details in finding the set and reset conditions from the circuit specifications.
 For each condition set and reset, there is an ON-set, OFF-set and Don't Care set.
@@
 \\
-
-The same procedure applies as well in finding the ON-set, OFF-set and Don't Care set for reset except substituting in reset for set and flipping the value of the wire from high to low and vice versa.
+We assume that the circuits we want to make fault-tolerant are synthesized according to these two implementations.
+
+%The same procedure applies as well in finding the ON-set, OFF-set and Don't Care set for reset except substituting in reset for set and flipping the value of the wire from high to low and vice versa.
 The set and reset conditions constructed this way then follows the desired circuit specification.
@@
 
-Even though the generalized C-element is presented as a C-element with set and reset as inputs, the transistor level implementation differs slightly.
+%Even though the generalized C-element is presented as a C-element with set and reset as inputs, the transistor level implementation differs slightly.
 We assume a transistor level implementation of the set and reset combined with the C-element so that there is only one delay for the entire logic block.
@@
 
-The main difference is that the set logic and the reset logic must be designed so that they do not turn `ON' at the same time.\\
-
-For the standard C-implementation, we allow for more variation in delay.
-For each wire in the circuit with a corresponding gate logic, we look at the set and reset logic as composition of various gates (such as AND, OR, NOT).
-Each of these gates can have their own delay that is arbitrary in length that is instantized as an intermediate wire.
-Thus, the logic must be synthesized more carefully to eliminate hazards that can occur in these intermediate wires.
-In particular the set and reset must be activated at states only when the wire is appropriately excited.
-As a result, the standard C-implementation has a number of set logic functions combined by an OR gate and fed into one input of the C-element.
-There will also be a number of reset logic functions combined by an OR gate and passed through an inverter and fed into another input of the C-element.
-This implementation uses the standard C-element so that if the set and reset inputs are mismatched, the output is held.
-In general, the synthesis can be changed so that there is a hazard-free implementation using only two-input gates.
+%The main difference is that the set logic and the reset logic must be designed so that they do not turn `ON' at the same time.\\
+
+The standard C-implementation is a gate-level implementation.
+Each wire from the specification is implemented as a C-element with non-looping cascades of gates as the C-element's two inputs.
+That is, each of the two inputs to the C-element is itself an output of a cascade of gates.
+The C-element operates like a typical C-element where if the two inputs are `1', then the output is `1'; and when the two inputs are `0', the output is `0'; and when the two inputs have different values, the output value is held.
+Additionally, Myers shows a method where the gate logic for the inputs to the C-element can always be re-implemented with two-input gates \cite{myers_book_2004}.
+Since the C-element itself is also a two-input circuit element, then the entire circuit is composed of two-input circuit elements.
+In such an implementation, each gate or C-element is assumed to have its own delay that is arbitrary in length.
+Thus, this gate-level implementation allows for more generic design.
 %explain sop?
+
 \subsection{Quasi Delay Insensitive Circuits}
@@
 There has also been some research for asynchronous circuits using some similar techniques.
-First, we present an overview of some common techniques for synchronous circuits, then introduce the current techniques for asynchronous circuits.
-Some of the techniques in asynchronous design borrows or are inspired by the much more developed fault-tolerant synchronous circuits field.
-However due to the difference in timing assumptions of the two types of circuits the techniques are not completely transferable.
+First, there is an overview of some common techniques for synchronous circuits, then there is a summary of the current techniques for asynchronous circuits.
+Some of the fault-tolerant techniques in asynchronous design borrow or are inspired by the much more developed synchronous circuits field.
+However, due to the difference in timing assumptions of the two types of circuits the techniques are not completely transferable.
 We describe why some of the solutions from synchronous circuits cannot be directly applied to asynchronous circuits.\\
@@
 %-TMR is still super important (possibly why TMR is not viable for async)
-In the early days there were certain systems for which eliminating faults and errors were very important.
+In the early days, there were certain systems for which eliminating faults and errors were very important.
 These include space and aviation control systems where due to the altitude there are more radiation and thus more faults.
@@
 We make the assumption that all signals are Boolean, that is, the signals are either `logic 0' or logic 1'.
-When the the gates and C-elements are excited, and their outputs transition, we assume that transition is instantaneous and that after the transition, the signals are still Boolean.
+When the gates and C-elements are excited, and their outputs transition, we assume that transition is instantaneous and that after the transition, the signals are still Boolean.
 Even in cases where the wires are affected by faults, we assume that the new value of the wires are Boolean, and if they are inputs into circuit elements, that the output of the circuit elements also remain Boolean.
@@
 For gates, such a function is easily defined.
-For example, an AND gate such as in figure \ref{fig:gates0} with two inputs $w_1$ and $w_2$ is modeled by the function
+For example, an AND gate such as in Figure \ref{fig:gates0} with two inputs $w_1$ and $w_2$ is modeled by the function
 \begin{figure}[h]
@@
 \captionof{figure}{AND gate}
+\label{fig:gates0}
 \end{figure}
@@
 For C-elements, these are memory holding devices so the function also requires the previous output.
-For example, the C-element in figure \ref{fig:element0} with two input wires $w_1$ and $w_2$ is modeled by the function\\
+For example, the C-element in Figure \ref{fig:element0} with two input wires $w_1$ and $w_2$ is modeled by the function\\
 \begin{figure}[h]
@@
 \captionof{figure}{C-element}
+\label{fig:element0}
 \end{figure}
@@
 Then, a stable element must satisfy $v= f(w_1,w_2)$.
-An example of an excited and stable AND gate is shown in figure \ref{fig:gates1}.
-An example of an excited and stable C-element is shown in figure \ref{fig:element1}.
+An example of an excited and stable AND gate is shown in Figure \ref{fig:gates1}.
+An example of an excited and stable C-element is shown in Figure \ref{fig:element1}.
 For C-elements, there are two situations in which the element is stable.
@@
 \captionof{figure}[AND excited and stable]{a) the AND element is excited  b) an excited element fires to become stable}
+\label{fig:gates1}
 \end{figure}
@@
 \captionof{figure}[C-element excited and stable]{a) the C-element is excited  b) two types of stable C-elements}
+\label{fig:element1}
 \end{figure}
@@
 To solve this problem we add C-elements to synchronize the two versions of the same signal.
-An example of this transformation applied to the simple inverter circuit is shown in figure \ref{fig:dupschemeex}.
+An example of this transformation applied to the simple inverter circuit is shown in Figure \ref{fig:dupschemeex}.
 Both the duplication and the additional C-elements configuration are shown.
@@
 However when faults do occur, the circuit may become unpredictable, which is a reason why we need to transform the circuit to protect against faults.
-An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.
+An example of what might happen when the circuit is not in a semi-modular state is shown in Figure \ref{fig:sm_counter2}.
 The logic circuit for wire $w$ is taken out of a semi-modular circuit.
@@
 
-We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in figure \ref{fig:dupscheme}: we make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
+We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in Figure \ref{fig:dupscheme}: we make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
 We also label the duplicated logic blocks as belonging to circuit A or circuit B in agreement to the wire naming.
-Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.
+Then we connect the output of the logic blocks to three layers of C-elements as shown in Figure \ref{fig:dupscheme}.
 We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ for circuit A and $c1^B$, $c2^B$, $c3^B$ for circuit B.
@@
 Another wrong approach for the fault-tolerant transformation is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault-tolerant circuit, then some signals may transition out of order.
-We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.
+We use the earlier example of Figure \ref{fig:counterexhalf} to show this as well.
 Following the same transitions outlined above, $b^A$ and $b^B$ can finish their transitions before $a^B$ and $c^A$ transitions.
@@
 
-%P3 states that the wire block must be in a state a-d) of figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
+%P3 states that the wire block must be in a state a-d) of Figure \ref{fig:l1helper}.  We consider what happens if a wire transitions from each state. 
 %logic gate excited = c1^A excited
@@
 \\
-%Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in figure \ref{fig:l21}.
+%Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in Figure \ref{fig:l21}.
 The only possible additional transitions would come from the logic block but we know that the already transitioned logic block cannot be excited again by Lemma 1.
@@
 For all traces $\sigma$ in the fault-tolerant circuit, $h^{A}(\sigma_n)$ or $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
-(h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
+(h might make the trace shorter, so the prefix will not be of length n)  The circuit also does not deadlock.
+%what was the point of the deadlock thing?
 \end{theorem}
@@
 Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: $c1^A$ and $c1^B$, if they transition, can only be excited after the previous $v^A$ and $v^B$ transitions complete.
-(Note if figure \ref{fig:l3helper} is true when $c1^A$ and $c1^B$ are excited infinitely often, then it is also true for when one or both of $c1^A$ and $c1^B$ stop after a finite number of transitions.
-This is because in the finite case, the wireblock stops in one of the first 3 states in figure \ref{fig:l3helper} and does not violate the transitions in the figure.
+(Note if Figure \ref{fig:l3helper} is true when $c1^A$ and $c1^B$ are excited infinitely often, then it is also true for when one or both of $c1^A$ and $c1^B$ stop after a finite number of transitions.
+This is because in the finite case, the wireblock stops in one of the first 3 states in Figure \ref{fig:l3helper} and does not violate the transitions in the figure.
 Thus, we only need to consider the case where both $c1^A$ and $c1^B$ are excited infinitely often)

### 2019-12-06 draft_final.tex
before ch 3, 4 DD edits

@@
 
-    \title{Fault-tolerant Asynchronous Circuits}
+    \title{Transient Fault Tolerant Asynchronous Circuits}
     \author{Zoey Zhou}
     \dept{Electrical Engineering}
-    \principaladviser{David Dill}
+    \principaladvisor{David Dill}
     \firstreader{Subhasish Mitra}
-    \secondreader{Clark Barrett\\(Computer Science)}
+    \secondreader{Clark Barrett}
 
@@
 \prefacesection{Abstract}
-
+Asynchronous digital circuits are circuits that don’t have clocks.
+They sometimes have advantages including speed, lower power consumption, and relative insensitivity to environmental conditions such as temperature.
+Transient faults, which are changes in the circuit that do not permanently damage the circuit, are a growing problem in digital circuits.
+Transient faults are mainly due to radiation effects such as Single Event Upsets (SEUs).
+These faults occur on the ground and are exacerbated in space.
+
+In this talk, I will present an overview of asynchronous circuits and in particular speed-independent control circuits, and our model for transient faults.
+I will then present a fault tolerant transformation of the circuit based on duplication.
+I will discuss how to define fault-tolerance formally.
+Then I will show using logic and formal methods why the transformed circuit is fault tolerant to single transient faults.
 \newpage
@@
 %% Acknowledgements.   The thematic purpose is the same (thanks).
-    \prefacesection{Acknowledgements}
-        I would like to thank Professor David Dill.
+%    \prefacesection{Acknowledgements}
+ %       I would like to thank Professor David Dill.
 
@@
 %% is restarted
+\tablespagefalse
     \afterpreface
@@
 
-However, because the signals can arrive at the input at any time, the design is more complicated to ensure that the entire circuit functions correctly.
+%However, because the signals can arrive at the input at any time, the design is more complicated to ensure that the entire circuit functions correctly.
 From a high level view the circuits are designed so that the signals progress irrespective of the delays.
@@
 The asynchronous delay model that we consider is the unbounded gate delay model.
-Circuits that can handle any delay under this model are called Speed Independent circuits.
+Circuits that can function correctly under arbitrary gate delays are called Speed Independent circuits.
 The unbounded gate delay model assumes that delays only appear on the gates and the delays can be arbitrarily long in the interval $(0,\infty)$.
@@
 %explain sop?
-
+\begin{comment}
 \subsection{Quasi Delay Insensitive Circuits}
@@
 There are no self-loops.
-
+\end{comment}
 \section{Fault Tolerant solutions}
@@
 %soft error protection <- error correcting codes for SRAM memory 
-Because faults cannot be eliminated in digital circuits, different methodologies have been used to make the circuits fault-tolerant.
-Much of the research done in this area are for synchronous circuits.
-There has also been some research for asynchronous circuits using some similar techniques.
-First, there is an overview of some common techniques for synchronous circuits, then there is a summary of the current techniques for asynchronous circuits.
-Some of the fault-tolerant techniques in asynchronous design borrow or are inspired by the much more developed synchronous circuits field.
-However, due to the difference in timing assumptions of the two types of circuits the techniques are not completely transferable.
-We describe why some of the solutions from synchronous circuits cannot be directly applied to asynchronous circuits.\\
+There has been significant previous work on fault-tolerant synchronous circuits.
+Various methods exist that allow a general circuit to be fault-tolerant to permanent and transient faults.
+However, results on asynchronous circuits are more limited.
+Usually, the method is fault-tolerant to only one of permanent or transient faults, and applies to a limited category of asynchronous circuits.
+Many fault-tolerant techniques in asynchronous circuits borrow from the developed synchronous circuits field.
+However, due to the differences of the two types of circuits, these techniques need to be modified to work in asynchronous circuits.
+The rest of this section gives an overview of some common fault-tolerance techniques for synchronous circuits, then there is a summary of the current techniques for asynchronous circuits.
+\\
 
@@
 %-TMR is still super important (possibly why TMR is not viable for async)
-In the early days, there were certain systems for which eliminating faults and errors were very important.
+
+%In the early days, there were certain systems for which eliminating faults and errors were very important.
 These include space and aviation control systems where due to the altitude there are more radiation and thus more faults.
@@
 
-Solutions for eliminating these transient fault-induced errors include physical, hardware, software or a mix of the previous.
+In synchronous circuits, solutions for eliminating transient faults include physical, hardware, software or a mix of the previous.
 Some commonly used techniques are transistor sizing, circuit hardening, hardware duplication, and time redundancy \cite{Mitra_08_softerrors}.
-Transistor sizing is a physics-based technique and does not reduce as much soft errors as the other techniques.
-Circuit hardening is on the physics level, where it uses intrinsic properties such as resistive or capacitive hardening, or combining the transistors differently to have less effects from transient faults.
-(?) Hardware duplication, is a common technique that tries to eliminate soft errors on the circuit level.
-This is achieved by having multiple duplicates of a circuit and often comparing the value from each duplicate to find and eliminate errors.
-For example, Triple Modular Redundancy (TMR) has been used since the beginning of the field and is still a good solution for eliminating single soft errors.
-The advantages are that it is able to eliminate nearly all soft errors but also due to the duplication, the area for each circuit and additional power increases substantially (correlates to the number of additional duplicates).
-Time redundancy techniques re-use the same circuitry to compute values multiple times to ensure there is no error.
-This technique is not completely hardware based and requires software to manage re-using the same circuity with the same inputs over time.
-The area of the circuit does not change but the speed of the circuit worsens substantially.
-\\
-
-There is also the additional distinction between error detection versus error correction.
+Transistor sizing is a physics-based technique and does not reduce transient faults as much as the other techniques.
+Circuit hardening is also on the physics level, it uses intrinsic properties such as resistive or capacitive hardening, or placing the transistors differently to have less effects from transient faults.
+Redundancy techniques work for both transient and permanent faults.
+The first type of redundancy is hardware duplication, which eliminates faults on the circuit level.
+This is achieved by duplicating a circuit multiple times and using a majority voter to eliminate the faults.
+For example, Triple Modular Redundancy (TMR) eliminates single faults.
+However, the disadvantage is that the power and area of the circuit increases substantially.
+Another type of redundancy is time redundancy.
+This technique re-use the same circuitry to compute values multiple times and compare the results.
+This technique requires software to computing with the same circuity multiple times.
+In this case, the area of the circuit does not change but the speed of the circuit worsens substantially.
+\\
+
+There is also the distinction between error detection versus error correction.
 In general, it is easier to detect an error than to correct it.
-For example, using hardware duplication, only 2 copies are required to detect an error but 3 copies (TMR) to correct the error.
-For different parts of the system there are also different strategies.
-For example, in memory components such as SRAM, soft error correction is usually done using error-correction codes.
-These codes are compared to the bits that are stored to ensure that there are no errors.
-They are designed to handle a predefined maximum number of errors.
-For example, Hamming codes where each codeword are at least a distance of 3 apart can handle one error.
-This method is not purely hardware based and a controller system and software are used to match the codes and detect and correct any errors.
-For a control circuit, there are also a variety of strategies.
-Again, one could make use of error correcting codes or parity bits to detect or correct errors in combinational logic \cite{McCluskey_99}.
+For example, using hardware duplication, only 2 duplicates are required to detect an error but 3 duplicates (TMR) are required to correct the error.
+There are also different strategies for different types of circuits.
+For example, in memory components such as SRAM, transient fault induced error is usually corrected using error-correction codes.
+Error-correcting codes can also be used for a control circuit to detect or correct errors in combinational logic \cite{McCluskey_99}.
 This uses a combination of hardware and software.
-A completely software approach is to run a program on some input, then run the program again on a transformed version of the input where the output can be mapped back to the original output \cite{Mitra_softwareerror}.
-If the output and the transformed output do not match then the fault is detected.
-Lastly, for hardware only methods, even now TMR is a commonly used method because of its robustness and ensures error correction.
+Another approach is software-based and inputs the original and a transformed version of the inputs to the circuit.
+The transformed version is designed such that if the circuit is fault-free, the outputs map back to the original outputs \cite{Mitra_softwareerror}.
+Finally, for hardware only approaches, TMR is a commonly used method because of its robustness and fault correction.
 \\
@@
 Triple Modular Redundancy is a technique where each combinational logic unit is copied three times and then fed into a latch that performs a majority voting operation.
-That is, if at least 2 out of the 3 signals agree on a value, the output becomes that value.
-Additionally, to counter possible faults on the single output wire, the majority vote unit can also be copied three times and its output wire fed appropriately as input to the three copies of the downstream combinational logic.
-This would resolve both transient and permanent single faults.
-However, the downside is that the circuit needs to be copied three times so the area is three times larger and the power consumption as well.
-In addition, there must be many adaptations for this to work in asynchronous circuits as the signals can arrive in different orders.
-We give an example of why TMR does not work in an asynchronous circuit as it does in a synchronous circuit below.
-We assume that in the original circuit that each logic block has some input wires and an output wire.
-In the TMR scheme, each logic block is triplicated and to remove single points of failure, we also triplicate the majority voter that the three copies of the output wire feeds into.
+If at least 2 out of the 3 signals agree on a value, the output becomes that value.
+Additionally, to counter possible faults on the output wire, the majority voting unit can also be copied three times and each output wire fed as input to one of the three copies of the downstream combinational logic.
+TMR eliminates both transient and permanent single faults.
+However, the downside is that the circuit needs to be copied three times, so the circuit area and power consumption is three times as much.
+Although this technique is powerful in synchronous circuits, it does not work in asynchronous circuits as is.
+We give an example of why TMR does not work in an asynchronous circuit below.
+We assume that in the original circuit, each logic block has some input wires and an output wire.
+In the TMR scheme, each logic block and majority voter is triplicated.
 There are also three distinct copies of each input signal that correspond to outputs from the three voters.
-This is the basic scheme that synchronous circuits with TMR uses.
 Because this circuit is asynchronous, we assume that each logic block is composed of gates that has some arbitrary delay that is independent of other gates.
-This is true under both delay assumptions of speed independent and delay insensitive circuits.
-We ignore whether a fault can be in the voter for now.
 \begin{center}
@@
 \captionof{figure}{TMR asynchronous circuit example with fault}
-Initially all output wire values are `0's.
-Then since the input signals are distinct copies of each other, it is possible for one set to finish transitions (new) before the other two sets and the first logic block transitions to a `1'.
+Initially, all output wire values are `0's.
+Then, since the input signals are distinct copies of each other, it is possible for one set to finish transitions (new) before the other two sets and the first logic block transitions to a `1'.
 Then a transient fault arrives on the output of the second logic block which transitions to a `1' as well.
 The majority voter would then transition to a `1'.
-However, the upset from transient faults usually happen within a short time period and the old inputs eventually force the output of the second logic block back to `0'.
-Then the majority voter would transition to a `0' so that causes a hazard on the output of the majority voter.
+However, the old inputs can force the output of the second logic block back to `0'.
+Then the majority voter would transition to a `0' which causes a hazard on the output of the majority voter.
 %depends on if the logic gate was combinational logic....
@@
 %NEEDS FIXING AND CHECKING
-It is also possible for the `1' from the majority voter to feed into other logic units which is effectively an early transition.
+%It is also possible for the `1' from the majority voter to feed into other logic units which is effectively an early transition.
 That early transition will then put the circuit into states that are not specified by the original state graph and thus the next states cannot be predicted.
-\\
+Almukhaizim and Sinanoglu (2007) solves this problem by requiring a hazard-free majority voter.
+Instead of a majority voter, this design requires that all three signals match to propagate the signal.
+However, with this new modification, TMR deadlocks when there are permanent faults.
+Thus, this design is only for transient faults in asynchronous circuits \\
 
 %also included detection schemes because there is so few works in the literature...
-David and Ginosar (1995) prove that a specific type of asynchronous circuit called self-timed combinational logic is self-checking under stuck-at-faults \cite{self_timed}.
-(Stuck-at-faults are permanent faults where a wire value is stuck at 0 or 1) That is if there is a single stuck-at-fault, the circuit will either stall or give an illegal output so that faults can be detected.
-Each input and output is encoded by 2 bits also known as dual rail encoding.
-10 represents 0, 01 represents 1, and 00 represents undefined or the system is not yet ready.
-11 is an illegal output that only occurs under certain faults.
-Each logic unit is composed of four subunits, three of which control the inputs and outputs and includes many C-elements.
-The fourth one implements the combinational logic.
-The combinational logic requires the implementation to be such that each output bit is monotonous given the input bits.
-A further restriction is that the combinational logic is composed of only AND and OR gates.
-\\
-
-Verdel and Makris proposes that simply porting the duplication strategy for error detection from synchronous circuits does not work for asynchronous circuits \cite{async_dup_ced}.
-This is because the duplication strategy relies on both the original and duplicate to output the same value.
-Some modifications that they propose to make the duplication error detection strategy work is to assume additional timing requirements.
-That both copies should output the same value within a certain time determined by a pre-set delay element.
-Everytime one of the signals transitions to a new value, and the duplicates are mismatched the timer starts and if they stay mismatched when the timer ends an error is detected.
-They look at stuck-at-faults and premature firing faults.
-There are also cases when the timer detection does not work and for those cases, they propose using additional hardware to look at the states of all the wires to see if an illegal state was reached.
-They present an example of a control circuit for data computations.
-The main restrictions of this method are the additional timing assumptions they make about two copies of a circuit, and that the extra hardware components are assumed to be fault-free.
-Also, it requires an additional comparison unit for each pair of signals which may be costly.
-Only one copy of the duplicates produces output signals that interfaces with the other units so that if there is an error on that signal it is not detected until some time after the error has propagated.
-\\
-
-Almukhaizim and Sinanoglu (2007) propose a Triple Modular Redundancy (TMR) based method of solving transient errors but requires a hazard-free majority voter.
-Transferring the TMR method that solves faults for the synchronous circuits to asynchronous requires the change that 2/3 copies agreeing is not good enough but 3/3 is needed to propagate a signal.
-This is due to the asynchronous property where signals can change at any given time and thus one signal changing plus a transient error may cause the output wire to transition prematurely.
-For permanent errors there is an additional problem of deadlock and this configuration does not solve it completely.
-\\
-\\
-In the paper by Manohar and Peng (2005), they add in new circuitry that solves faults for a specific asynchronous adder circuit \cite{PengManohar_asyncadder}.
-The faults that they consider are fabrication defects, permanent faults and unrecoverable failures.
-New nodes and edges are added to make it k fault-tolerant.
-They detect when there is a deadlock at which time it reconfigures the circuit by trial and error of all the possible combinations until the circuit is no longer deadlocked.
-\\
-
-Naqvi (2014) shows how to solve transient faults on muller pipelines \cite{Naqvi_mullerpipeline}.
-Muller pipelines make use of handshaking protocols.
-The assumptions they make are that only one fault occurs per handshake cycle.
-They used formal verification to show that it works for one pipeline component.
-\\
-\\
-Jang and Martin (2005)’s paper considers the problem of single SEUs in QDI circuits \cite{JangMartin_SEUQDI}.
-In the original functioning circuit, an SEU may cause a) a transition to a deadlocked state, an illegal state with no further possible transitions, b) abnormal, a transition to another state in the state graph and skip or adds certain transitions/signalling, c) tolerant where it transitions to an illegal state but the PRs are unaffected and eventually resumes to a valid state in the state graph.
-They solve this problem by duplicating the circuit and appending C-elements to the end of each of the original wires.
-In addition to duplicating the circuit they change the production rule set so that if the rule is about wire $X$ is true in the original circuit, in the new circuit the rule is $X^1$ and $X^2$ both have to be true.
-For example
+There are also permanent fault solutions in asynchronous circuits.  
+David and Ginosar (1995) show that faults can always be detected when there is a permanent stuck-at fault.  This is restricted to self-timed combinational logic composed of only AND and OR gates.  
+Manohar and Peng (2005) designed fault-tolerant asynchronous adders that can handle up to $k$ permanent faults \cite{PengManohar_asyncadder}.
+This is achieved by adding new circuitry and restarting different parts of the circuit when it deadlocks due to the faults.
+Verdel and Makris proposed a duplication method to detect permanent faults \cite{async_dup_ced}.
+They assumed that both duplicates output a new value within a certain amount of time of each other.
+For each pair of signals, they use a timer to detect when that timing is violated, and the circuit is in deadlock.
+However, this timer method does not catch all faults and they propose to add circuitry to detect when additional illegal states are reached.
+\\
+
+Naqvi (2014) gives a fault-tolerant solution to transient faults on muller pipelines \cite{Naqvi_mullerpipeline}.
+This is a duplication and design based technique that allows for one fault per handshake cycle.
+Formal verification is used to show that one pipeline component can be made fault-tolerant.
+\\
+
+Jang and Martin (2005)’s work is the closest existing work to ours.
+Their design makes Quasi-Delay-Insensitive (QDI) circuits fault-tolerant to single SEUs \cite{JangMartin_SEUQDI}.
+QDI uses a similar delay assumption as Speed-Independent circuits and can also model control circuits.
+However, QDI circuits are synthesized differently from the methods outlined for Speed-Independent circuits.
+Instead, the high-level specifications are computed into two Production Rules (PRs) for each gate.
+The PRs are like the set and reset logic for generalized C-elements.
+For each gate, there is a PR for when the output transitions to `1', and another PR for when the output transitions to `0'.
+For example, if a gate takes a set of wires as inputs and outputs a wire $x$, and a transition from $x=0$ to $x=1$ is denoted by $x\uparrow$, while a transition from $x=1$ to $x=0$ is denoted by $x\downarrow$, then the two PRs associated with the gate is :
+\begin{align*}
+B_u\mapsto x\uparrow \\
+B_d\mapsto x\downarrow 
+\end{align*}
+
+The Boolean expressions $B_u$ and $B_d$ are called guards, and take wires as inputs.
+Also like the generalized C-element, each gate is implemented at the transistor level and both guards evaluate at the same time.\\
+
+With this construction in mind, we look to their design.
+Their solution is duplication based and a layer of C-elements is added to the output of each of the original wires.
+In addition to duplicating the circuit, the PRs are modified so that if the PR requires wire $X$ to be true in the original circuit, then in the fault-tolerant circuit, the new PR requires both $X^1$ and $X^2$ to be true.
+For example:
 \begin{align*}
@@
 \end{align*}
-The last two production rules correspond to the additional C-elements added. 
-They prove that with this new circuit, single SEU errors do not cause transitions to deadlocked states, nor abnormal transitions and thus are corrected.
+The last two production rules correspond to the additional C-elements. 
+With this circuit transformation, single SEU errors do not cause transitions to deadlocked states, nor abnormal transitions and thus are corrected.
 Given the transistor-based QDI assumptions, any changes to the production rules are implemented at the transistor level and assumed to not add any delays.
-In addition, QDI logic is implemented in sum-of-products form and the production rules are excited only in the appropriate non-illegal states.
-Faults are assumed to occur on the input/output wires as well as the new wires that feed into the C-elements.
-Another assumption is every loop in the control circuit is at least length 3 to prevent deadlock.
-%not sure about this, may only be relevant for when they don't double the inputs
-\\
-
-The circuit transformation that Jang and Martin propose work for their assumptions and specific implementation of QDI circuits at the transistor level.
-However, it is not reasonable to assume that any PR can be implementation with transistors with no delay.
-Also, for a simple 2-element inverter circuit their transformation also can end up in a deadlocked state after an SEU.
-After the duplication and addition of C-element.
+Faults are assumed to occur on the input/output wires.
+It is also assumed that every loop in the control circuit is at least length 3 to prevent deadlock.
+\\
+
+Jang and Martin’s circuit transformation works under certain assumptions.
+However, the solution is not suitable for cases where those assumptions are not satisfied, such as if it is impossible to implement the gate at the transistor level with no delay, or if there are loops of length 2 in the circuit.
+For example, a simple two element inverter circuit can end up in a deadlocked state after an SEU with this transformation.
+Then if a 0->1 SEU occurs at $c_1^B$, it is possible for this circuit to deadlock.
 \begin{center}
@@
 \end{center}
-Then if a 0->1 SEU occurs at $c_1^B$, it is possible for this circuit to deadlock.
+
 \begin{center}
@@
 
-The approach that we use to make circuits fault-tolerant will be described in the next chaper.
-Some of the previous works makes additional assumptions such as the checking circuit is fault free or that only one fault can occur on an arbitrarily large transistor gate.
-We allow for standard two-input gates and assume that all gates in our model are subject to faults.
-Our fault-tolerant transformation procedure is for a class of circuits, semi-modular control circuits, which includes many circuits.
-
-\chapter{Asynchronous Circuit Concepts \& Definitions}
+We learn from previous work that it is difficult to design fault-tolerant asynchronous circuits.
+Many of the previous works make additional assumptions about where the fault can occur or the timing of delays or restrict the type of circuits.
+We add to this body of work with a new transient fault-tolerant design for a general class of asynchronous circuits, semi-modular control circuits.
+We assume the circuit is composed of two-input gates and that each gate has variable delay and is also subject to faults.
+
+\chapter{Asynchronous Circuit Concepts and Definitions}
 \section{Assumptions:  Boolean signals}
-We make the assumption that all signals are Boolean, that is, the signals are either `logic 0' or logic 1'.
-When the gates and C-elements are excited, and their outputs transition, we assume that transition is instantaneous and that after the transition, the signals are still Boolean.
+This work assumes that all signals are Boolean, that is, the signals are either `logic 0' or logic 1'.
+When the gates and C-elements are excited and their outputs transition, we assume that the transition is instantaneous and that, after the transition, the signals are still Boolean.
 Even in cases where the wires are affected by faults, we assume that the new value of the wires are Boolean, and if they are inputs into circuit elements, that the output of the circuit elements also remain Boolean.
@@
 Gates and elements (C-elements) are components that we allow in our circuit.
-In general, we call them elements.
-Each element has 2 input wires and 1 output wire.
+In general, we call them {\em elements}.
+Each element has two input wires and one output wire.
 The elements can be in two states, excited or stable.
@@
 \[
-f_{AND}(w_1,w_2)= w_1\wedge w_2
+f_{AND}(w_1,w_2,v)= w_1\wedge w_2
 \]
@@
 \[
-f_{C-E}(w_1,w_2) =\left\{
+f_{C-E}(w_1,w_2, v) =\left\{
   \begin{array}{@{}ll@{}}
@@
 \]
-
+When $f_{C-E}(w_1,w_2, v) =v$, we say the C-element is in the ``hold state''.  
 Each element is in one of two states, excited or stable.  
 \begin{definition}
-An element with inputs $w_1$, $w_2$, output $v$ and function $f$ is {\em excited} if $v\neq f(w_1,w_2)$.  
+An element with inputs $w_1$, $w_2$, output $v$ and function $f$ is {\em excited} if $v\neq f(w_1,w_2, v)$.  
 \end{definition}
-This definition can be extended to include elements with any number of inputs by replacing $w_1$ and $w_2$ with the inputs of a specific element.
-A natural extension to an excited element is to consider an element that is not excited.
+
 \begin{definition} 
-An element is stable if the element is not excited.
+An element is stable if the element is unexcited.
 \end{definition}
-Then, a stable element must satisfy $v= f(w_1,w_2)$.
+Then, a stable element must satisfy $v= f(w_1,w_2,v)$.
 An example of an excited and stable AND gate is shown in Figure \ref{fig:gates1}.
@@
 For C-elements, there are two situations in which the element is stable.
-One is where the output is being actively driven to its function value, i.e.
-when both inputs are 0 or both inputs are 1.
+One is where the output is being actively driven to its function value, {\em i.e.} when both inputs are 0 or both inputs are 1.
 The second is where the inputs are mismatched and the C-element is holding the previous output.
@@
 A stable element can have input wire changes, and the input changes may cause the element to become excited.
-A small point to note is that not all input changes cause the element to become excited, .
+\\
+
 When the element is excited, there are two possibilities for the element to become stable again.
@@
 %\end{definition}
-I%n other words, every circuit element must be stable infinitely often in a fair trace.
+%n other words, every circuit element must be stable infinitely often in a fair trace.
 This fits with the physical properties of circuits because the elements are not arbitrarily slow and if excited, they will eventually change.
@@
 In the rest of this chapter we define a way to compare two circuits and to show their equivalence.
-Then we propose our transformation method and show that under normal operation (no faults), the fault-tolerant circuit is equivalent to the original.
-Finally we show that if a single transient fault occurs, one side of the fault-tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
+Then we propose our transformation method and show that under normal operation without faults, the fault-tolerant circuit is equivalent to the original.
+Finally we show that if a single transient fault occurs, one side of the fault-tolerant circuit is equivalent to the original.\\
 \begin{figure}
@@
 \begin{definition}A {\em deadlocked state} is a state where there are no excitations in the wires in the circuit and is not a stopping state.\end{definition} %but stopping state= no excitations, so either does not introduce new stopping states after the transformation or what....
-A deadlocked state does not appear in a well designed circuit, but may appear after a circuit transformation (i.e., the new circuit stops at states where the original circuit do not), or when there are faults.
+A deadlocked state does not appear in a well designed circuit, but may appear after a circuit transformation ({\em i.e.}, the new circuit stops at states where the original circuit do not), or when there are faults.
 Thus we want to design a circuit transformation where there are no deadlocked states.\\ %end new
@@
 
-The original circuit is semi-modular by design.
-But the design only covers traces when the circuit starts in a specified initial state.
-That is, hazards may occur if the circuit goes into an unreachable state of the traces and the circuit is no longer semi-modular and furthermore becomes unpredictable.
+The original circuit is semi-modular by design, but semi-modularity is conditional on the initial state.
+That is, hazards may occur if the circuit starts in a state that is not normally reachable.
+Then the circuit is no longer semi-modular and furthermore becomes unpredictable.
 This does not happen in the fault-free case and the circuit starts in a valid initial state.
@@
 An example of what might happen when the circuit is not in a semi-modular state is shown in Figure \ref{fig:sm_counter2}.
-The logic circuit for wire $w$ is taken out of a semi-modular circuit.
-However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not semi-modularity consistent.
+The logic circuit for wire $w$ could appear in a semi-modular circuit.
+However, the state where the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1 is not consistent with semi-modular operation.
 The output wire $w$ is excited to 1 while the inputs from $x,y,z$ will cause $w$ to transition to 0.
-Depending on the timing of the gates, $w$ may stay at 0 or experience a glitch to 1 then back to 0.
-The extra layers of gates in the logic block can be thought of as extra delays that can store and propagate the wrong values.
-More detailed discussion on how to initialize and keep the circuit semi-modular is explored in the subsequent section.\\
-
-Given two circuits, how can we determine when their basic functionality is the same, especially if they are implemented with different gates and circuit elements?
+Depending on the timing of the gates, $w$ may stay at 0 or experience a glitch to 1 then back to 0.\\
+
+Given two circuits, how can we determine when their basic functionality is the same, especially if they are implemented with different circuit elements?
 We define a notion of equivalence between two circuits through their sets of traces.
@@
 
-We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in Figure \ref{fig:dupscheme}: we make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
-We also label the duplicated logic blocks as belonging to circuit A or circuit B in agreement to the wire naming.
-Then we connect the output of the logic blocks to three layers of C-elements as shown in Figure \ref{fig:dupscheme}.
+We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in Figure \ref{fig:dupscheme}: we make a duplicate copy of the elements of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.
+We also label the duplicated elements as belonging to circuit A or circuit B in agreement to the wire naming.
+Then we connect the output of the elements to three layers of C-elements as shown in Figure \ref{fig:dupscheme}.
 We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ for circuit A and $c1^B$, $c2^B$, $c3^B$ for circuit B.
-In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and inputs to two C-elements outputting $c2^A$ and $c2^B$.
-These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.
-These are then the inputs to the third layer of C-elements outputting $w^A$ and $w^B$.
-We can label one of the final C-element outputs as $w^A$ and the other output as $w^B$.
-These then connect to other logic blocks in circuit A and circuit B respectively.
-\\
+In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the elements and inputs to two C-elements, which output $c2^A$ and $c2^B$.
+These are then the inputs to the second layer of C-elements, which output $c3^A$ and $c3^B$.
+These are then the inputs to the third layer of C-elements, which output $w^A$ and $w^B$.
+We label one of the final C-element outputs $w^A$ and the other output $w^B$.
+These then connect to other elements in circuit A and circuit B respectively.
+\\
+
 Note that when labelling the C-elements and its outputs, which side is A and B can be somewhat arbitrary because the output pairs are symmetric.
-The symmetry is broken when connecting the final output wire $w^A$ to all the circuit A gate inputs and wire $w^B$ to all the circuit B gate inputs.
-All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
+The symmetry is broken when connecting the final output wire $w^A$ to all the circuit A element inputs and wire $w^B$ to all the circuit B element inputs.
+All circuit elements with the A label are part of the A-half circuit and all circuit elements with the B label are part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie.
 all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
@@
 To do this, we define a correspondence between states of the original circuit and states of the fault-tolerant circuit.
-As a result of the circuit transformation, a state of the fault-tolerant circuit has bits for 8 times as many wires as a state in the original circuit.
+As a result of the circuit transformation, a state of the fault-tolerant circuit has bits for eight times as many wires as a state in the original circuit.
 Half of those bits are obviously from the A half and half are from the B half of the circuit.
 The trace of a fault-tolerant circuit is defined on this combined set of wires.
-We first  define the half-circuit mapping $h^B$ for the A half, the half-circuit mapping $h^B$ is similarly defined for the B half.
-The half-circuit mapping $h^A: s^{\textit{full}} \to s^A$ where $s^{\textit{full}}$ is the combined state of a fault-tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
-The added wires such as $c1^A$, $c2^A$, $c3^A$ from the duplication procedure is hidden by $h^A$.
+We first define the half-circuit mapping $h^A$ for the A half.
+The mapping $h^B$ is defined for the B half.
+The half-circuit mapping is $h^A: s^{\textit{full}} \to s^A$ where $s^{\textit{full}}$ is the combined state of a fault-tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.
+The added wires such as $c1^A$, $c2^A$, $c3^A$ from the duplication procedure are hidden by $h^A$.
 We can extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$.
@@
 The resulting trace may have successive repeated states.
-So next we delete all but one of the neighboring repeats, to obtain a valid trace on the shortened list of wires.
-Theorem 1 in the upcoming section shows that $h^A(\sigma)$ will be a trace from the original circuit.
-Using this mapping we will show that the original circuit is equivalent to half of the fault-tolerant circuit in both the absence and presence of a single transient fault.
+So, next, we delete all but one of the neighboring repeats, to obtain a valid trace on the shortened list of wires.
+Theorem 1 in the upcoming section shows that $h^A(\sigma)$ will be a trace of the original circuit.
+Using this mapping we will show that the original circuit is equivalent to half of the fault-tolerant circuit in the absence of faults.
+In section 4.4, we will use the same mapping to show equivalence in the presence of a single transient fault.
+For the remainder of the dissertation, we assume without loss of generality that the A half of the fault-tolerant circuit operates without faults, {\em i.e.}, that all faults are in the B half.
 %do I need to define all the new transitions in duplicated circuit?  maybe
@@
 %[Why is this the best we can do?]
-We compare each half circuit because it is not easy to synchronize and compare the signals between both halves, especially if we reuse the logic blocks from the original circuit.
+\begin{comment}
+We compare each half circuit because it is not easy to synchronize and compare the signals between both halves, especially if we reuse the elements from the original circuit.
 A simple idea we tried was to insert another C-element before the input is fed into the logic, to synchronize the wires on both halves.
 The problem with that is in the original circuit, a wire value change propagates to all inputs at the same time.
-Adding another layer of C-elements creates delays at the input to logic blocks and the isochronic fork assumption is violated.
+Adding another layer of C-elements creates delays at the input to elements and the isochronic fork assumption is violated.
 Thus the resulting circuit will not function according to the desired specifications.
@@
 Thus the two halves need not have the same trace.
-One criticism may be that the current fault-tolerant transformation synchronizes at the outputs of the logic blocks.
-If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
-We have already shown earlier that synchronizing the input signals while keeping the original logic block can also result in error.
+One criticism may be that the current fault-tolerant transformation synchronizes at the outputs of the elements.
+If we want to reuse the same elements but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.
+We have already shown earlier that synchronizing the input signals while keeping the original element can also result in error.
 This points to looking at properties of each half circuit as the right thing to do.\\
@@
 Out of the various comparisons methods and circuit transformations that we tried, it is the most reasonable and results in some nice properties.
-We will next demonstrate that the half circuits are equivalent to the original circuit in the absence of faults.
-Then we show that a similar property is true even when a single fault may occur.
+\end{comment}
+We will next demonstrate that the half circuits are equivalent to the original circuit in the absence of faults.  Then we show that a similar property is true even when a single fault may occur.
 
 \section{Normal operation analysis}
-Now we will discuss the proper wire initializations before going into the Lemmas.
+Now we will discuss the proper wire initializations before going into the lemmas.
 Defining a set of traces of a circuit includes defining the initial state.
@@
 
-We show how to define the initial state for the fault-tolerant circuit if given the initial state for the original circuit.
-The values for the internal wires must also be set.
-These internal wires are initialized to a semi-modularity consistent value.
-Given this, we pick the following convenient initializations for the fault-tolerant circuit.
+We show how to define the initial state for the fault-tolerant circuit, given the initial state for the original circuit.
+The values for the internal wires must also be defined.
+These internal wires are initialized to a value consistent with the initial state of the original circuit.
 The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
@@
 The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s.
-The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.
+The intermediate wires are all other wires, which consists of all the wires within the elements for each output wire.
 Given these we will show how to define a corresponding initial state in the duplicated circuit.
 %should I delete intermediate?
-\begin{definition} A {\em valid initial state} $s'$ for the A-half of the fault-tolerant circuit is constructed from the initial state $s$ of the original circuit.  
-For the $w$ logic block and output wire $w$ in the original circuit, the wire values are copied to the corresponding logic block and output wire $w^A$ in the A-half.
+\begin{definition} A {\em valid initial state} $s'$ for the fault-tolerant circuit is constructed from the initial state $s$ of the original circuit.  
+For the element with output $w$ in the original circuit, the wire values are assigned to the corresponding element and output wires $w^A$ and $w^B$ in the fault-tolerant circuit.
 The additional wires from the C-element chain are also assigned the same value as $w$.
-That is, $s(w)=s'(w^A)=s'(c1^A)=s'(c2^A)=s'(c3^A)$.
+That is, $s(w)=s'(w^A)=s'(w^B)=s'(c1^A)=s'(c1^B)=s'(c2^A)=s'(c2^B)=s'(c3^A)=s'(c3^B)$.
 This is repeated for all output wires in the original circuit.
@@
 %\textbf{
-The same construction applies for the B-half circuit as well.  Given this definition, both the A-half and B-half initial states are constructed from the same initial state of the original circuit.  
 There is a larger set of states that could serve as initial states of the fault-tolerant circuit, but this definition is sufficient for our purposes.\\
@@
 The order and the wire transitions also matter.
-The semi-modularity property must be preserved: if the logic block output is excited then it must remain excited until a transition on its output occurs.
-Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
+The semi-modularity property must be preserved: if the element output is excited then it must remain excited until a transition on its output occurs.
+Since certain inputs which are valid states and arise from valid transitions may cause the element to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
 
 In normal operation, the fault-tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.  
-This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault-tolerant circuit.
-The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.
+This includes the internal wires which exist in the elements in the original circuit and through duplication also exist in the fault-tolerant circuit.
+The actual values of these wires do not matter if the inputs to the elements follow the semi-modularity property, and if the internal wires are initialized properly.
 This arises from the original synthesis method to synthesize the circuit from an underlying state graph.  
-Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.
-The semi-modularity property must be preserved: if the logic block output is excited then it must remain excited until a transition on its output occurs.
-Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
+Additionally, it does not suffice for the inputs to the elements to be from a valid trace of the state graph; the timing matters as well.
+The semi-modularity property must be preserved: if the element output is excited then it must remain excited until a transition on its output occurs.
+Since certain inputs which are valid states and arise from valid transitions may cause the element to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.
 %maybe needs an example
 Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.
-Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions.
+Then the internal wires of the element are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions.
 \\%newly added
@@
 That is, the set of traces of the fault-tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.
-And likewise after applying a mapping of $h^B$ to the fault-tolerant circuit.
-We show this through several Lemmas.
-Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the set of traces of the
+We will show consistency by using $h^A$ in all that follow.
+The same results hold for $h^B$, obviously.
+We show this through several lemmas.
+Lemma 1 shows that every transition of the fault-free half of the fault-tolerant circuit is consistent with a transition that could occur in the original circuit.
 %since it's a transition, then all previous transitions must also be in the set of traces, in fact they must all be a sequence of at least one trace (true because if excited, must be excited in all states of same name)
- original circuit.  This is a strong result; it is true for  {\em arbitrary behavior} of
+This is a strong result; it is true for  {\em arbitrary behavior} of
 wires in the other half circuit, so long as those wire values are well-formed Boolean values and also does not cause the fault-free half to deviate from well-formed Boolean values.  
@@
 \\
-
-Note that Lemma 1 allows for the possiblity of the fault-tolerant circuit to stop at states that are not stopping states in the original circuit.
-This is an important point as we do not want our transformed circuit to stop prematurely.
-We call such premature stopping states, if they exist, as deadlocked states:
-\begin{definition}A {\em deadlocked state} is a stopping state of the fault-tolerant circuit but not a stopping state of the original circuit.\end{definition}
-We use {\em deadlock} to mean the existence of such deadlocked states.  
-Then, Lemma 2 shows deadlock does not occur during normal operation.
-Combining these two Lemmas, we can show that all traces in the fault-tolerant circuit can be mapped to a trace in the original circuit.\\
 % and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
@@
 \begin{lemma}[0]
-Given two identical logic blocks $f$ and $g$, if the inputs into $f$ and $g$ have the same values then:\\
+Given two identical elements $f$ and $g$, if the inputs to $f$ and $g$ have the same values then:\\
 i)  if the outputs are the same value and $f$ is excited then $g$ is also excited.\\
@@
 %MAPPING PROPERTY?
-In the following lemmas and theorems we compare a state $s$ in the fault-tolerant circuit with its mapped state $h^A(s)$ in the original circuit.
-Due to the mapping and architecture of the circuits, for any wire block $w$, the inputs to the logic block of $w^A$ in the fault-tolerant circuit has the same value as the inputs to the logic block of $w$ in the original circuit.
+In the following lemmas and theorems, we compare a state $s$ in the fault-tolerant circuit with its mapped state $h^A(s)$ in the original circuit.
+Due to the mapping and architecture of the circuits, for any wire block $w$, the inputs to the element of $w^A$ in the fault-tolerant circuit have the same values as the inputs to the element of $w$ in the original circuit.
 This fact is used extensively in combination with Lemma 0.
@@
 \\
-%compare with original circuit: logic block with same inputs.....if input cause block to be excited... if output is same too then the state of logic block is identical.
-
+%compare with original circuit: element with same inputs.....if input cause block to be excited... if output is same too then the state of element is identical.
+
+Note that Lemma 1 allows for the possibility that the fault-tolerant circuit could stop at states that are not stopping states in the original circuit.
+This is an important point as we do not want our transformed circuit to stop prematurely.
+We call such premature stopping states, if they exist, as deadlocked states:
+\begin{definition}A {\em deadlocked state} is a stopping state of the fault-tolerant circuit but not a stopping state of the original circuit.\end{definition}
+We use {\em deadlock} to mean the existence of such deadlocked states.  
+Then, Lemma 2 shows deadlock does not occur during normal operation.
+Combining these two lemmas, we can show that all traces in the fault-tolerant circuit can be mapped to a trace in the original circuit.\\
+
+We allow arbitrarily faulty traces in Lemma 1, which is defined as follows:
+\begin{definition}An {\em arbitrarily faulty trace} of the fault-tolerant circuit is a sequence of states $s_1, s_2, ...$ where the B signals $(w^B, c1^B, c2^B, c3^B)$ in each state have arbitrary Boolean values, the A signals in $s_1$ are those of a valid initial state, and the A signals of $s_{i+1}$ are (related to all signals in $s_i$ by the element transition relation.)
+\end{definition}
+
+%Arbitrary faulty trace
 This leads to the definition and proof of Lemma 1 as follows:
@@
 \begin{lemma}[1]
-Consider a fault-tolerant circuit that is fault free and its A half begins in a valid initial state.
-For every trace $\sigma$ of this circuit, the following two properties hold: %still kind of weird wording
+Consider a fault-tolerant circuit that starts in a valid initial state.  For every arbitrarily faulty trace $\sigma$ of this circuit, the following two properties hold: %still kind of weird wording
 \begin{itemize}
 \item P1: The half-circuit mapping of a prefix of $\sigma$, written as $h^{A}(\sigma_n)$, is also a prefix of a trace of the original circuit, regardless of the wire values in the B half.
-%\item P2: The logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
+%\item P2: The elements in the A half are semi-modularity consistent for all states in $\sigma$
 \item P2: For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true in the fault-tolerant circuit: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.
-When one of these conditions holds, we say “the wireblock $w^A$ is excited.”  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault-tolerant circuit.
-(No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)
+(When one of these conditions holds, we say “the wireblock $w^A$ is excited.”)  A wire $w$ in state $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault-tolerant circuit.
+(Note that at most one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)
 \end{itemize}
@@
 \begin{proof}
-Let $\sigma$ be an arbitrary trace of the fault-tolerant circuit.  We will show by induction on $n$ that Lemma 1 is true for the length $n$ prefix of the trace $\sigma_n$.  
+Let $\sigma$ be an arbitrarily faulty trace of the fault-tolerant circuit.  We will show by induction on $n$ that Lemma 1 is true for the length $n$ prefix of the trace $\sigma_n$.  
 %We will show by induction on $n$ that for any prefix of the trace $\sigma_n$, where $n$ is an integer from 1 to the length of the trace, $h^A(\sigma_n)$ is a prefix of a trace of the original circuit.
 % true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
-We first show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state by construction.
+We first show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, which is a valid initial state by construction.
 \begin{itemize}
@@
  Thus $h^A(s_1)$ is a prefix of length 1 of a trace in the original circuit and satisfies P1.
-%\item We assigned the initial wire values so that the logic blocks are in a semi-modularity consistent state so P2 holds.
+%\item We assigned the initial wire values so that the elements are in a semi-modularity consistent state so P2 holds.
 \item 
@@
 Therefore only wire $c1^A$ may be excited.
-Since the mapping gives identical inputs then by Lemma 0 i) ii) if wire $w$ is excited in the original circuit, $c1^A$ is also excited in the fault-tolerant circuit.
+Since the mapping gives identical inputs then by Lemma 0, if wire $w$ is excited in the original circuit, $c1^A$ is also excited in the fault-tolerant circuit.
 And if wire $w$ is unexcited in the original circuit, then $c1^A$ is unexcited in the fault-tolerant circuit.
@@
 Then under the half circuit mapping, wire $w$ transitions from state $h^A(s_k)$ to state $h^A(s_{k+1})$.
-By P2, wire $w$ is also excited in state $h^A(s_k)$ and this is a valid transition (i.e., $T(h^A(s_k), h^A(s_{k+1}))$).
+By P2, wire $w$ is also excited in state $h^A(s_k)$ and this is a valid transition ({\em i.e.}, $T(h^A(s_k), h^A(s_{k+1}))$).
 Therefore $h^{A}(\sigma_{k+1})$ is a prefix of a trace of the original circuit.
@@
 Another consequence of $h^A(s_{k+1})=h^A(s_k)$ is that P1 holds.
-And lastly no output wire transitions implies the logic blocks stay in a semi-modularity consistent state so that P2 holds.
+And lastly no output wire transitions implies the elements stay in a semi-modularity consistent state so that P2 holds.
 
@@
 Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.
-The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.
+The output wires not changing also allow the elements to stay in a semi-modularity consistent state.
 The induction hypotheses are true for any transition from this case.
@@
 %Next we show P3 holds by examining $w$/$w^A$'s effects in the other wires/wire blocks.
-A change in wire $w$ fans out to other logic blocks which may change their excitations in response.
+A change in wire $w$ fans out to other elements which may change their excitations in response.
 Thus we partition the output wires in the original circuit into four categories: wires that are excited in the current state and excited in the next state, wires that are excited in the current state and unexcited in the next state, wires that are unexcited in the current state and are newly excited in the next state, and wires that are unexcited in the current state and unexcited in the next state.
@@
 For P2 to be true in state $s_{k+1}$, we must show that wireblock $v$ in the fault-tolerant circuit remains in cases 1-4.
-A transition on $w^A$ can only affect the logic block portion of the wireblock.
+A transition on $w^A$ can only affect the element portion of the wireblock.
 \\
@@
 \\
-In Cases 2-4, the logic block of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.
+In Cases 2-4, the element of the fault-tolerant circuit is unexcited while $v$ is still excited in the original circuit.
 By semi-modularity, wire $v$ remains excited in state $h^A(s_{k+1})$.
@@
 So the induction hypothesis holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
-By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
+By induction on the length of the trace, the first property shows that $h^{A}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
 %do I need to show the opposite?
@@
 \end{proof}
-By symmetry this is also true for the B half if we exchange A and B in the statement of Lemma 1.  
 Note as described previously, the proof for Lemma 1 does not place any restrictions on the other half of the circuit other than that the digital abstraction is not violated for C-elements with inputs from both halves of the circuit (e.g.
@@
 Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.
-It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1
-
-This leads to the next property that we will show: if both halves of the circuit start at the same valid initial state, the wire blocks of the circuit transition in a completely predictable pattern and thus deadlock does not occur.
-To avoid overly clunky sentences, we will assume that fault-tolerant circuits start from the same valid intial state in both halves.
-One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.
+It isn't all we need though: it guarantees that {\em if there is a next state} it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.\\  %maybe move this to in front of L1
+
+In Lemma 2.1, we now assume there are no faults in the fault-tolerant circuit.
 
@@
     \includegraphics{flowl2c3}
-  \caption[Lemma 2 transitions]{The wires in each row are in order of logic block, C1, C2, C3, W.
+  \caption[Lemma 2 transitions]{The wires in each row are in order of element, C1, C2, C3, W.
 Each row represents half of the duplicated circuit, ie.
 top row are A half wires and bottom row are B half wires.
-'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.
+'Un' denotes that the element is unexcited and 'Exc' denotes the element is excited.
 Blue arrows indicate a case change caused by transitions elsewhere in the circuit.
@@
 For every wire $w$ in the original circuit, the valid initial state initializes the wires in the fault-tolerant circuit to state a of Figure \ref{fig:l1helper} if wire $w$ is excited, or initializes to state e of Figure \ref{fig:l1helper} if wire $w$ is unexcited.
-Because the initialization is the same for both halves, then if $w$ is excited then the logic blocks in the fault-tolerant circuit are in case 3b of Figure \ref{fig:l21} and if $w$ is unexcited then the logic blocks are in case 1 of Figure \ref{fig:l21}.
+Because the initialization is the same for both halves, then if $w$ is excited then the elements in the fault-tolerant circuit are in case 3b of Figure \ref{fig:l21} and if $w$ is unexcited then the elements are in case 1 of Figure \ref{fig:l21}.
 Thus the lemma property holds for the base case.
@@
 It is easy to see that the only possible wire transitions in state $s_k$ are the transitions (black arrows) in the state diagram.
-%In addition, if $w$ is the transitioning wire block then because $w$ does not feedback to itself and the input wires do not transition, the logic blocks do not change excitations (other than when $c1$ transitions).
+%In addition, if $w$ is the transitioning wire block then because $w$ does not feedback to itself and the input wires do not transition, the elements do not change excitations (other than when $c1$ transitions).
 Thus the black arrows show the only possible transitions in the state diagram from state $s_k$.
@@
 
-%It is clear that transitions and logic block changes in the state diagram can occur.
+%It is clear that transitions and element changes in the state diagram can occur.
 Furthermore, we can easily verify that the wires in the C-element chains ($c1$, $c2$, $c3$, $w$) behave as the arrows indicate with no additional possibilities.
-Thus we need to show that no additional changes in the logic blocks can occur.
-%Because the arrows do not always indicate wire transitions (some are changes in excitation of the logic blocks which are in response to transitions of other output wires), we need only to verify for the transitions that do occur (black arrows), that they do not cause the other logic blocks (and itself) to behave inappropriately.
+Thus we need to show that no additional changes in the elements can occur.
+%Because the arrows do not always indicate wire transitions (some are changes in excitation of the elements which are in response to transitions of other output wires), we need only to verify for the transitions that do occur (black arrows), that they do not cause the other elements (and itself) to behave inappropriately.
 \begin{itemize}
 %\item
-%Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a logic block is excited it changes to case 2a or 2b. %this transition needs not occur, 
+%Case 1:  Nothing within the wire block can transition.  It is waiting for its input wires to change.  Once a element is excited it changes to case 2a or 2b. %this transition needs not occur, 
 \item
 Cases $2a\rightarrow 3a$, $2b\rightarrow 3c$, $3b\rightarrow 4a$, $3b\rightarrow 4b$, $4a\rightarrow 5$, $4b\rightarrow 5$, $5\rightarrow 6a$, $5\rightarrow 6b$, $6a\rightarrow 7$, $6b\rightarrow 7$, $7\rightarrow 8a$, $7\rightarrow 8b$, $8a\rightarrow 9$, $8b\rightarrow 9$: \\
-Let the transition be on wire block $w$.  The transition is on an intermediate wire so the logic blocks of $w$ do not change excitations other than when $c1$ transitions.  
-For the same reason, the transition does not affect the excitations in logic blocks of wire blocks other than $w$, thus those wire blocks stay in the same state in $s_{k+1}$.  
+Let the transition be on wire block $w$.  The transition is on an intermediate wire so the elements of $w$ do not change excitations other than when $c1$ transitions.  
+For the same reason, the transition does not affect the excitations in elements of wire blocks other than $w$, thus those wire blocks stay in the same state in $s_{k+1}$.  
 %In case 2a, when $c1^A$ transitions, 
-%It is also possible that the unexcited logic block becomes excited and go to case 3b at the next state.
-However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
+%It is also possible that the unexcited element becomes excited and go to case 3b at the next state.
+However the excited element cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.
 Case 2b is similar.
 %\item
-%Case 3a/3b/3c:  In case 3a, it is possible for the logic block in B-half to become excited, and change to 4a.
-The logic block in A-half cannot be excited again while $c1^A=1$ because that violates Lemma 1.
+%Case 3a/3b/3c:  In case 3a, it is possible for the element in B-half to become excited, and change to 4a.
+The element in A-half cannot be excited again while $c1^A=1$ because that violates Lemma 1.
 Case 3c is similar to 3a.
 From case 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.
-The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.
+The excited elements cannot become unexcited due to semi-modularity and Lemma 1.
 %\item
 %Case 4a/4b:
-%In case 4a, the logic block in B-half is excited and can transition to case 5.
-The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.
-The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as the above cases (Lemma 1).
+%In case 4a, the element in B-half is excited and can transition to case 5.
+The excited element cannot become unexcited due to semi-modularity and Lemma 1.
+The already transitioned element (unexcited) cannot be excited again due to same reasoning as the above cases (Lemma 1).
 Case 4b is similar.
@@
 %Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires and transitions according to the state graph in Figure \ref{fig:l21}.
-The only possible additional transitions would come from the logic block but we know that the already transitioned logic block cannot be excited again by Lemma 1.
+The only possible additional transitions would come from the element but we know that the already transitioned element cannot be excited again by Lemma 1.
 \item
@@
 Again let the transition be in wire block $w$.
-The transition is on an output wire which can change logic block excitations.
-We first show that the logic blocks are not excited in wire block $w$ itself after the transition.
+The transition is on an output wire which can change element excitations.
+We first show that the elements are not excited in wire block $w$ itself after the transition.
 This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
-It is also true that only wire blocks that $w^A$ and $w^B$ feed into, can change logic block excitations due to the transitions in $w^A$ and $w^B$.
+It is also true that only wire blocks that $w^A$ and $w^B$ feed into, can change element excitations due to the transitions in $w^A$ and $w^B$.
 Next, we examine the effects of the transitions on wire blocks $v$ where $w$ feeds into $v$ and $v$ may be in any cases of Figure \ref{fig:l21}.  
-%The above discussions showed that if a wire block is in cases 1-8a/8b, then their logic blocks cannot change excitation other than indicated by the state diagram.
+%The above discussions showed that if a wire block is in cases 1-8a/8b, then their elements cannot change excitation other than indicated by the state diagram.
 A similar reasoning can be applied to case 9.
-By Lemma 1, if any wire blocks are in case 9 and the transition is not in this wire block, then its logic blocks cannot change excitations.
-Wire blocks in cases 10a/10b are tricky because we must use a different technique to show that the logic blocks cannot be excited because half of the circuit has completed its transitions.
-%Wire blocks in cases 10a/10b are tricky because we cannot directly apply Lemma 1 on the half that has completed its transition to show that its logic block cannot be excited.
+By Lemma 1, if any wire blocks are in case 9 and the transition is not in this wire block, then its elements cannot change excitations.
+Wire blocks in cases 10a/10b are tricky because we must use a different technique to show that the elements cannot be excited because half of the circuit has completed its transitions.
+%Wire blocks in cases 10a/10b are tricky because we cannot directly apply Lemma 1 on the half that has completed its transition to show that its element cannot be excited.
 %In cases 1-8a/8b, all transitions happen on intermediate wires so the other wires blocks stay in their previous states.  
@@
 \item
-If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three: each half has either an excited logic block and excited wire block, unexcited logic block and excited wire block, or unexcited logic block and unexcited wire block.
-For excited logic block and excited wire block (e.g., A-half in case 2a), the new transition cannot cause the excited logic block to become unexcited as it would violate semi-modularity in the original circuit.
-For unexcited logic block and excited wire block (e.g., A-half in case 4a), the transition also cannot excite the logic block as it would violate P3 in Lemma 1.
-It is possible for unexcited logic blocks with unexcited wire blocks to become excited (e.g., both A and B-half in case 1); all such case changes are covered by the blue arrows.
+If $v$ is in cases $1,2a,2b,\dots9$, the wire blocks can be summarized into three: each half has either an excited element and excited wire block, unexcited element and excited wire block, or unexcited element and unexcited wire block.
+For excited element and excited wire block (e.g., A-half in case 2a), the new transition cannot cause the excited element to become unexcited as it would violate semi-modularity in the original circuit.
+For unexcited element and excited wire block (e.g., A-half in case 4a), the transition also cannot excite the element as it would violate P3 in Lemma 1.
+It is possible for unexcited elements with unexcited wire blocks to become excited (e.g., both A and B-half in case 1); all such case changes are covered by the blue arrows.
 Thus we have shown that for $v$ in cases 1-8a/8b, changes in $v$ caused by a transition in $w$ follow the state diagram.
-%Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in logic blocks of all wires in cases 10a/10b. \\  
+%Thus we need to show that when an output/input wire transitions in cases 9/10a/10b, the transition does not change excitations in elements of all wires in cases 10a/10b. \\  
 \item
-Next we show that a transition in $w$ does not change excitations in logic blocks of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
-First we assume that wire block $v$ is in case 10a, and that the $w^A$ transition excites the A-half of the logic block of $v$ in state $s_{k+1}$.
-The $w^B$ transition can be ignored because the logic block in the B-half of $v$ cannot be excited as it would violate P3 in Lemma 1.
+Next we show that a transition in $w$ does not change excitations in elements of all wires $v$ in cases 10a or 10b.  This is shown by contradiction.  
+First we assume that wire block $v$ is in case 10a, and that the $w^A$ transition excites the A-half of the element of $v$ in state $s_{k+1}$.
+The $w^B$ transition can be ignored because the element in the B-half of $v$ cannot be excited as it would violate P3 in Lemma 1.
 In state $s_k$, an output wire mismatch is possible only if the wire blocks are in cases 10a or 10b.
@@
 No other transitions occur.
-In that later state, the excited A-half logic block of $v$ is still excited due to semi-modularity in the original circuit.
+In that later state, the excited A-half element of $v$ is still excited due to semi-modularity in the original circuit.
 %semi-modularity...
@@
 Also SM
-Since the input wires on both halves of wire block $v$ are equal and $c1^A=c1^B$, then the B-half logic block must be excited too.
+Since the input wires on both halves of wire block $v$ are equal and $c1^A=c1^B$, then the B-half element must be excited too.
 The state for the B-half violates P3 of Lemma 1 and a contradiction is found.
 %may need a picture
- Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the logic blocks of a wire in case 10a.  Wires in case 10b are similar.
+ Therefore, a wire transition in $w^A$ or $w^B$ cannot excite the elements of a wire in case 10a.  Wires in case 10b are similar.
 \end{itemize}
-%Lastly we also show that the logic blocks are not excited in wire block $w$ itself after the transition.
+%Lastly we also show that the elements are not excited in wire block $w$ itself after the transition.
 This is immediate because $w$ does not feedback to itself and the input wires do not change their values.
@@
 
-%We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.
-For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.
+%We assume that the output wires cannot directly feed back into its element so that 10a or 10b cannot cause its own element to be excited.
+For other elements in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other elements.
 This is shown by contradiction.
-%Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
+%Assume that there exists another element in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).
 In state $s_k$ an output wire mismatch is possible only if it is in cases 10a or 10b.
@@
 Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in a later state (other than wire $v$).
-In that later state, the excited logic block of $v$ must still be excited due to semi-modularity.
-Since the input wires on both halves are equal, the logic block in the other half must be excited while its output wire is excited too.
+In that later state, the excited element of $v$ must still be excited due to semi-modularity.
+Since the input wires on both halves are equal, the element in the other half must be excited while its output wire is excited too.
 This violates Lemma 1 and produces a contradiction.
-Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
+Therefore a transition to 10a or 10b cannot excite the elements in case 10a or 10b in other wire blocks.\\
 %From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.
-Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.
+Again this cannot excite elements of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.
 
@@
 Next we consider what happens to the fault-tolerant circuit under a single transient fault.
-A {\em transient fault} on a wire $w$ causes a transition i.e.
-flips the bit of $w$.
-In light of this, we have expanded the definition of a transition to include the case where the wire value changes due to the transient fault.
+A {\em transient fault} on a wire $w$ causes a transition {\em i.e.} flips the bit of $w$.
+In light of this, we have allow faulty transitions, where a wire value changes due to a transient fault.
 After the transient event, the faulty wire transitions based on circuit rules.
@@
   \caption[Effects of a transient fault]{Effects of a transient fault.
-The left most figure is the state right before a transient fault occurs.
+The left-most figure is the state just before a transient fault occurs.
 The transition due to the transient fault is denoted by the red F and arrow.
 \\
-  a) An AND gate, the transient fault causes a transition in $w$ to 0 but the inputs resurrect it back to 1 sometime later.   \\
+  a) In an unexcited AND gate, the transient fault causes a transition in $w$ to 0 but the inputs restore it back to 1 sometime later.   \\
   b) An AND gate that is excited before the transient fault.  The transient fault causes a transition that would happen anyway, $w$ stays at the correct value 1 after the transition.\\
-  c) A C-element.  Its inputs are mismatched so the gate is in a hold state.  When the transient fault causes a transition to 0, the faulty 0 value may persist.
+  c) A C-element.  Its inputs are mismatched so the element is in a hold state.  When the transient fault causes a transition to 0, the faulty 0 value persists until the element becomes excited again.
   }
@@
 Examples of the transient fault occuring on elements in different states are shown in Figure \ref{fig:faultx}.
-Depending on the inputs and the element, the transient fault can cause a transition to a faulty value and transition back to the previous value; or it can cause a transition that would happen anyway and thus does not affect the element or circuit; or the faulty value may be stored in memory elements such as the C-element in the hold state.\\
+Depending on the inputs and the element, the transient fault can cause a transition to a faulty value that eventually transitions back to the previous value; or it can cause a transition that would happen anyway and thus does not affect the element or circuit; or the faulty value may persist because it is stored in memory elements such as the C-element in the hold state.\\
 
@@
 \begin{definition}
-A {\em faulty trace} is a trace of the circuit where for all $k$, a transition from $s_k$ to $s_{k+1}$ is either a transition through an excited element or primary input, or a transition through a transient fault.
+A {\em faulty trace} is a trace of the circuit where for all $k$, a transition from $s_k$ to $s_{k+1}$ is either a transition of an excited element or primary input, or a transient fault.
+There can be at most one transient fault in the trace.
 %there exists an $n$ where $\sigma_n$ is a prefix of a trace of the fault free circuit, then the $n+1$st transition is a transient fault.  After the fault occurs, the circuit continues to transition .
 \end{definition}
-Transitions after the fault is based on circuit rules and new transitions may occur.
-To see this, note that the fault-free traces do not necessarily include all possible states of the circuit.
-The circuit synthesis technique is designed such that if the circuit is in a state of the fault-free traces, the circuit follows the predefined transitions.
-However, a fault may cause $s_{n+1}$ to be in a previously unreachable state.
-Then the transitions are governed by the circuit rules of the gates that make up the circuit.\\ %end new
+Transitions after the fault are based on circuit rules.
+Note that, fault at state $s_i$ may cause $s_{i+1}$ to be in a state that is not reachable in normal operation.
+Subsequent transitions are governed by the circuit rules of the elements of the circuit.\\ %end new
 
 It is useful to extend the concept of excited wireblocks to include wireblocks from faulty traces.
-Since we assume the fault is in the B-half, the A-half is fault-free, and by Lemma 1, the wireblock in one of cases 1-5 of Figure \ref{fig:l1helper}.
+Recall, by Lemma 1, the wireblock is always in one of cases 1-5 of Figure \ref{fig:l1helper}, even if there are arbitrary faults in the B half.
 \begin{definition}
-An {\em excited wireblock} is any wireblock that is in cases 1-4 of Figure \ref{fig:l1helper}.  
+An {\em excited wireblock} is any wireblock that is in cases 1-4 of Figure \ref{fig:l1helper}. \\ An {\em unexcited wireblock} is in cases 5. 
 \end{definition}
@@
 
-The next major theorem, Theorem 2, states that the prefix of a faulty trace in the fault-tolerant circuit maps to the prefix of a fault-free trace of the original circuit, and the fault-tolerant circuit does not deadlock.
-The first part is already covered by Lemma 1.
-The main contribution of Theorem 2 is to show that the fault-tolerant circuit does not deadlock.
+The remaining lemmas show that the fault-tolerant circuit does not deadlock.
 To prove this, we first assume that the transient fault occurs in a wireblock $v$.
-Then, the transient fault can be split into two cases: the fault occurs on the $c2^B$ or $c3^B$ wires of $v$; or the fault occurs on the remaining wires $c1^B$ or $v^B$.
-For the first case, if the fault occurs on the $c2^B$ or $c3^B$ wires, we directly show that each wireblock follows transitions similar to the fault-free case.
+Then, the lemmas cover two cases: the fault occurs on the $c2^B$ or $c3^B$ wires of $v$; or the fault occurs on the remaining wires $c1^B$ or $v^B$.
+For the first case, if the fault occurs on the $c2^B$ or $c3^B$ wires, we show that at least one of $c1^A=c1^B$ or $w^A=w^B$ is true for every wireblock $w$ in all states.
 This result is shown in Lemma 3.
-However, for the second case, if the fault occurs on $c1^B$ or $v^B$ wires, we show that at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true for each wireblock.
+However, for the second case, if the fault occurs on $c1^B$ or $v^B$ wires, we show that at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true for every wireblock in all states.
 This result is shown in Lemma 4.
@@
 By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.
-The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\
+The transition is guaranteed to happen only if the B-half element is permanently excited too, and to the same value as the A-half.\\
 %
@@
 \begin{lemma}[3]
-For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wireblock $v$, then for each wireblock $w$ (including $v$), at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wireblock $v$, then for each wireblock $u$ (including $v$), at least one of $c1^A=c1^B$ or $u^A=u^B$ is true in all states of the trace.
 
@@
 \centering
-\includegraphics{L3helperfull}
-\caption[Fault-free transitions of $c1$ and $w$ wires]{The projection of the states in Figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.
+\includegraphics{L3helperfullu}
+\caption[Fault-free transitions of $c1$ and $u$ wires]{The projection of the states in Figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $u^A$, $u^B$.
 This forms the input and output characteristic of a wire block of a fault-free trace.}
@@
 \begin{proof}
-We first show that for each wireblock $w$, its $c1^A$, $c1^B$ and $w^A$, $w^B$ wires transition according to Figure \ref{fig:l3helper}.  
-We use NuSMV to prove this.
+Let $\sigma$ be a faulty trace with a transient fault on wires $c2^B$ or $c3^B$ of wireblock $v$.
+We show by induction that all non-fault wireblocks of the circuit progress through state machine of Figure \ref{fig:l21}, and the faulty wireblock $v$ progresses through state machine of Figure \ref{fig:l3helper}.
+The two state machines are related by the following property:  the state machine of Figure \ref{fig:l3helper} is the projection of the state machine of Figure \ref{fig:l21} onto the wires $c1^A$, $c1^B$ and $u^A$, $u^B$.\\
+
+We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state with no faults.
+By definition of the valid initial state, all non-fault wireblocks are in cases 1 or 3b of Figure \ref{fig:l21}.
+Also by this definition, $c1$ and $v$ wires of wireblock $v$ are all ones or all zeros, which are cases in Figure \ref{fig:l3helper}.
+Thus, the base case satisfies the induction hypothesis.\\
+
+The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of faulty traces of the fault-tolerant circuit.
+To show the induction hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.
+Let $w$ represent the transitioning wireblock from state $s_k$.
+By the induction hypothesis, $w$ is either not $v$, in which case $w$ may be in any one of the cases in Figure
+ \ref{fig:l21}; or $w$ is $v$, in which case $w$ may be in any one of the cases in Figure \ref{fig:l3helper}.  For each case, we check that the wire block transitions accordingly.
+
+\begin{itemize}
+\item Case where $w$, the transitioning wireblock, is not $v$:  By the induction hypothesis, since wireblock $w$ is in a case of Figure \ref{fig:l21} in state $s_k$, it transitions according to Figure \ref{fig:l21} in state $s_{k+1}$.
+Wire $v$ stays in the same case in Figure \ref{fig:l3helper}.
+Also, $v$ has so far not produced a faulty output on $v^A$ or $v^B$, therefore the inputs to all other wireblocks are correct.
+For all other wireblocks, they either stay in the same case, or transition to a new case according to Figure \ref{fig:l21}.
+The induction hypothesis holds.
+
+\item Case where $w$, the transitioning wireblock, is $v$:  We use NuSMV to prove this.
+NuSMV simulates all possible states of the faulty wireblock $v$.
+First we construct the wireblock $v$ in NuSMV, that is, the $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$, $v^A$ and $v^B$ wires and their circuit elements (not including $c1^A$, $c1^B$).
+These wires are initialized to a valid initial state and then the wires transition according to circuit rules.
+Then, a transient fault occurs on wires $c2^B$ or $c3^B$ anytime.
+The model for wires $c1^A$, $c1^B$ are a special case.
+By the induction hypothesis, wireblock $v$ transitions according to Figure \ref{fig:l3helper} up to state $s_k$.
+So in NuSMV, $c1^A$ and $c1^B$ also transition according to Figure \ref{fig:l3helper}.
+Under this model, every reachable state is a possible state for $s_k$.
+ NuSMV checks the specifications that for each reachable state, if there is a transition, the wireblock transitions according to the state machine in Figure \ref{fig:l3helper}.  \\
+Again, because $v$ has not produced a faulty output on $v^A$ or $v^B$, therefore the inputs to all other wireblocks are correct.
+For all other wireblocks, they either stay in the same case, or transition to a new case according to Figure \ref{fig:l21}.
+The induction hypothesis holds.
+\end{itemize}
+
+Thus, in all possible next states $s_{k+1}$, the induction hypothesis holds and the induction step is complete. \\
+
+For all cases in Figure \ref{fig:l21} and in Figure \ref{fig:l3helper}, at least one of $c1^A=c1^B$ or $u^A=u^B$ is true.
+It follows that for each wireblock $u$, at least one of $c1^A=c1^B$ or $u^A=u^B$ is true.
+%
+%We use NuSMV to prove this.
 For each wireblock $w$ of a fault-free trace, by projecting the states in Figure \ref{fig:l21} from Lemma 2.1, the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) follow the state diagram shown in Figure \ref{fig:l3helper}.
@@
 We can view the circuit as composed of two components, the faulty wireblock $v$ and the rest of the circuit.
-The faulty wireblock $v$ takes inputs from the rest of the circuit and has logic blocks that converts the inputs into wire values $c1^A$ and $c1^B$.
+The faulty wireblock $v$ takes inputs from the rest of the circuit and has elements that converts the inputs into wire values $c1^A$ and $c1^B$.
 Wireblock $v$ produces outputs $v^A$ and $v^B$, which the rest of the circuit takes as inputs.
@@
 \\
-
-The strategy of the proof by NuSMV focuses on interactions between wireblock $v$ and the rest of the circuit.
+%
+%The strategy of the proof by NuSMV focuses on interactions between wireblock $v$ and the rest of the circuit.
 Assume $c1^A$ and $c1^B$ transition as in the fault-free trace, then if $v^A$ and $v^B$ follow the state diagram (Figure \ref{fig:l3helper}), this validates our assumptions for $c1^A$ and $c1^B$.
@@
 \\
-
-Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: $c1^A$ and $c1^B$, if they transition, can only be excited after the previous $v^A$ and $v^B$ transitions complete.
+%
+%Wires $c1^A$ and $c1^B$ of a fault-free trace transition as follows: $c1^A$ and $c1^B$, if they transition, can only be excited after the previous $v^A$ and $v^B$ transitions complete.
 (Note if Figure \ref{fig:l3helper} is true when $c1^A$ and $c1^B$ are excited infinitely often, then it is also true for when one or both of $c1^A$ and $c1^B$ stop after a finite number of transitions.
@@
 Thus, we only need to consider the case where both $c1^A$ and $c1^B$ are excited infinitely often)
-We model $c1^A$ and $c1^B$ in NuSMV as such.  
-%in NuSMV, we model $c1^A$ and $c1^B$ as being excited only after the previous $v^A$ and $v^B$ transitions complete. 
-We also model the rest of wireblock $v$, that is, the $c2^A$, $c2^B$, $c3^A$, $c3^B$, $v^A$ and $v^B$ wires and their circuit elements.
-These wires are initialized to a valid initial state and then the wires transition accordingly.
-Then, a transient fault occurs on wires $c2^B$ or $c3^B$ anytime during the trace.
-Under this scenario, NuSMV checks the specifications that the wires $v^A$ and $v^B$ transition according to the state diagram (Figure \ref{fig:l3helper}).
-\\
-
-Running the NuSMV model show that these properties are indeed true.
+%We model $c1^A$ and $c1^B$ in NuSMV as such.  
+%%in NuSMV, we model $c1^A$ and $c1^B$ as being excited only after the previous $v^A$ and $v^B$ transitions complete. 
+%We also model the rest of \\
+%
+%Running the NuSMV model show that these properties are indeed true.
 Then, wireblock $v$ transitions according to Figure \ref{fig:l3helper}.
@@
 \\
-
-For all states in Figure \ref{fig:l3helper}, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true. It follows that for each wireblock $w$, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
+%
+%For all states in Figure \ref{fig:l3helper}, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true. It follows that for each wireblock $w$, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
 
@@
 \caption[Wireblock transitions with fault on $c1^B$ or $w^B$]{The wires in each row are in order of $c1$, $c2$, $c3$ and $w$.
-Each row represents half of the duplicated circuit, i.e.
-top row are A half wires and bottom row are B half wires.
+Each row represents half of the duplicated circuit, {\em i.e.} top row are A half wires and bottom row are B half wires.
 Note that cases 6-10 are symmetric to cases 1-5 with the 0's and 1's inverted.}
@@
 \begin{lemma}[4]
-For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then for each wireblock $u$, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true.\end{lemma}
+For any faulty trace $\sigma$ in the fault-tolerant circuit, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then for each wireblock $u$, at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true in all states of the trace .\end{lemma}
 \begin{proof}
-We first show that each wireblock $u$ follow the state graph of Figure \ref{fig:l4}. 
-We will show by induction on $n$ that this is true for the length $n$ prefix of the trace $\sigma_n$.\\ %how to make it seem like prefix not trace modifies sigma_n
+Let $\sigma$ be a faulty trace with a fault on wires $c1^B$ or $v^B$ of wireblock $v$.
+We show by induction that each wireblock of the circuit progresses through state machine of Figure \ref{fig:l4}.
+%We will show by induction on $n$ that this is true for the length $n$ prefix of the trace $\sigma_n$.
+\\ %how to make it seem like prefix not trace modifies sigma_n
 
 We show the induction hypothesis holds in the base case of $\sigma_1$ consisting of state $s_1$, a valid initial state with no faults.
-As noted in Lemma 2.1, each wireblock must be in case 1 or case 3b of Figure \ref{fig:l21}.
-Projecting these wireblocks onto its $c1$, $c2$ and $c3$ wires result in case 1 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
-
-The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of traces of the fault-tolerant circuit. 
+By definition of the valid initial state, each wireblock must be in case 1 or 6 in Figure \ref{fig:l4}, thus the base case satisfies the induction hypothesis.\\
+
+The induction step is to assume that the induction hypothesis is true for all length $k$ prefixes of faulty traces of the fault-tolerant circuit. 
 To show the induction hypothesis is true for all length $k+1$ prefixes, equivalently we show the hypothesis is true for all possible next states $s_{k+1}$ from the state $s_k$.
@@
 By the induction hypothesis, $w$ in state $s_k$ may be in any one of the cases in Figure \ref{fig:l4}, so for each case, we check  that the wire block transitions accordingly.
-We make a further simplification and only analyze when $w$ is in cases 1-5 because transitions from case 6-10 is symmetric to transitions from case 1-5 with 0's and 1's inverted.
+We make a further simplification and only analyze when $w$ is in cases 1-5 because transitions from case 6-10 are symmetric to transitions from case 1-5 with 0's and 1's inverted.
 For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7 as case 1 has to case 2, and so on.\\
@@
 So, the induction hypothesis holds for all length $k+1$ prefixes of traces and the induction step is complete.
-By induction on the length of the trace, in each trace $\sigma$, each wireblock $u$ transitions according to Figure \ref{fig:l4}. \\
+\\
 
@@
 \end{proof}
-Lemma 4 shows that at least one of the $c2$ or $c3$ wire pairs have the same values. \\
+%Lemma 4 shows that at least one of the $c2$ or $c3$ wire pairs have the same values. \\
 %all output wire pairs at an assumed deadlock state must be equal, which causes a contradiction, and thus the fault-tolerant circuit does not deadlock under a single transient fault.\\
@@
 Then the inputs to the A-half and B-half of wireblock $w$ have the same values.
-By the $h^A()$ mapping, the inputs to the $w$ logic block in the original circuit also have the same values.
+By the $h^A()$ mapping, the inputs to the $w$ element in the original circuit also have the same values.
 By Lemma 0 i), since wire $w$ is excited in the original circuit, then wire $c1^B$ is also excited.
@@
 
-We first show at deadlock that for each wireblock $w$, its output wire pairs have the same values $w^A = w^B$.
+We first show at deadlock that for each wireblock $w$, the output wire pairs have the same value $w^A = w^B$.
 Let the wireblock with the transient fault be called $v$.
-The fault can occur on wires $c1^B$, $c2^B$, $c3^B$ or $v^B$.
-If the fault occurs on wires $c2^B$ or $c3^B$, Lemma 3 states that at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
-However, if $c1^A=c1^B$, then by Lemma 5, $w^A = w^B$ at deadlock.
+The fault can occur on wires $c1^B$, $c2^B$, $c3^B$ or $v^B$ of $v$.
+If the fault occurs on wires $c2^B$ or $c3^B$ of $v$, then Lemma 3 states that for each wireblock $w$, at least one of $c1^A=c1^B$ or $w^A=w^B$ is true.
+However, for the wireblocks where $c1^A=c1^B$, by Lemma 5, $w^A = w^B$ at deadlock.
 Thus, at deadlock, each wireblock $w$ has $w^A = w^B$.\\
 
-And if the fault occurs on wires $c1^B$ or $v^B$, we apply similar reasoning.
-For each wireblock $w$, Lemma 4 states that $c2^A=c2^B$ or $c3^A=c3^B$ (or both).
-In either case, since the circuit is in deadlock, then by Lemma 5 the output wires of the wireblock have the property $w^A = w^B$.
-\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
+And if the fault occurs on wires $c1^B$ or $v^B$ of $v$, we apply similar reasoning.
+For each wireblock $w$, Lemma 4 states that at least one of $c2^A=c2^B$ or $c3^A=c3^B$ is true.
+In both cases, since the circuit is in deadlock, then by Lemma 5, the output wires of a wireblock in that case, have the property $w^A = w^B$.
+Thus, at deadlock, each wireblock $w$ has $w^A = w^B$.\\%Don't know if this version is better than just saying cases 1 2 6 can be in deadlock, and of those w^A=w^B
 
@@
 Assume that the circuit is deadlocked, that is, the circuit is stopped in a state $s$ where $h^A(s)$ is not a stopping state in the original circuit.
-By definition, there must exist a wire $v$ with value $p$ that is excited in state $h^A(s)$.
-In other words, wireblock $v$ is excited and $v^A$ also has value $p$.
-The inputs to $v$ in the original circuit and the inputs to $c1^A$ in the fault-tolerant circuit have the same values.
-In addition, since $w^A = w^B$ for all wireblocks, then the inputs to $c1^B$ also have the same values.
-By Lemma 0 iv), since wire $v$ is excited in the original circuit, then both wires $c1^A$ and $c1^B$ have value $\neg{p}$ in a deadlocked state.
-Then, by Lemma 5, wires $w^{A}$ and $w^B$ have value $\neg{p}$ as well.
+By definition, there must exist a wire $v$ in the original circuit that is excited in state $h^A(s)$.
+Then, by Lemma 1, wireblock $v$ of the fault-tolerant circuit is excited in state $s$.
+Let variable $p=h^A(s)(v)$ so that wire $v$ in state $h^A(s)$ has value $p$.
+By definition of the $h^A$ mapping, $v^A$ has value $p$ in state $s$.
+Also by definition of the $h^A$ mapping, the inputs to $c1^A$ in the fault-tolerant circuit have the same values as the corresponding inputs to $v$ in the original circuit.
+Using the property that we just showed, since $w^A = w^B$ for all wireblocks, then the corresponding inputs to $c1^B$ also have the same values as the inputs to $c1^A$.
+By Lemma 0 iv), since wire $v$ is excited in the original circuit and has value $p$, and wires $c1^A$ and $c1^B$ are unexcited in the deadlocked state $s$, then wires $c1^A$ and $c1^B$ have value $\neg{p}$.
+Then, by Lemma 5, wires $v^{A}$ and $v^B$ have value $\neg{p}$ as well.
 \\
@@
 
-However, this shows wire $v^A$ does transition to $\neg{p}$ and wireblock $v$ is not excited, which is a contradiction.
-Therefore, the initial assumption is wrong and the circuit cannot be under deadlock.
+However, this shows wire $v^A$ has a value of both $\neg{p}$ and $p$, which is a contradiction.  Therefore, the initial assumption is wrong and the circuit cannot be under deadlock.
 %taking on values of both $p$ and $\neg{p}$
 %excited blocks, and stopping states
-%the fallible part of the logic is that if inputs to B is the same it may not be excited (it is in our case because I know the structure of the logic block) but in a general implementation it could not be, ie if it depends on previous inputs etc
+%the fallible part of the logic is that if inputs to B is the same it may not be excited (it is in our case because I know the structure of the element) but in a general implementation it could not be, ie if it depends on previous inputs etc
 
@@
 In this work, we have proposed a fault-tolerant circuit transformation of asynchronous control circuits using duplication and a chain of C-elements.
-This is more transistor efficient than TMR and the doubled inputs duplication approaches.
+Depending on how they are implemented, this method may be more transistor efficient than the TMR and the doubled inputs duplication approaches.
 We also proposed a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.
-And finally we showed the transformation of the circuit makes it fault tolerat to transient faults at the gate level implementation of the asynchronous circuit\\
+And finally we showed that the transformed asynchronous circuit is fault-tolerant to transient faults at the gate level implementation.
+It is fault-tolerant in the sense that a prefix of the trace of the fault-tolerant circuit is also a prefix of the trace of the original circuit, and the fault-tolerant circuit does not deadlock.\\
+
+Table \ref{fig:tablec} shows a comparison of the existing work and my proposed design.
+Because this is a particularly hard problem for asynchronous circuits, many solutions include multiple assumptions and limit the types of circuits.
+My design extends the space of solutions to semi-modular control circuits with a generalized two-input gate implementation.
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{tablecompare}
+\caption{Comparison of exising work and my proposed design}
+\label{fig:tablec}
+\end{figure}
 
 Some limitations of this work are that we assume multiple SEUs cannot occur simultaneously, in general.
-(It is ok if the faults are only in the c2 and c3 wires, or all faults are in one half).
-We also assume outputs of C-elements are always 0 or 1 even if one signal may be faulty.
+Although, for special cases such as when multiple faults occur but only on the c2 and c3 wires of different wireblocks, or if all the faults are in one half of the circuit, this fault-tolerant design will work.
+Another assumption that we made was that outputs of C-elements are always 0 or 1 even if one signal may be faulty.
+This is an idealized version, in reality hazards may occur.
 And we also limit our circuit model to semi-modular control circuits.\\
@@
 
+\nocite{*}
 \bibliography{biblio}
 \bibliographystyle{unsrt}
-%\bibliographystyle{plain}
+%\bibliographystyle{apa}
 

### 2019-12-06 draft_final.tex
before final ch 2 changes

@@
 The main contribution of this work is proposing a new fault-tolerant design for asynchronous circuits.
-The new design expands fault-tolerance to semi-modular speed independent circuits composed of two-input gates and C-elements.
+The new design expands fault-tolerance to semi-modular speed-independent circuits composed of two-input gates and C-elements.
 This work also proves that the proposed fault-tolerant design is tolerant to transient faults.
@@
 
-\section{Synchronous vs Asynchronous circuits}
-Digital circuits can be divided into two types, synchronous and asynchronous.
+\section{Synchronous vs Asynchronous Circuits}
+Digital circuits can be divided into two types: synchronous and asynchronous.
 In digital circuits, the time it takes for gates to process input signals into output signals and for these signals to reach the next gates vary widely.
@@
 The asynchronous delay model that we consider is the unbounded gate delay model.
-Circuits that can function correctly under arbitrary gate delays are called Speed Independent circuits.
+Circuits that can function correctly under arbitrary gate delays are called speed-independent circuits.
 The unbounded gate delay model assumes that delays only appear on the gates and the delays can be arbitrarily long in the interval $(0,\infty)$.
@@
 E.
-Muller proposed essentially this class of speed independent circuits, which are sometimes called Muller circuits \cite{Muller_59}.
+Muller proposed essentially this class of speed-independent circuits, which are sometimes called Muller circuits \cite{Muller_59}.
 Since then a number of synthesis methods following this design has been produced.
@@
 (The term wires and signals are used interchangeably as the state graph is converted into a circuit.)  Then depending on the underlying implementation, such as generalized C-element and standard C-implementations, the appropriate inputs and logic functions that allow the circuit to function according to the state graph is synthesized.
-The end result is a hazard-free and speed independent asynchronous circuit.
+The end result is a hazard-free and speed-independent asynchronous circuit.
 The construction we describe begins with a semi-modular circuit, possibly resulting from the previously described process, and transforms it into a circuit that can tolerate any single transient fault.
@@
 
-\section{Organization of this work}
+\section{Organization of This Work}
 %why are async circuits important, timing delay etc
@@
 
-\chapter{Related Works}
+\chapter{Related Work}
 \section{Fault Model}
@@
 
-Faults can be split into permanent and non-permanent faults.
+Faults can be classified as permanent and non-permanent faults.
 Permanent faults are faults that affect the functional behavior of a system or circuit permanently.
@@
 
-\subsection{Speed Independent Circuits}
+\subsection{Speed-independent Circuits}
 Circuits are composed of logic elements and wires.
@@
 This delay model is the basis for Muller circuits \cite{Muller_59}.
-Circuits that operate correctly regardless of the delay are called Speed Independent Circuits.
+Circuits that operate correctly regardless of the delay are called speed-independent circuits.
 The designer specifies the correct operation of the circuit.
@@
 
-We consider semi-modular circuits because they are a subset of speed independent circuits and is a large enough class to include some interesting and useable circuits.
+We consider semi-modular circuits because they are a subset of speed-independent circuits and is a large enough class to include some interesting and useable circuits.
 A simple explanation of semi-modularity is that once a wire is excited, it stays excited until it transitions to the excited value.
@@
 %ADD SPECIFIC CONDITIONS THAT ALLOW SYNTHESIS
-When the state graph has the following properties, it is possible to synthesize a hazard free and speed independent asynchronous circuit following the state graph.
+When the state graph has the following properties, it is possible to synthesize a hazard free and speed-independent asynchronous circuit following the state graph.
 Each variable from the state graph is implemented as a gate logic that takes other variables/wires as inputs and outputs a variable/wire.
@@
 Instead if that condition is relaxed so that some of the forks are allowed to be isochronic, then a more general class of circuits can be constructed.
-Note that in the case where all forks are isochronic, then this becomes the same as speed independent circuits.
+Note that in the case where all forks are isochronic, then this becomes the same as speed-independent circuits.
 \\
@@
 \end{comment}
-\section{Fault Tolerant solutions}
+\section{Fault-tolerant Solutions}
 
@@
 \chapter{Asynchronous Circuit Concepts and Definitions}
-\section{Assumptions:  Boolean signals}
+\section{Assumptions:  Boolean Signals}
 This work assumes that all signals are Boolean, that is, the signals are either `logic 0' or logic 1'.
@@
 \section{Circuit Elements}
-Gates and elements (C-elements) are components that we allow in our circuit.
+Boolean gates and C-elements are components that are allowed in our circuit.
 In general, we call them {\em elements}.
@@
 The elements can be in two states, excited or stable.
-Examples of gates are AND, OR, NOT etc.
-
-For each element, there exists a function that maps the inputs into a binary value.
-This function is represented by $f:[I \to \{0,1\}] \to \{0,1\}$ where $I$ is the set of input wires of the element, a subset of $W$.
-If we assume a two input element, we name the input wires $w_1$ and $w_2$.
-The function models the designed operation of the element such that if the element had no delay, $f(w_1,w_2)$ is the output value of the element.
-With asynchronous delay, if the inputs remain constant, then the output will eventually take the value of $f(w_1,w_2)$.
-For gates, such a function is easily defined.
-For example, an AND gate such as in Figure \ref{fig:gates0} with two inputs $w_1$ and $w_2$ is modeled by the function
+Examples of gates are AND, OR, NOT etc.\\
+
+An element is defined by a function $f$ that maps the inputs and previous output into a binary value.
+We name the two input wires $w_1$ and $w_2$ and the output wire $v$.
+The function models the designed operation of the element such that if the element had no delay, $f(w_1,w_2, v)$ is the output value of the element.
+With asynchronous delay, if the inputs and previous output remain constant, then the output will eventually take the value of $f(w_1,w_2, v)$.
+For Boolean gates, such a function is easily defined.
+For example, an AND gate such as in Figure \ref{fig:gates0} with inputs $w_1$ and $w_2$ and output $v$ is modeled by the function 
+\[
+f_{AND}(w_1,w_2,v)= w_1\wedge w_2
+\]
+
 \begin{figure}[h]
@@
 \end{figure}
+
+For Boolean gates, $f(w_1, w_2,v)$ does not depend on $v$.  
+C-elements are memory holding devices, so the function depends on the previous output $v$.
+For example, the C-element in Figure \ref{fig:element0} with two input wires $w_1$ and $w_2$ is modeled by the function
 \[
-f_{AND}(w_1,w_2,v)= w_1\wedge w_2
+f_{C-E}(w_1,w_2, v) =\left\{
+  \begin{array}{@{}ll@{}}
+    0, & \text{if}\ w_1=0 \wedge w_2=0\\
+    1, & \text{if}\ w_1=1 \wedge w_2=1\\
+    v, & \text{otherwise}
+
+  \end{array}\right. 
 \]
 
-For C-elements, these are memory holding devices so the function also requires the previous output.
-For example, the C-element in Figure \ref{fig:element0} with two input wires $w_1$ and $w_2$ is modeled by the function\\
 \begin{figure}[h]
@@
 \end{figure}
-\[
-f_{C-E}(w_1,w_2, v) =\left\{
-  \begin{array}{@{}ll@{}}
-    0, & \text{if}\ w_1=0 \wedge w_2=0\\
-    1, & \text{if}\ w_1=1 \wedge w_2=1\\
-    v, & \text{otherwise}
-
-  \end{array}\right. 
-\]
+
 When $f_{C-E}(w_1,w_2, v) =v$, we say the C-element is in the ``hold state''.  
@@
 Again, not all input changes will cause the element to become stable.
-In fact, semi-modular circuits utilizes input changes that allow the element to stay excited.
-If the output changes in an excited state, the element becomes stable and we call this action a {\em firing} of the element.
+If the output changes in an excited state, the element becomes stable and we say that the element {\em fires}.
 
@@
 Other than elements, a circuit also consists of primary inputs and primary outputs.
-Primary inputs are all inputs that are not the output of an element in the circuit.
+Primary inputs are inputs that are not the output of an element in the circuit.
 Primary outputs are outputs of an element in the circuit that connects to another device or element outside of the circuit.
-Primary inputs and outputs can be thought of as the interface with outside of the circuit.
+Primary inputs and outputs can be thought of as the interface with the outside of the circuit.
 They can be the outputs and inputs of a different circuit, or connected to physical mechanisms such as a user pushing a button.
-An example of a circuit with primary inputs and outputs is:  .
 
 \section{States}
-Let $W$ be the set denoting the union of all wires of elements and the primary inputs of a circuit, then $S$ is the set of functions $[W\to \{0,1\}]$ which maps each element of $W$ to a boolean value.
+Let $W$ be the set denoting the union of all wires of elements and the primary inputs of a circuit, then $S$ is the set of functions $[W\to \{0,1\}]$ which map each element of $W$ to a boolean value.
 An element of $S$ is called a {\em state}.
-
-Assigning values to all wires of a circuit names a state.
-An example of a state for a circuit containing 3 wires is `101'.
-From the set definition, states are unique and no two states share the same values.
-
-\section{Behavior of a circuit}    
-Circuits respond to input changes and produces outputs that accomplish some specified task.
+If $w$ is a wire and $s$ a state in $S$, then $s(w)$ is the Boolean value of the wire in that state.
+
+\section{Behavior of a Circuit}    
+Circuits respond to input changes and produce outputs that accomplish some specified task.
 Thus the function of a circuit depends on its dynamic behavior and how its state changes over time.
-Under the state representation of a circuit, if the value of a wire changes, the state also changes.
-If the wire changes from a previous state $s$ to a new state $s'$, then there is a transition relation between the two states.
-Defined more formally with $s(w)$ denoting the value of wire $w$ in state $s$:
+The possible transitions between consecutive states are defined by the transition relation of a circuit.
 \begin{definition}
-For all $s$ and $s'$ in S, the \emph{transition relation} $T(s,s')$ holds when there is exactly one wire $w \in W$ such that $s(w)\neq s'(w)$, and wire $w$ must be either the output of an excited element in state $s$, or $w$ is a primary input.
+For all $s$ and $s'$ in S, the \emph{transition relation} $T(s,s')$ holds when there is exactly one wire $w \in W$ such that $s(w)\neq s'(w)$, and wire $w$ is either the output of an excited element in state $s$, or $w$ is a primary input.
 \end{definition}
@@
 
-We define a {\em trace} to describe a path the circuit can take.
-Different paths can occur because there may be multiple transitions from each state.
+We define a {\em trace} to describe a trajectory that the circuit can take.
+Different trajectories can occur because there may be multiple alternative transitions from each state.
 We call the succession of states the trace, which is formally defined as follows:
@@
 We also use $\sigma_n$ as shorthand to denote the sequence of the first $n$ states of $\sigma$.
-When there multiple transitions from a state, multiple traces exist depending on which wire transitions.
-Thus we want to define a set of traces for all the traces that form.
-In addition the initial state is important in naming a trace and by extension for a set of traces.
+When there are multiple transitions from a state, multiple traces exist or transitions occur.  Thus, we want to define a set of traces for all possibilities.\\
+
+The {\em initial state} is important in defining the set of traces of a circuit.
 The {\em initial state} specifies the state of the wires in the circuit as well as the primary inputs.
@@
 \end{definition} 
- The circuit may be waiting for a primary input change.
+A stopping state typically occurs when the circuit waits for a primary input change.
 %Thus, the only possible transitions from a stopping state are from changes in the primary inputs.  In other words, in a stopping state, the circuit is waiting for the primary inputs to changes.\\
@@
 \end{definition}
-A complete trace of finite length must end in a stopping state where the primary inputs never change and the circuit is stopped.
+A complete trace of finite length must end in a stopping state, where the primary inputs never change and the circuit is stopped.
 In other words, for any state of a complete trace, if there are excited elements, one of them must fire, causing the circuit to transition to another state.
@@
 This fits with the physical properties of circuits because the elements are not arbitrarily slow and if excited, they will eventually change.
-A set of traces can describe a circuit completely, in addition we may be interested in the states that the circuit visits in these traces. 
+A set of traces describes a circuit completely. \\
+
+We may be interested in the states that the circuit visits in these traces. 
 A {\em reachable state} is defined in this way.
@@
 \end{definition}
-Thus, unreachable states are states that are not in any of the traces with initial state $s_1$.
-Since all functionality of a circuit can be described by a set of traces starting in a specified state, then the circuit will never enter those unreachable states.
+Thus, unreachable states are states that do not appear in any of the traces with initial state $s_1$.
+Since all functionality of a circuit can be described by a set of traces starting in a specified state, the circuit will never enter those unreachable states.
 
 \section{Semi-modularity}
-Semi-modular circuits are a subset of speed independent circuits and is a large enough class to include circuits used in real applications.
+Semi-modular circuits are a subset of speed-independent circuits. 
+The class of semi-modular circuits is large enough to include circuits used in real applications.
 Also, they have been extensively studied, with algorithms to synthesize and analyze them.
-A simple explanation of semi-modularity is that once an element is excited, it stays excited until it fires and its output changes.
+A simple explanation of semi-modularity is that whenever an element is excited, it stays excited until it fires and its output changes.
 Formally this can be defined as follows: %proof that semi-modular circuits are also speed independent
 \begin{definition}
-An asynchronous circuit is {\em semi-modular} if for every pair of successive states in its set of traces $s_{i}$ and $s_{i+1}$, if element $j$ is excited in state $s_i$ and did not fire, then $j$ is also excited in state $s_{i+1}$.
+An asynchronous circuit is {\em semi-modular} if for every pair of successive states $s_{i}$ and $s_{i+1}$ in every trace, if element $j$ is excited in state $s_i$ and did not fire, then $j$ is also excited in state $s_{i+1}$.
 %An asynchronous circuit is {\em semi-modular} if for every pair of successive states in its set of traces $s_{i}$ and $s_{i+1}$, and let $v$ and $w$ be output wires such that $s_i(w) \neq s_{i+1}(w)$ (wire $w$ transitions) and $w\neq v$, then if $v$ is excited in state $s_i$, $v$ is also excited in state $s_{i+1}$
@@
 
-\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
-\chaptermark{Fault Tolerant Circuit}
-\section{Traces and circuit equivalence}
+\chapter{Fault-tolerant Circuit Under Normal Operation and Single Transient Fault}
+\chaptermark{Fault-tolerant Circuit}
+\section{Traces and Circuit Equivalence}
 We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all of its circuit elements.
@@
 If inputs to the gate remain constant, the output $v$ will eventually take the value specified by $f_v(s|_I)$  %maybe change v again, also the f(s) vs f(I) thing...
-\section{Fault Tolerant transformation}
+\section{Fault-tolerant Transformation}
 
@@
 
-\section{Normal operation analysis}
+\section{Normal Operation Analysis}
 Now we will discuss the proper wire initializations before going into the lemmas.
@@
 
-\section{Single transient fault analysis}
+\section{Single Transient Fault Analysis}
 %fix this
@@
 In this work, we have proposed a fault-tolerant circuit transformation of asynchronous control circuits using duplication and a chain of C-elements.
-Depending on how they are implemented, this method may be more transistor efficient than the TMR and the doubled inputs duplication approaches.
+Compared to a similar approach by Jang and Martin, the main advantage of this method is that it only needs standard two-input elements and does not assume hazard-free operation of arbitrarily large transistor logic blocks.
 We also proposed a method of comparing the fault-tolerant circuit with the original circuit, by comparing traces with the half circuit.
-And finally we showed that the transformed asynchronous circuit is fault-tolerant to transient faults at the gate level implementation.
+And finally, we showed that the transformed asynchronous circuit is fault-tolerant to transient faults at the gate level implementation.
 It is fault-tolerant in the sense that a prefix of the trace of the fault-tolerant circuit is also a prefix of the trace of the original circuit, and the fault-tolerant circuit does not deadlock.\\
@@
 Because this is a particularly hard problem for asynchronous circuits, many solutions include multiple assumptions and limit the types of circuits.
-My design extends the space of solutions to semi-modular control circuits with a generalized two-input gate implementation.
+My design extends the space of solutions to semi-modular control circuits with a two-input element implementation.
 \begin{figure}
@@
 Although, for special cases such as when multiple faults occur but only on the c2 and c3 wires of different wireblocks, or if all the faults are in one half of the circuit, this fault-tolerant design will work.
-Another assumption that we made was that outputs of C-elements are always 0 or 1 even if one signal may be faulty.
-This is an idealized version, in reality hazards may occur.
-And we also limit our circuit model to semi-modular control circuits.\\
-
-Some future work to extend this model would be to allow for arbiters, mutual exclusion elements by making them transient fault-tolerant as well.
-We can also extend fault tolerance to permanent faults, we have an initial idea of adding a timer and restart mechanism to get past the deadlock that accompanies permanent faults.
+\\
+
+Another assumption that we make is that outputs of C-elements are always 0 or 1 even if one signal may be faulty.
+This assumption ignores the possibility of metastable states in elements.
+While such metastable states would often resolve while propagating through chains of multiple C-elements, a general solution would be an interesting topic for future work.
+We also limit our circuit model to semi-modular control circuits.\\
+
+Some future work to extend this model would be to allow circuits with mutual exclusion elements by making them transient fault-tolerant as well.
+We can also extend fault tolerance to permanent faults.
 
